### 2020-09-21 parts/02-abstract.tex
Initial project template uploaded.

% A B S T R A C T
% ---------------

\begin{center}\textbf{Abstract}\end{center}

%This paper proposes a strategy for testing and comparing three control algorithms, LQR, LQG, and ADP, to control two two-DOF helicopters from a mobile device.  We will be using Raspberry Pi 3's as terminals for the wireless communication and MATLAB as our primary coding language.

This project proposes a modular and cost-effective smart real-time motion control
framework for a group of two degrees of freedom (2-DOF) helicopters.  The helicopters are
controlled by a mobile device which sends position signals over a wireless network to a
microcontroller.  The microcontroller uses control algorithms to determine the amount of voltage
to apply to DC motors.  This project tests and compares three control algorithms, LQR, LQG, and
ADP as well as theorizes possible methods to improve the control in future projects.

\cleardoublepage
%\newpage

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

### 2020-09-21 parts/03-acknowledgements.tex
Initial project template uploaded.

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}\textbf{Acknowledgements}\end{center}

    \par Special Thanks to Andrew Fandel, Anthony Birge, and Dr. Suruz Miah for their work with Machine Learning on a 2-DOF Helicopter.
    \par Thanks to Mr. Christopher Mattus for his assistance in setting up our lab environment.
    \par Thank you to everyone else who helped make this project possible and sucessful.

\cleardoublepage
%\newpage

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

### 2020-09-21 parts/10-introduction.tex
Initial project template uploaded.

%======================================================================
\chapter{Introduction}
\label{ch: Chapter1}
%======================================================================

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
Helicopters are of a paramount importance as
they are used in many civilian and military applications due to their ability for vertical take-off and landing. To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics. Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions. Such methods are expensive and time-consuming to develop. Implementation of motion control techniques using cost-effective hardware is still a challenge.

In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position. Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices. This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.

%----------------------------------------------------------------------
\section{Literature Review}
%----------------------------------------------------------------------
Our project requires a great deal of research as some of our tasks have not been attempted before.  As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.

Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices. In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}. A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters. See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein. Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.

The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.  This involves creating a linearized system model to calculate the LQR state-feedback gain.  A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.  SMC is a nonlinear control technique to drive the system states onto a surface in the state space.  This method has been used  by~\cite{Ahmed2010-Sliding}.  Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.  The ADP technique does not rely on knowledge of the system model.  Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.  Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.

As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms. This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms. Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into 6 chapters.  Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.  Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.  Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.  Chapter \ref{ch: Chapter4} contains the results from our simulations.  Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.  Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

### 2020-09-21 poster.tex
Initial project template uploaded.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.0 (29/03/13)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

\usepackage{tikz}
\usepackage{todonotes}
\usepackage{epstopdf}
\epstopdfsetup{suffix = {}}
\usepackage{hyperref}
\usepackage{subfigure}  % Written by Steven Douglas Cochran
\usepackage{amssymb,amsmath,bm}    % From the American Mathematical Society
\usepackage{siunitx} % for units like degree, ...
\sisetup{unitsep=\cdot,binary-units=true}
\usepackage{mathtools}
\usepackage{xcolor,soul}
\usepackage{geometry}
\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=BUred,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=BUred,bg=gray!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=gray!10} % Colors of the body of highlighted blocks

% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.022\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.25in} % Reduce the top margin size
\setlength{\leftmargin}{-0.25in}
\setlength{\rightmargin}{-0.25in}

%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables
%\usepackage{subfigure}

%-----------------------------------------------------------
% TITLE SECTION
%-----------------------------------------------------------

\title{Smart Control of 2 Degree of Freedom Helicopters} % Poster title

\author{Glenn Janiak, Ken Vonckx, Advisor: Dr. Suruz Miah} % Author(s)

\institute{Department of Electrical and Computer Engineering, Bradley University, Peoria IL} %Institution(s)
\vskip -.5cm

%-----------------------------------------------------------
% POSTER CONTENT
%-----------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{1ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
%\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t]

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The first column

%-----------------------------------------------------------
% OBJECTIVE AND CONTRIBUTION
%-----------------------------------------------------------

\begin{alertblock}{Objective and Contribution}
%
\textbf{Objective}
\vskip -0.75cm
\begin{itemize}
    \item Develop a platform allowing mobile devices to control the motion of a group of helicopters
\end{itemize}
%\begin{itemize}
%    \item Develop a platform that allows mobile devices to control helicopters with the least amount of error via an embedded system 
%\end{itemize}
%
\vskip -1cm
\textbf{Contribution}
\vskip -0.75cm
\begin{itemize}
    \item Determine trade-offs between traditional control techniques and machine learning
    %\item Embedded System Implementation
    %\item Mobile Device Control 
    \item Multi-Helicopter Application
\end{itemize}
\vskip -0.75cm
\textbf{Applications}
\vskip -0.75cm
\begin{itemize}
    \item Teleoperation approach to search and rescue 
    \item Aerial turbulence resistance 
\end{itemize}

%

\end{alertblock}

%-----------------------------------------------------------
% PROBLEM SETUP
%-----------------------------------------------------------
\vskip -1cm
\begin{block}{Problem Setup}
\vskip -1cm
%\begin{enumerate}
%    \item Develop and linearize system model
%    \item Simulate algorithms in MATLAB
%    \item Test algorithms on desktop computer using USB connection 
%    \item Test algorithms on Raspberry Pi microcontroller
%    \item Test algorithms on mobile device
%\end{enumerate}

\begin{figure}
    \centering
    % \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=\textwidth,keepaspectratio=true]{figs/ProblemStatementImage_Gray2}}
    \fcolorbox{gray!20}{gray!20}{\includegraphics[height=.15\textheight,width=\textwidth,keepaspectratio=true]{figs/ipe/highLevel_gry_grn.eps}
    }
    \caption{High level architecture of the proposed system.}
    \label{fig:highLevelDiagram}
\end{figure}
\begin{figure}
    \centering
    % \missingfigure{Insert figure.}
    \fcolorbox{gray!10}{gray!10}{
    \includegraphics[height=.2\textheight,width=.92\textwidth,keepaspectratio=true]{figs/img/quanserAero.png}
    }
    \caption{2-DOF helicopter (Quanser Aero).}
    %\caption{DC motors are attached to main and tail rotors which allow the helicopter to change its pitch and yaw respectively.}
    \label{fig:helicoterModel}
\end{figure}
\vskip -1cm
$\bullet$ State-space representation of 2-DOF helicopter
\begin{align*}
\begin{bmatrix}
    \dot\theta\\
    \dot\psi\\
    \ddot{\theta}\\
    \ddot{\psi}
\end{bmatrix}&=
%\label{eq:matrixA}
\begin{bmatrix}
    0 & 0 & 1 & 0 \\
    0 & 0 & 0 & 1 \\
    0 & -K_{sp}/J_p & -D_p/J_p & 0 \\
    0 & 0 & 1 & -D_y/J_y 
\end{bmatrix} 
%\label{eq:stateMatrix} 
\begin{bmatrix}
    \theta\\
    \psi\\
    \dot{\theta}\\
    \dot{\psi}
\end{bmatrix}
\\&+
%\label{eq:matrixB}
\begin{bmatrix}
    0 & 0 \\
    0 & 0 \\
    K_{pp}/J_p & K_{py}/J_p \\
    K_{yp}/J_y & K_{yy}/J_y 
\end{bmatrix}
%\label{eq:inputMatrix}
\begin{bmatrix}
    V_p \\
    V_y 
\end{bmatrix}
\end{align*}

\vskip -1cm
\end{block}

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The second column

%-----------------------------------------------------------
% LQR
%-----------------------------------------------------------

\begin{block}{Motion (Trajectory) Control Algorithm}
\vskip -1cm
%\begin{itemize}
%    \item Determines optimal control gain for dynamic systems
%%    \begin{subequations}
%%        \small
%%        \begin{align}
%%            & \dot{x} = Ax + Bu\\
%%            & u = -Kx\\
%%            & J(u) = \int_{0}^{\infty} (x^TQx + u^TRu + 2x^TNu)dt\\
%%            & A^TS+SA-(SB+N)R^{-1}(B^TS+N^T)+Q=0\\
%%            & K=R^{-1}(B^TS+N^T)
%%        \end{align}
%%    \label{eq:LQR_EQ}
%%    \end{subequations}
\begin{figure}
    \centering
    % \missingfigure{Insert figure.}
    \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.92\textwidth,keepaspectratio=true]{figs/ipe/algorithmFramework}}
    \caption{A desired orientation is given by a user.  The difference between this input and the actual position is calculated.  The controller the calculates the proper amount of voltage to apply to the DC motors.}
    \label{fig:algorithmFramework}
\end{figure}
%\end{itemize} 
\vskip -1cm
\begin{enumerate}
    \item Employ state-space representation of 2-DOF helicopter:
    \begin{align*}
        \dot{\mathbf{x}} = \mathbf{A}\mathbf{x} + \mathbf{B}\mathbf{u}
    \end{align*}
    \item Use state feedback law
    \begin{center}
        \vskip -1cm
        $\mathbf{u} = -\mathbf{K}\mathbf{x}$
    \end{center}
    \vskip -1cm
    to minimize the quadratic cost function:
    \begin{align*}
        J(\mathbf{u}) = \int_0^\infty (\mathbf{x}^T\mathbf{Q}\mathbf{x} + \mathbf{u}^T\mathbf{R}\mathbf{u} + 2\mathbf{x}^T\mathbf{N}\mathbf{u})\mathrm{dt}
    \end{align*}
    \item Find the solution $\mathbf{S}$ to the Riccati equation
    \begin{align*}
        \mathbf{A}^T\mathbf{S}+\mathbf{SA}-(\mathbf{SB}+\mathbf{N})\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)+\mathbf{Q}=0
    \end{align*}    
    \item Calculate gain, $\mathbf{K}$
    \begin{center}
        $\mathbf{K}=\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)$
    \end{center}
\end{enumerate}

%\vskip -2.5cm
\end{block}

%-----------------------------------------------------------
% LQG
%-----------------------------------------------------------

\begin{block}{Optimal Noise Resistant Control Algorithm}
\vskip -1cm
\begin{itemize}
    \item Utilizes gain calculated in LQR
    \item Added Kalman filter to reduce external disturbances to the system
%    \begin{subequations}
%        \small
%        \begin{align}
%            & some eq = x\\
%            & some eq = y\\
%            & some eq = z
%        \end{align}
%    \label{eq:LQG_EQ}
%    \end{subequations}
\end{itemize} 
%\todo[inline]{Insert Dr. Miah's LQG image from his slides here}
\begin{figure}
    \centering
    % \missingfigure{Insert figure.}
    \fcolorbox{gray!10}{gray!10}{\includegraphics[width=1.05\textwidth,keepaspectratio=true]{figs/img/LQG_SimulinkResize.png}}
    \caption{Noise resistant 2-DOF helicopter model.}
    \label{fig:LQGModel}
\end{figure}

%\vskip -2.5cm
\end{block}

\end{column} % End of second column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The third column
%-----------------------------------------------------------
% ADP
%-----------------------------------------------------------

\begin{block}{Reinforcement Learning Algorithm}
\vskip -1cm
\begin{itemize}
    %\item Reinforcement learning based approach
    \item Uses neural network based on difference between desired and actual orientation to determine optimal gain
    %\item Unlike LQR, ADP operates only in discrete-time and calculates new gains as the system is running
%    \begin{subequations}
%        \small
%        \begin{align}
%            & some eq = x\\
%            & some eq = y\\
%            & some eq = z
%        \end{align}
%    \label{eq:ADP_EQ}
%    \end{subequations}
\end{itemize} 
%\begin{enumerate}
%    \item Apply input to the system and calculate error e(k) at time k
%    \item Use Euler's method to convert the error model into discrete-time and record data every $\tau \sec$
%    \begin{center}
%        $e_{k+1}=f(e_k)+G(e_k)u_k$
%    \end{center}
%    \item 
%    %\item Minimize the cost function
%    %\begin{center}
%        $J(u)=\sum_{k=0}^{\infty} e_k^TQe_k+u_k^TRu_k$
%    %\end{center}
%    %\item Define value function
%    %\begin{center}
%        $V(e_k)=$
%    %\end{center}    
%    \item Solve for gain, K
%    \begin{center}
%        $K=0.5R^{-1}B^TP$
%    \end{center}
%\end{enumerate}

\begin{figure}
    \centering
    \fcolorbox{gray!10}{gray!10}{\includegraphics[width=.9\textwidth,keepaspectratio=true]{figs/ipe/ADP_Neural_Network.eps}}
    \caption{ADP Neural Network}
    \label{fig:NeuralNetwork}
\end{figure}

\vskip 1.5cm
%(1) t = kτ where τ is given
%(2)Advance the system by applying determined inputs to the system and measure system states
%(3)Calculate state error as e[k] = xref[k] − x[k], save state error
%(4) If t 6= T, increment k and start at (1)
%(5) If t = T, update K using collected error data
%(5a)Use error states since last update of K as inputs to the neural network
%(5b)Recursively determine wc values for each of the instances
%(5c)Approximate new wc value using regression analysis of the individually calculated wc values
%(6)Calculate new K using wc values
%(7) Increment k and start at (1)

\vskip -2.5cm
\end{block}
%-----------------------------------------------------------
% Subsystem Block Diagram
%-----------------------------------------------------------
%\begin{block}{Subsystem Block Diagram}
%\begin{figure}
%    \centering
%        \missingfigure{Insert figure.}
%    % \boxed{\includegraphics[width=.92\textwidth,keepaspectratio=true]{figs/ipe/subsystemBlockDiagramAlternate2}}
%    \label{fig:subsystem}
%\end{figure}
%\end{block}

%-----------------------------------------------------------
% SIMULATION RESULTS
%-----------------------------------------------------------

\begin{block}{Simulation Results}
\vskip -1cm
%\begin{itemize}
%    \item \todo[inline]{add LQR and LQG simulation results}
%\end{itemize}

%Before implementing the algorithm, it was simulated using the industry standard robot simulator V-REP. With numerous robot models available, V-REP is able to accurately and consistently produce like those expected in real--world scenarios. Preliminary simulation results can be seen in Fig.~\ref{fig:vrepResults}.

\begin{figure}
    \centering
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch}
    \label{fig:simStepPitch}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw}
    \label{fig:simStepYaw}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Pitch_Volt}
    \label{fig:simPitchVolt}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQG_PIvLQR_PI_Sim/Yaw_Volt}
    \label{fig:simYawVolt}
    }
    \caption{A comparison between LQG and LQR control for a step input is shown for \subref{fig:simStepPitch}~the~main~rotor and \subref{fig:simStepYaw}~the~tail~rotor and the corresponding voltages in \subref{fig:simPitchVolt}~and~\subref{fig:simYawVolt}}
    \label{fig:simResults}
\end{figure}
\vskip -2cm
\end{block}

\end{column} % End of third column

\begin{column}{\sepwid}\end{column}

\begin{column}{\onecolwid} % The fourth column

%-----------------------------------------------------------
% EXPERIMENTAL RESULTS
%-----------------------------------------------------------

\begin{block}{Experimental Results}
\vskip -1cm
%\begin{itemize}
%    \item ADP Algorithm
%\end{itemize}
\begin{figure}
    \centering
    \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.9\textwidth,keepaspectratio=true]{figs/ipe/setup.eps}}
    \caption{Experimental Setup}
    \label{fig:Setup}
\end{figure}

\begin{figure}
    \centering
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/ADPvLQR_P_USB/Pitch_ADP_LQR}
    \label{fig:stepPitchADP}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/ADPvLQR_P_USB/Yaw_ADP_LQR}
    \label{fig:stepYawADP}
    }
    \caption{ADP experimental results for \subref{fig:stepPitchADP}~the~main~rotor and \subref{fig:stepYawADP}~the~tail~rotor given a step input}
    \label{fig:ADP_Results}
\end{figure}
%\begin{itemize}
%    \item Comparison between different controller architectures (proportional controller and proportional controller with integral term)
%\end{itemize}
\vskip -.5cm

\begin{figure}
    \centering
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQR_PIvLQR_P_USB/step/Pitch_LQR_RMSE}
    \label{fig:stepPitch}
    }
    \subfigure[][]{
    %\missingfigure{Insert figure.}
    \includegraphics[width=.46\textwidth,keepaspectratio=true]{figs/matlab/LQR_PIvLQR_P_USB/step/Yaw_LQR_RMSE}
    \label{fig:stepYaw}
    }
    \caption{Comparison between P and PI control for a step input is shown for \subref{fig:stepPitch}~the~main~rotor and \subref{fig:stepYaw}~the~tail~rotor}
    \label{fig:expResults}
\end{figure}
\vskip -2cm
\end{block}

\begin{figure}
  \centering
  \subfigure[][]{
  \label{fig:time0}
  \includegraphics[width=0.4\textwidth]{figs/img/timeEquals0.jpg}
  }
  \subfigure[][]{
  \label{fig:time10}
  \includegraphics[width=0.4\textwidth,height=0.057\textheight]{figs/img/timeEquals10_2}
  }  
  \caption{\subref{fig:time0} Time = 0~and~\subref{fig:time10} Time = 10}
  \label{fig:posistionAtTime}
\end{figure}

%\begin{block}{Conclusion}

%As seen in the experimental results, this system brings moderate accuracy considering its implementation. With a total cost of around \$140 for the system mounted on the mobile robot and around \$23 for the beacons, this system is much more attainable for those conducting research in mapping and localization algorithms and inexpensive to scale to commercial applications.

%\end{block}

%-----------------------------------------------------------
% Conclusion and Future Work
%-----------------------------------------------------------

\begin{alertblock}{Conclusion and Future Work}
\begin{itemize}
    \item Model-based reinforcement learning technique (ADP)  is useful when system model is unknown
   % \item PI controller greatly reduces steady-state error, however increases overshoot and settling time
    \vskip .75cm
    \item Implement PI controller for ADP algorithm
    \item Use digital compass to increase accuracy of orientation and help identify initial position
\end{itemize}

\end{alertblock}

\end{column} % End of the fourth column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-09-21 preamble.tex
Initial project template uploaded.

% Load your needed packages and other commands of yours here:
%\usepackage{} % ... note that old .sty files can be included here

%--------------------------------------------------------------------------
% Do NOT edit the rest of the preample UNLESS YOU KNOW WHAT YOU'RE DOING!
%--------------------------------------------------------------------------

\ifthenelse{\boolean{PrintVersion}}{
\usepackage[top=1in,bottom=1in,left=0.75in,right=1.25in]{geometry}   % For twoside document
}{
\usepackage[top=1in,bottom=1in,left=0.75in,right=1.25in]{geometry}   % For oneside document
}

\usepackage{amsmath,amssymb,amstext} % Lots of math symbols and environments
\usepackage{graphicx} % For including graphics

\usepackage{nomentbl} 
\makenomenclature

\usepackage{ifpdf}

\newcommand{\href}[1]{#1} % does nothing, but defines the command so the
    % print-optimized version will ignore \href tags (redefined by hyperref pkg).
%\newcommand{\texorpdfstring}[2]{#1} % does nothing, but defines the command
% Anything defined here may be redefined by packages added below...

% Hyperlinks make it very easy to navigate an electronic document.
% In addition, this is where you should specify the thesis title
% and author as they appear in the properties of the PDF document.
% Use the "hyperref" package 
% N.B. HYPERREF MUST BE THE LAST PACKAGE LOADED; ADD ADDITIONAL PKGS ABOVE
\usepackage[\ifpdf pdftex,\fi letterpaper=true,pagebackref=false]{hyperref} % with basic options
		% N.B. pagebackref=true provides links back from the References to the body text. This can cause trouble for printing.
\hypersetup{
    plainpages=false,       % needed if Roman numbers in frontpages
    pdfpagelabels=true,     % adds page number as label in Acrobat's page count
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in Acrobat's bookmarks
    pdftoolbar=true,        % show Acrobat's toolbar?
    pdfmenubar=true,        % show Acrobat's menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
%    pdftitle={uOttawa\ LaTeX\ Thesis\ Template},    % title: CHANGE THIS TEXT!
%    pdfauthor={Author},    % author: CHANGE THIS TEXT! and uncomment this line
%    pdfsubject={Subject},  % subject: CHANGE THIS TEXT! and uncomment this line
%    pdfkeywords={keyword1} {key2} {key3}, % list of keywords, and uncomment this line if desired
    pdfnewwindow=true,      % links in new window
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=blue,         % color of internal links
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
\ifthenelse{\boolean{PrintVersion}}{   % for improved print quality, change some hyperref options
\hypersetup{	% override some previously defined hyperref options
%    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black}
}{} % end of ifthenelse (no else)

\usepackage{fancyhdr,lastpage} % Change caption style; changes headers and page styles etc.

### 2020-09-21 systemLevelFunctionalRequirements.tex
Initial project template uploaded.

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[12pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%%%\usepackage[document]{ragged2e}

%%% Examples of Article customizations
% These packages are optional, depending on whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{letterpaper} % or letterpaper (US) or a5paper or....
\geometry{margin=1in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options
\graphicspath{
{figs/ipe/}
}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{epstopdf}
\epstopdfsetup{suffix = {}}
\usepackage{siunitx}
\sisetup{unitsep = \cdot}
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

\usepackage{caption}        %Allows modification of captions
% \usepackage{indentfirst}    %Allows for indenting first paragraphs

\usepackage{hyperref}
\usepackage{todonotes}

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customize the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\usepackage{tikz}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{enumerate}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations

%%% The "real" document content comes below...

\title{Smart Control of 2-DOF Helicopter}
\author{Glenn Janiak \and Kenneth Vonckx \and \underline{Advisor}: Dr. Suruz Miah
}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

% \setlength{\parindent}{4em} % this should indent paragraphs

\begin{document}
\maketitle

\section{Project Description}
%\todo[inline]{} Previously used
%The aim of this project is to utilize machine learning techniques to control a team of helicopters.  Helicopters are very nonlinear and the dynamics complex, so control of them is challenging.  Convectional control techniques, such as (LQR) and LQG, are too simple to for this application.  Most research today based on simple control.  Additionally, this project will apply the concept of internet of things by providing a user interface for direct control via mobile devices.

Helicopters are of a paramount importance as they are used in many civilian and military applications due to their ability for vertical take-off and landing.  To enable their use in such applications, intensive research has been conducted in the literature to date since helicopters involve complex nonlinear dynamics.  Most of the work on helicopter-based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions.  Such methods are expensive and time-consuming to develop.  Implementation of motion control techniques using cost-effective hardware is still a challenge.

In this project, we are proposing an algorithm for smart control of a team of two degree-of-freedom (2-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position.  Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices.  This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.

%billions of dollars for
%aurdio (hobbies) platform for quanser

\section{System Architecture}
%Multiple helicopters will be controlled via embedded hardware interfacing devices which will receive input from a smart mobile device.  This general architecture is shown in \autoref{fig:ProblemStatementImage}.
%
% \autoref{fig:highLevel} shows the high-level system architecture of the proposed project for control of a team of helicopters.  %
% %
% \begin{figure}
%   \centering
%   \begin{mdframed}[backgroundcolor=yellow!20, roundcorner=7pt,outerlinewidth=1.2pt,outerlinecolor=blue!50]
%   \includegraphics[scale=0.749]{figs/ipe/highLevel_yel_grn}
%   \end{mdframed}
%   \caption{General High-Level System Architecture}
%   \label{fig:highLevel}
% \end{figure}
% %
% As shown, mobile devices will serve as terminals for users to communicate with the helicopters.  Mobile devices can be used in a wider variety of locations over stationary and is desired by more people.  Information sent by the users will be transmitted through a wireless TCP/IP network.  Their inputs will interface with our proposed smart control algorithm and change the configuration of the helicopters.  In particular, we will be applying Linear Quadratic Regression (LQR), Linear Quadratic Gaussian (LQG), and a machine learning based algorithm for the control of these helicopters, Approximate Dynamic Programming (ADP).

% %Each of the helicopters we will be using have fixed bases as shown in \autoref{fig:QuanserAero} (courtesy of Quanser Inc.).

% Each of the helicopters used will have fixed bases as shown in \autoref{fig:QuanserAero} (courtesy of Quanser Inc.).

% \begin{figure}
%   \centering
%   \captionsetup{justification=centering,margin=3cm}
%   \includegraphics{figs/img/QuanserAero}
%   \caption{Quanser Aero 2-DOF Helicopter \newline (\url{https://www.quanser.com/products/quanser-aero/})}
%   \label{fig:QuanserAero}
% \end{figure}
% %
% The tail of the helicopter has a motor that controls its yaw motion.  Similarly, the main rotor changes the pitch of the helicopter.  The directions in which the motors spin will be determined by the polarity of the applied voltages.  This will be regulated by our smart control algorithm.

% \section{Modes of Operations}
% %\label{sec:modesOfOperations}
% We plan on allowing the user to control the helicopter using three modes of operation.  A short description of each mode is given below.

% \begin{enumerate}[\textbf{Mode~\#}1:]
%     \item Allows the user to control the helicopters to a given configuration. For example, setting the pitch to 45 degrees and the yaw to 90 degrees will move the helicopter that much from the initial configuration.
%     \item Allows the user to choose a time varying input signal, so the helicopter will have a wave-like motion shifting from one configuration to another.  Examples include sine and square waves.
%     \item Allows the user to control the algorithm that the user wishes to apply.  They will be able to choose from LQR, LQG, or ADP.
% \end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-10-01 systemLevelFunctionalRequirements.tex
Updated functional requirements document with information based on our discussions

@@
 
-\title{Smart Control of 2-DOF Helicopter}
-\author{Glenn Janiak \and Kenneth Vonckx \and \underline{Advisor}: Dr. Suruz Miah
-}
+\title{Robotic Cart System}
+\author{Kalli Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}
+
 %\date{} % Activate to display a given date or no date (if empty),
@@
 \section{Project Description}
-%\todo[inline]{} Previously used
-%The aim of this project is to utilize machine learning techniques to control a team of helicopters.
-Helicopters are very nonlinear and the dynamics complex, so control of them is challenging.
-Convectional control techniques, such as (LQR) and LQG, are too simple to for this application.
-Most research today based on simple control.
-Additionally, this project will apply the concept of internet of things by providing a user interface for direct control via mobile devices.
+Robotic carts are of paramount importance to conduct many indoor or outdoor tasks.
+There are many applications of autonomous robotic carts.
+For example, in a grocery store, a customer (especially a person with disability) may need more than one cart but is incapable of pushing two carts simultaneously.
+Therefore, a second cart that is capable of identifying the customer to follow and is able to track and follow the customer through the store would be very useful.
+In an indoor office environment, such an autonomous robotic cart may be used to carry items such as files from one office to another.
+In an outdoor environment, such a cart may be used to carry sheets of glass.
 
-Helicopters are of a paramount importance as they are used in many civilian and military applications due to their ability for vertical take-off and landing.
-To enable their use in such applications, intensive research has been conducted in the literature to date since helicopters involve complex nonlinear dynamics.
-Most of the work on helicopter-based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions.
-Such methods are expensive and time-consuming to develop.
-Implementation of motion control techniques using cost-effective hardware is still a challenge.
+There are many solutions available in the market for such robotic carts.
+However, all of them require line of sight communication.
+In this project, we are proposing a robotic cart using mainly analog signals using cost-effective wireless communication.
+Implementation of a fully functional robotic cart will be out of the scope of this project but is an ultimate goal for this project in the coming years.
+However, this project is expected to encourage further research in this area as well as provide a foundation for that research.
 
-In this project, we are proposing an algorithm for smart control of a team of two degree-of-freedom (2-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position.
-Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices.
-This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.
+%------------------------------------------------
+\section{System Architecture}
+\subsection{System Block Diagram}
+The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device. \textlangle Darrah's block description here\textrangle
 
-%billions of dollars for
-%aurdio (hobbies) platform for quanser
+A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering, margin=3cm}
+    % Uncomment the below line once Kalli's block diagram figure is included in the figs folder
+    % \includegraphics{figs/img/sysBlockDiag}
+    \caption{Block Diagram of the Robotic Cart System}
+    \label{fig:sysBlockDiag}
+\end{figure}
 
-\section{System Architecture}
-%Multiple helicopters will be controlled via embedded hardware interfacing devices which will receive input from a smart mobile device.
-This general architecture is shown in \autoref{fig:ProblemStatementImage}.
-%
-% \autoref{fig:highLevel} shows the high-level system architecture of the proposed project for control of a team of helicopters.  %
-% %
-% \begin{figure}
-%   \centering
-%   \begin{mdframed}[backgroundcolor=yellow!20, roundcorner=7pt,outerlinewidth=1.2pt,outerlinecolor=blue!50]
-%   \includegraphics[scale=0.749]{figs/ipe/highLevel_yel_grn}
-%   \end{mdframed}
-%   \caption{General High-Level System Architecture}
-%   \label{fig:highLevel}
-% \end{figure}
-% %
-% As shown, mobile devices will serve as terminals for users to communicate with the helicopters.
-Mobile devices can be used in a wider variety of locations over stationary and is desired by more people.
-Information sent by the users will be transmitted through a wireless TCP/IP network.
-Their inputs will interface with our proposed smart control algorithm and change the configuration of the helicopters.
-In particular, we will be applying Linear Quadratic Regression (LQR), Linear Quadratic Gaussian (LQG), and a machine learning based algorithm for the control of these helicopters, Approximate Dynamic Programming (ADP).
+\subsection{System Inputs and Outputs}
+\subsubsection{Inputs}
+There are four inputs to the robotic cart system.
+\begin{enumerate}
+    \item Power - Both the mobile cart and the remote will require power from a battery.
+    \item On/Off Switch - The user must be able to turn both the cart and the remote off to save power when the robotic cart system is not in use.
+    \item Movement of the Remote - The user will control the mobile cart by moving with the remote.
+    \item Mode Selection - The user must be able to select which mode of operation the robotic cart system should use.
+\end{enumerate}
+
+\subsubsection{Outputs}
+There are two outputs from the robotic cart system.
+\begin{enumerate}
+    \item Cart Position Trajectory on 2D Plane - The cart will move to follow the remote.
+    \item Status Indicators - Both the mobile cart and the remote will have status indicators to provide the user with the status of the system.
+\end{enumerate}
+
+%------------------------------------------------
+\section{Requirements and Specifications}
+\subsection{Requirements}
+The robotic cart system will meet the following requirements:
+\begin{enumerate}
+    \item Cart must follow remote at a reasonable distance
+    \item Cart must be able to travel at a speed reasonable for walking
+    \item User must be alerted if cart falls too far behind
+    \item Cart must not require line-of-sight to follow remote
+    \item Cart must avoid obstacles
+\end{enumerate}
+
+\subsection{Specifications}
+Based on the requirements, the robotic cart system must meet the following specifications:
+\begin{enumerate}
+    \item Cart must be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
+    \item Cart must be able to travel at 2 m/s
+    \item User must be alerted if the cart falls more than 2 meters behind
+    \item Cart must be not require line-of-sight to follow remote
+    \item Cart must not collide with obstacles while following remote
+\end{enumerate}
 

### 2020-10-01 systemLevelFunctionalRequirements.tex
Added BU logo and draft block diagram

@@
 \usepackage{siunitx}
-\sisetup{unitsep = \cdot}
+\sisetup{inter-unit-product = \cdot}
 \usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
@@
 
+\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Command to make the lines in the title page
+
 %%% END Article customizations
@@
 
-\title{Robotic Cart System}
+\title{
+    \begin{center}
+        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
+        \vskip10pt
+        \HRule \\[0.4cm]
+        {\Huge \bfseries Robotic Cart System \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
+        \HRule \\[0.4cm]
+    \end{center}
+    }
 \author{Kalli Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}
@@
 
+\setlength{\marginparwidth}{2cm}
+
 \begin{document}
 \maketitle
+
+% \newpage
+% \tableofcontents % Table of contents
+\newpage % Start lab look on a new page
 
@@
     \captionsetup{justification=centering, margin=3cm}
-    % Uncomment the below line once Kalli's block diagram figure is included in the figs folder
-    % \includegraphics{figs/img/sysBlockDiag}
+    \includegraphics[width=6.5in]{figs/img/sysBlockDiag}
     \caption{Block Diagram of the Robotic Cart System}

### 2020-10-06 systemLevelFunctionalRequirements.tex
Moved block diagram and added to document
Update systemLevelFunctionalRequirements.tex
Updated systemLevelFunctionalRequirements System Block Diagram Section

@@
 \subsection{System Block Diagram}
-The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device. \textlangle Darrah's block description here\textrangle
+The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device.
+The system, as a whole, will take into consideration of the world around it and avoid obstacles while trying to follow the remote target.
+The system will also be trying to follow the remote pointer even if it loses the line of site detection.
+If the robot loses track or falls to far behind the remote the remote will indicate this to the user.
 
 A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
-\begin{figure}
+\begin{figure}[b]
     \centering
     \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=6.5in]{figs/img/sysBlockDiag}
+    \includegraphics[width=6.5in]{figs/system_block_diagram}
     \caption{Block Diagram of the Robotic Cart System}

### 2020-10-06 systemLevelFunctionalRequirements.tex
Updated block diagram
Spelling and grammar update

--- 2020-10-01 systemLevelFunctionalRequirements.tex
@@
     }
-\author{Kalli Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}
+\author{Kallistah Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}
 
@@
 \subsection{System Block Diagram}
-The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device. \textlangle Darrah's block description here\textrangle
+The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device.
+The system, as a whole, will take into consideration the world around it and avoid obstacles while trying to follow the remote target.
+The system will also be trying to follow the remote pointer even if it loses the line of sight detection.
+If the robot loses track or falls too far behind the remote, the remote will indicate this to the user.
 
 A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
-\begin{figure}
+\begin{figure}[b]
     \centering
     \captionsetup{justification=centering, margin=3cm}
-    \includegraphics[width=6.5in]{figs/img/sysBlockDiag}
+    \includegraphics[width=6.5in]{figs/system_block_diagram}
     \caption{Block Diagram of the Robotic Cart System}

### 2020-10-06 systemLevelFunctionalRequirements.tex
Fixed sentence in systemLevelFunctionalRequirements
Relaxed wording on requirements

@@
 \begin{enumerate}
-    \item Cart must follow remote at a reasonable distance
-    \item Cart must be able to travel at a speed reasonable for walking
-    \item User must be alerted if cart falls too far behind
-    \item Cart must not require line-of-sight to follow remote
-    \item Cart must avoid obstacles
+    \item Cart should follow remote at a reasonable distance
+    \item Cart should be able to travel at a speed reasonable for walking
+    \item User should be alerted if cart falls too far behind
+    \item Cart should not require line-of-sight to follow remote
+    \item Cart should avoid obstacles
 \end{enumerate}
@@
 \begin{enumerate}
-    \item Cart must be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
-    \item Cart must be able to travel at 2 m/s
-    \item User must be alerted if the cart falls more than 2 meters behind
-    \item Cart must be not require line-of-sight to follow remote
-    \item Cart must not collide with obstacles while following remote
+    \item Cart should be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
+    \item Cart should be able to travel at 2 m/s
+    \item User should be alerted if the cart falls more than 2 meters behind
+    \item Cart should not require line-of-sight to follow remote
+    \item Cart should not collide with obstacles while following remote
 \end{enumerate}
-
-% %Each of the helicopters we will be using have fixed bases as shown in \autoref{fig:QuanserAero} (courtesy of Quanser Inc.).
-
-% Each of the helicopters used will have fixed bases as shown in \autoref{fig:QuanserAero} (courtesy of Quanser Inc.).
-
-% \begin{figure}
-%   \centering
-%   \captionsetup{justification=centering,margin=3cm}
-%   \includegraphics{figs/img/QuanserAero}
-%   \caption{Quanser Aero 2-DOF Helicopter \newline (\url{https://www.quanser.com/products/quanser-aero/})}
-%   \label{fig:QuanserAero}
-% \end{figure}
-% %
-% The tail of the helicopter has a motor that controls its yaw motion.
-Similarly, the main rotor changes the pitch of the helicopter.
-The directions in which the motors spin will be determined by the polarity of the applied voltages.
-This will be regulated by our smart control algorithm.
-
-% \section{Modes of Operations}
-% %\label{sec:modesOfOperations}
-% We plan on allowing the user to control the helicopter using three modes of operation.  A short description of each mode is given below.
-
-% \begin{enumerate}[\textbf{Mode~\#}1:]
-%     \item Allows the user to control the helicopters to a given configuration.
-For example, setting the pitch to 45 degrees and the yaw to 90 degrees will move the helicopter that much from the initial configuration.
-%     \item Allows the user to choose a time varying input signal, so the helicopter will have a wave-like motion shifting from one configuration to another.  Examples include sine and square waves.
-%     \item Allows the user to control the algorithm that the user wishes to apply.  They will be able to choose from LQR, LQG, or ADP.
-% \end{enumerate}
 

### 2020-10-20 parts/A-coppSimModeling.tex
Added appendix in final report for CoppeliaSim modeling

%======================================================================
\chapter{Modeling in CoppeliaSim}
\label{ch: Chapter1}
%======================================================================

%----------------------------------------------------------------------
\section{Problem Statement}
%----------------------------------------------------------------------
It is important to be able to simulate a robot's behavior before using the actual robot to help find unexpected behaviors. CoppeliaSim is commercial robot simulation software with the ability to simulate a robot whose behavior is very close to the real robot. However, if the robot of interest is not already included in CoppeliaSim's library, it must be modeled. The following sections explain how to model the Runt Rover robot in CoppeliaSim.

%----------------------------------------------------------------------
\section{Dimensions and 3D Modeling}
%----------------------------------------------------------------------
The Runt Rover robot is geometrically simple, with only a few dimensions being necessary to model the shape of the body and wheels. The dimensions used in this guide are shown in \autoref{fig:runtRoverDims}

\begin{figure}
    \centering
    \includegraphics[width=3.5in]{figs/img/runtRoverDimensions}
    \caption{Dimensions of the Runt Rover Robot}
    \label{fig:runtRoverDims}
\end{figure}

The final 3D models are shown in \autoref{fig:runtRoverModels}. An arrow was placed on the body to indicate orientation during simulation.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/img/runtRoverChassis}
        \caption{Chassis}
        \label{fig:runtRoverChassis}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/img/runtRoverWheel}
        \caption{Wheel}
        \label{fig:runtRoverWheel}
    \end{subfigure}
    \caption{Modeled Parts}
    \label{fig:runtRoverModels}
\end{figure}

%----------------------------------------------------------------------
\section{Importing Models}
%----------------------------------------------------------------------
The next step is to import the 3D models into CoppeliaSim. This is accomplished using File \textgreater \ Import \textgreater \ Mesh. If the models were dimensioned in millimeters, the scale must be changed to 0.001 since CoppeliaSim uses meters. Since there are multiple colors in the models, there will be multiple shapes in CoppeliaSim. These can be grouped by dragging one shape onto another. Also, the shapes can be renamed. In modeling the Runt Rover, one chassis and four wheels are needed. The wheels must be placed in the correct locations on the axles.

%----------------------------------------------------------------------
\section{Adding Motors}
%----------------------------------------------------------------------
The robot can be given motors by means of revolute joints. These can be added using Add \textgreater \ Joint \textgreater \ Revolute. For the Runt Rover, one revolute joint was placed at each wheel. The joints should be named according to the wheel location since their names are used to interface the robot with Matlab. These joints are then made invisible by moving them to visibility layer 10. This is achieved in the Object Common Properties dialog box. The joints can be viewed by turning on visibility for layer 10 using the Layers dialog box. In the Object Properties dialog box, there is a button to open the Dynamic Properties dialog box. In this box, make sure the ``Motor enabled'' checkbox is enabled.

%----------------------------------------------------------------------
\section{Dynamic Shapes}
%----------------------------------------------------------------------
The 3D models do not have any dynamic properties within CoppeliaSim. It is recommended to use primitive shapes for the dynamic properties to reduce computation during simulation. For the Runt Rover, the wheels can be dynamically represented as cylinders, and the chassis can be dynamically represented as a cuboid. To add a primitive cylinder, use Add \textgreater \ Primitive Shape \textgreater \ Cylinder, and specify the size to be the same as a wheel. To add a cuboid, use Add \textgreater \ Primitive Shape \textgreater \ Cuboid, and specify the size to be the same as the chassis. These bodies must now be configured with the appropriate dynamic properties.

In the dynamic properties dialog box, make sure the ``Body is respondable'' checkbox is enabled, and enable the first four checkboxes and disable the last four checkboxes in the local respondable mask. Repeat this process on all of the dynamic shapes, alternating between selecting the first four and selecting the last four checkboxes in the local respondable mask. To give the robot mass and inertia, make sure the ``Body is dynamic'' checkbox is enabled, and click the ``Compute mass and inertia'' button. These dynamic shapes should be named according to the parts they represent (FrontLeftWheelDyn, for example). In the Object Common Properties dialog box, assign the dynamic shapes to visibility layer 9 to make them invisible.

%----------------------------------------------------------------------
\section{Linkage}
%----------------------------------------------------------------------
Now it is time to link everything together into one robot. First assign each graphical shape to its corresponding dynamic shape by dragging and dropping it onto the dynamic shape. Then assign the dynamic shapes for the wheels to the corresponding revolute joints in the same way. Finally, assign the revolute joints to the dynamic chassis. The name of the dynamic chassis is the name that will be used to interface with Matlab, so change it to ``RuntRover.'' Assign this shape to be the model base in the Object Common Properties dialog box. To make the bounding box the correct size, select the revolute joints and enable the ``Ignored by model bounding box'' and the ``Invisible during selection'' checkboxes in the Object Common Properties dialog box. Now enable the ``Select base of model instead'' checkbox for each of the visible objects. This allows us to select the entire robot by clicking on any part.

%----------------------------------------------------------------------
\section{Saving the Model}
%----------------------------------------------------------------------
To save this model, go to File \textgreater Save model as \textgreater CoppeliaSim model. The default location should be in the CoppeliaSim models directory. Create a new directory to contain your models and save the model within that directory. Your model will now be available in the CoppeliaSim library.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

### 2020-10-20 systemLevelFunctionalRequirements.tex
Updated the system level presentation
Updated speed requirement

@@
     }
-\author{Kallistah Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}
+\author{Kallistah Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisors}: Dr. Suruz Miah and Dr. Prasad Shastry}
 
@@
 There are four inputs to the robotic cart system.
-\begin{enumerate}
+\begin{itemize}
     \item Power - Both the mobile cart and the remote will require power from a battery.
@@
     \item Mode Selection - The user must be able to select which mode of operation the robotic cart system should use.
-\end{enumerate}
+\end{itemize}
 
@@
 There are two outputs from the robotic cart system.
-\begin{enumerate}
-    \item Cart Position Trajectory on 2D Plane - The cart will move to follow the remote.
+\begin{itemize}
+    \item Movement of the Cart - The cart will move to follow the remote.
     \item Status Indicators - Both the mobile cart and the remote will have status indicators to provide the user with the status of the system.
-\end{enumerate}
+\end{itemize}
 
@@
 The robotic cart system will meet the following requirements:
-\begin{enumerate}
+\begin{itemize}
     \item Cart should follow remote at a reasonable distance
@@
     \item Cart should avoid obstacles
-\end{enumerate}
+\end{itemize}
 
@@
 Based on the requirements, the robotic cart system must meet the following specifications:
-\begin{enumerate}
+\begin{itemize}
     \item Cart should be able to follow the remote while maintaining a distance of 1 to 1.5 meters.
-    \item Cart should be able to travel at 2 m/s
+    \item Cart should be able to travel at speeds up to 2 m/s
     \item User should be alerted if the cart falls more than 2 meters behind
@@
     \item Cart should not collide with obstacles while following remote
-\end{enumerate}
+\end{itemize}
 

### 2020-10-27 parts/A-coppSimModeling.tex
~

@@
 \chapter{Modeling in CoppeliaSim}
-\label{ch: Chapter1}
+\label{ch:Chapter1}
 %======================================================================
@@
 %----------------------------------------------------------------------
-It is important to be able to simulate a robot's behavior before using the actual robot to help find unexpected behaviors.
-CoppeliaSim is commercial robot simulation software with the ability to simulate a robot whose behavior is very close to the real robot.
-However, if the robot of interest is not already included in CoppeliaSim's library, it must be modeled.
+It is important to be able to simulate a robot's behavior before using the
+actual robot to help find unexpected behaviors. CoppeliaSim is commercial robot
+simulation software with the ability to simulate a robot that would operate in
+exactly the way it would happen with a real robot. However, the robot of
+interest is not currently included in CoppeliaSim's library that leads to
+creating a model of the robot and simulating it before practical implementation.
 The following sections explain how to model the Runt Rover robot in CoppeliaSim.
@@
 %%% mode: latex
-%%% TeX-master: "../finalReportMainV1"
+%%% TeX-master: "../finalReport"
 %%% End:

### 2021-02-10 code/stepTest.c
Created a code folder with stepper motor test code inside

@@ -1,0 +1,122 @@
+/**
+ * @file stepper_example.c
+ */
+
+#include <stdio.h>
+#include <signal.h>
+#include <rc/motor.h>
+#include <rc/time.h>
+#include <rc/start_stop.h>
+
+// Number of degrees per step on the stepper motor
+#define DEG_PER_STEP 1.8
+
+// Motor ports used on BBBlue
+#define M1 3
+#define M2 4
+
+void step(int direction, int numSteps);
+
+// interrupt handler to catch ctrl-c
+static void __signal_handler(__attribute__ ((unused)) int dummy)
+{
+        rc_set_state(EXITING);
+        return;
+}
+
+/**
+ * This template contains these critical components
+ * - ensure no existing instances are running and make new PID file
+ * - start the signal handler
+ * - initialize subsystems you wish to use
+ * - while loop that checks for EXITING condition
+ * - cleanup subsystems at the end
+ *
+ * @return     0 during normal operation, -1 on error
+ */
+int main()
+{
+    double position = 0;
+    int direction = 1;
+    int stepSize = 5;
+    
+    // make sure another instance isn't running
+    // if return value is -3 then a background process is running with
+    // higher privaledges and we couldn't kill it, in which case we should
+    // not continue or there may be hardware conflicts. If it returned -4
+    // then there was an invalid argument that needs to be fixed.
+    if(rc_kill_existing_process(2.0)<-2) return -1;
+
+    // make PID file to indicate your project is running
+    // due to the check made on the call to rc_kill_existing_process() above
+    // we can be fairly confident there is no PID file already and we can
+    // make our own safely.
+    rc_make_pid_file();
+
+    // set signal handler so the loop can exit cleanly
+    signal(SIGINT, __signal_handler);
+
+    // Keep looping until state changes to EXITING
+    rc_set_state(RUNNING);
+    rc_motor_init();
+    while(rc_get_state()!=EXITING){
+        // Step 90 degrees
+        while (position < 90)
+        {
+            step(direction, stepSize);
+            position += 1.8*stepSize;
+        }
+        rc_usleep(500000);
+        
+        // Reverse direction and reset position
+        direction *= -1;
+        position = 0;
+    }
+
+    // Close file descriptors
+    rc_remove_pid_file();    // remove pid file LAST
+    return 0;
+}
+
+void step(int direction, int numSteps)
+{
+    static int state = 0;
+
+    for (int i = 0; i < numSteps; ++i)
+    {
+        // Handle directional control
[…]

### 2021-02-11 code/GPIO_Test.c
Added Test code and custom library headers
[ Added ] Start of a custom library directory with xbee comunication headers
[ Added ] Testing code for Robot Control Library GPIO and UART testing
[ Added ] Testing code for the custom xbee com librarys and response behavior

@@ -1,0 +1,93 @@
+/* GPIO Test 
+*    Test of Remote Control Library GPIO header
+*    by takinga given GPIO port and atempting
+*    to open it and then toggle the pins output
+*    several times to confirm that its functional
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdlib.h>
+#include <stdbool.h>
+
+// Linix Library headers
+#include <unistd.h>
+
+// Robot Controll Library headers
+#include <rc/gpio.h>
+
+#define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
+
+void msleep(int milliSeconds) { usleep(milliSeconds*1000); }
+
+int main(int argc, char* argv[]){
+	printf("\tStarting GPIO Test...\n");
+
+	// Initalize variables
+	int success = 0;
+	int chip = 3;
+	int pin = 2;
+
+	// Check for Help menue argument
+	if(argc > 1 && !strcmp(argv[1],"-help")){
+		printf("\t--- [ Help ] ---\n");
+		printf("\t> Set Pin: -p [int]\n");
+		printf("\t> Set Chip: -c [int]\n");
+		return 0;
+	}
+
+	// Check for single character arguments
+	int argId = 1;
+	char* ptr;
+	while(argId < argc) {
+		// Check if current main argumetn is in valid format "-[Char]"
+		char* mainArg = argv[argId++];
+		bool mainFailed = !((mainArg[0] == '-') && (mainArg[2] == '\0'));
+		if(!mainFailed) {
+			switch (mainArg[1]) {
+			case 'c': // Chip Select Argument
+				if(argId < argc) {
+					char* subArg = argv[argId++];
+				 	if(subArg[0] >= '0' && subArg[0] <= '9') {
+					 	chip = strtol(subArg, &ptr, 10);
+						break;
+					}
+				}
+				ASSERT(false,"ERROR: -c(Set Chip) should be in format of \"-c [int]\".\n")
+			case 'p': // Pin Select argument
+				if(argId < argc) {
+					char* subArg = argv[argId++];
+				 	if(subArg[0] >= '0' && subArg[0] <= '9') {
+					 	pin = strtol(subArg, &ptr, 10);
+						break;
+					}
+				}
[…]

### 2021-02-11 code/G_UART_Test.c

@@ -1,0 +1,83 @@
+/* Gated UART Test 
+*    Test of ATCom and XBeeCom Custom Libraries
+*    And a Test of if all connected XBees are cordinators
+*    will the response packet from a remote endpoint
+*    be recived by all the corrdinators even if only
+*    one connected cordinator sent the inital command to it
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+#include <unistd.h>
+
+// Robot Control Library headers
+#include <rc/uart.h>
+#include <rc/gpio.h>
+
+// Custom headers
+#define DEBUG_XBEECOM 1
+#include "../Lib/ATCom.h"
+
+#define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
+
+void msleep(int milliSeconds) { usleep(milliSeconds*1000); }
+
+int main(){
+	printf("\tStarting Gated UART Test...\n");
+
+	// Initalize state variables
+	int bus_1 = 1;
+	int bus_2 = 2;
+
+	// Initalize storage variables
+	int success;
+	uint8_t buff[255];
+
+	
+	// Initalize UART ports to XBees
+	success = XBee_InitUART(bus_1);
+	ASSERT(success != -1, "\tERROR: Failed to Initalize UART Port %d.\n",bus_1);
+	
+	success = XBee_InitUART(bus_2);
+	ASSERT(success != -1, "\tERROR: Failed to Initalize UART Port %d.\n",bus_2);
+
+	// Send Remote DB command to XBee Cordinator 1
+	success = SendRemoteATCommand(bus_1, 0x1111, 0x6462);
+	if(success == -1) {  printf("\tERROR: Failed to write command to UART Port %d.\n",bus_1); return -1; }
+	printf("\tBytes Sent: %d\n", success);
+
+	sleep(1);
+
+	// Read back command from XBee Cordinaor 1
+	success = ReadCommand(bus_1, buff, 256);
+	if(success == -1) {  printf("\tERROR: Failed to read frame from UART Port %d.\n",bus_1); return -1; }
+
+	printf("\tBytes Recived: %d", success);
+	if(success > 0) printf("\n\t");
+	for(int i=0; i<success; i++)
+		printf("%X ",buff[i]);
+	printf("\n");
+
+	// Read back command from XBee Cordinaor 2
[…]

### 2021-02-11 code/Lib/ATCom.h

@@ -1,0 +1,106 @@
+#ifndef AT_COM_H
+#define AT_COM_H
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+
+// Custom headers
+#include "XBeeCom.h"
+
+// Prototypes
+int SendRemoteATCommand(int bus, uint16_t destAddr, uint16_t cmd);
+int SendLocalATCommand(int bus, uint16_t cmd);
+int ReadATResponseData(int bus, unsigned char* buf, int bufSize);
+
+// Send a Remote AT Command to given local destination address
+// @peram bus: UART bus address for the Beagle Bone Blue
+// @peram destAddr: 16-bit destination address(MY) of destination XBee
+// @peram cmd: 16-bit command to send to destination XBee
+// @return Number of sent bytes or -1 for failure
+int SendRemoteATCommand(int bus, uint16_t destAddr, uint16_t cmd){
+	// Create framework for Remote AT command
+    // Header - [Local Addr] - cmd_mode(2) - [Command] - [Checksum]
+    static unsigned char msg[19] = {
+        0x7E, 0x00,0x0F, 0x17, 0x01, 
+        //0x00,0x00,0x00,0x00,0x00,0x00,0x00,0x00,
+        0xFF,0xFF,0xFF,0xFF,0xFF,0xFF,0xFF,0xFF,
+        0x00,0x00, 0x02, 0x00,0x00, 0x00 //0x64,0x62, 0x00
+    };
+
+	// Write 16-bit destination peram (Stored post order LINUX)
+	msg[13] = ((unsigned char*)&destAddr)[1];
+    msg[14] = ((unsigned char*)&destAddr)[0];
+
+    // Write 16-bit command peram (Stored post order LINUX)
+	msg[16] = ((unsigned char*)&cmd)[1];
+    msg[17] = ((unsigned char*)&cmd)[0];
+
+	// Calculate and Write checksum with patern
+	msg[18] = CalculateChecksum(msg,19);
+
+    // Send Command
+    return SendCommand(bus, msg, 19);
+}
+
+// Send a Local AT Command over UART
+// @peram bus: UART bus address for the Beagle Bone Blue
+// @peram cmd: 16-bit command to send to destination XBee
+// @return Number of sent bytes or -1 for failure
+int SendLocalATCommand(int bus, uint16_t cmd){
+    // Create framework for Local AT command
+    // Header - [Command] - [Checksum]
+    static unsigned char msg[9] = {
[…]

### 2021-02-11 code/Lib/XBeeCom.h

@@ -1,0 +1,142 @@
+#ifndef XEBB_COM_H
+#define XBEE_COM_H
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+
+// Robot Control Library headers
+#include <rc/uart.h>
+
+// Prototypes
+int XBee_InitUART(int bus);
+int SendCommand(int bus, unsigned char* msg, int length);
+int ReadCommand(int bus, unsigned char* buf, int bufSize);
+unsigned char CalculateChecksum(unsigned char* msg, int length);
+bool CheckChecksum(unsigned char* msg, int length);
+unsigned char GetFrameState(unsigned char* msg, int length);
+
+// Initalize UART port to XBee
+// @peram bus: UART bus address for the Beagle Bone Blu
+// @return 0 for success or -1 for failure
+int XBee_InitUART(int bus){
+        // int rc_uart_init(int bus, int baudrate, float timeout, int canonical_en, int stop_bits, int parity_en);
+        return rc_uart_init(bus, 9600, 0.1f, 0, 1, 0);
+}
+
+// Close UART port to XBee
+// @peram bus: UART bus address for the Beagle Bone Blu
+// @return 0 for success or -1 for failure
+int XBee_CloseUART(int bus){
+        // int rc_uart_init(int bus, int baudrate, float timeout, int canonical_en, int stop_bits, int parity_en);
+        return  rc_uart_close(bus);
+}
+
+// Send a given Command using UART connection
+// @peram bus: UART bus address for the Beagle Bone Blue
+// @peram msg: pointer to buffer containg command message
+// @peram length: length of message in the given buffer
+// @return number of sent bytes or -1 for failure
+int SendCommand(int bus, unsigned char* msg, int length){
+        // Send Command
+        // int rc_uart_write(int bus, uint8_t* data, size_t bytes);
+        int success = rc_uart_write(bus, msg , length);
+	if(success == -1) return -1;
+
+#if DEBUG_XBEECOM
+	// Print out Command that was sent in hex
+	printf("\t[DEBUG] CMD: ");
+	for(uint16_t i=0; i < length; i++)
+		printf("0x%02X ",msg[i]);
+        printf("\n");
+#endif
+
+        return success;
+}
+
+// Read in Command response into given buffer
+// @peram bus: UART bus address for the Beagle Bone Blue
+// @peram buf: pointer to unsigned char buffer to hold input
[…]

### 2021-02-11 code/UART_Test.c

@@ -1,0 +1,77 @@
+/* UART Test 
+*    Test of Remote Control Library UART header
+*    by takinga given UART bus and atempting
+*    to open it then send a predefined message out
+*    and then read a message coming into the port
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+
+// Linix Library headers
+#include <unistd.h>
+
+// Robot Controll Library headers
+#include <rc/uart.h>
+
+#define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
+
+void msleep(int milliSeconds) { usleep(milliSeconds * 1000); }
+
+int main(int argc, char* argv[]) {
+	// Initalize Storage Variables
+	int success;       // Success/Respose from external functions
+	uint8_t buff[255]; // Recived Message buffer
+
+	// Initalize Property Variables
+	uint8_t msg[8] = { 0x7E,0x00,0x04,0x08,0x01,0x64,0x62,0x30 };
+	//uint8_t msg[13] = {0x7E,0x00,0x09,0x01,0x01,0x00,0x03,0x00,0x74,0x65,0x73,0x74,0x3A};
+	//uint8_t msg[19] = { 0x7E, 0x00, 0x0f, 0x17, 0x01, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x00, 0x11, 0x11, 0x02, 0x64, 0x62, 0xFD };
+	int bus = 1;
+
+	// Help menue argument
+	if (argc > 1 && !strcmp(argv[1], "-help")) {
+		printf("\t--- [Help] ---\n");
+		printf("\t> Set Bus: -b [0-9]\n");
+		return 0;
+	}
+
+	// Check for set bus argument
+	if (argc > 1) {
+		ASSERT(!strcmp(argv[1], "-b"), "\tERROR: Invalid argument \"%s\" type help for list of valid arguments.\n", argv[1]);
+		ASSERT(argc > 2, "\tERROR: Bus Select must be in the format of \"-b [0-9]\"\n");
+		char inpChar = argv[2][0];
+		ASSERT((inpChar >= '0' && inpChar <= '9'), "\tERROR: Invalid Input for -b since \"%s\" is not a number between 0-9.\n", argv[2])
+			bus = inpChar - '0';
+	}
+
+	printf("\tStarting UART Test on bus %d...\n", bus);
+
[…]

### 2021-02-24 code/ATCom_Lib_Test.c
Updated XBee Code
>[Added]   Modified Makefile Projct template that now alowes for a include directory
>[Changed] Updated code to assume path from include directory insted of hardcoded includes to it

>[Added]   A common Core Library header for common helpfull components
>[Changed] Updated Exsisting code to use Core Library functionality insted of redefining it per main file

>[Added]   New AT Communication Library test to test the ATCom.h Library

>[Changed] Varius bug fixes
>[Changed] General Clean up Gated UART Test Code and UI

@@ -1,0 +1,107 @@
+/* AT Command Library Test 
+*    Test of ATCom and some elements from other Custom Librarys.
+*    First testing local AT commands and then
+*    testing remote AT coommands as well as that
+*    response data can be extracted from the AT command responses
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+//#include <stdbool.h>
+#include <stdint.h>
+
+// Custom headers
+#include "CoreLib.h"
+#define DEBUG_XBEECOM 0
+#include "ATCom.h"
+
+int LocalATCom_Test(int bus);
+int RemoteATCom_Test(int bus, uint16_t destAddr);
+
+int main(){
+	printf("\tStarting Gated UART Test...\n");
+
+	// Initalize state variables
+	int bus = 1;
+	uint16_t remoteAddr = 0x0003;
+
+	// Initalize storage variables
+	int success;
+	
+	// Initalize UART ports to XBees
+	success = XBee_InitUART(bus);
+	ASSERT(success != -1, "\tERROR: Failed to Initalize UART Port %d.\n", bus);
+
+	// Test Local DB AT Command
+	LocalATCom_Test(bus);
+
+	// Test Remote DB AT Command
+	RemoteATCom_Test(bus, remoteAddr);
+
+	// Close UART ports to XBees
+	success = XBee_CloseUART(bus);
+	ASSERT(success != -1, "\tERROR: Failed to Close UART Port %d.\n", bus);
+
+	return 0;
+}
+
+int LocalATCom_Test(int bus) {
+	// Initalize storage variables
+	int success;
+	uint8_t buff[255];
+	uint8_t strength = 0;
+
+	// Send local DB command to XBee Cordinator 1
+	printf("\tSending Local AT Command...\n");
+	success = SendLocalATCommand(bus, 0x6462);
+	ASSERT(success != -1, "\tERROR: Failed to write command to UART Port %d.\n", bus);
+	printf("\tBytes Sent: %d\n", success);
+
+	msleep(100); // Safety Delay (Non-Esential)
+
+	// Read back local command from XBee Cordinaor 1
+	success = ReadCommand(bus, buff, 256);
+	ASSERT(success != -1, "\tERROR: Failed to read frame from UART Port %d.\n", bus);
+	int msgLength = success;
+
+	printf("\tBytes Recived to bus %d: %d\n", bus, msgLength);
[…]

### 2021-02-24 code/Example/example.c

@@ -1,0 +1,16 @@
+/* example.c
+*	main code file for modified example template
+*/
+
+/// --- Includes --- ///
+// Paths can be rgular global headers,
+// dependent of project sorce folder, or
+// dependent of the Include directory (default is "../Lib/")
+#include <stdio.h>
+
+int main() {
+	/// --- Main Program --- ///
+	printf("Hello World! :D\n");
+
+	return 0;
+}

### 2021-02-24 code/GPIO_Test.c

@@ -17,9 +17,8 @@
 // Robot Controll Library headers
 #include <rc/gpio.h>
 
-#define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
-
-void msleep(int milliSeconds) { usleep(milliSeconds*1000); }
+// Custom Library headers
+#include "CoreLib.h"
 
 int main(int argc, char* argv[]){
 	printf("\tStarting GPIO Test...\n");

### 2021-02-24 code/G_UART_Test.c

@@ -18,12 +18,9 @@
 #include <rc/gpio.h>
 
 // Custom headers
-#define DEBUG_XBEECOM 1
-#include "../Lib/ATCom.h"
-
-#define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
-
-void msleep(int milliSeconds) { usleep(milliSeconds*1000); }
+#include "CoreLib.h"
+#define DEBUG_XBEECOM 0
+#include "ATCom.h"
 
 int main(){
 	printf("\tStarting Gated UART Test...\n");
@@ -31,11 +28,11 @@ int main(){
 	// Initalize state variables
 	int bus_1 = 1;
 	int bus_2 = 2;
+	uint16_t remoteAddr = 0x1111;
 
 	// Initalize storage variables
 	int success;
 	uint8_t buff[255];
-
 	
 	// Initalize UART ports to XBees
 	success = XBee_InitUART(bus_1);
@@ -45,32 +42,41 @@ int main(){
 	ASSERT(success != -1, "\tERROR: Failed to Initalize UART Port %d.\n",bus_2);
 
 	// Send Remote DB command to XBee Cordinator 1
-	success = SendRemoteATCommand(bus_1, 0x1111, 0x6462);
+	printf("\tSending Remote AT Command...\n");
+	success = SendRemoteATCommand(bus_1, remoteAddr, 0x6462);
 	if(success == -1) {  printf("\tERROR: Failed to write command to UART Port %d.\n",bus_1); return -1; }
 	printf("\tBytes Sent: %d\n", success);
 
-	sleep(1);
+	msleep(100);
 
-	// Read back command from XBee Cordinaor 1
+	// Read back remote command from XBee Cordinaor 1
 	success = ReadCommand(bus_1, buff, 256);
 	if(success == -1) {  printf("\tERROR: Failed to read frame from UART Port %d.\n",bus_1); return -1; }
 
-	printf("\tBytes Recived: %d", success);
-	if(success > 0) printf("\n\t");
-	for(int i=0; i<success; i++)
-		printf("%X ",buff[i]);
-	printf("\n");
+	printf("\tBytes Recived to bus %d: %d", bus_1, success);
+	if(success > 0) fprintHexBuffer(buff, success, "\t\n", "\n");
 
-	// Read back command from XBee Cordinaor 2
-	success = ReadCommand(bus_1, buff, 256);
[…]

### 2021-02-24 code/Lib/ATCom.h

@@ -8,17 +8,19 @@
 #include <stdint.h>
 
 // Custom headers
+#include "CoreLib.h"
 #include "XBeeCom.h"
 
 // Prototypes
 int SendRemoteATCommand(int bus, uint16_t destAddr, uint16_t cmd);
 int SendLocalATCommand(int bus, uint16_t cmd);
+int StripATResponseData(unsigned char* msg, int length, unsigned char* buf, int bufSize);
 int ReadATResponseData(int bus, unsigned char* buf, int bufSize);
 
 // Send a Remote AT Command to given local destination address
-// @peram bus: UART bus address for the Beagle Bone Blue
-// @peram destAddr: 16-bit destination address(MY) of destination XBee
-// @peram cmd: 16-bit command to send to destination XBee
+// @param bus: UART bus address for the Beagle Bone Blue
+// @param destAddr: 16-bit destination address(MY) of destination XBee
+// @param cmd: 16-bit command to send to destination XBee
 // @return Number of sent bytes or -1 for failure
 int SendRemoteATCommand(int bus, uint16_t destAddr, uint16_t cmd){
 	// Create framework for Remote AT command
@@ -30,11 +32,11 @@ int SendRemoteATCommand(int bus, uint16_t destAddr, uint16_t cmd){
         0x00,0x00, 0x02, 0x00,0x00, 0x00 //0x64,0x62, 0x00
     };
 
-	// Write 16-bit destination peram (Stored post order LINUX)
+	// Write 16-bit destination param (Stored post order LINUX)
 	msg[13] = ((unsigned char*)&destAddr)[1];
     msg[14] = ((unsigned char*)&destAddr)[0];
 
-    // Write 16-bit command peram (Stored post order LINUX)
+    // Write 16-bit command param (Stored post order LINUX)
 	msg[16] = ((unsigned char*)&cmd)[1];
     msg[17] = ((unsigned char*)&cmd)[0];
 
@@ -46,61 +48,66 @@ int SendRemoteATCommand(int bus, uint16_t destAddr, uint16_t cmd){
 }
 
 // Send a Local AT Command over UART
-// @peram bus: UART bus address for the Beagle Bone Blue
-// @peram cmd: 16-bit command to send to destination XBee
+// @param bus: UART bus address for the Beagle Bone Blue
+// @param cmd: 16-bit command to send to destination XBee
 // @return Number of sent bytes or -1 for failure
 int SendLocalATCommand(int bus, uint16_t cmd){
     // Create framework for Local AT command
[…]

### 2021-02-24 code/Lib/CoreLib.h

@@ -1,0 +1,47 @@
+// Library of general usefull core featrues and functionality
+#ifndef CORE_LIB_H
+#define CORE_LIB_H
+
+/// ----- Headers----- ///
+
+// C Library headers
+#include <unistd.h>
+
+/// ----- Defenitions----- ///
+
+// Define Assert statement
+#define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
+
+/// ----- Prototypes ----- ///
+
+void msleep(int milliSeconds);
+void printHexBuffer(void* buf, int bufSize);
+void fprintHexBuffer(void* buf, int bufSize, char* header, char* footer);
+
+/// ----- Function Defenitions ----- ///
+
+// Milliseconds Sleep
+// @param milliSeconds: Time in milliseconds to sleep for
+void msleep(int milliSeconds) { usleep((milliSeconds)*1000); }
+
+// Print out byte array in hexidecimal
+// @param buf: Pointer to array of bytes to print out
+// @param bufSize: sice of given buffer 'buf' in bytes
+void printHexBuffer(void* buf, int bufSize){
+	for(int i=0; i<bufSize; i++)
+		printf("%02X ", ((unsigned char*)buf)[i]);
+}
+
+// Print out byte array in hexidecimal with endcaps
+// @param buf: Pointer to array of bytes to print out
+// @param bufSize: sice of given buffer 'buf' in bytes
+// @param header: Formated string to print out before the buffer
+// @param footer: Formated string to print out affter the buffer
+void fprintHexBuffer(void* buf, int bufSize, char* header, char* footer){
+	printf(header);
+	for(int i=0; i<bufSize; i++)
+		printf("%02X ", ((unsigned char*)buf)[i]);
+	printf(footer);
+}
+
+#endif

### 2021-02-24 code/Lib/XBeeCom.h

@@ -10,8 +10,12 @@
 // Robot Control Library headers
 #include <rc/uart.h>
 
+// Cutom lIbrary headers
+#include "CoreLib.h"
+
 // Prototypes
 int XBee_InitUART(int bus);
+int XBee_CloseUART(int bus);
 int SendCommand(int bus, unsigned char* msg, int length);
 int ReadCommand(int bus, unsigned char* buf, int bufSize);
 unsigned char CalculateChecksum(unsigned char* msg, int length);
@@ -47,10 +51,11 @@ int SendCommand(int bus, unsigned char* msg, int length){
 
 #if DEBUG_XBEECOM
 	// Print out Command that was sent in hex
-	printf("\t[DEBUG] CMD: ");
-	for(uint16_t i=0; i < length; i++)
-		printf("0x%02X ",msg[i]);
-        printf("\n");
+        fprintHexBuffer(msg, length, "\t[DEBUG] CMD: ", "\n");
+	//printf("\t[DEBUG] CMD: ");
+	//for(uint16_t i=0; i < length; i++)
+	//	printf("0x%02X ",msg[i]);
+        //printf("\n");
 #endif
 
         return success;
@@ -67,7 +72,7 @@ int ReadCommand(int bus,  unsigned char* buf, int bufSize){
         int num_Bytes = rc_uart_read_bytes(bus, buf, bufSize);
 	if(num_Bytes == -1) { return -1; }
 
-         // Check for valid checksum
+         // Check that the response is not empty
         if(num_Bytes == 0){
 #if DEBUG_XBEECOM
                 printf("\t[DEBUG] Did not recive a response message.\n");
@@ -76,31 +81,25 @@ int ReadCommand(int bus,  unsigned char* buf, int bufSize){
         }
 
 #if DEBUG_XBEECOM
-        else {
-		printf("\t[DEBUG] Recived: %d Bytes\n",num_Bytes);
-		printf("\t[DEBUG] MSG: ");
-		for(int i=0; i < num_Bytes; i++)
-			printf("0x%02X ",buf[i]);
-		printf("\n");
-	}
+	printf("\t[DEBUG] Recived: %d Bytes\n",num_Bytes);
+        fprintHexBuffer(buf, num_Bytes, "\t[DEBUG] MSG: ", "\n");
+	//printf("\t[DEBUG] MSG: ");
+	//for(int i=0; i < num_Bytes; i++)
+	//	printf("0x%02X ",buf[i]);
[…]

### 2021-02-24 code/UART_Test.c

@@ -15,9 +15,8 @@
 // Robot Controll Library headers
 #include <rc/uart.h>
 
-#define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
-
-void msleep(int milliSeconds) { usleep(milliSeconds * 1000); }
+// Custom Library headers
+#include "CoreLib.h"
 
 int main(int argc, char* argv[]) {
 	// Initalize Storage Variables
@@ -53,7 +52,7 @@ int main(int argc, char* argv[]) {
 	ASSERT(success != -1, "\tERROR: Failed to Initalize UART Port %d.\n", bus)
 
 		// int rc_uart_write(int bus, uint8_t* data, size_t bytes);
-		success = rc_uart_write(bus, msg, 13);
+		success = rc_uart_write(bus, msg, 8);
 	ASSERT(success != -1, "\tERROR: Failed to write to  UART Port %d.\n", bus)
 
 		printf("\tBytes Sent: %d\n", success);

### 2021-02-25 code/step_lib/step.c
Added stepper library

@@ -1,0 +1,66 @@
+#include "step.h"
+#include <rc/motor.h>
+#include <rc/time.h>
+
+// Function to initialize a stepper motor
+void stepper_init(StepperMotor* stepper, int m1, int m2)
+{
+    // Set the motor ports
+    stepper->m1 = m1;
+    stepper->m2 = m2;
+
+    // Set the current state
+    stepper->state = 0;
+}
+
+// Function to step the motor a specified number of steps
+void step(StepperMotor* stepper, int direction, int numSteps)
+{
+    for (int i = 0; i < numSteps; ++i)
+    {
+        // Handle directional control
+        if(direction > 0)
+        {
+            stepper->state++;
+        }
+        else if (direction < 0)
+        {
+            stepper->state--;
+        }
+
+        // Handle state rollover
+        if(stepper->state >= 4)
+        {
+            stepper->state = 0;
+        }
+        else if(stepper->state < 0)
+        {
+            stepper->state = 3;
+        }
+
+        // Winding states
+        switch(stepper->state)
+        {
+            case 0:
+            default:
+                rc_motor_set(stepper->m1, 1);
+                rc_motor_set(stepper->m2, 1);
+                break;
+            case 1:
+                rc_motor_set(stepper->m1,-1);
+                rc_motor_set(stepper->m2,1);
+                break;
+            case 2:
+                rc_motor_set(stepper->m1,-1);
+                rc_motor_set(stepper->m2,-1);
+                break;
+            case 3:
+                rc_motor_set(stepper->m1,1);
+                rc_motor_set(stepper->m2,-1);
+                break;
+        }
+
+        // Sleep to allow motor to turn
+        rc_usleep(12000);
+    }
+}

### 2021-02-25 code/step_lib/step.h

@@ -1,0 +1,26 @@
+#ifndef _STEP_H_
+#define _STEP_H_
+
+// Number of degrees per step on the stepper motor
+#define DEG_PER_STEP 1.8
+
+typedef struct
+{
+    // Motor driver ports used for the stepper motor
+    int m1;
+    int m2;
+
+    // Direction of the motor
+    int direction;
+
+    // State of the windings
+    int state;
+} StepperMotor;
+
+// Function to initialize a stepper motor
+void stepper_init(StepperMotor* stepper, int m1, int m2);
+
+// Function to step the motor a specified number of steps
+void step(StepperMotor* stepper, int direction, int numSteps);
+
+#endif

### 2021-02-25 code/G_UART_Test.c
Numerous code updates (pulled all code from BBBlue)

@@ -1,89 +1,0 @@
-/* Gated UART Test 
-*    Test of ATCom and XBeeCom Custom Libraries
-*    And a Test of if all connected XBees are cordinators
-*    will the response packet from a remote endpoint
-*    be recived by all the corrdinators even if only
-*    one connected cordinator sent the inital command to it
-*/
-
-// C Library headers
-#include <stdio.h>
-#include <string.h>
-#include <stdbool.h>
-#include <stdint.h>
-#include <unistd.h>
-
-// Robot Control Library headers
-#include <rc/uart.h>
-#include <rc/gpio.h>
-
-// Custom headers
-#include "CoreLib.h"
-#define DEBUG_XBEECOM 0
-#include "ATCom.h"
-
-int main(){
-	printf("\tStarting Gated UART Test...\n");
-
-	// Initalize state variables
-	int bus_1 = 1;
-	int bus_2 = 2;
-	uint16_t remoteAddr = 0x1111;
-
-	// Initalize storage variables
-	int success;
-	uint8_t buff[255];
-	
-	// Initalize UART ports to XBees
-	success = XBee_InitUART(bus_1);
-	ASSERT(success != -1, "\tERROR: Failed to Initalize UART Port %d.\n",bus_1);
-	
-	success = XBee_InitUART(bus_2);
-	ASSERT(success != -1, "\tERROR: Failed to Initalize UART Port %d.\n",bus_2);
-
-	// Send Remote DB command to XBee Cordinator 1
-	printf("\tSending Remote AT Command...\n");
-	success = SendRemoteATCommand(bus_1, remoteAddr, 0x6462);
-	if(success == -1) {  printf("\tERROR: Failed to write command to UART Port %d.\n",bus_1); return -1; }
-	printf("\tBytes Sent: %d\n", success);
-
-	msleep(100);
-
-	// Read back remote command from XBee Cordinaor 1
-	success = ReadCommand(bus_1, buff, 256);
-	if(success == -1) {  printf("\tERROR: Failed to read frame from UART Port %d.\n",bus_1); return -1; }
-
-	printf("\tBytes Recived to bus %d: %d", bus_1, success);
-	if(success > 0) fprintHexBuffer(buff, success, "\t\n", "\n");
-
-	// Read back remote command from XBee Cordinaor 2
-	success = ReadCommand(bus_2, buff, 256);
[…]

### 2021-02-25 code/Lib/ATCom.h

@@ -15,7 +15,8 @@
 int SendRemoteATCommand(int bus, uint16_t destAddr, uint16_t cmd);
 int SendLocalATCommand(int bus, uint16_t cmd);
 int StripATResponseData(unsigned char* msg, int length, unsigned char* buf, int bufSize);
-int ReadATResponseData(int bus, unsigned char* buf, int bufSize);
+int ReadRemoteATResponseData(int bus, unsigned char* buf, int bufSize);
+int ReadLocalATResponseData(int bus, unsigned char* buf, int bufSize);
 
 // Send a Remote AT Command to given local destination address
 // @param bus: UART bus address for the Beagle Bone Blue
@@ -98,14 +99,31 @@ int StripATResponseData(unsigned char* msg, int msgLength, unsigned char* buf, i
 // @param buf: unsigned char buffer to store recived data in
 // @param bufSize: size of the given buffer
 // @return Number of data bytes recived or -1 for failure
-int ReadATResponseData(int bus, unsigned char* buf, int bufSize){
+int ReadRemoteATResponseData(int bus, unsigned char* buf, int bufSize){
     // Setup variables
     int length = 0;
-    uint8_t msg[256];
+    uint8_t msg[20];
 
     // Read in Command Response
-    length = ReadCommand(bus, msg, 256);
-    if(length == -1) return -1;
+    length = ReadCommand(bus, msg, 20);
+    if(length < 0) return length;
+
+    return StripATResponseData(msg, length, buf, bufSize);
+}
+
+// Read Data from a AT Command Response over UART
+// @param bus: UART bus address for the Beagle Bone Blue
+// @param buf: unsigned char buffer to store recived data in
+// @param bufSize: size of the given buffer
+// @return Number of data bytes recived or -1 for failure
+int ReadLocalATResponseData(int bus, unsigned char* buf, int bufSize){
+    // Setup variables
+    int length = 0;
+    uint8_t msg[10];
+
+    // Read in Command Response
+    length = ReadCommand(bus, msg, 10);
+    if(length < 0) return length;
 
     return StripATResponseData(msg, length, buf, bufSize);
 }

### 2021-02-25 code/Lib/CoreLib.h

@@ -5,12 +5,16 @@
 /// ----- Headers----- ///
 
 // C Library headers
+#include <stdio.h>
 #include <unistd.h>
 
 /// ----- Defenitions----- ///
 
 // Define Assert statement
 #define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
+#define ASSERT_NOMSG(condition) if(!(condition)){return -1;}
+
+#define DEBUG_ASSERT(condition,ftext...) ASSERT_NOMSG(condition)
 
 /// ----- Prototypes ----- ///
 

### 2021-02-25 code/Lib/XBeeArray.h

@@ -1,0 +1,110 @@
+#ifndef XBEE_ARRAY_H
+#define XBEE_ARRAY_H
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+#include <unistd.h>
+
+// Robot Control Library headers
+#include <rc/gpio.h>
+
+// Custom headers
+#include "CoreLib.h"
+#include "ATCom.h"
+
+#if XBEE_ARRAY_DEBUG
+    #undef DEBUG_ASSERT
+    #define DEBUG_ASSERT(condition,ftext...) ASSERT(condition,ftext)
+#endif
+
+struct XBeeArray_Settings {
+	int top_uart_bus, side_uart_bus;
+	int io_chip_0, io_pin_0;
+	int io_chip_1, io_pin_1;
+    uint16_t remoteAddr;
+};
+
+int XBeeArray_Init(struct XBeeArray_Settings array);
+int XBeeArray_Close(struct XBeeArray_Settings array);
+int XBeeArray_GetStrengths(struct XBeeArray_Settings array, unsigned char strengths[5]);
+
+int XBeeArray_Init(struct XBeeArray_Settings array) {
+    int result;
+
+    // Initalize UART busses
+    result = XBee_InitUART(array.top_uart_bus);
+    DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize top UART on bus %d\n", array.top_uart_bus);
+    XBee_InitUART(array.side_uart_bus);
+    DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize side UART on bus %d\n", array.side_uart_bus);
+
+    // Initalize GPIO pins
+	result = rc_gpio_init(array.io_chip_0, array.io_pin_0, GPIOHANDLE_REQUEST_OUTPUT);
+	DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", array.io_chip_0, array.io_pin_0);
+    result = rc_gpio_init(array.io_chip_1, array.io_pin_1, GPIOHANDLE_REQUEST_OUTPUT);
+	DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", array.io_chip_1, array.io_pin_1);
+
+    return 0;
+}
+
[…]

### 2021-02-25 code/Lib/XBeeCom.h

@@ -27,14 +27,14 @@ unsigned char GetFrameState(unsigned char* msg, int length);
 // @return 0 for success or -1 for failure
 int XBee_InitUART(int bus){
         // int rc_uart_init(int bus, int baudrate, float timeout, int canonical_en, int stop_bits, int parity_en);
-        return rc_uart_init(bus, 9600, 0.1f, 0, 1, 0);
+        return rc_uart_init(bus, 115200, 0.1f, 0, 1, 0);
 }
 
 // Close UART port to XBee
 // @peram bus: UART bus address for the Beagle Bone Blu
 // @return 0 for success or -1 for failure
 int XBee_CloseUART(int bus){
-        // int rc_uart_init(int bus, int baudrate, float timeout, int canonical_en, int stop_bits, int parity_en);
+        // int rc_uart_close(int bus);
         return  rc_uart_close(bus);
 }
 
@@ -52,10 +52,6 @@ int SendCommand(int bus, unsigned char* msg, int length){
 #if DEBUG_XBEECOM
 	// Print out Command that was sent in hex
         fprintHexBuffer(msg, length, "\t[DEBUG] CMD: ", "\n");
-	//printf("\t[DEBUG] CMD: ");
-	//for(uint16_t i=0; i < length; i++)
-	//	printf("0x%02X ",msg[i]);
-        //printf("\n");
 #endif
 
         return success;
@@ -70,27 +66,27 @@ int ReadCommand(int bus,  unsigned char* buf, int bufSize){
          // Read in response
          // int rc_uart_read_bytes(int bus, uint8_t* buf, size_t bytes);
         int num_Bytes = rc_uart_read_bytes(bus, buf, bufSize);
-	if(num_Bytes == -1) { return -1; }
+	if(num_Bytes == -1) { printf("\tRC Read Bytes Failed.\n"); return -1; }
 
          // Check that the response is not empty
         if(num_Bytes == 0){
 #if DEBUG_XBEECOM
                 printf("\t[DEBUG] Did not recive a response message.\n");
 #endif
-                return -1;
+                printf("\tDid not recive a response message. D:\n");
+                return -3;
         }
 
 #if DEBUG_XBEECOM
 	printf("\t[DEBUG] Recived: %d Bytes\n",num_Bytes);
         fprintHexBuffer(buf, num_Bytes, "\t[DEBUG] MSG: ", "\n");
[…]

### 2021-02-25 code/Lib/step.h

@@ -1,6 +1,24 @@
-#include "step.h"
+#ifndef _STEP_H_
+#define _STEP_H_
+
 #include <rc/motor.h>
 #include <rc/time.h>
+
+// Number of degrees per step on the stepper motor
+#define DEG_PER_STEP 1.8
+
+typedef struct
+{
+    // Motor driver ports used for the stepper motor
+    int m1;
+    int m2;
+
+    // Direction of the motor
+    int direction;
+
+    // State of the windings
+    int state;
+} StepperMotor;
 
 // Function to initialize a stepper motor
 void stepper_init(StepperMotor* stepper, int m1, int m2)
@@ -21,21 +39,11 @@ void step(StepperMotor* stepper, int direction, int numSteps)
         // Handle directional control
         if(direction > 0)
         {
-            stepper->state++;
+            stepper->state = (stepper->state + 1)%4;
         }
         else if (direction < 0)
         {
-            stepper->state--;
-        }
-
-        // Handle state rollover
-        if(stepper->state >= 4)
-        {
-            stepper->state = 0;
-        }
-        else if(stepper->state < 0)
-        {
-            stepper->state = 3;
+            stepper->state = (stepper->state - 1)%4;
         }
 
         // Winding states
@@ -64,3 +72,5 @@ void step(StepperMotor* stepper, int direction, int numSteps)
         rc_usleep(12000);
     }
 }
+
+#endif

### 2021-02-25 code/Tests/Mux_UART_Testing/MUX_UART_Test.c

@@ -1,0 +1,56 @@
+/* Multiplexer Array Test 
+*    
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+#include <unistd.h>
+
+// Robot Control Library headers
+#include <rc/uart.h>
+#include <rc/gpio.h>
+
+// Custom headers
+#define DEBUG_XBEECOM 0
+#define XBEE_ARRAY_DEBUG 1
+#include "CoreLib.h"
+#include "ATCom.h"
+#include "XBeeArray.h"
+
+int main(){
+	printf("\tStarting Multiplexer XBee Array Test...\n");
+
+	// Initalize state variables
+	struct XBeeArray_Settings array = {
+		5,1,   // Uart buses Top(1) and Side(5) 
+		3,1,  // GPIO 0 (Chip 1 Pin 25)
+		3,2,  // GPIO 1 (Chip 1 Pin 17)
+		0x1111 // Target Remote XBee's 16-bit address
+	};
+
+	// Initalize storage variables
+	int result;
+	unsigned char strengths[5];
+
+	// Initalize XBee Reflector Array
+	printf("\tInitalizeing XBee Reflector Array...\n");
+	result = XBeeArray_Init(array);
+	ASSERT(result == 0, "\tERROR: Failed to Initalize XBee Array.\n");
+
+	// Get Stenght Values from the XBee Reflector Array
+	printf("\tGetting Strength values from XBee Reflector Array...\n");
+	result = XBeeArray_GetStrengths(array, strengths);
+	ASSERT(result == 0, "\tERROR: Failed to Get Signal Strength values from the XBee Array.\n");
+	printf("\tTop Strength: %02X\n", strengths[0]);
+	fprintHexBuffer(strengths+1, 4, "\tSide Strengths: ", "\n");
+
+	// Close XBee Reflector Array
+	printf("\tCloseing XBee Reflector Array...\n");
+	result = XBeeArray_Close(array);
+	ASSERT(result == 0, "\tERROR: Failed to Close XBee Array.\n");
+
+	return result;
+}

### 2021-02-25 code/Tests/stepTest/stepTest.c

@@ -7,6 +7,7 @@
 #include <rc/motor.h>
 #include <rc/time.h>
 #include <rc/start_stop.h>
+#include "../../Lib/step.h" // Stepper motor library
 
 // Number of degrees per step on the stepper motor
 #define DEG_PER_STEP 1.8
@@ -14,8 +15,6 @@
 // Motor ports used on BBBlue
 #define M1 3
 #define M2 4
-
-void step(int direction, int numSteps);
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
@@ -58,15 +57,22 @@ int main()
 
     // Keep looping until state changes to EXITING
     rc_set_state(RUNNING);
+    
+    // Initialize the motor drivers
     rc_motor_init();
+
+    // Create and initialize a stepper motor on motor drivers 3 and 4
+    StepperMotor stepper;
+    stepper_init(&stepper, 3, 4);
+
     while(rc_get_state()!=EXITING){
         // Step 90 degrees
         while (position < 90)
         {
-            step(direction, stepSize);
+            step(&stepper, direction, stepSize);
             position += 1.8*stepSize;
         }
-        rc_usleep(500000);
+        // rc_usleep(500000);
         
         // Reverse direction and reset position
         direction *= -1;
@@ -76,47 +82,4 @@ int main()
     // Close file descriptors
     rc_remove_pid_file();    // remove pid file LAST
     return 0;
-}
-
-void step(int direction, int numSteps)
-{
-    static int state = 0;
-
-    for (int i = 0; i < numSteps; ++i)
-    {
-        // Handle directional control
-        if(direction > 0) {
-            state++;
-        } else if (direction < 0) {
-            state--;
-        }
-
-        // Handle state rollover
-        if(state >= 4) state = 0;
-        else if(state < 0) state = 3;
-
-        // Winding states
-        switch(state) {
-            case 0:
-            default:
-                rc_motor_set(M1,1);
-                rc_motor_set(M2,1);
-                break;
-            case 1:
-                rc_motor_set(M1,-1);
-                rc_motor_set(M2,1);
-                break;
-            case 2:
-                rc_motor_set(M1,-1);
-                rc_motor_set(M2,-1);
-                break;
-            case 3:
-                rc_motor_set(M1,1);
-                rc_motor_set(M2,-1);
-                break;
-        }
-
-        // Sleep to allow motor to turn
-        rc_usleep(12000);
-    }
 }

### 2021-02-25 code/step_lib/step.h

@@ -1,26 +1,0 @@
-#ifndef _STEP_H_
-#define _STEP_H_
-
-// Number of degrees per step on the stepper motor
-#define DEG_PER_STEP 1.8
-
-typedef struct
-{
-    // Motor driver ports used for the stepper motor
-    int m1;
-    int m2;
-
-    // Direction of the motor
-    int direction;
-
-    // State of the windings
-    int state;
-} StepperMotor;
-
-// Function to initialize a stepper motor
-void stepper_init(StepperMotor* stepper, int m1, int m2);
-
-// Function to step the motor a specified number of steps
-void step(StepperMotor* stepper, int direction, int numSteps);
-
-#endif

### 2021-02-25 code/Lib/step.h
Updated stepper library

@@ -43,7 +43,8 @@ void step(StepperMotor* stepper, int direction, int numSteps)
         }
         else if (direction < 0)
         {
-            stepper->state = (stepper->state - 1)%4;
+            // Note: (state + 3)%4 is the same as decrementing state by 1 and wrapping at 0
+            stepper->state = (stepper->state + 3)%4;
         }
 
         // Winding states

### 2021-02-25 code/Tests/stepTest/stepTest.c

@@ -36,8 +36,8 @@ static void __signal_handler(__attribute__ ((unused)) int dummy)
 int main()
 {
     double position = 0;
-    int direction = 1;
-    int stepSize = 5;
+    int direction = -1;
+    int numSteps = 5;
     
     // make sure another instance isn't running
     // if return value is -3 then a background process is running with
@@ -69,10 +69,11 @@ int main()
         // Step 90 degrees
         while (position < 90)
         {
-            step(&stepper, direction, stepSize);
-            position += 1.8*stepSize;
+            fflush(stdout);
+            step(&stepper, direction, numSteps);
+            position += 1.8*numSteps;
         }
-        // rc_usleep(500000);
+        rc_usleep(500000);
         
         // Reverse direction and reset position
         direction *= -1;
@@ -80,6 +81,7 @@ int main()
     }
 
     // Close file descriptors
+    rc_motor_cleanup();
     rc_remove_pid_file();    // remove pid file LAST
     return 0;
 }

### 2021-03-02 code/Tests/Array_Recorder/Array_Recorder.c
Added array recorder for gathering data

@@ -1,0 +1,82 @@
+/* Array_Recorder.c
+*    
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+#include <unistd.h>
+#include <stdlib.h>
+
+// Robot Control Library headers
+#include <rc/uart.h>
+#include <rc/gpio.h>
+
+// Custom headers
+#define DEBUG_XBEECOM 0
+#define XBEE_ARRAY_DEBUG 1
+#include "CoreLib.h"
+#include "ATCom.h"
+#include "XBeeArray.h"
+
+int main(int argc, char* argv[]){
+	printf("\tStarting Multiplexer XBee Array Test...\n");
+
+	// Initalize state variables
+	struct XBeeArray_Settings array = {
+		5,1,   // Uart buses Top(1) and Side(5) 
+		3,1,  // GPIO 0 (Chip 1 Pin 25)
+		3,2,  // GPIO 1 (Chip 1 Pin 17)
+		0x1111 // Target Remote XBee's 16-bit address
+	};
+
+	// Initalize storage variables
+	int result;
+	unsigned char strengths[5];
+	FILE* fp;
+
+	// Read in peramiters
+	ASSERT(argc >= 3, "Not enugh input peramiters provided.\n");
+	double ideal_angle = atof(argv[1]);
+	double ideal_distance = atof(argv[2]);
+
+	// Initalize XBee Reflector Array
+	printf("\tInitalizeing XBee Reflector Array...\n");
+	result = XBeeArray_Init(array);
+	ASSERT(result == 0, "\tERROR: Failed to Initalize XBee Array.\n");
+
+	// Get Stenght Values from the XBee Reflector Array
+	printf("\tGetting Strength values from XBee Reflector Array...\n");
+	result = XBeeArray_GetStrengths(array, strengths);
+	ASSERT(result == 0, "\tERROR: Failed to Get Signal Strength values from the XBee Array.\n");
+	printf("\tTop Strength: %02X\n", strengths[0]);
+	fprintHexBuffer(strengths+1, 4, "\tSide Strengths: ", "\n");
+
+	// Record output
+	fp = fopen("Strengths.csv", "a");
+	ASSERT(fp != NULL, "\tERROR: Failed to open file.\n");
+	
+	if(ftell(fp) == 0) {
[…]

### 2021-03-02 code/Lib/CoreLib.h
Added location test code

@@ -8,10 +8,14 @@
 #include <stdio.h>
 #include <unistd.h>
 
+// Robot Control Library headers
+#include <rc/start_stop.h>
+
 /// ----- Defenitions----- ///
 
 // Define Assert statement
 #define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
+#define MAIN_ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); rc_set_state(EXITING);}
 #define ASSERT_NOMSG(condition) if(!(condition)){return -1;}
 
 #define DEBUG_ASSERT(condition,ftext...) ASSERT_NOMSG(condition)

### 2021-03-02 code/Lib/step.h

@@ -3,6 +3,7 @@
 
 #include <rc/motor.h>
 #include <rc/time.h>
+#include "CoreLib.h"
 
 // Number of degrees per step on the stepper motor
 #define DEG_PER_STEP 1.8
@@ -21,18 +22,23 @@ typedef struct
 } StepperMotor;
 
 // Function to initialize a stepper motor
-void stepper_init(StepperMotor* stepper, int m1, int m2)
+int stepper_init(StepperMotor* stepper, int m1, int m2)
 {
+    // Initialize the motor drivers
+    ASSERT(rc_motor_init() != -1, "\tERROR: Failed to initialize motors\n");
+
     // Set the motor ports
     stepper->m1 = m1;
     stepper->m2 = m2;
 
     // Set the current state
     stepper->state = 0;
+
+    return 0;
 }
 
 // Function to step the motor a specified number of steps
-void step(StepperMotor* stepper, int direction, int numSteps)
+int step(StepperMotor* stepper, int direction, int numSteps)
 {
     for (int i = 0; i < numSteps; ++i)
     {
@@ -52,26 +58,33 @@ void step(StepperMotor* stepper, int direction, int numSteps)
         {
             case 0:
             default:
-                rc_motor_set(stepper->m1, 1);
-                rc_motor_set(stepper->m2, 1);
+                ASSERT(rc_motor_set(stepper->m1, 1) != -1, "\tERROR: Failed to set motor %d\n", stepper->m1);
+                ASSERT(rc_motor_set(stepper->m2, 1) != -1, "\tERROR: Failed to set motor %d\n", stepper->m2);
                 break;
             case 1:
-                rc_motor_set(stepper->m1,-1);
-                rc_motor_set(stepper->m2,1);
+                ASSERT(rc_motor_set(stepper->m1, -1) != -1, "\tERROR: Failed to set motor %d\n", stepper->m1);
+                ASSERT(rc_motor_set(stepper->m2, 1) != -1, "\tERROR: Failed to set motor %d\n", stepper->m2);
                 break;
             case 2:
-                rc_motor_set(stepper->m1,-1);
-                rc_motor_set(stepper->m2,-1);
+                ASSERT(rc_motor_set(stepper->m1, -1) != -1, "\tERROR: Failed to set motor %d\n", stepper->m1);
+                ASSERT(rc_motor_set(stepper->m2, -1) != -1, "\tERROR: Failed to set motor %d\n", stepper->m2);
[…]

### 2021-03-02 code/Tests/Loc_Testing/Loc_Test.c

@@ -1,0 +1,190 @@
+/* Multiplexer Array Test 
+*    
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+#include <unistd.h>
+#include <signal.h>
+#include <math.h>
+
+// Robot Control Library headers
+#include <rc/uart.h>
+#include <rc/gpio.h>
+#include <rc/start_stop.h>
+
+// Custom headers
+#define DEBUG_XBEECOM 0
+#define XBEE_ARRAY_DEBUG 0
+#include "CoreLib.h"
+#include "ATCom.h"
+#include "XBeeArray.h"
+#include "step.h"
+
+#define STEPS_PER_MEASUREMENT 5
+#define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*DEG_PER_STEP)
+#define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
+
+// interrupt handler to catch ctrl-c
+static void __signal_handler(__attribute__ ((unused)) int dummy)
+{
+        rc_set_state(EXITING);
+        return;
+}
+
+// Local functions
+int getMeasurement(struct XBeeArray_Settings array, unsigned int current, unsigned char* strengths, unsigned char* distance_strengths, unsigned char* directional_strengths);
+double getDistance(unsigned char* distance_strengths, int num_strengths);
+int getAngle(unsigned char* directional_strengths, int num_strengths);
+
+int main(){
+    printf("\tStarting Location Test...\n");
+
+    // set signal handler so the loop can exit cleanly
+    signal(SIGINT, __signal_handler);
+
+    // make sure another instance isn't running
+    // if return value is -3 then a background process is running with
+    // higher privaledges and we couldn't kill it, in which case we should
+    // not continue or there may be hardware conflicts. If it returned -4
+    // then there was an invalid argument that needs to be fixed.
+    if(rc_kill_existing_process(2.0)<-2) return -1;
+
+    // make PID file to indicate your project is running
+    // due to the check made on the call to rc_kill_existing_process() above
+    // we can be fairly confident there is no PID file already and we can
+    // make our own safely.
+    rc_make_pid_file();
+
+    // Initalize state variables
+    int position = 0; // Angular position of reflector array (degrees)
+    int direction = 1; // Direction of stepper motor
+    unsigned int current = 0; // Current measurement number
+    struct XBeeArray_Settings array = {
[…]

### 2021-03-04 code/Lib/XBeeArray.h
Bug fixes and Updates to code
[Added] Sweep abuility to array recorder and proper argument processing
[Fixed] Array_Recorder not doing multiple checks for remote at command
[Fixed] Array_Recorder Debug log was breaking command check loops

@@ -63,14 +63,20 @@ int XBeeArray_Close(struct XBeeArray_Settings array) {
 
 int XBeeArray_GetStrengths(struct XBeeArray_Settings array, unsigned char strengths[5]){
     int result;
+    int readAttempts = 0;
 
-    // Send Remote AT Command from the top XBee
-    result = SendRemoteATCommand(array.top_uart_bus, array.remoteAddr, 0x6462);
-    DEBUG_ASSERT(result != -1, "\t[DEBUG] ERROR: Failed to write Remote AT command to UART Port %d.\n", array.top_uart_bus);
+    readAttempts = 0;
+    do {
+        readAttempts++;
+        
+        // Send Remote AT Command from the top XBee
+        result = SendRemoteATCommand(array.top_uart_bus, array.remoteAddr, 0x6462);
+        DEBUG_ASSERT(result != -1, "\t[DEBUG] ERROR: Failed to write Remote AT command to UART Port %d.\n", array.top_uart_bus);
 
-    // Read in Signel Stength for the remote from the top XBee
-    result = ReadRemoteATResponseData(array.top_uart_bus, &(strengths[0]), 1);
-    DEBUG_ASSERT(result != -1, "\t[DEBUG] ERROR: Failed to read Remote AT command response data on UART Port %d.\n", array.top_uart_bus);
+        // Read in Signel Stength for the remote from the top XBee
+        result = ReadRemoteATResponseData(array.top_uart_bus, &(strengths[0]), 1);
+    }  while(result < 0 && readAttempts < 4);
+    DEBUG_ASSERT(result >= 0, "\t[DEBUG] ERROR: Failed to read Remote AT command response data on UART Port %d.\n", array.top_uart_bus);
 
     // Flush Side UART in preperation for local AT commands
     msleep(1);
@@ -85,7 +91,7 @@ int XBeeArray_GetStrengths(struct XBeeArray_Settings array, unsigned char streng
         result = rc_gpio_set_value(array.io_chip_1, array.io_pin_1, (i>>1)&1);
 		DEBUG_ASSERT(result != -1, "\t[DEBUG] ERROR: Failed to set pin value for GPIO %d_%d.\n", array.io_chip_1, array.io_pin_1);      
         
-        int readAttempts = 0;
+        readAttempts = 0;
         do {
             readAttempts++;
 
@@ -95,8 +101,8 @@ int XBeeArray_GetStrengths(struct XBeeArray_Settings array, unsigned char streng
 
[…]

### 2021-03-04 code/Tests/Array_Recorder/Array_Recorder.c

@@ -9,22 +9,46 @@
 #include <stdint.h>
 #include <unistd.h>
 #include <stdlib.h>
-
-// Robot Control Library headers
-#include <rc/uart.h>
-#include <rc/gpio.h>
+#include <signal.h>
+#include <math.h>
 
 // Custom headers
 #define DEBUG_XBEECOM 0
 #define XBEE_ARRAY_DEBUG 1
-#include "CoreLib.h"
-#include "ATCom.h"
 #include "XBeeArray.h"
+#include "step.h"
 
+#define STEPS_PER_MEASUREMENT 5
+#define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*DEG_PER_STEP)
+#define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
+
+// interrupt handler to catch ctrl-c
+static void __signal_handler(__attribute__ ((unused)) int dummy) {
+        rc_set_state(EXITING);
+        return;
+}
+
+// Prototypes
+int ProcessArguments(int argc, char* argv[], double* angle, double* distance, double* height, bool* useSweep);
+int AddRecored(FILE* fp, struct XBeeArray_Settings array, double angle, double distance, double height);
+int StripFloat(char* str, float* value);
+
+// Main
 int main(int argc, char* argv[]){
-	printf("\tStarting Multiplexer XBee Array Test...\n");
+	printf("\tStarting Array Value Recorder...\n");
+
+	// set signal handler so the loop can exit cleanly
+    signal(SIGINT, __signal_handler);
+
+	// Set up PID file for this program
+	if(rc_kill_existing_process(2.0)<-2) return -1;
+    rc_make_pid_file();
 
 	// Initalize state variables
+	bool useSweep = false;
+	double init_angle = 0; //atof(argv[1]);
+	double init_distance = 1; //atof(argv[2]);
+	double init_height = 0;
 	struct XBeeArray_Settings array = {
 		5,1,   // Uart buses Top(1) and Side(5) 
 		3,1,  // GPIO 0 (Chip 1 Pin 25)
@@ -34,49 +58,164 @@ int main(int argc, char* argv[]){
 
 	// Initalize storage variables
 	int result;
-	unsigned char strengths[5];
+	StepperMotor sm;
 	FILE* fp;
 
 	// Read in peramiters
-	ASSERT(argc >= 3, "Not enugh input peramiters provided.\n");
-	double ideal_angle = atof(argv[1]);
[…]

### 2021-03-04 code/Lib/XBeeArray.h
Updated code with today's work and updated lab notebook

@@ -75,6 +75,12 @@ int XBeeArray_GetStrengths(struct XBeeArray_Settings array, unsigned char streng
 
         // Read in Signel Stength for the remote from the top XBee
         result = ReadRemoteATResponseData(array.top_uart_bus, &(strengths[0]), 1);
+
+        if(result < 0)
+        {
+            msleep(100);
+            DEBUG_ASSERT(rc_uart_flush(array.side_uart_bus) == 0, "\t[DEBUG] failed to flush UART for bus %d.\n", array.side_uart_bus);
+        }
     }  while(result < 0 && readAttempts < 4);
     DEBUG_ASSERT(result >= 0, "\t[DEBUG] ERROR: Failed to read Remote AT command response data on UART Port %d.\n", array.top_uart_bus);
 
@@ -101,6 +107,12 @@ int XBeeArray_GetStrengths(struct XBeeArray_Settings array, unsigned char streng
 
             // Read in signal strength from side XBee 'i'
             result = ReadLocalATResponseData(array.side_uart_bus, &(strengths[i+1]), 1);
+
+            if(result < 0)
+            {
+                msleep(1);
+                DEBUG_ASSERT(rc_uart_flush(array.side_uart_bus) == 0, "\t[DEBUG] failed to flush UART for bus %d.\n", array.side_uart_bus);
+            }
         } while(result < 0 && readAttempts < 4);
         DEBUG_ASSERT(result >= 0, "\t[DEBUG] ERROR: Failed to read Local AT command response data on UART Port %d.\n", array.side_uart_bus);
     }

### 2021-03-04 code/Tests/AngleTest/Angle_Test.c

@@ -1,0 +1,91 @@
+/* Array_Recorder.c
+*    
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+#include <unistd.h>
+#include <stdlib.h>
+#include <signal.h>
+#include <math.h>
+
+// Custom headers
+#define DEBUG_XBEECOM 0
+#define XBEE_ARRAY_DEBUG 1
+#include "XBeeArray.h"
+#include "step.h"
+
+// interrupt handler to catch ctrl-c
+static void __signal_handler(__attribute__ ((unused)) int dummy) {
+        rc_set_state(EXITING);
+        return;
+}
+
+// Prototypes
+int StripFloat(char* str, float* value);
+
+// Main
+int main(){
+    printf("\tStarting Angle Test...\n");
+
+    // set signal handler so the loop can exit cleanly
+    signal(SIGINT, __signal_handler);
+
+    // Set up PID file for this program
+    if(rc_kill_existing_process(2.0)<-2) return -1;
+    rc_make_pid_file();
+
+    // Initalize state variables
+    struct XBeeArray_Settings array = {
+        5,1,   // Uart buses Top(1) and Side(5) 
+        3,1,  // GPIO 0 (Chip 1 Pin 25)
+        3,2,  // GPIO 1 (Chip 1 Pin 17)
+        0x1111 // Target Remote XBee's 16-bit address
+    };
+
+    // Initalize storage variables
+    int result;
+    unsigned char strengths[5];
+    StepperMotor sm;
+
+    // Initalize XBee Reflector Array
+    printf("\tInitalizeing XBee Reflector Array...\n");
+    result = XBeeArray_Init(array);
+    MAIN_ASSERT(result == 0, "\tERROR: Failed to Initialize XBee Array.\n");
+
+    // Initialize Stepper Motor
+    printf("\tInitializing Stepper Motor...\n");
+    MAIN_ASSERT(stepper_init(&sm, 3, 4) != -1, "\tERROR: Failed to initialize Stepper Motor.\n");
+    
+    // Main Program loop
+    rc_set_state(RUNNING);
+    while(rc_get_state() == RUNNING)
+    {
+        // Get Strength Values from the XBee Reflector Array
+        result = XBeeArray_GetStrengths(array, strengths);
+        ASSERT(result == 0, "\tERROR: Failed to Get Signal Strength values from the XBee Array.\n");
+
[…]

### 2021-03-04 code/Tests/Array_Recorder/Array_Recorder.c

@@ -85,7 +85,7 @@ int main(int argc, char* argv[]){
 		int segment = 0;
 		int direction = 1;
 		float angleOffset = 0;
-		while(rc_get_state() != EXITING && segment < (NUM_MEASUREMENTS*2)-1) {
+		while(rc_get_state() != EXITING && segment < (NUM_MEASUREMENTS*2)) {
 			// Add recored
 			double curAngle = fmod((init_angle + (double)angleOffset), 360.0);
 			result = AddRecored(fp, array, curAngle, init_distance, init_height);
@@ -96,6 +96,7 @@ int main(int argc, char* argv[]){
         	result = step(&sm, direction, 5);
 			MAIN_ASSERT(result != -1, " ")
 			angleOffset += (DEG_PER_MEASUREMENT * direction);
+            ++segment;
 		}
 	} else {
 		// Add record
@@ -126,25 +127,30 @@ int AddRecored(FILE* fp, struct XBeeArray_Settings array, double angle, double d
 	int result;
 	unsigned char strengths[5];
 	
-	// Get Stenght Values from the XBee Reflector Array
-	result = XBeeArray_GetStrengths(array, strengths);
-	ASSERT(result == 0, "\tERROR: Failed to Get Signal Strength values from the XBee Array.\n");
-	
 	// Write out header if the file is empty
 	if(ftell(fp) == 0) {
 		result = fprintf(fp, "angle,distance,height,top,side1,side2,side3,side4\n");
 		ASSERT(result >= 0, "\tERROR: Failed to write to the file\n");
 	}
 
-	// Write out the ange, distance, and height values to the file
-	result = fprintf(fp, "%1.1f,%1.1f,%1.1f\n",angle,distance,height);
-	ASSERT(result >= 0, "\tERROR: Failed to write to the file\n");
+    for (int m = 0; m < 100; ++m)
+    {
+        // Get Stenght Values from the XBee Reflector Array
+        result = XBeeArray_GetStrengths(array, strengths);
+        ASSERT(result == 0, "\tERROR: Failed to Get Signal Strength values from the XBee Array.\n");
+        
+        // Write out the ange, distance, and height values to the file
+        result = fprintf(fp, "%1.1f,%1.1f,%1.1f",angle,distance,height);
+        ASSERT(result >= 0, "\tERROR: Failed to write to the file\n");
 
-	// Write out strength values to the file
-	for(int i=0;i<5;i++) {
-		result = fprintf(fp, ",%d", strengths[i]);
[…]

### 2021-03-04 code/Tests/Loc_Testing/Loc_Test.c

@@ -18,7 +18,7 @@
 
 // Custom headers
 #define DEBUG_XBEECOM 0
-#define XBEE_ARRAY_DEBUG 0
+#define XBEE_ARRAY_DEBUG 1
 #include "CoreLib.h"
 #include "ATCom.h"
 #include "XBeeArray.h"
@@ -64,9 +64,9 @@ int main(){
     int direction = 1; // Direction of stepper motor
     unsigned int current = 0; // Current measurement number
     struct XBeeArray_Settings array = {
-        5,1,   // Uart buses Top(1) and Side(5) 
-        3,1,  // GPIO 0 (Chip 1 Pin 25)
-        3,2,  // GPIO 1 (Chip 1 Pin 17)
+        5,1,   // Uart buses Top(5) and Side(1) 
+        3,1,  // GPIO 0 (Chip 3 Pin 1)
+        3,2,  // GPIO 1 (Chip 3 Pin 2)
         0x1111 // Target Remote XBee's 16-bit address
     };
 
@@ -171,20 +171,20 @@ int getAngle(unsigned char* directional_strengths, int num_strengths)
 {
     // Calculate a value based on the surrounding strengths as well as the current one
     double val = 0.5*directional_strengths[num_strengths-1] + directional_strengths[0] + 0.5*directional_strengths[1];
-    // Find the maximum value
-    double max = val;
-    int max_idx = 0;
+    // Find the minimum value
+    double min = val;
+    int min_idx = 0;
     for (int i = 1; i < num_strengths-1; ++i)
     {
         val = 0.5*directional_strengths[i-1] + directional_strengths[i] + 0.5*directional_strengths[i + 1];
-        if (val > max)
+        if (val < min)
         {
-            max = val;
-            max_idx = i;
+            min = val;
+            min_idx = i;
         }
     }
 
     // Convert the index to an angle in degrees
-    int angle = max_idx*9;
+    int angle = min_idx*9;
     return angle;
 }

### 2021-03-09 code/Tests/Loc_Testing/Loc_Test.c
Updated code

@@ -1,4 +1,4 @@
-/* Multiplexer Array Test 
+/* 
 *    
 */
 
@@ -15,6 +15,7 @@
 #include <rc/uart.h>
 #include <rc/gpio.h>
 #include <rc/start_stop.h>
+#include <rc/motor.h>
 
 // Custom headers
 #define DEBUG_XBEECOM 0
@@ -27,6 +28,10 @@
 #define STEPS_PER_MEASUREMENT 5
 #define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*DEG_PER_STEP)
 #define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
+#define MOVING_AVG_SIZE 10 // Size of the moving average window
+
+#define MOTOR_LEFT 1
+#define MOTOR_RIGHT 2
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
@@ -36,9 +41,21 @@ static void __signal_handler(__attribute__ ((unused)) int dummy)
 }
 
 // Local functions
-int getMeasurement(struct XBeeArray_Settings array, unsigned int current, unsigned char* strengths, unsigned char* distance_strengths, unsigned char* directional_strengths);
+int getMeasurement(struct XBeeArray_Settings array, unsigned int curStep, unsigned char* strengths, unsigned char* distance_strengths, unsigned char* directional_strengths);
 double getDistance(unsigned char* distance_strengths, int num_strengths);
 int getAngle(unsigned char* directional_strengths, int num_strengths);
+double avg_dbl(double* array, int size);
+double avg_int(int* array, int size);
+int sign(double x);
+double wrapToPi(double theta);
+
+// Control parameters
+double Kp = 1; // Linear speed proportional gain
+double Kw = 4; // Angular speed proportional gain
+double L = 0.21668; // Distance between wheels [m]
+double R = 0.0492125; // Radius of wheels [m]
+double vMax = 0.1; // Maximum linear speed [m/s]
+double omegaMax = M_PI/2; // Maximum angular speed [rad/s]
 
 int main(){
     printf("\tStarting Location Test...\n");
@@ -62,11 +79,11 @@ int main(){
     // Initalize state variables
     int position = 0; // Angular position of reflector array (degrees)
     int direction = 1; // Direction of stepper motor
-    unsigned int current = 0; // Current measurement number
[…]

### 2021-03-11 code/Tests/Quadrature_Recorder/Quadrature_Recorder.c
Added Quadrature Recorder
[Desc] Recorder for testing PWM speed to Quadrature Count

@@ -1,0 +1,210 @@
+/* Array_Recorder.c
+*    
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+#include <unistd.h>
+#include <stdlib.h>
+#include <signal.h>
+#include <math.h>
+
+// Robot Control Headers
+#include <rc/button.h>
+#include <rc/motor.h>
+
+// Custom Headers
+#include "CoreLib.h"
+
+// interrupt handler to catch ctrl-c
+static void __signal_handler(__attribute__ ((unused)) int dummy) {
+        rc_set_state(EXITING);
+        return;
+}
+
+// Prototypes
+int ProcessArguments(int argc, char* argv[],  int* _pwmFrequency, int* _motor1, int* _motor2, double* _duty);
+int AddRecored(FILE* fp, int pwm, float duty, int steps1, int steps2 );
+int StripFloat(char* str, float* value);
+int StripInt(char* str, int* value);
+
+// Main
+int main(int argc, char* argv[]){
+	printf("\tStarting Array Value Recorder...\n");
+
+	// set signal handler so the loop can exit cleanly
+    signal(SIGINT, __signal_handler);
+
+	// Set up PID file for this program
+	if(rc_kill_existing_process(2.0)<-2) return -1;
+    rc_make_pid_file();
+
+	// Initalize state variables
+	int _pwmFrequency = RC_MOTOR_DEFAULT_PWM_FREQ;
+	int _motor1 = 1, _motor2 = 2;
+	int _encoder1 = 1, _encoder2 = 2;
+	double _duty = 0;
+
+	// Initalize storage variables
+	int result;
+	FILE* fp;
+
+	// Read in peramiters
+	result = ProcessArguments(argc, argv, &_pwmFrequency, &_duty);
+	MAIN_ASSERT(result != -1, "\tERROR: Failed to Read in Arguments.\n");
+
+    // Initialize Motors
+    printf("\tInitializing Stepper Motor...\n");
+    MAIN_ASSERT(rc_motor_init_freq(_pwmFrequency) != -1, "\tERROR: Failed to initialize Motors.\n");
+
+	// Initalize Encoders
+	printf("\tInitalizeing Quadrature Encoders...\n");
+	result = rc_encoder_init();
[…]

### 2021-03-11 code/Tests/Loc_Testing/Loc_Test.c
Committing code that KIND OF WORKS!!!!

@@ -28,7 +28,9 @@
 #define STEPS_PER_MEASUREMENT 5
 #define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*DEG_PER_STEP)
 #define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
-#define MOVING_AVG_SIZE 10 // Size of the moving average window
+#define MOVING_AVG_SIZE 1 // Size of the moving average window
+
+#define DUTY_MAX 0.25
 
 #define MOTOR_LEFT 1
 #define MOTOR_RIGHT 2
@@ -48,6 +50,7 @@ double avg_dbl(double* array, int size);
 double avg_int(int* array, int size);
 int sign(double x);
 double wrapToPi(double theta);
+double wrapTo180(double theta);
 
 // Control parameters
 double Kp = 1; // Linear speed proportional gain
@@ -55,7 +58,7 @@ double Kw = 4; // Angular speed proportional gain
 double L = 0.21668; // Distance between wheels [m]
 double R = 0.0492125; // Radius of wheels [m]
 double vMax = 0.1; // Maximum linear speed [m/s]
-double omegaMax = M_PI/2; // Maximum angular speed [rad/s]
+double omegaMax = M_PI/6; // Maximum angular speed [rad/s]
 
 int main(){
     printf("\tStarting Location Test...\n");
@@ -92,9 +95,20 @@ int main(){
     unsigned char strengths[5]; // Temporary storage during measurement
     unsigned char distance_strengths[NUM_MEASUREMENTS]; // Strengths from transmitter
     unsigned char directional_strengths[4*NUM_MEASUREMENTS]; // Strengths from side XBees
-    double distance[MOVING_AVG_SIZE]; // Distances to remote in m
-    int angle[MOVING_AVG_SIZE]; // Angles to remote in degrees
+    double distance[MOVING_AVG_SIZE] = {0, }; // Distances to remote in m
+    int angle[MOVING_AVG_SIZE] = {0, }; // Angles to remote in radians
     unsigned int curMsmt = 0; // Next location to store the distance and angle in the moving average arrays
+    double avg_dist = 0; // Average of distance array in meters
+    double avg_ang = 0; // Average of angle array in degrees
+    double avg_ang_rad = 0; // Average of angle array in radians
+    double targetX = 0; // Estimated X coordinate of remote w.r.t. robot's local frame
[…]

### 2021-03-11 code/MainProgram/MainProgram.c
Added MainProgram

@@ -1,0 +1,392 @@
+/* 
+*    Main Program
+*/
+
+// C Library headers
+#include <stdio.h>
+#include <string.h>
+#include <stdbool.h>
+#include <stdint.h>
+#include <unistd.h>
+#include <signal.h>
+#include <math.h>
+
+// Robot Control Library headers
+#include <rc/uart.h>
+#include <rc/gpio.h>
+#include <rc/start_stop.h>
+#include <rc/motor.h>
+#include <rc/encoder_eqep.h>
+
+// Custom headers
+#define DEBUG_XBEECOM 0
+#define XBEE_ARRAY_DEBUG 1
+#include "CoreLib.h"
+#include "ATCom.h"
+#include "XBeeArray.h"
+#include "step.h"
+
+#define STEPS_PER_MEASUREMENT 5
+#define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*DEG_PER_STEP)
+#define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
+#define MOVING_AVG_SIZE 1 // Size of the moving average window
+
+#define MOTOR_LEFT 1
+#define MOTOR_RIGHT 2
+
+// Encoder defines
+#define ENCODER_LEFT MOTOR_LEFT
+#define ENCODER_RIGHT MOTOR_RIGHT
+#define COUNTS_PER_REV 1200
+
+// interrupt handler to catch ctrl-c
+static void __signal_handler(__attribute__ ((unused)) int dummy)
+{
+        rc_set_state(EXITING);
+        return;
+}
+
+// Local functions
+int getMeasurement(struct XBeeArray_Settings array, unsigned int curStep, unsigned char* strengths, unsigned char* distance_strengths, unsigned char* directional_strengths);
+double getDistance(unsigned char* distance_strengths, int num_strengths);
+int getAngle(unsigned char* directional_strengths, int num_strengths);
+double avg_dbl(double* array, int size);
+double avg_int(int* array, int size);
+int sign(double x);
+double absVal(double x);
+double wrapToPi(double theta);
+double wrapTo180(double theta);
+
+// Control parameters
+double Kp = 1; // Linear speed proportional gain
+double Kw = 4; // Angular speed proportional gain
+double L = 0.21668; // Distance between wheels [m]
+double R = 0.0492125; // Radius of wheels [m]
+double vMax = 0.1; // Maximum linear speed [m/s]
[…]

### 2021-03-12 code/Tests/Quadrature_Recorder/Quadrature_Recorder.c
Fixed some bugs in quadrature recorder

@@ -15,6 +15,7 @@
 // Robot Control Headers
 #include <rc/button.h>
 #include <rc/motor.h>
+#include <rc/encoder_eqep.h>
 
 // Custom Headers
 #include "CoreLib.h"
@@ -26,7 +27,7 @@ static void __signal_handler(__attribute__ ((unused)) int dummy) {
 }
 
 // Prototypes
-int ProcessArguments(int argc, char* argv[],  int* _pwmFrequency, int* _motor1, int* _motor2, double* _duty);
+int ProcessArguments(int argc, char* argv[],  int* _pwmFrequency, double* _duty);
 int AddRecored(FILE* fp, int pwm, float duty, int steps1, int steps2 );
 int StripFloat(char* str, float* value);
 int StripInt(char* str, int* value);
@@ -41,6 +42,7 @@ int main(int argc, char* argv[]){
 	// Set up PID file for this program
 	if(rc_kill_existing_process(2.0)<-2) return -1;
     rc_make_pid_file();
+	rc_set_state(RUNNING);
 
 	// Initalize state variables
 	int _pwmFrequency = RC_MOTOR_DEFAULT_PWM_FREQ;
@@ -62,7 +64,7 @@ int main(int argc, char* argv[]){
 
 	// Initalize Encoders
 	printf("\tInitalizeing Quadrature Encoders...\n");
-	result = rc_encoder_init();
+	result = rc_encoder_eqep_init();
 	MAIN_ASSERT(result == 0, "\tERROR: Failed to Initialize  Quadrature Encoders.\n");
 
 	// Open output file in Append mode
@@ -70,7 +72,6 @@ int main(int argc, char* argv[]){
 	MAIN_ASSERT(fp != NULL, "\tERROR: Failed to open file.\n");
 	
 	// Main Program loop
-	rc_set_state(RUNNING);
 	const int _numSteps = 10;
 	int steps1[_numSteps];
 	int steps2[_numSteps];
@@ -82,16 +83,16 @@ int main(int argc, char* argv[]){
 		// Run through moment sequence
 		for(int i = 0; i < _numSteps; i++) {
 			// Clear Encoder steps
-			MAIN_ASSERT(rc_encoder_write(_encoder1, 0) != -1, "\tERROR: Failed to write to encoder 1.\n");
[…]

### 2021-03-25 code/Lib/odometry.h
Added headers for odometry and robot parameters

@@ -1,0 +1,45 @@
+#ifndef ODOMETRY_H
+#define ODOMETRY_H
+
+#include <rc/encoder_eqep.h>
+
+#include "CoreLib.h"
+#include "robot.h"
+
+// Encoder defines
+#define ENCODER_LEFT 1
+#define ENCODER_RIGHT 2
+#define COUNTS_PER_REV 1200
+
+double odometry_getAngle();
+double odometry_getDistance();
+int odometry_setZeroRef();
+
+double odometry_getAngle()
+{
+    int leftEncVal = -rc_encoder_eqep_read(ENCODER_LEFT);
+    int rightEncVal = rc_encoder_eqep_read(ENCODER_RIGHT);
+    double theta_rad = (leftEncVal - rightEncVal)*2*M_PI*R/(1200*L);
+    double theta = theta_rad*180/M_PI;
+
+    return theta;
+}
+
+double odometry_getDistance()
+{
+    int leftEncVal = -rc_encoder_eqep_read(ENCODER_LEFT);
+    int rightEncVal = rc_encoder_eqep_read(ENCODER_RIGHT);
+    double distance = (leftEncVal + rightEncVal)*2*M_PI*R/(1200*2);
+
+    return distance;
+}
+
+int odometry_setZeroRef()
+{
+    ASSERT(rc_encoder_eqep_write(ENCODER_LEFT, 0) == 0, "\tERROR: Failed to reset left encoder\n");
+    ASSERT(rc_encoder_eqep_write(ENCODER_RIGHT, 0) == 0, "\tERROR: Failed to reset right encoder\n")
+
+    return 0;
+}
+
+#endif

### 2021-03-25 code/Lib/robot.h

@@ -1,0 +1,14 @@
+#ifndef ROBOT_H
+#define ROBOT_H
+
+// Robot Geometry
+double L = 0.21668; // Distance between wheels [m]
+double R = 0.0492125; // Radius of wheels [m]
+
+// Control parameters
+double Kp = 1; // Linear speed proportional gain
+double Kw = 4; // Angular speed proportional gain
+double vMax = 0.12; // Maximum linear speed [m/s]
+double omegaMax = M_PI/6; // Maximum angular speed [rad/s]
+
+#endif

### 2021-03-25 code/MainProgram/MainProgram.c
Updated MainProgram

@@ -2,6 +2,11 @@
 *    Main Program
 */
 
+// Development tools
+#define DEBUG_XBEECOM 0
+#define XBEE_ARRAY_DEBUG 1
+#define MOTORS_OFF 0
+
 // C Library headers
 #include <stdio.h>
 #include <string.h>
@@ -17,27 +22,24 @@
 #include <rc/start_stop.h>
 #include <rc/motor.h>
 #include <rc/encoder_eqep.h>
+#include <rc/button.h>
 
 // Custom headers
-#define DEBUG_XBEECOM 0
-#define XBEE_ARRAY_DEBUG 1
 #include "CoreLib.h"
+#include "robot.h"
 #include "ATCom.h"
 #include "XBeeArray.h"
 #include "step.h"
+#include "extraMath.h"
+#include "odometry.h"
 
 #define STEPS_PER_MEASUREMENT 5
 #define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*DEG_PER_STEP)
 #define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
-#define MOVING_AVG_SIZE 1 // Size of the moving average window
+#define MOVING_AVG_SIZE 2 // Size of the moving average window
 
 #define MOTOR_LEFT 1
 #define MOTOR_RIGHT 2
-
-// Encoder defines
-#define ENCODER_LEFT MOTOR_LEFT
-#define ENCODER_RIGHT MOTOR_RIGHT
-#define COUNTS_PER_REV 1200
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
@@ -46,27 +48,26 @@ static void __signal_handler(__attribute__ ((unused)) int dummy)
         return;
 }
 
+// Function to stop program on pause press
+static void __on_pause_press(void)
+{
+        rc_set_state(EXITING);
+        return;
+}
+
 // Local functions
-int getMeasurement(struct XBeeArray_Settings array, unsigned int curStep, unsigned char* strengths, unsigned char* distance_strengths, unsigned char* directional_strengths);
+int getMeasurement(struct XBeeArray_Settings array, unsigned int curStep, unsigned char* strengths, unsigned char* distance_strengths, int* directional_strengths);
 double getDistance(unsigned char* distance_strengths, int num_strengths);
-int getAngle(unsigned char* directional_strengths, int num_strengths);
+int getAngle(int* directional_strengths, int num_strengths);
[…]

### 2021-03-25 code/Tests/EncoderAngle_Testing/EncoderAngleTest.c
Added odometry tests

@@ -1,0 +1,90 @@
+// C Library headers
+#include <stdio.h>
+#include <signal.h>
+
+// Robot Control Library headers
+#include <rc/time.h>
+#include <rc/start_stop.h>
+#include <rc/button.h>
+
+#include "extraMath.h"
+#include "CoreLib.h"
+#include "odometry.h"
+#include "robot.h"
+
+// interrupt handler to catch ctrl-c
+static void __signal_handler(__attribute__ ((unused)) int dummy)
+{
+        rc_set_state(EXITING);
+        return;
+}
+
+// Function to print angle on pause press
+static void __on_pause_press(void)
+{
+    double angle = odometry_getAngle();
+    printf("Angle: %f degrees\n", angle);
+    return;
+}
+
+// Function to reset encoders on mode press
+static void __on_mode_press(void)
+{
+    odometry_setZeroRef();
+    return;
+}
+
+int main()
+{
+    // set signal handler so the loop can exit cleanly
+    signal(SIGINT, __signal_handler);
+
+    // make sure another instance isn't running
+    // if return value is -3 then a background process is running with
+    // higher privaledges and we couldn't kill it, in which case we should
+    // not continue or there may be hardware conflicts. If it returned -4
+    // then there was an invalid argument that needs to be fixed.
+    if(rc_kill_existing_process(2.0)<-2) return -1;
+
+    // make PID file to indicate your project is running
+    // due to the check made on the call to rc_kill_existing_process() above
+    // we can be fairly confident there is no PID file already and we can
+    // make our own safely.
+    rc_make_pid_file();
+
+    // Initialize pause button
+    if(rc_button_init(RC_BTN_PIN_PAUSE, RC_BTN_POLARITY_NORM_HIGH, RC_BTN_DEBOUNCE_DEFAULT_US))
+    {
+        fprintf(stderr,"ERROR: failed to init buttons\n");
+        return -1;
+    }
+    // Set the callback function
+    rc_button_set_callbacks(RC_BTN_PIN_PAUSE, __on_pause_press, NULL);
+
+    // Initialize mode button
+    if(rc_button_init(RC_BTN_PIN_MODE, RC_BTN_POLARITY_NORM_HIGH, RC_BTN_DEBOUNCE_DEFAULT_US))
+    {
+        fprintf(stderr,"ERROR: failed to init buttons\n");
+        return -1;
+    }
[…]

### 2021-03-25 code/Tests/EncoderDistance_Testing/EncoderDistanceTest.c

@@ -1,0 +1,90 @@
+// C Library headers
+#include <stdio.h>
+#include <signal.h>
+
+// Robot Control Library headers
+#include <rc/time.h>
+#include <rc/start_stop.h>
+#include <rc/button.h>
+
+#include "extraMath.h"
+#include "CoreLib.h"
+#include "odometry.h"
+#include "robot.h"
+
+// interrupt handler to catch ctrl-c
+static void __signal_handler(__attribute__ ((unused)) int dummy)
+{
+        rc_set_state(EXITING);
+        return;
+}
+
+// Function to print distance on pause press
+static void __on_pause_press(void)
+{
+    double distance = odometry_getDistance();
+    printf("Distance: %f [m]\n", distance);
+    return;
+}
+
+// Function to reset encoders on mode press
+static void __on_mode_press(void)
+{
+    odometry_setZeroRef();
+    return;
+}
+
+int main()
+{
+    // set signal handler so the loop can exit cleanly
+    signal(SIGINT, __signal_handler);
+
+    // make sure another instance isn't running
+    // if return value is -3 then a background process is running with
+    // higher privaledges and we couldn't kill it, in which case we should
+    // not continue or there may be hardware conflicts. If it returned -4
+    // then there was an invalid argument that needs to be fixed.
+    if(rc_kill_existing_process(2.0)<-2) return -1;
+
+    // make PID file to indicate your project is running
+    // due to the check made on the call to rc_kill_existing_process() above
+    // we can be fairly confident there is no PID file already and we can
+    // make our own safely.
+    rc_make_pid_file();
+
+    // Initialize pause button
+    if(rc_button_init(RC_BTN_PIN_PAUSE, RC_BTN_POLARITY_NORM_HIGH, RC_BTN_DEBOUNCE_DEFAULT_US))
+    {
+        fprintf(stderr,"ERROR: failed to init buttons\n");
+        return -1;
+    }
+    // Set the callback function
+    rc_button_set_callbacks(RC_BTN_PIN_PAUSE, __on_pause_press, NULL);
+
+    // Initialize mode button
+    if(rc_button_init(RC_BTN_PIN_MODE, RC_BTN_POLARITY_NORM_HIGH, RC_BTN_DEBOUNCE_DEFAULT_US))
+    {
+        fprintf(stderr,"ERROR: failed to init buttons\n");
+        return -1;
[…]

### 2021-03-25 code/Tests/UART_Testing/UART_Test.c
Committing other file changes from BBBlue

@@ -48,7 +48,7 @@ int main(int argc, char* argv[]) {
 	printf("\tStarting UART Test on bus %d...\n", bus);
 
 	// int rc_uart_init(int bus, int baudrate, float timeout, int canonical_en, int stop_bits, int parity_en);
-	success = rc_uart_init(bus, 9600, 0.1f, 0, 1, 0);
+	success = rc_uart_init(bus, 115200, 0.1f, 0, 1, 0);
 	ASSERT(success != -1, "\tERROR: Failed to Initalize UART Port %d.\n", bus)
 
 		// int rc_uart_write(int bus, uint8_t* data, size_t bytes);

### 2021-03-26 code/Lib/extraMath.h
Doing some cleanup on the code

@@ -24,6 +24,12 @@ EXTRA_MATH_FUNC_HEAD double max(double x1, double x2);
 EXTRA_MATH_FUNC_HEAD int clamp_i(int x, int min, int max);
 EXTRA_MATH_FUNC_HEAD double clamp(double x, double min, double max);
 
+EXTRA_MATH_FUNC_HEAD double avg_i(int* array, int size);
+EXTRA_MATH_FUNC_HEAD double avg(double* array, int size);
+
+EXTRA_MATH_FUNC_HEAD double wrapToPi(double theta);
+EXTRA_MATH_FUNC_HEAD double wrapTo180(double theta);
+
 // Modulo for Intagers
 // @param x: First operand value of modulo operator
 // @param a: Second operand value of modulo operator
@@ -92,6 +98,60 @@ EXTRA_MATH_FUNC_HEAD int clamp_i(int x, int min, int max) {
 // @param max: Maximum value of range
 EXTRA_MATH_FUNC_HEAD double clamp(double x, double min, double max) {
     return (x < min) ? min : ((x > max) ? max : x);
+}
+
+// Returns average of an array of integers
+// @param x1: Array of integers
+// @param x2: Size of array
+EXTRA_MATH_FUNC_HEAD double avg_i(int* array, int size) {
+    int sum = 0;
+    for (int i = 0; i < size; ++i)
+    {
+        sum += array[i];
+    }
+    return (double)sum/size;
+}
+
+// Returns average of an array of doubles
+// @param x1: Array of doubles
+// @param x2: Size of array
+EXTRA_MATH_FUNC_HEAD double avg(double* array, int size) {
+    double sum = 0;
+    for (int i = 0; i < size; ++i)
+    {
+        sum += array[i];
+    }
+    return sum/size;
+}
+
+// Wraps theta between -pi and pi
+// @param theta: Angle to wrap (in radians)
+EXTRA_MATH_FUNC_HEAD double wrapToPi(double theta)
+{
+    while(theta > M_PI)
+    {
+        theta -= 2*M_PI;
+    }
+    while(theta < -M_PI)
+    {
+        theta += 2*M_PI;
+    }
+    return theta;
+}
+
+// Wraps theta between -180 and 180
+// @param theta: Angle to wrap (in degrees)
+EXTRA_MATH_FUNC_HEAD double wrapTo180(double theta)
+{
+    while(theta > 180)
+    {
+        theta -= 360;
+    }
[…]

### 2021-03-26 code/Lib/odometry.h

@@ -11,11 +11,14 @@
 #define ENCODER_RIGHT 2
 #define COUNTS_PER_REV 1200
 
-double odometry_getAngle();
-double odometry_getDistance();
+double odometry_getAngle(double R, double L);
+double odometry_getDistance(double R);
 int odometry_setZeroRef();
 
-double odometry_getAngle()
+// Estimates the rotation angle of the robot relative to the last time the zero reference was set
+// @param R: Radius of the wheels
+// @param L: Distance between wheels
+double odometry_getAngle(double R, double L)
 {
     int leftEncVal = -rc_encoder_eqep_read(ENCODER_LEFT);
     int rightEncVal = rc_encoder_eqep_read(ENCODER_RIGHT);
@@ -25,7 +28,9 @@ double odometry_getAngle()
     return theta;
 }
 
-double odometry_getDistance()
+// Estimates the distance the robot has traveled since the last time the zero reference was set
+// @param R: Radius of the wheels
+double odometry_getDistance(double R)
 {
     int leftEncVal = -rc_encoder_eqep_read(ENCODER_LEFT);
     int rightEncVal = rc_encoder_eqep_read(ENCODER_RIGHT);
@@ -34,6 +39,7 @@ double odometry_getDistance()
     return distance;
 }
 
+// Sets the zero reference for getAngle and getDistance
 int odometry_setZeroRef()
 {
     ASSERT(rc_encoder_eqep_write(ENCODER_LEFT, 0) == 0, "\tERROR: Failed to reset left encoder\n");

### 2021-03-26 code/Lib/robot.h

@@ -1,14 +1,131 @@
 #ifndef ROBOT_H
 #define ROBOT_H
 
-// Robot Geometry
-double L = 0.21668; // Distance between wheels [m]
-double R = 0.0492125; // Radius of wheels [m]
+// C Library headers
+// #include <stdio.h>
+// #include <string.h>
+// #include <stdbool.h>
+// #include <stdint.h>
+// #include <stdlib.h>
+// #include <unistd.h>
+// #include <signal.h>
+// #include <math.h>
 
-// Control parameters
-double Kp = 1; // Linear speed proportional gain
-double Kw = 4; // Angular speed proportional gain
-double vMax = 0.12; // Maximum linear speed [m/s]
-double omegaMax = M_PI/6; // Maximum angular speed [rad/s]
+// Robot Control Library headers
+// #include <rc/uart.h>
+// #include <rc/gpio.h>
+#include <rc/motor.h>
+#include <rc/encoder_eqep.h>
+// #include <rc/button.h>
+
+// Custom headers
+#include "CoreLib.h"
+// #include "ATCom.h"
+#include "XBeeArray.h"
+#include "step.h"
+// #include "extraMath.h"
+// #include "odometry.h"
+
+typedef struct
+{
+    // Robot Geometry
+    double L; // Distance between wheels [m]
+    double R; // Radius of wheels [m]
+
+    // Speed limits
+    double vMax; // Maximum linear speed [m/s]
+    double omegaMax; // Maximum angular speed [rad/s]
+
+    int left_motor;
+    int right_motor;
+
+    // Array of XBees
+    struct XBeeArray_Settings array;
+
+    // Stepper motor
+    StepperMotor sm;
+
+} Robot_t;
+
+int robot_init(Robot_t* robot);
+int robot_close(Robot_t* robot);
+int robot_setSpeeds(Robot_t* robot, double v, double omega);
+
+// Initializes the robot
+// @param robot: The robot object to initialize
+int robot_init(Robot_t* robot)
+{
+    // Assign robot variables
+    robot->L = 0.21668;
+    robot->R = 0.0492125;
+    robot->vMax = 0.12;
+    robot->omegaMax = M_PI/6;
+    robot->left_motor = 1;
+    robot->right_motor = 2;
+    robot->array = {
+        5,1,   // Uart buses Top(5) and Side(1) 
+        3,1,   // GPIO 0 (Chip 3 Pin 1)
[…]

### 2021-03-26 code/MainProgram/MainProgram.c

@@ -12,6 +12,7 @@
 #include <string.h>
 #include <stdbool.h>
 #include <stdint.h>
+#include <stdlib.h>
 #include <unistd.h>
 #include <signal.h>
 #include <math.h>
@@ -38,9 +39,6 @@
 #define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
 #define MOVING_AVG_SIZE 2 // Size of the moving average window
 
-#define MOTOR_LEFT 1
-#define MOTOR_RIGHT 2
-
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
 {
@@ -59,12 +57,10 @@ static void __on_pause_press(void)
 int getMeasurement(struct XBeeArray_Settings array, unsigned int curStep, unsigned char* strengths, unsigned char* distance_strengths, int* directional_strengths);
 double getDistance(unsigned char* distance_strengths, int num_strengths);
 int getAngle(int* directional_strengths, int num_strengths);
-int set_robot_speeds(double v, double omega);
-double avg_dbl(double* array, int size);
-double avg_int(int* array, int size);
-double absVal(double x);
-double wrapToPi(double theta);
-double wrapTo180(double theta);
+
+// Global control parameters
+const double Kp = 1; // Linear speed proportional gain
+const double Kw = 4; // Angular speed proportional gain
 
 int main(){
     printf("\tStarting Main Program...\n");
@@ -112,12 +108,8 @@ int main(){
     int position = 0; // Angular position of reflector array (degrees)
     int direction = 1; // Direction of stepper motor
     unsigned int curStep = 0; // Current step number
-    struct XBeeArray_Settings array = {
-        5,1,   // Uart buses Top(5) and Side(1) 
-        3,1,   // GPIO 0 (Chip 3 Pin 1)
-        3,2,   // GPIO 1 (Chip 3 Pin 2)
-        0x1111 // Target Remote XBee's 16-bit address
-    };
+
+    Robot_t robot;
 
     // Initalize storage variables
     int result;
@@ -136,32 +128,18 @@ int main(){
     double omega = 0; // Desired angular velocity
     double theta = 0; // Angle (in rad) of robot with respect to where it was when the last target point was computed
 
-    // Initalize XBee Reflector Array
-    printf("\tInitializing XBee Reflector Array...\n");
-    result = XBeeArray_Init(array);
[…]

### 2021-03-29 code/Lib/XBeeArray.h
Updated MainProgram.c and some libraries

@@ -20,48 +20,48 @@
     #define DEBUG_ASSERT(condition,ftext...) ASSERT(condition,ftext)
 #endif
 
-struct XBeeArray_Settings {
-	int top_uart_bus, side_uart_bus;
-	int io_chip_0, io_pin_0;
-	int io_chip_1, io_pin_1;
+typedef struct {
+    int top_uart_bus, side_uart_bus;
+    int io_chip_0, io_pin_0;
+    int io_chip_1, io_pin_1;
     uint16_t remoteAddr;
-};
+} XBeeArray_Settings;
 
-int XBeeArray_Init(struct XBeeArray_Settings array);
-int XBeeArray_Close(struct XBeeArray_Settings array);
-int XBeeArray_GetStrengths(struct XBeeArray_Settings array, unsigned char strengths[5]);
+int XBeeArray_Init(XBeeArray_Settings* array);
+int XBeeArray_Close(XBeeArray_Settings* array);
+int XBeeArray_GetStrengths(XBeeArray_Settings* array, unsigned char strengths[5]);
 
-int XBeeArray_Init(struct XBeeArray_Settings array) {
+int XBeeArray_Init(XBeeArray_Settings* array) {
     int result;
 
     // Initalize UART busses
-    result = XBee_InitUART(array.top_uart_bus);
-    DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize top UART on bus %d\n", array.top_uart_bus);
-    XBee_InitUART(array.side_uart_bus);
-    DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize side UART on bus %d\n", array.side_uart_bus);
+    result = XBee_InitUART(array->top_uart_bus);
+    DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize top UART on bus %d\n", array->top_uart_bus);
+    XBee_InitUART(array->side_uart_bus);
+    DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize side UART on bus %d\n", array->side_uart_bus);
 
     // Initalize GPIO pins
-	result = rc_gpio_init(array.io_chip_0, array.io_pin_0, GPIOHANDLE_REQUEST_OUTPUT);
[…]

### 2021-03-29 code/Lib/odometry.h

@@ -15,7 +15,7 @@ double odometry_getAngle(double R, double L);
 double odometry_getDistance(double R);
 int odometry_setZeroRef();
 
-// Estimates the rotation angle of the robot relative to the last time the zero reference was set
+// Estimates the rotation angle (in degrees) of the robot relative to the last time the zero reference was set
 // @param R: Radius of the wheels
 // @param L: Distance between wheels
 double odometry_getAngle(double R, double L)

### 2021-03-29 code/Lib/robot.h

@@ -40,7 +40,7 @@ typedef struct
     int right_motor;
 
     // Array of XBees
-    struct XBeeArray_Settings array;
+    XBeeArray_Settings array;
 
     // Stepper motor
     StepperMotor sm;
@@ -59,10 +59,10 @@ int robot_init(Robot_t* robot)
     robot->L = 0.21668;
     robot->R = 0.0492125;
     robot->vMax = 0.12;
-    robot->omegaMax = M_PI/6;
+    robot->omegaMax = M_PI/4;
     robot->left_motor = 1;
     robot->right_motor = 2;
-    robot->array = {
+    robot->array = (XBeeArray_Settings){
         5,1,   // Uart buses Top(5) and Side(1) 
         3,1,   // GPIO 0 (Chip 3 Pin 1)
         3,2,   // GPIO 1 (Chip 3 Pin 2)
@@ -71,7 +71,7 @@ int robot_init(Robot_t* robot)
 
     // Initalize XBee Reflector Array
     printf("\tInitializing XBee Reflector Array...\n");
-    ASSERT(XBeeArray_Init(robot->array) == 0, "\tERROR: Failed to Initialize XBee Array.\n");
+    ASSERT(XBeeArray_Init(&(robot->array)) == 0, "\tERROR: Failed to Initialize XBee Array.\n");
 
     // Initialize Stepper Motor
     printf("\tInitializing Stepper Motor...\n");
@@ -94,7 +94,7 @@ int robot_close(Robot_t* robot)
 {
     // Close XBee Reflector Array
     printf("\tClosing XBee Reflector Array...\n");
-    MAIN_ASSERT(XBeeArray_Close(robot->array) == 0, "\tERROR: Failed to close XBee Array.\n");
+    MAIN_ASSERT(XBeeArray_Close(&(robot->array)) == 0, "\tERROR: Failed to close XBee Array.\n");
 
     // Close the stepper motor
     printf("\tClosing Stepper Motor...\n");

### 2021-03-29 code/MainProgram/MainProgram.c

@@ -42,25 +42,26 @@
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
 {
-        rc_set_state(EXITING);
-        return;
+    rc_set_state(EXITING);
+    return;
 }
 
 // Function to stop program on pause press
 static void __on_pause_press(void)
 {
-        rc_set_state(EXITING);
-        return;
+    rc_set_state(EXITING);
+    return;
 }
 
 // Local functions
-int getMeasurement(struct XBeeArray_Settings array, unsigned int curStep, unsigned char* strengths, unsigned char* distance_strengths, int* directional_strengths);
+int getMeasurement(XBeeArray_Settings* array, unsigned int curStep, unsigned char* strengths, unsigned char* distance_strengths, int* directional_strengths);
 double getDistance(unsigned char* distance_strengths, int num_strengths);
 int getAngle(int* directional_strengths, int num_strengths);
 
 // Global control parameters
 const double Kp = 1; // Linear speed proportional gain
 const double Kw = 4; // Angular speed proportional gain
+const int maxTargetAngle = 30; // Maximum angle change for a single measurement
 
 int main(){
     printf("\tStarting Main Program...\n");
@@ -126,14 +127,14 @@ int main(){
     // double targetY = 0; // Estimated Y coordinate of remote w.r.t. robot's local frame
     double v = 0; // Desired linear velocity
     double omega = 0; // Desired angular velocity
-    double theta = 0; // Angle (in rad) of robot with respect to where it was when the last target point was computed
+    double theta = 0; // Angle (in degrees) of robot with respect to where it was when the last target point was computed
 
     // Initialize Robot
     printf("\tInitializing Robot...\n");
     robot_init(&robot);
 
     // Fill out the measurement arrays
-    result = getMeasurement(robot.array, curStep, strengths, distance_strengths, directional_strengths);
+    result = getMeasurement(&(robot.array), curStep, strengths, distance_strengths, directional_strengths);
     MAIN_ASSERT(result == 0, "\tERROR: Failed to get measurement.\n");
     int num_sweeps = 0;
     while (num_sweeps < MOVING_AVG_SIZE)
@@ -151,8 +152,8 @@ int main(){
         if ((position >= (90 - DEG_PER_MEASUREMENT)) || (position <= 0))
         {
             // Calculate the distance to the remote
[…]

### 2021-03-30 code/Lib/XBeeArray.h
Fixed things to be able to compile MainProgram

@@ -42,10 +42,10 @@ int xbeeArray_Init(xbeeArray_settings* array) {
     XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize side UART on bus %d\n", (*array).side_uart_bus);
 
     // Initalize GPIO pins
-	result = rc_gpio_init((*array).io_chip_0, (*array).io_pin_0, GPIOHANDLE_REQUEST_OUTPUT);
-	XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", (*array).io_chip_0, (*array).io_pin_0);
+    result = rc_gpio_init((*array).io_chip_0, (*array).io_pin_0, GPIOHANDLE_REQUEST_OUTPUT);
+    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", (*array).io_chip_0, (*array).io_pin_0);
     result = rc_gpio_init((*array).io_chip_1, (*array).io_pin_1, GPIOHANDLE_REQUEST_OUTPUT);
-	XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", (*array).io_chip_1, (*array).io_pin_1);
+    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", (*array).io_chip_1, (*array).io_pin_1);
 
     return 0;
 }
@@ -94,9 +94,9 @@ int xbeeArray_GetStrengths(xbeeArray_settings* array, ubyte strengths[5]){
     for(int i=0; i<4; i++) {
         // Set Multiplexer chanel to 'i'
         result = rc_gpio_set_value((*array).io_chip_0, (*array).io_pin_0, (i)&1);
-		XBEE_ARRAY_DEBUG_ASSERT(result != -1, "\t[DEBUG] ERROR: Failed to set pin value for GPIO %d_%d.\n", (*array).io_chip_0, (*array).io_pin_0);
+        XBEE_ARRAY_DEBUG_ASSERT(result != -1, "\t[DEBUG] ERROR: Failed to set pin value for GPIO %d_%d.\n", (*array).io_chip_0, (*array).io_pin_0);
[…]

### 2021-03-30 code/Lib/core.h

@@ -19,9 +19,9 @@
 
 // Define Main Assert statement
 #ifndef CORE_MAIN_ASSERT_LAMBDA
-	#define CORE_MAIN_ASSERT_LAMBDA
+    #define CORE_MAIN_ASSERT_LAMBDA
 #endif
-#define MAIN_ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); CORE_MAIN_ASSERT_LAMBDA; return -1;}
+#define MAIN_ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); rc_set_state(EXITING);;}
 #undef CORE_MAIN_ASSERT_LAMBDA
 
 // Array size statement
@@ -47,8 +47,8 @@ void msleep(int milliSeconds) { usleep((milliSeconds)*1000); }
 // @param buf: Pointer to array of bytes to print out
 // @param bufSize: sice of given buffer 'buf' in bytes
 void printHexBuffer(void* buf, int bufSize){
-	for(int i=0; i<bufSize; i++)
-		printf("%02X ", ((ubyte*)buf)[i]);
+    for(int i=0; i<bufSize; i++)
+        printf("%02X ", ((ubyte*)buf)[i]);
 }
 
 // Print out byte array in hexidecimal with endcaps
@@ -57,10 +57,10 @@ void printHexBuffer(void* buf, int bufSize){
 // @param header: Formated string to print out before the buffer
 // @param footer: Formated string to print out affter the buffer
 void fprintHexBuffer(void* buf, int bufSize, char* header, char* footer){
-	printf(header);
-	for(int i=0; i<bufSize; i++)
-		printf("%02X ", ((ubyte*)buf)[i]);
-	printf(footer);
+    printf(header);
+    for(int i=0; i<bufSize; i++)
+        printf("%02X ", ((ubyte*)buf)[i]);
+    printf(footer);
 }
 
 #endif

### 2021-03-30 code/Lib/odometry.h

@@ -4,7 +4,6 @@
 #include <rc/encoder_eqep.h>
 
 #include "core.h"
-#include "../constants/robotSettings.h"
 
 // Encoder defines
 #define ODOMETRY_ENCODER_LEFT 1
@@ -15,7 +14,6 @@ double odometry_GetAngle();
 double odometry_GetDistance();
 int odometry_SetZeroRef();
 
-double odometry_GetAngle()
 // @param R: Radius of the wheels
 // @param L: Distance between wheels
 double odometry_getAngle(double R, double L)
@@ -28,7 +26,6 @@ double odometry_getAngle(double R, double L)
     return theta;
 }
 
-double odometry_GetDistance()
 // @param R: Radius of the wheels
 double odometry_getDistance(double R)
 {

### 2021-03-30 code/Lib/robot.h

@@ -1,30 +1,14 @@
 #ifndef ROBOT_H
 #define ROBOT_H
 
-// C Library headers
-// #include <stdio.h>
-// #include <string.h>
-// #include <stdbool.h>
-// #include <stdint.h>
-// #include <stdlib.h>
-// #include <unistd.h>
-// #include <signal.h>
-// #include <math.h>
-
 // Robot Control Library headers
-// #include <rc/uart.h>
-// #include <rc/gpio.h>
 #include <rc/motor.h>
 #include <rc/encoder_eqep.h>
-// #include <rc/button.h>
 
 // Custom headers
-#include "CoreLib.h"
-// #include "ATCom.h"
-#include "XBeeArray.h"
-#include "step.h"
-// #include "extraMath.h"
-// #include "odometry.h"
+#include "core.h"
+#include "xbeeArray.h"
+#include "stepMotor.h"
 
 typedef struct
 {
@@ -40,10 +24,10 @@ typedef struct
     int right_motor;
 
     // Array of XBees
-    XBeeArray_Settings array;
+    xbeeArray_settings array;
 
     // Stepper motor
-    StepperMotor sm;
+    stepMotor_motor sm;
 
 } Robot_t;
 
@@ -62,7 +46,7 @@ int robot_init(Robot_t* robot)
     robot->omegaMax = M_PI/4;
     robot->left_motor = 1;
     robot->right_motor = 2;
-    robot->array = (XBeeArray_Settings){
+    robot->array = (xbeeArray_settings){
         5,1,   // Uart buses Top(5) and Side(1) 
         3,1,   // GPIO 0 (Chip 3 Pin 1)
         3,2,   // GPIO 1 (Chip 3 Pin 2)
@@ -71,11 +55,11 @@ int robot_init(Robot_t* robot)
 
     // Initalize XBee Reflector Array
     printf("\tInitializing XBee Reflector Array...\n");
-    ASSERT(XBeeArray_Init(&(robot->array)) == 0, "\tERROR: Failed to Initialize XBee Array.\n");
+    ASSERT(xbeeArray_Init(&(robot->array)) == 0, "\tERROR: Failed to Initialize XBee Array.\n");
 
     // Initialize Stepper Motor
     printf("\tInitializing Stepper Motor...\n");
-    ASSERT(stepper_init(&(robot->sm), 3, 4) != -1, "\tERROR: Failed to initialize Stepper Motor.\n");
[…]

### 2021-03-30 code/Lib/stepMotor.h

@@ -8,7 +8,7 @@
 // Number of degrees per step on the stepper motor
 #define STEP_MOTOR_DEG_PER_STEP 1.8
 
-typedef struct stepMotor_motor
+typedef struct
 {
     // Motor driver ports used for the stepper motor
     int m1;

### 2021-03-30 code/MainProgram/MainProgram.c

@@ -27,10 +27,10 @@
 
 // Custom headers
 #include "core.h"
-#include "../constants/robotSettings.h"
+#include "robot.h"
 #include "atCom.h"
 #include "xbeeArray.h"
-#include "setpMotor.h"
+#include "stepMotor.h"
 #include "extraMath.h"
 #include "odometry.h"
 
@@ -62,12 +62,6 @@ int getAngle(int* directional_strengths, int num_strengths);
 const double Kp = 1; // Linear speed proportional gain
 const double Kw = 4; // Angular speed proportional gain
 const int maxTargetAngle = 30; // Maximum angle change for a single measurement
-
-// Global Constants
-const double Kp = 1; // Linear speed proportional gain
-const double Kw = 4; // Angular speed proportional gain
-const double vMax = 0.12; // Maximum linear speed [m/s]
-const double omegaMax = M_PI/6; // Maximum angular speed [rad/s]
 
 int main(){
     printf("\tStarting Main Program...\n");
@@ -146,7 +140,7 @@ int main(){
     while (num_sweeps < MOVING_AVG_SIZE)
     {
         // Move the stepper motor
-        step(&robot.sm, direction, STEPS_PER_MEASUREMENT);
+        stepMotor_Step(&robot.sm, direction, STEPS_PER_MEASUREMENT);
 
         // Update current step number
         curStep += direction;
@@ -183,7 +177,7 @@ int main(){
     while(rc_get_state() != EXITING)
     {
         // Move the stepper motor
-        step(&robot.sm, direction, STEPS_PER_MEASUREMENT);
+        stepMotor_Step(&robot.sm, direction, STEPS_PER_MEASUREMENT);
 
         // Update current step number
         curStep += direction;

### 2021-03-30 code/Lib/XBeeArray.h
Changed pointer to struct member access to arrow notation

@@ -36,16 +36,16 @@ int xbeeArray_Init(xbeeArray_settings* array) {
     int result;
 
     // Initalize UART busses
-    result = xbeeCom_InitUART((*array).top_uart_bus);
-    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize top UART on bus %d\n", (*array).top_uart_bus);
-    xbeeCom_InitUART((*array).side_uart_bus);
-    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize side UART on bus %d\n", (*array).side_uart_bus);
+    result = xbeeCom_InitUART(array->top_uart_bus);
+    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize top UART on bus %d\n", array->top_uart_bus);
+    xbeeCom_InitUART(array->side_uart_bus);
+    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize side UART on bus %d\n", array->side_uart_bus);
 
     // Initalize GPIO pins
-    result = rc_gpio_init((*array).io_chip_0, (*array).io_pin_0, GPIOHANDLE_REQUEST_OUTPUT);
-    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", (*array).io_chip_0, (*array).io_pin_0);
-    result = rc_gpio_init((*array).io_chip_1, (*array).io_pin_1, GPIOHANDLE_REQUEST_OUTPUT);
-    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", (*array).io_chip_1, (*array).io_pin_1);
+    result = rc_gpio_init(array->io_chip_0, array->io_pin_0, GPIOHANDLE_REQUEST_OUTPUT);
+    XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize output gpio %d_%d.\n", array->io_chip_0, array->io_pin_0);
+    result = rc_gpio_init(array->io_chip_1, array->io_pin_1, GPIOHANDLE_REQUEST_OUTPUT);
[…]

### 2021-03-30 code/Tests/AngleTest/Angle_Test.c
Fixed stepMotor includes

@@ -16,7 +16,7 @@
 #define DEBUG_XBEECOM 0
 #define XBEE_ARRAY_DEBUG 1
 #include "xbeeArray.h"
-#include "setpMotor.h"
+#include "stepMotor.h"
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy) {

### 2021-03-30 code/Tests/Array_Recorder/Array_Recorder.c

@@ -16,7 +16,7 @@
 #define DEBUG_XBEECOM 0
 #define XBEE_ARRAY_DEBUG 1
 #include "xbeeArray.h"
-#include "setpMotor.h"
+#include "stepMotor.h"
 
 #define STEPS_PER_MEASUREMENT 5
 #define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*STEP_MOTOR_DEG_PER_STEP)

### 2021-03-30 code/Tests/Loc_Testing/Loc_Test.c

@@ -23,7 +23,7 @@
 #include "core.h"
 #include "atCom.h"
 #include "xbeeArray.h"
-#include "setpMotor.h"
+#include "stepMotor.h"
 
 #define STEPS_PER_MEASUREMENT 5
 #define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*STEP_MOTOR_DEG_PER_STEP)

### 2021-03-30 code/Tests/LockedNav_Testing/LockedNav_Test.c

@@ -24,7 +24,7 @@ void emergencyStop();
 #include "core.h"
 #include "extraMath.h"
 #include "xbeeArray.h"
-#include "setpMotor.h"
+#include "stepMotor.h"
 
 // Set up Data Storage Structes
 #define DATA_BUFFER_SIZE 5

### 2021-03-30 code/Tests/stepTest/stepTest.c

@@ -7,7 +7,7 @@
 #include <rc/motor.h>
 #include <rc/time.h>
 #include <rc/start_stop.h>
-#include "../../lib/setpMotor.h" // Stepper motor library
+#include "../../lib/stepMotor.h" // Stepper motor library
 
 // Number of degrees per step on the stepper motor
 #define STEP_MOTOR_DEG_PER_STEP 1.8

### 2021-03-30 code/Lib/extraMath.h
More fixes

@@ -84,7 +84,7 @@ EXTRA_MATH_FUNC_HEAD double max(double x1, double x2) {
     return (x1 > x2) ? x1 : x2;
 }
 
-// Clamp a ingeger value to a range
+// Clamp an integer value to a range
 // @param x: Value to clamp
 // @param min: Minimum value of range
 // @param max: Maximum value of range
@@ -128,30 +128,14 @@ EXTRA_MATH_FUNC_HEAD double avg(double* array, int size) {
 // @param theta: Angle to wrap (in radians)
 EXTRA_MATH_FUNC_HEAD double wrapToPi(double theta)
 {
-    while(theta > M_PI)
-    {
-        theta -= 2*M_PI;
-    }
-    while(theta < -M_PI)
-    {
-        theta += 2*M_PI;
-    }
-    return theta;
+    return mod(theta, M_PI);
 }
 
 // Wraps theta between -180 and 180
 // @param theta: Angle to wrap (in degrees)
 EXTRA_MATH_FUNC_HEAD double wrapTo180(double theta)
 {
-    while(theta > 180)
-    {
-        theta -= 360;
-    }
-    while(theta < -180)
-    {
-        theta += 360;
-    }
-    return theta;
+    return mod(theta, 180.0);
 }
 
 #undef EXTRA_MATH_FUNC_HEAD

### 2021-03-30 code/Lib/odometry.h

@@ -16,7 +16,7 @@ int odometry_SetZeroRef();
 
 // @param R: Radius of the wheels
 // @param L: Distance between wheels
-double odometry_getAngle(double R, double L)
+double odometry_GetAngle(double R, double L)
 {
     int leftEncVal = -rc_encoder_eqep_read(ODOMETRY_ENCODER_LEFT);
     int rightEncVal = rc_encoder_eqep_read(ODOMETRY_ENCODER_RIGHT);
@@ -27,7 +27,7 @@ double odometry_getAngle(double R, double L)
 }
 
 // @param R: Radius of the wheels
-double odometry_getDistance(double R)
+double odometry_GetDistance(double R)
 {
     int leftEncVal = -rc_encoder_eqep_read(ODOMETRY_ENCODER_LEFT);
     int rightEncVal = rc_encoder_eqep_read(ODOMETRY_ENCODER_RIGHT);

### 2021-03-30 code/Lib/robot.h

@@ -40,7 +40,7 @@ int robot_setSpeeds(Robot_t* robot, double v, double omega);
 int robot_init(Robot_t* robot)
 {
     // Assign robot variables
-    robot->L = 0.21668;
+    robot->L = 0.202406;
     robot->R = 0.0492125;
     robot->vMax = 0.12;
     robot->omegaMax = M_PI/4;

### 2021-03-30 code/MainProgram/MainProgram.c

@@ -227,7 +227,7 @@ int main(){
             while (abs(theta - targetAngle) > 2 && rc_get_state() != EXITING)
             {
                 // Determine the angle of the robot relative to where it was when the last measurement was completed
-                theta = odometry_getAngle(robot.R, robot.L);
+                theta = odometry_GetAngle(robot.R, robot.L);
                 // printf("Target angle: %f\n Robot angle: %f\n", targetAngle, theta);
             }
 #endif

### 2021-03-30 code/Tests/EncoderAngle_Testing/EncoderAngleTest.c

@@ -10,7 +10,9 @@
 #include "extraMath.h"
 #include "core.h"
 #include "odometry.h"
-#include "../constants/robotSettings.h"
+
+double L = 0.202406;
+double R = 0.0492125;
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
@@ -22,7 +24,7 @@ static void __signal_handler(__attribute__ ((unused)) int dummy)
 // Function to print angle on pause press
 static void __on_pause_press(void)
 {
-    double angle = odometry_GetAngle();
+    double angle = odometry_GetAngle(R, L);
     printf("Angle: %f degrees\n", angle);
     return;
 }

### 2021-03-30 code/Tests/EncoderDistance_Testing/EncoderDistanceTest.c

@@ -10,7 +10,9 @@
 #include "extraMath.h"
 #include "core.h"
 #include "odometry.h"
-#include "../constants/robotSettings.h"
+
+// double L = 0.202406;
+double R = 0.0492125;
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
@@ -22,7 +24,7 @@ static void __signal_handler(__attribute__ ((unused)) int dummy)
 // Function to print distance on pause press
 static void __on_pause_press(void)
 {
-    double distance = odometry_GetDistance();
+    double distance = odometry_GetDistance(R);
     printf("Distance: %f [m]\n", distance);
     return;
 }

### 2021-03-30 code/Tests/Loc_Testing/Loc_Test.c

@@ -7,6 +7,7 @@
 #include <string.h>
 #include <stdbool.h>
 #include <stdint.h>
+#include <stdlib.h>
 #include <unistd.h>
 #include <signal.h>
 #include <math.h>

### 2021-03-30 code/Tests/LockedNav_Testing/LockedNav_Test.c

@@ -53,9 +53,6 @@ double updateDistance(DistanceData* dData);
 double updateAngle(AngleData* aData);
 int setWheelVelocitys(double v, double w);
 
-static inline double wrapToPi(double theta) { return mod(theta, M_PI); }
-static inline double wrapTo180(double theta) { return mod(theta, 180.0); }
-
 int main() {
     printf("\tStarting Locked Navigation Test...\n");
 

### 2021-04-01 code/Tests/Array_Recorder/Array_Recorder.c
Assorted modifications

@@ -29,9 +29,10 @@ static void __signal_handler(__attribute__ ((unused)) int dummy) {
 }
 
 // Prototypes
-int ProcessArguments(int argc, char* argv[], double* angle, double* distance, double* height, bool* useSweep);
+int ProcessArguments(int argc, char* argv[], double* angle, double* distance, double* height, bool* useSweep, int* numScans);
 int AddRecored(FILE* fp, xbeeArray_settings* arrayP, double angle, double distance, double height);
 int StripFloat(char* str, float* value);
+int StripInt(char* str, int* value);
 
 // Main
 int main(int argc, char* argv[]){
@@ -49,6 +50,7 @@ int main(int argc, char* argv[]){
 	double init_angle = 0; //atof(argv[1]);
 	double init_distance = 1; //atof(argv[2]);
 	double init_height = 0;
+	int numScans = 100;
 	xbeeArray_settings array = {
 		5,1,   // Uart buses Top(1) and Side(5) 
 		3,1,  // GPIO 0 (Chip 1 Pin 25)
@@ -62,7 +64,7 @@ int main(int argc, char* argv[]){
 	FILE* fp;
 
 	// Read in peramiters
-	result = ProcessArguments(argc, argv, &init_angle, &init_distance, &init_height, &useSweep);
+	result = ProcessArguments(argc, argv, &init_angle, &init_distance, &init_height, &useSweep, &numScans);
 	MAIN_ASSERT(result != -1, "\tERROR: Failed to Read in Arguments.\n");
 
 	// Initalize XBee Reflector Array
@@ -85,14 +87,15 @@ int main(int argc, char* argv[]){
 		int segment = 0;
 		int direction = 1;
 		float angleOffset = 0;
-		while(rc_get_state() != EXITING && segment < (NUM_MEASUREMENTS*2)) {
+		while(rc_get_state() != EXITING && segment < (NUM_MEASUREMENTS*2)-2) {
 			// Add recored
+			msleap(300);
 			double curAngle = fmod((init_angle + (double)angleOffset), 360.0);
-			result = AddRecored(fp, &array, curAngle, init_distance, init_height);
+			result = AddRecored(fp, &array, curAngle, init_distance, init_height, numScans);
 			MAIN_ASSERT(result != -1, " ");
 
 			// Move the stepper motor
-			direction = (segment < NUM_MEASUREMENTS) ? 1: -1;
[…]

### 2021-04-06 parts/03-acknowledgements.tex
Updated acknowledgements page

@@
 
-    \par Special Thanks to Andrew Fandel, Anthony Birge, and Dr. Suruz Miah for their work with Machine Learning on a 2-DOF Helicopter.
-    \par Thanks to Mr. Christopher Mattus for his assistance in setting up our lab environment.
-    \par Thank you to everyone else who helped make this project possible and sucessful.
+    \par Special thanks to Mr. Christopher Mattus for his assistance in procuring the parts and modifying the hardware for our project.
+    \par Thank you to everyone else who helped make this project possible and successful.
 

### 2021-04-06 parts/60-conclusion_and_future_work.tex
Create 60-conclusion_and_future_work.tex

--- 2020-09-21 parts/10-introduction.tex
@@
 %======================================================================
-\chapter{Introduction}
-\label{ch: Chapter1}
+\chapter{Conclusion and Future Work}
+\label{ch: Chapter6}
 %======================================================================
@@
 %----------------------------------------------------------------------
-\section{Problem Statement}
+\section{Conclusion}
 %----------------------------------------------------------------------
@@
 %----------------------------------------------------------------------
-\section{Literature Review}
+\section{Future Work}
 %----------------------------------------------------------------------
@@
 
-%----------------------------------------------------------------------
-\section{Report Organization}
-%----------------------------------------------------------------------
-This report is organised into 6 chapters.
-Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.
-Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.
-Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.
-Chapter \ref{ch: Chapter4} contains the results from our simulations.
-Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.
-Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.
-
 %%% Local Variables:

### 2021-04-06 parts/02-abstract.tex

@@
 
-%This paper proposes a strategy for testing and comparing three control algorithms, LQR, LQG, and ADP, to control two two-DOF helicopters from a mobile device.
-We will be using Raspberry Pi 3's as terminals for the wireless communication and MATLAB as our primary coding language.
-
-This project proposes a modular and cost-effective smart real-time motion control
-framework for a group of two degrees of freedom (2-DOF) helicopters.  The helicopters are
-controlled by a mobile device which sends position signals over a wireless network to a
-microcontroller.  The microcontroller uses control algorithms to determine the amount of voltage
-to apply to DC motors.  This project tests and compares three control algorithms, LQR, LQG, and
-ADP as well as theorizes possible methods to improve the control in future projects.
+Robotic carts are of paramount importance for customers with disabilities in grocery stores.
+Although there are numerous robotic carts currently available, many times the hardware to implement the robot is quite costly.
+This project aims to develop a prototype of a smart robotic cart using radio frequency (RF) signals.
+The proposed robotic cart is cost-effective since it simply utilizes analog signal strengths to locate and follow the customer.
+An array of RF modules is mounted on top of the robotic cart, and a remote RF module is held by the customer.
+The direction and the line-of-sight (LoS) distance of the remote are estimated based on signal strengths received by the RF modules on the robot.
+The robot uses that direction and LoS distance to compute actuator commands for the robotic cart to follow the remote.
+The robot was first simulated using CoppeliaSim, a commercial robot simulator.
+A prototype was then built and used to evaluate the performance of the robot.
 

### 2021-04-06 parts/10-introduction.tex
Update 10-introduction.tex

@@
 %----------------------------------------------------------------------
-Helicopters are of a paramount importance as
-they are used in many civilian and military applications due to their ability for vertical take-off and landing.
-To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics.
-Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions.
-Such methods are expensive and time-consuming to develop.
-Implementation of motion control techniques using cost-effective hardware is still a challenge.
-
-In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position.
-Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices.
-This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.
+Robotic carts are a prevalent invention designed to aid users in a number of important indoor and outdoor tasks.
+There are robotic systems currently available in the market that perform these tasks in a variety of ways.
+For example, in a grocery store, a customer may require the need of more than one cart but cannot push or pull two carts simultaneously.
+One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items.
+Moreover, robots used for this purpose are more costly than they are worth.
+In this project, we are proposing a robotic cart that would primarily use analog signals with the use of cost-effective wireless communication to identify the customer and be able to track and follow the customer through the store.
+The implementation of such a fully functional robotic cart will outreach the scope of the project but is the overall goal for this project in the coming years while encouraging further research in this field.
+Applications of the proposed robotic cart include, but are not limited to, delivery carts to follow mail personnel and carry the deliveries, file transfer carts in offices, hospital carts to aid nurses and doctors by carrying medicine or surgery supplies, and carts in construction sites to carry tools and other supplies across the job site.
 
@@
 %----------------------------------------------------------------------
-Our project requires a great deal of research as some of our tasks have not been attempted before.
-As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.
+Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores.
+See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example.
+Currently, the work being done focuses on a few different methods of having a robotic cart interface with the customer and follow them through the store.
 
-Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices.
-In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}.
-A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters.
-See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein.
-Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.
+\vspace*{12pt}
+\noindent
+One such method that has been utilized to make a cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}.
+Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow them through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
+Therein, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.
 
-The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.
-This involves creating a linearized system model to calculate the LQR state-feedback gain.
-A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.
-SMC is a nonlinear control technique to drive the system states onto a surface in the state space.
-This method has been used  by~\cite{Ahmed2010-Sliding}.
-Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.
-The ADP technique does not rely on knowledge of the system model.
-Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.
-Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.
+\vspace*{12pt}
+\noindent
+In the current project, we are implementing XBee S2C RF radios, which are inexpensive and easily configurable, as a remote target device that is carried by the user.
+The robot will be able to track this remote instead of using line of sight methods~\cite{Miah2018-Intelligent}.
+In addition to the XBee S2C RF radios, we will equip the robot with a parabolic reflector, which improves Wi-Fi reception at various distances and angles, \textit{i.e.,} angle of arrivals of RF signals from the remote, based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent}~\cite{Li2013ANA}.
 
-As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms.
-This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms.
-Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.
+\vspace*{12pt}
+\noindent
+The approach using signal strength of RF signals also requires an understanding of multipath interference which is common in Wi-Fi based wireless positioning sensing systems.
+Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using course estimation calculations such as received signal strength indicator (RSSI) and time difference of arrival (TDoA) is key to compensate for the multipath interference in received signals.
+The work in ~\cite{ladd_bekris_rudys_kavraki_wallach_2005} shows a different approach to the multipath issue by using an IEEE 802.11b wireless ethernet device to measure RF signals.
+This device system was used because it is communicable between a mobile device and a localization based service with low complexity for the user.
+Also, in~\cite{lindhe_johansson_bicchi_2007}, the research states several other ways to counteract the multipath fading with methods such as antenna diversity, frequency spreading, or adaptive antenna arrays.
+The method used in this paper was to sample the radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position in an indoor environment.
+Lastly, in~\cite{Lindhe2009} the method that is utilized exploits multipath fading by measuring the signal-to-noise ratio (SNR) and adjusting the robot's motion to spend more time where the channel strength is greater.
+
+\vspace*{12pt}
+\noindent
+All of the solutions that were found required direct line-of-sight between the robot and the user.
+In this project we aim to use the XBee S2C RF radios and a parabolic reflector combined into a rotating system similar to the one presented in~\cite{Miah2018-Intelligent} in order to have the robot track the customer through a store without using line-of-sight sensing.
+The major challenge of this implementation will be estimating the distance between the robot and the remote in varying environments.
 
@@
 %----------------------------------------------------------------------
-This report is organised into 6 chapters.
-Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.
-Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.
-Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.
-Chapter \ref{ch: Chapter4} contains the results from our simulations.
-Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.
-Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.
+This report is organised into the following 6 chapters:
+
+\begin{itemize}
+	\item Chapter \ref{ch: Chapter1} discusses the background and goals of our project and what other similar projects have accomplished
+	\item Chapter \ref{ch: Chapter2} explains how our robotic cart system is broken down fundamentally and the system components we used to build the robot
+	\item Chapter \ref{ch: Chapter3} goes over the design of our parabolic reflector arrays and how we set them up on the robot
+	\item Chapter \ref{ch: Chapter4} provides an explanation of the algorithms we used to create the code to make the robot move
+	\item Chapter \ref{ch: Chapter5} discusses the implementation of all the parts onto the robot and our experimental results we got when running the robot
+	\item Chapter \ref{ch: Chapter6} concludes our project work and discusses future endeavors on this project
+\end{itemize}
 

### 2021-04-06 parts/30-customized_parabolic_reflector_array.tex
Create 30-customized_parabolic_reflector_array.tex
Started updating reflector array chapter

--- 2020-09-21 parts/10-introduction.tex
@@
 %======================================================================
-\chapter{Introduction}
-\label{ch: Chapter1}
+\chapter{Customized Reflector Array}
+\label{ch: Chapter3}
 %======================================================================
@@
 %----------------------------------------------------------------------
-\section{Problem Statement}
+\section{Reflector Design}
 %----------------------------------------------------------------------
-Helicopters are of a paramount importance as
-they are used in many civilian and military applications due to their ability for vertical take-off and landing.
-To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics.
-Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions.
-Such methods are expensive and time-consuming to develop.
-Implementation of motion control techniques using cost-effective hardware is still a challenge.
+The XBee RF modules that were used detect signals from any direction.
+For this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming.
+To accomplish this, two different models of reflector arrays were designed and constructed.
 
-In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position.
-Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices.
-This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.
+\subsection{Purely Paraboloidal Reflector}
+The first design, shown in \autoref{fig:paraboloidalReflector}, uses a reflector with a purely paraboloidal shape.
+This shape was selected since all signals entering the reflector parallel to the axis of the reflector will pass through the focus of the paraboloid.
+By mounting the XBee such that the center of the antenna coincides with the focus of the paraboloid, the signal strength of the signals entering parallel to the axis will be maximized.
+\begin{figure}
+    \centering
+    \includegraphics[width=3.5in]{figs/img/paraboloidalReflector.png}
+    \caption{Purely Paraboloidal Reflector Array}
+    \label{fig:paraboloidalReflector}
+\end{figure}
+
+\subsection{Combined Parabolic/Paraboloidal Reflector}
+The second design, shown in \autoref{fig:parabolicReflector}, is the same on the lower half as the first design.
+However, the upper half is simply a surface where the horizontal cross-section is a parabola.
+The purpose for this design is similar to that of the first design, but the parabolic shape on the top will allow stronger detected signal strength of signals coming from above the reflector.
+Since the remote will be held by a person, it will generally be above the robot.
+The parabolic/paraboloidal reflector design is intended to allow better reception of signals from above.
+\begin{figure}
+    \centering
+    \includegraphics[width=3.5in]{figs/img/parabolicReflector.png}
+    \caption{Parabolic/Paraboloidal Reflector Array}
+    \label{fig:parabolicReflector}
+\end{figure}
 
 %----------------------------------------------------------------------
-\section{Literature Review}
+\section{Reflector Construction}
 %----------------------------------------------------------------------
-Our project requires a great deal of research as some of our tasks have not been attempted before.
-As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.
-
-Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices.
-In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}.
-A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters.
-See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein.
-Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.
-
-The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.
-This involves creating a linearized system model to calculate the LQR state-feedback gain.
-A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.
-SMC is a nonlinear control technique to drive the system states onto a surface in the state space.
-This method has been used  by~\cite{Ahmed2010-Sliding}.
-Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.
-The ADP technique does not rely on knowledge of the system model.
-Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.
-Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.
-
-As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms.
-This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms.
-Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.
+The reflector dishes were created using a 3D printer. After printing, the dishes were lined with reflective foil tape
 
 %----------------------------------------------------------------------
-\section{Report Organization}
+\section{Experimental Results}
 %----------------------------------------------------------------------
-This report is organised into 6 chapters.
-Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.
-Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.
-Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.
-Chapter \ref{ch: Chapter4} contains the results from our simulations.
-Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.
-Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.
 

### 2021-04-07 parts/30-customized_parabolic_reflector_array.tex

@@
 %----------------------------------------------------------------------
-The reflector dishes were created using a 3D printer. After printing, the dishes were lined with reflective foil tape
+With the recent advancements in 3D printing technology, it is not difficult to create an object with a parabolic shape.
+In this project, the reflector dishes were created using a 3D printer.
+The reflector array was designed to be modular, where the dishes, top plate, and bottom frame were printed separately.
+After printing, the dishes were lined with foil tape to provide the reflective surface to focus the signals onto the antenna of the XBee.
+A layer of foil tape was also placed on the top plate to provide a ground plane for the XBee.
+The parts were then fastened together using M3 screws and nuts.
 

### 2021-04-07 parts/20-system_architecture.tex
Create 20-system_architecture.tex
Update 20-system_architecture.tex

--- 2020-09-21 parts/10-introduction.tex
@@
 %======================================================================
-\chapter{Introduction}
-\label{ch: Chapter1}
+\chapter{System Architecture}
+\label{ch: Chapter2}
 %======================================================================
@@
 %----------------------------------------------------------------------
-\section{Problem Statement}
+\section{System Block Diagram}
 %----------------------------------------------------------------------
-Helicopters are of a paramount importance as
-they are used in many civilian and military applications due to their ability for vertical take-off and landing.
-To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics.
-Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions.
-Such methods are expensive and time-consuming to develop.
-Implementation of motion control techniques using cost-effective hardware is still a challenge.
+The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target, which is held by the user or customer, as shown in \autoref{fig:sys_block_diag}.
+The proposed smart robotic cart is a wheeled robot that sends and receives radio signals to follow the remote target which acts as the beacon for the robotic cart system.
 
-In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position.
-Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices.
-This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.
+\vspace*{12pt}
+\noindent
+
+The high-level system block diagram of the proposed robotic cart (prototype) is shown in \autoref{fig:sys_block_diag}.
+There are four inputs to the proposed cart system.
+The robotic cart is supplied power through a battery that is mounted in the chassis of the robotic cart.
+There will be an on/off switch to allow the system to be powered down when not in use.
+The motion of the cart is dependent on the motion of the remote.
+A stretch goal for the project are mode selection buttons that allow the user to put the robotic cart system into different operating modes.
+
+\vspace*{12pt}
+\noindent
+
+The main output of the system is the position trajectory of the robotic cart in its environment.
+When the user moves with the remote, the cart is designed to follow the user.
+The other output of the robotic cart system is a status indication in the form of LED lights.
+These lights will be used to notify the user of the status of the robotic cart.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[scale=0.9]{figs/system_block_diagram_2}
+    \caption{System level block diagram detailing inputs and outputs to the
+      mobile cart system.}
+	\label{fig:sys_block_diag}
+\end{figure}
 
 %----------------------------------------------------------------------
-\section{Literature Review}
+\section{Subsystem Block Diagrams}
 %----------------------------------------------------------------------
-Our project requires a great deal of research as some of our tasks have not been attempted before.
-As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.
+The Mobile Cart and the Remote Target subsystems are two separate operations within the robotic cart system that run simultaneously.
+The two subsystems communicate with one another by relaying radio messages between them.
+The first block diagram is of the Remote Target subsystem shown in \autoref{fig:remote_block_diag}.
+Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 7.4 volt Li-Po battery with a voltage regulation circuit since the XBee has a smaller input voltage of 3.3 volts.
 
-Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices.
-In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}.
-A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters.
-See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein.
-Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[scale=0.9]{figs/remote_target_block_diagram}
+  \caption{Remote Target block diagram}
+  \label{fig:remote_block_diag}
+\end{figure}
 
-The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.
-This involves creating a linearized system model to calculate the LQR state-feedback gain.
-A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.
-SMC is a nonlinear control technique to drive the system states onto a surface in the state space.
-This method has been used  by~\cite{Ahmed2010-Sliding}.
-Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.
-The ADP technique does not rely on knowledge of the system model.
-Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.
-Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.
+\vspace*{12pt}
+\noindent
+The Mobile Cart subsystem block diagram is shown in \autoref{fig:mobile_block_diag}.
+The cart requires a power source, which will be a Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue).
+The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart.
+The mode selection buttons for changing the operating mode of the robotic cart is a stretch goal of the project and will be implemented on the cart if we have time.
+The final input to the mobile cart subsystem is the XBee network messages received from the remote target.
 
-As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms.
-This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms.
-Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.
+\vspace*{12pt}
+\noindent
+There are three outputs of the mobile cart subsystem.
+The first is the wheel velocities that move the cart.
+There will also be LEDs to indicate the status of the system to the user.
+Lastly, the cart will send radio messages to the remote target by means of a parabolic array of XBee radio modules.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[scale=0.82]{figs/mobile_cart_block_diagram}
+  \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
+  \label{fig:mobile_block_diag}
+\end{figure}
 
 %----------------------------------------------------------------------
-\section{Report Organization}
+\section{System Components}
 %----------------------------------------------------------------------
-This report is organised into 6 chapters.
-Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.
-Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.
-Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.
-Chapter \ref{ch: Chapter4} contains the results from our simulations.
-Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.
-Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.
+There are several components that are required for the mobile cart system.
+Although some of these parts are available in the Bradley University laboratory, other parts must be purchased.
+The parts that exist in the lab are shown in \autoref{tab:Partslablist}.
+Also, \autoref{tab:Partslist} shows the list of parts that we must purchase.
+The parts lists shown are the parts needed to build two mobile cart systems.
+
+\begin{table}[h!]
+  \centering
+  \begin{tabular}{c|c}
+      \toprule
+      \textbf{Quantity} & \textbf{Parts}\\
+      \toprule
+      2 & Budget Bot Chassis\\
+      4 & 10 uF Ceramic Capacitor\\
+      4 & LM1117 Regulator\\
+      2 & Battery Packs for Budget Bot\\
+      8 & 9V Batteries\\
+      4 & Solderable PCB Boards\\
+      3 & XBee USB Adapter\\
+      \bottomrule
+      %\multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
+      %\bottomrule
+  \end{tabular}
+  \caption{Parts Available in Laboratory}
+  \label{tab:Partslablist}
+\end{table}
+
+\begin{table}[h!]
+  \centering
+  \begin{tabular}{c|c|c}
+    \toprule
+    \textbf{Quantity} & \textbf{Parts} & \textbf{Price}\\
+    \toprule
+    4 & Pololu 37D Metal Gear motor 4751 & \$ 39.95\\
+    12 & XBee S2C Module & \$ 23.10\\
+    10 & XBee Adapter Board & \$ 4.99\\
+    2 & Twotrees 4 Lead Nema 17 Stepper Motor & \$ 9.99\\
+    1 & 4-Pin JST SH Connector - 20 Pack & \$ 7.99\\
+    1 & 6-Pin JST SH Connector - 10 Pack & \$ 9.99\\
+    1 & Aluminum Foil Tape - 2 in x 5 yd & \$ 6.05\\
+    \bottomrule
+    \multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
+    \bottomrule
+  \end{tabular}
+  \caption{Purchased parts for the Robotic Cart Project}
+  \label{tab:Partslist}
+\end{table}
+
+\vspace*{12pt}
+\noindent
+The main components for this project are the Budget Bot Chassis (\autoref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (\autoref{fig:beagleboneBlue}), and the XBee S2C Modules (\autoref{fig:XBeeModule}).
+Another major component is the reflector array that
+will be used to directionalize the RF signals received from the remote target that is with the user.
+
+\begin{figure}
+  \centering
+  \begin{minipage}[t]{0.32\textwidth}
+    \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
+    \captionsetup{width=\textwidth}
+    \caption{Budget Bot Chassis}
+    \label{fig:budgetBotChassis}
+  \end{minipage}%
+  \begin{minipage}[t]{0.32\textwidth}
+    \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
+    \captionsetup{width=\textwidth}
+    \caption{BeagleBone Blue}
+    \label{fig:beagleboneBlue}
+  \end{minipage}
+  \begin{minipage}[t]{0.32\textwidth}
+    \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
+    \captionsetup{width=\textwidth}
+    \caption{XBee S2C Module}
+    \label{fig:XBeeModule}
+  \end{minipage}
+\end{figure}
+
+\vspace*{12pt}
+\noindent
+The reflector array will be mounted on top of the cart where it will be attached with a stepper motor.
+There are two reflector designs that we will be evaluating in this project.
+The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of signals that come into the reflector directly perpendicularly.
+Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array.
+The paraboloidal reflector design may not be able to pick up the signals from the remote as well because of this.
+To solve this problem, we designed a combination parabolic/paraboloidal reflector, as shown in \autoref{fig:parabolicReflector}.
+The lower half of this reflector is paraboloidal in shape to limit the signals coming from below.
+The upper part of the reflector is strictly parabolic.
+This shape focuses the signals in the horizontal plane, but allows signals from above to still be received.
+We plan to construct both of these reflector designs by 3d printing the frames, then lining them with reflective foil tape.
+Both models will then be tested to determine which design works better.
+
+\begin{figure}[h!]
+  \centering
+  \begin{minipage}[t]{0.5\textwidth}
+    \centering
+    \includegraphics[height=2in]{figs/img/paraboloidalReflector}
+    \captionsetup{width=\textwidth, justification=raggedright}
+    \caption{Paraboloidal Reflector Model}
+    \label{fig:parabolodialReflector}
+  \end{minipage}
+  \begin{minipage}[t]{0.4\textwidth}
+    \centering
+    \includegraphics[height=2in]{figs/img/parabolicReflector}
+    \captionsetup{width=\textwidth, justification=raggedright}
+    \caption{Combined Parabolic/Paraboloidal Reflector}
+    \label{fig:parabolicReflector}
+  \end{minipage}
+\end{figure}
+
+\subsection{Operation of Mobile Cart System}
+The Mobile Cart will controlled by a central embedded computer which we are using the BeagleBone Blue for.
+Two DC motors will be used to drive wheels to move the cart.
+Five XBee modules will be used to allow communication with the remote target.
+One of these radio sensors will be mounted on top of the cart to broadcast in all directions.
+The other four sensors will be placed inside parabolic reflectors at right angles to each other.
+This sensor array will be mounted on a stepper motor to allow rotation.
 

### 2021-04-07 parts/40-algorithms.tex
Create 40-algorithms.tex

--- 2020-09-21 parts/10-introduction.tex
@@
 %======================================================================
-\chapter{Introduction}
-\label{ch: Chapter1}
+\chapter{Algorithms}
+\label{ch: Chapter4}
 %======================================================================
@@
 %----------------------------------------------------------------------
-\section{Problem Statement}
+\section{Robot Model}
 %----------------------------------------------------------------------
-Helicopters are of a paramount importance as
-they are used in many civilian and military applications due to their ability for vertical take-off and landing.
-To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics.
-Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions.
-Such methods are expensive and time-consuming to develop.
-Implementation of motion control techniques using cost-effective hardware is still a challenge.
-
-In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position.
-Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices.
-This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.
+The robot used in this project was a differential drive mobile robot.
 
 %----------------------------------------------------------------------
-\section{Literature Review}
+\section{Localization Algorithm}
 %----------------------------------------------------------------------
-Our project requires a great deal of research as some of our tasks have not been attempted before.
-As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.
-
-Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices.
-In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}.
-A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters.
-See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein.
-Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.
-
-The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.
-This involves creating a linearized system model to calculate the LQR state-feedback gain.
-A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.
-SMC is a nonlinear control technique to drive the system states onto a surface in the state space.
-This method has been used  by~\cite{Ahmed2010-Sliding}.
-Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.
-The ADP technique does not rely on knowledge of the system model.
-Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.
-Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.
-
-As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms.
-This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms.
-Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.
+The localization algorithm is used to estimate the position of the remote with respect to the robot's local coordinate system.
 
 %----------------------------------------------------------------------
-\section{Report Organization}
+\section{Navigation Algorithm}
 %----------------------------------------------------------------------
-This report is organised into 6 chapters.
-Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.
-Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.
-Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.
-Chapter \ref{ch: Chapter4} contains the results from our simulations.
-Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.
-Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.
+The navigation algorithm is used to drive the robot toward the remote.
 

### 2021-04-07 parts/20-system_architecture.tex

@@
 The parts that exist in the lab are shown in \autoref{tab:Partslablist}.
-Also, \autoref{tab:Partslist} shows the list of parts that we must purchase.
-The parts lists shown are the parts needed to build two mobile cart systems.
+Also, \autoref{tab:Partslist} shows the list of parts that we purchased.
+The parts compiled in the lists are the required parts needed to build two smart robotic cart systems.
 
@@
 The main components for this project are the Budget Bot Chassis (\autoref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (\autoref{fig:beagleboneBlue}), and the XBee S2C Modules (\autoref{fig:XBeeModule}).
-Another major component is the reflector array that
-will be used to directionalize the RF signals received from the remote target that is with the user.
+Another major component is the reflector array that will be used to directionally receive the RF signals from the remote target that is with the user.
 
@@
 \noindent
-The reflector array will be mounted on top of the cart where it will be attached with a stepper motor.
+The reflector array will be mounted on top of the cart with a stepper motor.
 There are two reflector designs that we will be evaluating in this project.
-The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of signals that come into the reflector directly perpendicularly.
+The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of the signals that come into the reflector perpendicularly.
 Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array.
@@
 This shape focuses the signals in the horizontal plane, but allows signals from above to still be received.
-We plan to construct both of these reflector designs by 3d printing the frames, then lining them with reflective foil tape.
+We plan to construct both of these reflector designs by 3D printing the frames, then lining them with reflective foil tape.
 Both models will then be tested to determine which design works better.
@@
 \subsection{Operation of Mobile Cart System}
-The Mobile Cart will controlled by a central embedded computer which we are using the BeagleBone Blue for.
-Two DC motors will be used to drive wheels to move the cart.
-Five XBee modules will be used to allow communication with the remote target.
+The mobile cart will be controlled by a central embedded computer which is the BeagleBone Blue since it is ideal in robotics control.
+Two DC motors will be used to drive wheels and move the cart.
+Five XBee modules on the cart will be used to allow communication with the remote target.
 One of these radio sensors will be mounted on top of the cart to broadcast in all directions.

### 2021-04-08 code/Lib/core.h
Archiving latest version of Array_Recorder

@@ -14,8 +14,12 @@
 /// ----- Defenitions----- ///
 
 // Define Assert statement
-#define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
 #define ASSERT_NOMSG(condition) if(!(condition)){return -1;}
+#ifndef CORE_DISABLE_MESSAGES
+    #define ASSERT(condition,failTxt...) if(!(condition)){ printf(failTxt); return -1;}
+#else
+    #define ASSERT(condition,failTxt...) ASSERT_NOMSG(condition)
+#endif
 
 // Define Main Assert statement
 #ifndef CORE_MAIN_ASSERT_LAMBDA
@@ -36,6 +40,7 @@ typedef unsigned char ubyte;
 void msleep(int milliSeconds);
 void printHexBuffer(void* buf, int bufSize);
 void fprintHexBuffer(void* buf, int bufSize, char* header, char* footer);
+//void core_Print();
 
 /// ----- Function Defenitions ----- ///
 

### 2021-04-08 code/Tests/Array_Recorder/Array_Recorder.c

@@ -12,7 +12,11 @@
 #include <signal.h>
 #include <math.h>
 
+// Robotics libarary header
+#include <rc/button.h>
+
 // Custom headers
+#define CORE_DISABLE_MESSAGES 1
 #define DEBUG_XBEECOM 0
 #define XBEE_ARRAY_DEBUG 1
 #include "xbeeArray.h"
@@ -28,9 +32,15 @@ static void __signal_handler(__attribute__ ((unused)) int dummy) {
         return;
 }
 
+// Function to stop program on pause press
+static void __on_pause_press(void) {
+    rc_set_state(EXITING);
+    return;
+}
+
 // Prototypes
 int ProcessArguments(int argc, char* argv[], double* angle, double* distance, double* height, bool* useSweep, int* numScans);
-int AddRecored(FILE* fp, xbeeArray_settings* arrayP, double angle, double distance, double height);
+int AddRecored(FILE* fp, xbeeArray_settings* arrayP, double angle, double distance, double height, int numScan);
 int StripFloat(char* str, float* value);
 int StripInt(char* str, int* value);
 
@@ -80,17 +90,39 @@ int main(int argc, char* argv[]){
 	fp = fopen("Strengths.csv", "a");
 	MAIN_ASSERT(fp != NULL, "\tERROR: Failed to open file.\n");
 	
+	// Set up pause button
+	MAIN_ASSERT(
+		rc_button_init(RC_BTN_PIN_PAUSE, RC_BTN_POLARITY_NORM_HIGH, RC_BTN_DEBOUNCE_DEFAULT_US),
+		"\tERROR: Failed to initalize pause button!!!\n"
+	);
+	rc_button_set_callbacks(RC_BTN_PIN_PAUSE, __on_pause_press, NULL);
+
+	// Setup mode button for start
+	MAIN_ASSERT(
+		rc_button_init(RC_BTN_PIN_MODE, RC_BTN_POLARITY_NORM_HIGH, RC_BTN_DEBOUNCE_DEFAULT_US),
+		"\tERROR: Failed to initalize mode button!!!\n"
+	);
+	printf("\tPress Mode button to start...\n");
+    do {msleep(10);} while (rc_button_get_state(RC_BTN_PIN_MODE) == RC_BTN_STATE_RELEASED); 
+
 	// Main Program loop
 	rc_set_state(RUNNING);
 	if(useSweep){
+		// Dumb-Auto align array with stopper
+		stepMotor_Step(&sm, -1, 50);
+		msleep(500);
+
[…]

### 2021-04-08 parts/20-system_architecture.tex

@@
 The Mobile Cart subsystem block diagram is shown in \autoref{fig:mobile_block_diag}.
-The cart requires a power source, which will be a Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue).
+The cart requires a power source, which will be a 7.4 volt, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue).
 The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart.
@@
     1 & Aluminum Foil Tape - 2 in x 5 yd & \$ 6.05\\
+    2 & Ovonic 7.4V 8000mAh LiPo Battery & \$ 40.99\\
+    4 & Multiplexers & \$ 15.99\\
     \bottomrule

### 2021-04-08 code/Lib/core.h
core_printf

@@ -37,7 +37,8 @@ typedef unsigned char ubyte;
 
 /// ----- Prototypes ----- ///
 
-void msleep(int milliSeconds);
+inline void msleep(int milliSeconds);
+inline void core_printf( const char* format, ...);
 void printHexBuffer(void* buf, int bufSize);
 void fprintHexBuffer(void* buf, int bufSize, char* header, char* footer);
 //void core_Print();
@@ -46,7 +47,17 @@ void fprintHexBuffer(void* buf, int bufSize, char* header, char* footer);
 
 // Milliseconds Sleep
 // @param milliSeconds: Time in milliseconds to sleep for
-void msleep(int milliSeconds) { usleep((milliSeconds)*1000); }
+inline void msleep(int milliSeconds) { usleep((milliSeconds)*1000); }
+
+// Core Formated Print
+inline void core_printf( const char* format, ...) {
+#ifndef CORE_DISABLE_MESSAGES
+    va_list argptr;
+    va_start(argptr, format);
+    printf(format, argptr); 
+    va_end(argptr);
+#endif
+}
 
 // Print out byte array in hexidecimal
 // @param buf: Pointer to array of bytes to print out

### 2021-04-08 code/Lib/XBeeCom.h
Updated Libraries with core_printf

@@ -66,14 +66,13 @@ int xbeeCom_ReadCommand(int bus,  ubyte* buf, int bufSize){
          // Read in response
          // int rc_uart_read_bytes(int bus, uint8_t* buf, size_t bytes);
         int num_Bytes = rc_uart_read_bytes(bus, buf, bufSize);
-        if(num_Bytes == -1) { printf("\tRC Read Bytes Failed.\n"); return -1; }
+        ASSERT(num_Bytes != -1, "\tRC Read Bytes Failed.\n");
 
          // Check that the response is not empty
         if(num_Bytes == 0){
 #if DEBUG_XBEECOM
                 printf("\t[DEBUG] Did not recive a response message.\n");
 #endif
-                printf("\tDid not recive a response message. D:\n");
                 return -3;
         }
 
@@ -84,7 +83,7 @@ int xbeeCom_ReadCommand(int bus,  ubyte* buf, int bufSize){
 
         // Check for valid checksum
         if(!xbeeCom_CheckChecksum(buf,num_Bytes)) {
-                printf("\tInvalid Checksum :(\n");
+                core_printf("\tInvalid Checksum :(\n");
                 return -2;
         }
 #if DEBUG_XBEECOM
@@ -129,7 +128,7 @@ ubyte xbeeCom_GetFrameState(ubyte* msg, int length){
         if(frameType == 0x97 && length > 17) { return msg[17]; }
         else if(frameType == 0x88 && length > 7) { return msg[7]; }
         else {
-                printf("\tInvalied frame type 0x%02X or formating encountered.\n",frameType);
+                core_printf("\tInvalied frame type 0x%02X or formating encountered.\n",frameType);
                 return 255;
         }
 }

### 2021-04-08 code/Lib/extraMath.h
Save latest code

@@ -128,14 +128,14 @@ EXTRA_MATH_FUNC_HEAD double avg(double* array, int size) {
 // @param theta: Angle to wrap (in radians)
 EXTRA_MATH_FUNC_HEAD double wrapToPi(double theta)
 {
-    return mod(theta, M_PI);
+    return mod(theta + M_PI, 2*M_PI) - M_PI;
 }
 
 // Wraps theta between -180 and 180
 // @param theta: Angle to wrap (in degrees)
 EXTRA_MATH_FUNC_HEAD double wrapTo180(double theta)
 {
-    return mod(theta, 180.0);
+    return mod(theta + 180.0, 360.0) - 180.0;
 }
 
 #undef EXTRA_MATH_FUNC_HEAD

### 2021-04-08 code/Lib/odometry.h

@@ -31,7 +31,7 @@ double odometry_GetDistance(double R)
 {
     int leftEncVal = -rc_encoder_eqep_read(ODOMETRY_ENCODER_LEFT);
     int rightEncVal = rc_encoder_eqep_read(ODOMETRY_ENCODER_RIGHT);
-    double distance = (leftEncVal + rightEncVal)*2*M_PI*R/(1200*2);
+    double distance = (leftEncVal + rightEncVal)*2*M_PI*R/(ODOMETRY_COUNTS_PER_REV*2);
 
     return distance;
 }

### 2021-04-08 code/Lib/robot.h

@@ -7,8 +7,12 @@
 
 // Custom headers
 #include "core.h"
+#include "extraMath.h"
 #include "xbeeArray.h"
 #include "stepMotor.h"
+
+static double vLMax = 1.291988; // Maximum linear velocity of left wheel in m/s
+static double vRMax = 1.265705; // Maximum linear velocity of right wheel in m/s
 
 typedef struct
 {
@@ -40,9 +44,9 @@ int robot_setSpeeds(Robot_t* robot, double v, double omega);
 int robot_init(Robot_t* robot)
 {
     // Assign robot variables
-    robot->L = 0.202406;
+    robot->L = 0.199;
     robot->R = 0.0492125;
-    robot->vMax = 0.12;
+    robot->vMax = 0.13;
     robot->omegaMax = M_PI/4;
     robot->left_motor = 1;
     robot->right_motor = 2;
@@ -97,12 +101,32 @@ int robot_close(Robot_t* robot)
 // @param omega: Angular velocity
 int robot_setSpeeds(Robot_t* robot, double v, double omega)
 {
-    double omegaR = (v - omega*robot->L/2)/robot->R; // right wheel angular speed [rad/s]
-    double omegaL = (v + omega*robot->L/2)/robot->R; // left wheel angular speed [rad/s]
+    // Minimum duty cycle to apply to make sure the robot moves
+    // (does not apply if velocity is 0)
+    static const double minDuty = 0.25;
+    
+    // Velocities below this threshold will be treated as 0
+    static const double threshold = 1E-3;
 
-    // Convert angular wheel speeds to duty cycles
-    double dutyR = omegaR*0.05/robot->omegaMax; // Right wheel duty cycle
-    double dutyL = -omegaL*0.05/robot->omegaMax; // Left wheel duty cycle
+    double vR = (v - omega*robot->L/2); // right wheel linear speed [rad/s]
+    double vL = (v + omega*robot->L/2); // left wheel linear speed [rad/s]
+    
+    double dutyR = 0;
+    double dutyL = 0;
+
+    // Only compute duty cycle if the velocity is above the threshold. Otherwise, leave it at 0
+    if (fabs(vR) > threshold)
+    {
+        // Convert linear wheel speed to duty cycle by dividing by the maximum speed
+        dutyR = sign(vR)*clamp(vR/vRMax, minDuty, 1.0); // Right wheel duty cycle
+    }
+
[…]

### 2021-04-08 code/MainProgram/MainProgram.c

@@ -59,9 +59,9 @@ double getDistance(ubyte* distance_strengths, int num_strengths);
 int getAngle(int* directional_strengths, int num_strengths);
 
 // Global control parameters
-const double Kp = 1; // Linear speed proportional gain
+const double Kp = 2; // Linear speed proportional gain
 const double Kw = 4; // Angular speed proportional gain
-const int maxTargetAngle = 30; // Maximum angle change for a single measurement
+const int maxTargetAngle = 15; // Maximum angle change for a single measurement
 
 int main(){
     printf("\tStarting Main Program...\n");
@@ -131,7 +131,7 @@ int main(){
 
     // Initialize Robot
     printf("\tInitializing Robot...\n");
-    robot_init(&robot);
+    MAIN_ASSERT(robot_init(&robot) == 0, "\tERROR: Failed to initialize robot.\n");
 
     // Fill out the measurement arrays
     result = getMeasurement(&(robot.array), curStep, strengths, distance_strengths, directional_strengths);
@@ -202,12 +202,14 @@ int main(){
             
             // Find the target angle
             targetAngle = avg_i(angle, MOVING_AVG_SIZE);
-            // printf("Angle to remote: %.0f\n", targetAngle);
+            printf("Angle to remote: %.0f\n", targetAngle);
             //Saturate the target angle to avoid turning too fast
             targetAngle = clamp(targetAngle, -maxTargetAngle, maxTargetAngle);
             
             // Convert target angle to radians
             targetAngle_rad = targetAngle*M_PI/180;
+
+            // Get rectangular coordinates
             targetX = targetDistance*cos(targetAngle_rad);
             // targetY = targetDistance*sin(targetAngle);
 
@@ -224,11 +226,11 @@ int main(){
             // Pause measurements until robot is turned to target angle
             MAIN_ASSERT(robot_setSpeeds(&robot, v, omega) == 0, "\tERROR: Failed to set motor speeds\n");
 #if !MOTORS_OFF // Odometry only works if the motors move
-            while (abs(theta - targetAngle) > 2 && rc_get_state() != EXITING)
+            while (abs(theta - targetAngle) > 0.5 && rc_get_state() != EXITING)
             {
                 // Determine the angle of the robot relative to where it was when the last measurement was completed
                 theta = odometry_GetAngle(robot.R, robot.L);
-                // printf("Target angle: %f\n Robot angle: %f\n", targetAngle, theta);
[…]

### 2021-04-08 code/Tests/EncoderAngle_Testing/EncoderAngleTest.c

@@ -11,7 +11,7 @@
 #include "core.h"
 #include "odometry.h"
 
-double L = 0.202406;
+double L = 0.199;
 double R = 0.0492125;
 
 // interrupt handler to catch ctrl-c

### 2021-04-08 parts/50-implementation.tex
Create 50-implementation.tex
Cleared out empty sections of final report

--- 2020-09-21 parts/10-introduction.tex
@@
 %======================================================================
-\chapter{Introduction}
-\label{ch: Chapter1}
+\chapter{Implementation}
+\label{ch: Chapter5}
 %======================================================================
@@
 %----------------------------------------------------------------------
-\section{Problem Statement}
+\section{Robot Assembly}
 %----------------------------------------------------------------------
-Helicopters are of a paramount importance as
-they are used in many civilian and military applications due to their ability for vertical take-off and landing.
-To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics.
-Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions.
-Such methods are expensive and time-consuming to develop.
-Implementation of motion control techniques using cost-effective hardware is still a challenge.
-
-In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position.
-Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices.
-This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.
 
 %----------------------------------------------------------------------
-\section{Literature Review}
+\section{Code Trial and Implementation}
 %----------------------------------------------------------------------
-Our project requires a great deal of research as some of our tasks have not been attempted before.
-As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.
-
-Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices.
-In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}.
-A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters.
-See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein.
-Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.
-
-The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.
-This involves creating a linearized system model to calculate the LQR state-feedback gain.
-A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.
-SMC is a nonlinear control technique to drive the system states onto a surface in the state space.
-This method has been used  by~\cite{Ahmed2010-Sliding}.
-Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.
-The ADP technique does not rely on knowledge of the system model.
-Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.
-Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.
-
-As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms.
-This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms.
-Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.
 
 %----------------------------------------------------------------------
-\section{Report Organization}
+\section{Experimental Results}
 %----------------------------------------------------------------------
-This report is organised into 6 chapters.
-Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.
-Chapter \ref{ch: Chapter2} explains how to create a mathematical model for the system.
-Chapter \ref{ch: Chapter3} provides a breif explanation of the control algorithms and architectures used.
-Chapter \ref{ch: Chapter4} contains the results from our simulations.
-Chapter \ref{ch: Chapter5} disucsses results from USB, Raspberry Pi, and Mobile Device implementation.
-Chapter \ref{ch: Chapter6} concludes the paper and provides insight into future directions.
 

### 2021-04-08 parts/60-conclusion_and_future_work.tex
Cleared out empty sections of final report

@@
 %----------------------------------------------------------------------
-Helicopters are of a paramount importance as
-they are used in many civilian and military applications due to their ability for vertical take-off and landing.
-To enable their use in such applications, intensive research has been conducted to date since helicopters involve complex nonlinear dynamics.
-Most of the work on helicopter based research requires dedicated computers for controlling their motion to specific configurations and resistant to turbulent conditions.
-Such methods are expensive and time-consuming to develop.
-Implementation of motion control techniques using cost-effective hardware is still a challenge.
-
-In this project, we are proposing an algorithm for smart control of a team of two degree-of freedom (two-DOF) helicopters using conventional motion control in cooperation with machine learning techniques where a user will be able to configure helicopters from any initial position.
-Even though conventional techniques have been tested with simple platforms in the literature, the current project employs conventional motion control strategies in cooperation with machine learning technique (reinforcement learning, for instance) for a team of helicopters as well as introducing user control via mobile devices.
-This project is expected to encourage research in this area as well as serve as an educational tool in teaching environments.
 
@@
 %----------------------------------------------------------------------
-Our project requires a great deal of research as some of our tasks have not been attempted before.
-As a result, we have examined research papers, work complete by other projects at Bradley University, and documentation/teaching materials from Quanser Inc.
-
-Among the major challenges in developing unmanned systems is to implement a modular, cost-effective, and robust teleoperation system, where the motion of a group of helicopters is controlled by mobile devices.
-In some cases, computer simulations are conducted to reveal the performance control structures of a 2-DOF helicopter~\cite{DArpino2010}.
-A large body of research has been conducted in the literature to focus on developing different control structures, such as linear-quadratic regulators (LQR)/Gaussian (LQG), sliding-mode controls (SMC), and advance nonlinear controls, that are specifically applied to 2-DOF helicopters.
-See~\cite{Subramanian2016-Robust,Ahmed2010-Sliding}, for example, and some references therein.
-Furthermore,  soft-computing tools, such as fuzzy-logic, neural networks, and a few combinations of them are employed for controlling the motion of a 2-DOF helicopter~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy,Gao2016-DataDriven,Hernandez2012-Decentralized}.
-
-The documentation of Quanser AERO\footnote{See \href{https://www.quanser.com/}{https://www.quanser.com/} for details} employs LQR and LQG motion control techniques for teaching purposes.
-This involves creating a linearized system model to calculate the LQR state-feedback gain.
-A model reference adaptive control (MARC) scheme using Lyapunov functions has been used by~\cite{Subramanian2016-Robust} for adaptive motion control of a 2-DOF helicopter.
-SMC is a nonlinear control technique to drive the system states onto a surface in the state space.
-This method has been used  by~\cite{Ahmed2010-Sliding}.
-Fuzzy-logic controllers use an inference engine to produce an output as used in~\cite{Chang2017-Fuzzy,Kayacan2016-Fuzzy}.
-The ADP technique does not rely on knowledge of the system model.
-Instead, it uses data to reconstruct the states as preformed by~\cite{Gao2016-DataDriven}.
-Authors in~\cite{Hernandez2012-Decentralized} used high order neural networks (HONN) to approximate non-linearities in the system model.
-
-As can be noticed, most of the motion control techniques are either tested using computer simulations or use dedicated computational platforms, that may not be modular and/or cost-effective, for developing motion control algorithms.
-This is due to the fact that the aforementioned techniques are mainly to propose novel motion control techniques and not focused on hardware implementation platforms.
-Therefore, the current work considers implementing a conventional motion control technique using modular and cost-effective hardware platforms in the context of a teleoperation system, where a human operator has the ability to control the motion of a team of helicopters using a smart mobile device.
 

### 2021-04-08 code/Lib/robot.h
Updated robot.h

@@ -108,8 +108,8 @@ int robot_setSpeeds(Robot_t* robot, double v, double omega)
     // Velocities below this threshold will be treated as 0
     static const double threshold = 1E-3;
 
-    double vR = (v - omega*robot->L/2); // right wheel linear speed [rad/s]
-    double vL = (v + omega*robot->L/2); // left wheel linear speed [rad/s]
+    double vR = (v - omega*robot->L/2); // right wheel linear speed [m/s]
+    double vL = (v + omega*robot->L/2); // left wheel linear speed [m/s]
     
     double dutyR = 0;
     double dutyL = 0;
@@ -118,14 +118,14 @@ int robot_setSpeeds(Robot_t* robot, double v, double omega)
     if (fabs(vR) > threshold)
     {
         // Convert linear wheel speed to duty cycle by dividing by the maximum speed
-        dutyR = sign(vR)*clamp(vR/vRMax, minDuty, 1.0); // Right wheel duty cycle
+        dutyR = sign(vR)*clamp(fabs(vR)/vRMax, minDuty, 1.0); // Right wheel duty cycle
     }
 
     // Only compute duty cycle if the velocity is above the threshold. Otherwise, leave it at 0
     if (fabs(vL) > threshold)
     {
         // Convert angular wheel speeds to duty cycles by dividing by the maximum speed of each wheel
-        dutyL = sign(vL)*clamp(vL/vLMax, minDuty, 1.0); // Left wheel duty cycle
+        dutyL = -sign(vL)*clamp(fabs(vL)/vLMax, minDuty, 1.0); // Left wheel duty cycle
     }
 
 #if !MOTORS_OFF

### 2021-04-13 parts/03-acknowledgements.tex
Updated acknowledgements
Update 03-acknowledgements.tex

@@
 
-    \par Special thanks to Mr. Christopher Mattus for his assistance in procuring the parts and modifying the hardware for our project.
+    \par Special thanks to Mr. Christopher Mattus for his assistance in procuring the parts and modifying 		\par the hardware for our project.
+    \par Special thanks to Shreel Patel for his assistance with charging the battery on the robot.
     \par Thank you to everyone else who helped make this project possible and successful.

### 2021-04-13 parts/10-introduction.tex
Update 10-introduction.tex

@@
 One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items.
-Moreover, robots used for this purpose are more costly than they are worth.
+Moreover, robots used for this purpose are costlier than they are worth.
+
+\vspace*{12pt}
+\noindent
 In this project, we are proposing a robotic cart that would primarily use analog signals with the use of cost-effective wireless communication to identify the customer and be able to track and follow the customer through the store.
 The implementation of such a fully functional robotic cart will outreach the scope of the project but is the overall goal for this project in the coming years while encouraging further research in this field.
+
+\vspace*{12pt}
+\noindent
 Applications of the proposed robotic cart include, but are not limited to, delivery carts to follow mail personnel and carry the deliveries, file transfer carts in offices, hospital carts to aid nurses and doctors by carrying medicine or surgery supplies, and carts in construction sites to carry tools and other supplies across the job site.
@@
 %----------------------------------------------------------------------
-Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores.
-See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example.
+Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}.
 Currently, the work being done focuses on a few different methods of having a robotic cart interface with the customer and follow them through the store.
@@
 One such method that has been utilized to make a cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}.
-Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow them through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
+Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
 Therein, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.
@@
 The robot will be able to track this remote instead of using line of sight methods~\cite{Miah2018-Intelligent}.
-In addition to the XBee S2C RF radios, we will equip the robot with a parabolic reflector, which improves Wi-Fi reception at various distances and angles, \textit{i.e.,} angle of arrivals of RF signals from the remote, based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent}~\cite{Li2013ANA}.
+In addition to the XBee S2C RF radios, we will equip the robot with a parabolic reflector, which improves radio reception at various distances and angles, \textit{i.e.,} angle of arrivals of RF signals from the remote, based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent}~\cite{Li2013ANA}.
 
@@
 \noindent
-The approach using signal strength of RF signals also requires an understanding of multipath interference which is common in Wi-Fi based wireless positioning sensing systems.
+The approach using signal strength of RF signals also requires an understanding of multipath interference which is common in RF based wireless positioning sensing systems.
 Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using course estimation calculations such as received signal strength indicator (RSSI) and time difference of arrival (TDoA) is key to compensate for the multipath interference in received signals.
+
+\vspace*{12pt}
+\noindent
 The work in ~\cite{ladd_bekris_rudys_kavraki_wallach_2005} shows a different approach to the multipath issue by using an IEEE 802.11b wireless ethernet device to measure RF signals.
 This device system was used because it is communicable between a mobile device and a localization based service with low complexity for the user.
+
+\vspace*{12pt}
+\noindent
 Also, in~\cite{lindhe_johansson_bicchi_2007}, the research states several other ways to counteract the multipath fading with methods such as antenna diversity, frequency spreading, or adaptive antenna arrays.
 The method used in this paper was to sample the radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position in an indoor environment.
+
+\vspace*{12pt}
+\noindent
 Lastly, in~\cite{Lindhe2009} the method that is utilized exploits multipath fading by measuring the signal-to-noise ratio (SNR) and adjusting the robot's motion to spend more time where the channel strength is greater.
@@
 \noindent
-All of the solutions that were found required direct line-of-sight between the robot and the user.
+All of the solutions that were found required line-of-sight communication between the robot and the user.
 In this project we aim to use the XBee S2C RF radios and a parabolic reflector combined into a rotating system similar to the one presented in~\cite{Miah2018-Intelligent} in order to have the robot track the customer through a store without using line-of-sight sensing.
@@
 %----------------------------------------------------------------------
-This report is organised into the following 6 chapters:
+This report is organized into six chapters:
 
 \begin{itemize}
-	\item Chapter \ref{ch: Chapter1} discusses the background and goals of our project and what other similar projects have accomplished
-	\item Chapter \ref{ch: Chapter2} explains how our robotic cart system is broken down fundamentally and the system components we used to build the robot
-	\item Chapter \ref{ch: Chapter3} goes over the design of our parabolic reflector arrays and how we set them up on the robot
-	\item Chapter \ref{ch: Chapter4} provides an explanation of the algorithms we used to create the code to make the robot move
-	\item Chapter \ref{ch: Chapter5} discusses the implementation of all the parts onto the robot and our experimental results we got when running the robot
-	\item Chapter \ref{ch: Chapter6} concludes our project work and discusses future endeavors on this project
+	\item Chapter \ref{ch: Chapter1} discusses the background and goals of the project and what other similar projects have accomplished.
+	\item Chapter \ref{ch: Chapter2} explains how the robotic cart system in this project is broken down fundamentally, and the components used to build the robot.
+	\item Chapter \ref{ch: Chapter3} goes over the design of the parabolic reflector arrays and how they were set up on the robot.
+	\item Chapter \ref{ch: Chapter4} provides an explanation of the algorithms that were used to create the code to make the robot move.
+	\item Chapter \ref{ch: Chapter5} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
+	\item Chapter \ref{ch: Chapter6} concludes the project work and discusses future endeavors on this project.
 \end{itemize}

### 2021-04-13 parts/20-system_architecture.tex
Update 20-system_architecture.tex

@@
 \noindent
-
 The high-level system block diagram of the proposed robotic cart (prototype) is shown in \autoref{fig:sys_block_diag}.
 There are four inputs to the proposed cart system.
-The robotic cart is supplied power through a battery that is mounted in the chassis of the robotic cart.
+The robotic cart is supplied with power through a battery that is mounted in the chassis of the robotic cart.
 There will be an on/off switch to allow the system to be powered down when not in use.
 The motion of the cart is dependent on the motion of the remote.
-A stretch goal for the project are mode selection buttons that allow the user to put the robotic cart system into different operating modes.
+A stretch-goal for the project are mode selection buttons that allow the user to put the robotic cart system into different operating modes.
 
@@
 \noindent
-
 The main output of the system is the position trajectory of the robotic cart in its environment.
@@
 The first block diagram is of the Remote Target subsystem shown in \autoref{fig:remote_block_diag}.
-Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 7.4 volt Li-Po battery with a voltage regulation circuit since the XBee has a smaller input voltage of 3.3 volts.
+Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 7.4V Li-Po battery with a voltage regulation circuit since the XBee has a smaller input voltage of 3.3 volts.
 
@@
 The Mobile Cart subsystem block diagram is shown in \autoref{fig:mobile_block_diag}.
-The cart requires a power source, which will be a 7.4 volt, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue).
+The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue).
 The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart.
-The mode selection buttons for changing the operating mode of the robotic cart is a stretch goal of the project and will be implemented on the cart if we have time.
+The mode selection buttons for changing the operating mode of the robotic cart is a stretch-goal of the project and will be implemented on the cart if we have time.
 The final input to the mobile cart subsystem is the XBee network messages received from the remote target.
@@
 Although some of these parts are available in the Bradley University laboratory, other parts must be purchased.
-The parts that exist in the lab are shown in \autoref{tab:Partslablist}.
-Also, \autoref{tab:Partslist} shows the list of parts that we purchased.
+The parts that exist in the lab are listed in \autoref{tab:Partslablist}.
+Also, \autoref{tab:Partslist} shows the list of parts that were purchased.
 The parts compiled in the lists are the required parts needed to build two smart robotic cart systems.
@@
   \centering
+  \caption{Parts Available in Laboratory}
   \begin{tabular}{c|c}
@@
   \end{tabular}
-  \caption{Parts Available in Laboratory}
+  %\caption{Parts Available in Laboratory}
   \label{tab:Partslablist}
@@
   \centering
+  \caption{Purchased parts for the Robotic Cart Project}
   \begin{tabular}{c|c|c}
@@
   \end{tabular}
-  \caption{Purchased parts for the Robotic Cart Project}
+  %\caption{Purchased parts for the Robotic Cart Project}
   \label{tab:Partslist}
@@
 The reflector array will be mounted on top of the cart with a stepper motor.
-There are two reflector designs that we will be evaluating in this project.
+There are two reflector designs that were evaluated in this project.
 The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of the signals that come into the reflector perpendicularly.
@@
 The paraboloidal reflector design may not be able to pick up the signals from the remote as well because of this.
-To solve this problem, we designed a combination parabolic/paraboloidal reflector, as shown in \autoref{fig:parabolicReflector}.
+
+\vspace*{12pt}
+\noindent
+To solve this problem, a combination parabolic/paraboloidal reflector was designed, as shown in \autoref{fig:parabolicReflector}.
 The lower half of this reflector is paraboloidal in shape to limit the signals coming from below.
@@
 This shape focuses the signals in the horizontal plane, but allows signals from above to still be received.
-We plan to construct both of these reflector designs by 3D printing the frames, then lining them with reflective foil tape.
+The plan is to construct both of these reflector designs by 3D printing the frames, then lining them with reflective foil tape.
 Both models will then be tested to determine which design works better.
@@
 \subsection{Operation of Mobile Cart System}
-The mobile cart will be controlled by a central embedded computer which is the BeagleBone Blue since it is ideal in robotics control.
-Two DC motors will be used to drive wheels and move the cart.
-Five XBee modules on the cart will be used to allow communication with the remote target.
-One of these radio sensors will be mounted on top of the cart to broadcast in all directions.
-The other four sensors will be placed inside parabolic reflectors at right angles to each other.
-This sensor array will be mounted on a stepper motor to allow rotation.
+The mobile cart was controlled by a central embedded computer which is the BeagleBone Blue since it is ideal in robotics control.
+Two DC motors were used to drive wheels and move the cart.
+Five XBee modules on the cart were used to allow communication with the remote target.
+One of these radio sensors was mounted on top of the cart to broadcast in all directions.
+The other four sensors were placed inside parabolic reflectors at right angles to each other.
+This sensor array was mounted on a stepper motor to allow rotation.
 

### 2021-04-13 parts/20-system_architecture.tex
Update 20-system_architecture.tex

@@
 \noindent
-To solve this problem, a combination parabolic/paraboloidal reflector was designed, as shown in \autoref{fig:parabolicReflector}.
+To solve this problem, a combination parabolic/paraboloidal reflector was designed, as shown in \autoref{fig:parabolicReflector1}.
 The lower half of this reflector is paraboloidal in shape to limit the signals coming from below.
@@
     \caption{Combined Parabolic/Paraboloidal Reflector}
-    \label{fig:parabolicReflector}
+    \label{fig:parabolicReflector1}
   \end{minipage}
@@
 
-\subsection{Operation of Mobile Cart System}
+\subsection{Operation of Robotic Cart System}
 The mobile cart was controlled by a central embedded computer which is the BeagleBone Blue since it is ideal in robotics control.

### 2021-04-13 parts/30-customized_parabolic_reflector_array.tex
Cleared out empty sections of final report
Update 30-customized_parabolic_reflector_array.tex

@@
 The XBee RF modules that were used detect signals from any direction.
-For this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming.
+In this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming.
 To accomplish this, two different models of reflector arrays were designed and constructed.
 
-\subsection{Purely Paraboloidal Reflector}
-The first design, shown in \autoref{fig:paraboloidalReflector}, uses a reflector with a purely paraboloidal shape.
-This shape was selected since all signals entering the reflector parallel to the axis of the reflector will pass through the focus of the paraboloid.
-By mounting the XBee such that the center of the antenna coincides with the focus of the paraboloid, the signal strength of the signals entering parallel to the axis will be maximized.
+\subsection{Paraboloidal Reflector}
+The first design, shown in \autoref{fig:paraboloidalReflector}, uses a reflector with a paraboloidal shape.
+This shape was selected since all signals entering the reflector parallel to the axis of the reflector will be focused at the focal point of the paraboloid.
+By mounting the XBee such that the center of the antenna coincides with the focal point of the paraboloid, the signal strength of the signals entering parallel to the axis will be maximized.
 \begin{figure}
@@
 
-%----------------------------------------------------------------------
-\section{Experimental Results}
-%----------------------------------------------------------------------
-
 %%% Local Variables:

### 2021-04-13 parts/20-system_architecture.tex
Update 20-system_architecture.tex

@@
 %----------------------------------------------------------------------
-The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target, which is held by the user or customer, as shown in \autoref{fig:sys_block_diag}.
+The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target, which is held by the user or customer, as shown in Fig.~ \ref{fig:sys_block_diag}.
 The proposed smart robotic cart is a wheeled robot that sends and receives radio signals to follow the remote target which acts as the beacon for the robotic cart system.

### 2021-04-13 parts/20-system_architecture.tex
Update 20-system_architecture.tex

--- 2021-04-13 parts/20-system_architecture.tex
@@
 %----------------------------------------------------------------------
-The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target, which is held by the user or customer, as shown in \autoref{fig:sys_block_diag}.
+The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target, which is held by the user or customer, as shown in Fig.
+\ref{fig:sys_block_diag}.
 The proposed smart robotic cart is a wheeled robot that sends and receives radio signals to follow the remote target which acts as the beacon for the robotic cart system.
@@
 \noindent
-The high-level system block diagram of the proposed robotic cart (prototype) is shown in \autoref{fig:sys_block_diag}.
+The high-level system block diagram of the proposed robotic cart (prototype) is shown in Fig.
+\ref{fig:sys_block_diag}.
 There are four inputs to the proposed cart system.
@@
 The two subsystems communicate with one another by relaying radio messages between them.
-The first block diagram is of the Remote Target subsystem shown in \autoref{fig:remote_block_diag}.
+The first block diagram is of the Remote Target subsystem shown in Fig.
+\ref{fig:remote_block_diag}.
 Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 7.4V Li-Po battery with a voltage regulation circuit since the XBee has a smaller input voltage of 3.3 volts.
@@
 \noindent
-The Mobile Cart subsystem block diagram is shown in \autoref{fig:mobile_block_diag}.
+The Mobile Cart subsystem block diagram is shown in Fig.
+\ref{fig:mobile_block_diag}.
 The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue).
@@
 The parts that exist in the lab are listed in \autoref{tab:Partslablist}.
-Also, \autoref{tab:Partslist} shows the list of parts that were purchased.
+Also, Fig.
+\ref{tab:Partslist} shows the list of parts that were purchased.
 The parts compiled in the lists are the required parts needed to build two smart robotic cart systems.
@@
 \noindent
-The main components for this project are the Budget Bot Chassis (\autoref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (\autoref{fig:beagleboneBlue}), and the XBee S2C Modules (\autoref{fig:XBeeModule}).
+The main components for this project are the Budget Bot Chassis (Fig.
+\ref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (Fig.
+\ref{fig:beagleboneBlue}), and the XBee S2C Modules (Fig.
+\ref{fig:XBeeModule}).
 Another major component is the reflector array that will be used to directionally receive the RF signals from the remote target that is with the user.
@@
 There are two reflector designs that were evaluated in this project.
-The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of the signals that come into the reflector perpendicularly.
+The first, shown in Fig.
+\ref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of the signals that come into the reflector perpendicularly.
 Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array.
@@
 \noindent
-To solve this problem, a combination parabolic/paraboloidal reflector was designed, as shown in \autoref{fig:parabolicReflector1}.
+To solve this problem, a combination parabolic/paraboloidal reflector was designed, as shown in Fig.
+\ref{fig:parabolicReflector1}.
 The lower half of this reflector is paraboloidal in shape to limit the signals coming from below.

### 2021-04-13 parts/30-customized_parabolic_reflector_array.tex
Update 30-customized_parabolic_reflector_array.tex

@@
 \subsection{Paraboloidal Reflector}
-The first design, shown in \autoref{fig:paraboloidalReflector}, uses a reflector with a paraboloidal shape.
+The first design, shown in Fig.
+\ref{fig:paraboloidalReflector}, uses a reflector with a paraboloidal shape.
 This shape was selected since all signals entering the reflector parallel to the axis of the reflector will be focused at the focal point of the paraboloid.
@@
 \subsection{Combined Parabolic/Paraboloidal Reflector}
-The second design, shown in \autoref{fig:parabolicReflector}, is the same on the lower half as the first design.
+The second design, shown in Fig.
+\ref{fig:parabolicReflector}, is the same on the lower half as the first design.
 However, the upper half is simply a surface where the horizontal cross-section is a parabola.

### 2021-04-13 code/Tests/Array_Recorder/Array_Recorder.c
Updates to Array_Recorder

@@ -1,5 +1,5 @@
-/* Array_Recorder.c
-*    
+/* 
+*    Array_Recorder.c
 */
 
 // C Library headers
@@ -16,20 +16,20 @@
 #include <rc/button.h>
 
 // Custom headers
-#define CORE_DISABLE_MESSAGES 1
+//#define CORE_DISABLE_MESSAGES 1
 #define DEBUG_XBEECOM 0
-#define XBEE_ARRAY_DEBUG 1
+#define XBEE_ARRAY_DEBUG 0
 #include "xbeeArray.h"
 #include "stepMotor.h"
 
 #define STEPS_PER_MEASUREMENT 5
-#define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*STEP_MOTOR_DEG_PER_STEP)
-#define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
+#define DEG_PER_MEASUREMENT (STEPS_PER_MEASUREMENT*STEP_MOTOR_DEG_PER_STEP)
+#define NUM_MEASUREMENTS (int)(81/DEG_PER_MEASUREMENT)
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy) {
-        rc_set_state(EXITING);
-        return;
+    rc_set_state(EXITING);
+    return;
 }
 
 // Function to stop program on pause press
@@ -40,141 +40,142 @@ static void __on_pause_press(void) {
 
 // Prototypes
 int ProcessArguments(int argc, char* argv[], double* angle, double* distance, double* height, bool* useSweep, int* numScans);
-int AddRecored(FILE* fp, xbeeArray_settings* arrayP, double angle, double distance, double height, int numScan);
+int Addrecord(FILE* fp, xbeeArray_settings* arrayP, double angle, double distance, double height, int numScan);
 int StripFloat(char* str, float* value);
 int StripInt(char* str, int* value);
 
 // Main
 int main(int argc, char* argv[]){
-	printf("\tStarting Array Value Recorder...\n");
+    printf("\tStarting Array Value Recorder...\n");
 
-	// set signal handler so the loop can exit cleanly
+    // set signal handler so the loop can exit cleanly
     signal(SIGINT, __signal_handler);
 
-	// Set up PID file for this program
-	if(rc_kill_existing_process(2.0)<-2) return -1;
+    // Set up PID file for this program
[…]

### 2021-04-13 code/Tests/DutyCycle_Testing/DutyCycleTest.c

@@ -1,0 +1,84 @@
+// C Library headers
+#include <stdio.h>
+#include <signal.h>
+
+// Robot Control Library headers
+#include <rc/time.h>
+#include <rc/start_stop.h>
+#include <rc/button.h>
+
+#include "extraMath.h"
+#include "core.h"
+#include "odometry.h"
+#include "robot.h"
+
+double duty = 0.17;
+
+//double L = 0.199;
+double R = 0.0492125;
+
+int main()
+{
+    // make sure another instance isn't running
+    // if return value is -3 then a background process is running with
+    // higher privaledges and we couldn't kill it, in which case we should
+    // not continue or there may be hardware conflicts. If it returned -4
+    // then there was an invalid argument that needs to be fixed.
+    if(rc_kill_existing_process(2.0)<-2) return -1;
+
+    // make PID file to indicate your project is running
+    // due to the check made on the call to rc_kill_existing_process() above
+    // we can be fairly confident there is no PID file already and we can
+    // make our own safely.
+    rc_make_pid_file();
+
+    // Initalize Encoders
+    printf("\tInitalizing Quadrature Encoders...\n");
+    MAIN_ASSERT(rc_encoder_eqep_init() == 0, "\tERROR: Failed to Initialize  Quadrature Encoders.\n");
+    
+    printf("\tInitalizing Motors...\n");
+    ASSERT(rc_motor_init() != -1, "\tERROR: Failed to initialize motors\n");
+
+    odometry_SetZeroRef();
+
+    // Create the robot object
+    Robot_t robot;
+    robot.left_motor = 1;
+    robot.right_motor = 2;
+
+    // Record starting time
+    uint64_t startTime = rc_nanos_since_boot();
+    
+    // Drive the robot at the desired duty cycle
+    rc_motor_set(robot.right_motor, duty);
+    rc_motor_set(robot.left_motor, -duty);
+
+    // Wait for 2 seconds
+    while (rc_nanos_since_boot() - startTime < 2E9){}
+
+    //Get the encoder readings
+    int leftEncVal = -rc_encoder_eqep_read(ODOMETRY_ENCODER_LEFT);
+    int rightEncVal = rc_encoder_eqep_read(ODOMETRY_ENCODER_RIGHT);
+
+    // Turn off the motors
+    rc_motor_set(robot.right_motor, 0);
+    rc_motor_set(robot.left_motor, 0);
+
[…]

### 2021-04-13 code/MainProgram/MainProgram.c
Update MainProgram

@@ -59,8 +59,8 @@ double getDistance(ubyte* distance_strengths, int num_strengths);
 int getAngle(int* directional_strengths, int num_strengths);
 
 // Global control parameters
-const double Kp = 2; // Linear speed proportional gain
-const double Kw = 4; // Angular speed proportional gain
+const double Kv = 2; // Linear speed proportional gain
+const double Kw = 8; // Angular speed proportional gain
 const int maxTargetAngle = 15; // Maximum angle change for a single measurement
 
 int main(){
@@ -200,9 +200,13 @@ int main(){
             targetDistance = avg(distance, MOVING_AVG_SIZE);
             // printf("Distance to remote: %.4f\n", targetDistance);
             
+            // Fix target distance to 1 m for now
+            // TODO: Get rid of this once the angle part is working
+            targetDistance = 1; 
+            
             // Find the target angle
             targetAngle = avg_i(angle, MOVING_AVG_SIZE);
-            printf("Angle to remote: %.0f\n", targetAngle);
+            // printf("Angle to remote: %.0f\n", targetAngle);
             //Saturate the target angle to avoid turning too fast
             targetAngle = clamp(targetAngle, -maxTargetAngle, maxTargetAngle);
             
@@ -214,7 +218,7 @@ int main(){
             // targetY = targetDistance*sin(targetAngle);
 
             // Calculate motor control signals
-            v = sign(targetX)*Kp*targetDistance;
+            v = sign(targetX)*Kv*targetDistance;
             v = clamp(v, -robot.vMax, robot.vMax); // Saturate velocity
             omega = Kw*targetAngle_rad;
             omega = clamp(omega, -robot.omegaMax, robot.omegaMax); // Saturate velocity
@@ -225,12 +229,16 @@ int main(){
 
             // Pause measurements until robot is turned to target angle
             MAIN_ASSERT(robot_setSpeeds(&robot, v, omega) == 0, "\tERROR: Failed to set motor speeds\n");
+            int counter = 0;
 #if !MOTORS_OFF // Odometry only works if the motors move
             while (abs(theta - targetAngle) > 0.5 && rc_get_state() != EXITING)
             {
                 // Determine the angle of the robot relative to where it was when the last measurement was completed
                 theta = odometry_GetAngle(robot.R, robot.L);
-                printf("Target angle: %f\t Robot angle: %f\n", targetAngle, theta);
+                if (counter % 40 == 0)
[…]

### 2021-04-15 code/lib/angleNN.c
Added Neural Network to try to predict angle

@@ -1,0 +1,212 @@
+#include "angleNN.h"
+#include <stdio.h>
+
+// Number of nodes in hidden layer
+#define NUM_NODES 50
+
+static int matmul(int r1, int c1, const double mat1[r1][c1], int r2, int c2, const double mat2[r2][c2], double result[r1][c2]);
+static double relu(double x);
+
+const double W1[NUM_NODES][ANGLE_NN_NUM_INPUTS] = 
+{
+    { 0.32400522,     0.59347755,    -0.4550447,      0.1103395,      0.071392484,    1.7329662,     -5.2477016,     -5.995041,      -1.970479,       0.17253232 },
+    {-0.25083315,     0.10202199,    -0.28324264,    -0.21815819,     0.2315822,      0.20819858,     0.02849251,     0.17260998,     0.20856878,     0.22088781 },
+    {-0.36464375,     0.43990836,     0.103821866,   -0.045257814,    0.03780396,    -2.084199,       8.098524,       4.01482,       -6.4209867,     -6.630199   },
+    { 0.13913068,    -0.030551298,   -0.14037517,     0.15223742,    -0.19292814,    -0.056183487,   -0.017855855,   -0.20431317,     0.26780877,    -0.26253036 },
+    { 0.12465286,     0.4494285,     -0.29499716,     0.11725501,     0.48926094,     1.8401811,     -5.7910147,     -6.337228,      -1.6584923,     -0.01856326 },
+    {-0.6211599,      1.6852309,     -0.20656037,    -0.21377984,    -0.3109885,     -2.4757023,     11.124451,       2.3496215,     -14.148427,    -11.773359   },
+    { 0.24295881,     0.01216355,    -0.264147,      -0.14123718,     0.040681094,   -0.31548136,     0.22221199,    -0.20102245,    -0.30217814,    -0.11225483 },
+    { 0.06389251,     0.160415,      -0.36102182,     0.081927784,   -0.028795477,    0.11835364,    -0.040851876,    0.08176798,    -0.0368132,     -0.30580887 },
+    {-0.26275772,     0.5490117,      0.045560576,    0.1291681,      0.11564901,     1.2392452,     -5.2796674,     -6.456324,      -1.7078327,     -0.018635953},
[…]

### 2021-04-15 code/lib/angleNN.h

@@ -1,0 +1,15 @@
+#ifndef ANGLENN_H
+#define ANGLENN_H
+/* Neural network to predict angle
+ * Architecture:
+ *  - 10 inputs (top, side1, side2, side3, side4, normTop, normSide1, normSide2, normSide3, normSide4)
+ *  - 50 nodes (plus 1 bias node) in the hidden layer
+ *  - 1 node in the output layer
+ *  - All activations are the relu function
+*/
+
+#define ANGLE_NN_NUM_INPUTS 10
+
+double angleNN_predict(double inputs[ANGLE_NN_NUM_INPUTS][1]);
+
+#endif

### 2021-04-15 code/Lib/XBeeArray.h
Various updates to make robot work.

@@ -35,7 +35,7 @@ int xbeeArray_GetStrengths(xbeeArray_settings* array, ubyte strengths[5]);
 int xbeeArray_Init(xbeeArray_settings* array) {
     int result;
 
-    // Initalize UART busses
+    // Initalize UART buses
     result = xbeeCom_InitUART(array->top_uart_bus);
     XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to initalize top UART on bus %d\n", array->top_uart_bus);
     xbeeCom_InitUART(array->side_uart_bus);
@@ -53,7 +53,7 @@ int xbeeArray_Init(xbeeArray_settings* array) {
 int xbeeArray_Close(xbeeArray_settings* array) {
     int result;
 
-    // Close UART busses
+    // Close UART buses
     result = xbeeCom_CloseUART(array->top_uart_bus);
     XBEE_ARRAY_DEBUG_ASSERT(result == 0, "\t[DEBUG] ERROR: Failed to close top UART on bus %d\n", array->top_uart_bus);
     result = xbeeCom_CloseUART(array->side_uart_bus);
@@ -74,23 +74,23 @@ int xbeeArray_GetStrengths(xbeeArray_settings* array, ubyte strengths[5]){
         result = atCom_SendRemote(array->top_uart_bus, array->remoteAddr, 0x6462);
         XBEE_ARRAY_DEBUG_ASSERT(result != -1, "\t[DEBUG] ERROR: Failed to write Remote AT command to UART Port %d.\n", array->top_uart_bus);
 
-        // Read in Signel Stength for the remote from the top XBee
+        // Read in signal strength for the remote from the top XBee
         result = atCom_ReadRemoteResponseData(array->top_uart_bus, &(strengths[0]), 1);
 
         if(result < 0)
         {
-            msleep(10);
+            usleep(1000*10);
             XBEE_ARRAY_DEBUG_ASSERT(rc_uart_flush(array->top_uart_bus) == 0, "\t[DEBUG] failed to flush UART for bus %d.\n", array->top_uart_bus);
         }
     }  while(result < 0 && readAttempts < 4);
     XBEE_ARRAY_DEBUG_ASSERT(result >= 0, "\t[DEBUG] ERROR: Failed to read Remote AT command response data on UART Port %d.\n", array->top_uart_bus);
 
-    // Flush Side UART in preperation for local AT commands
-    msleep(1);
[…]

### 2021-04-15 code/Lib/robot.h

@@ -7,12 +7,8 @@
 
 // Custom headers
 #include "core.h"
-#include "extraMath.h"
 #include "xbeeArray.h"
 #include "stepMotor.h"
-
-static double vLMax = 1.291988; // Maximum linear velocity of left wheel in m/s
-static double vRMax = 1.265705; // Maximum linear velocity of right wheel in m/s
 
 typedef struct
 {
@@ -46,7 +42,7 @@ int robot_init(Robot_t* robot)
     // Assign robot variables
     robot->L = 0.199;
     robot->R = 0.0492125;
-    robot->vMax = 0.13;
+    robot->vMax = 0.2;
     robot->omegaMax = M_PI/4;
     robot->left_motor = 1;
     robot->right_motor = 2;
@@ -82,15 +78,15 @@ int robot_close(Robot_t* robot)
 {
     // Close XBee Reflector Array
     printf("\tClosing XBee Reflector Array...\n");
-    MAIN_ASSERT(xbeeArray_Close(&(robot->array)) == 0, "\tERROR: Failed to close XBee Array.\n");
+    ASSERT(xbeeArray_Close(&(robot->array)) == 0, "\tERROR: Failed to close XBee Array.\n");
 
     // Close the stepper motor
     printf("\tClosing Stepper Motor...\n");
-    MAIN_ASSERT(stepMotor_Cleanup() != -1, "\tERROR: Failed to close Stepper Motor\n");
+    ASSERT(stepMotor_Cleanup() != -1, "\tERROR: Failed to close Stepper Motor\n");
 
     // Close the encoders
     printf("\tClosing Encoders...\n");
-    MAIN_ASSERT(rc_encoder_eqep_cleanup() != -1, "\tERROR: Failed to close Encoders\n");
+    ASSERT(rc_encoder_eqep_cleanup() != -1, "\tERROR: Failed to close Encoders\n");
 
     return 0;
 }
@@ -101,32 +97,12 @@ int robot_close(Robot_t* robot)
 // @param omega: Angular velocity
 int robot_setSpeeds(Robot_t* robot, double v, double omega)
 {
-    // Minimum duty cycle to apply to make sure the robot moves
-    // (does not apply if velocity is 0)
-    static const double minDuty = 0.25;
-    
-    // Velocities below this threshold will be treated as 0
-    static const double threshold = 1E-3;
+    double omegaR = (v - omega*robot->L/2)/robot->R; // right wheel angular speed [rad/s]
[…]

### 2021-04-15 code/MainProgram/MainProgram.c

@@ -229,16 +229,25 @@ int main(){
 
             // Pause measurements until robot is turned to target angle
             MAIN_ASSERT(robot_setSpeeds(&robot, v, omega) == 0, "\tERROR: Failed to set motor speeds\n");
-            int counter = 0;
+
 #if !MOTORS_OFF // Odometry only works if the motors move
-            while (abs(theta - targetAngle) > 0.5 && rc_get_state() != EXITING)
+            double anglediff = fabs(theta - targetAngle);
+            uint64_t lastPrint = rc_nanos_since_boot();
+            uint64_t curTime;
+            while (anglediff > 0.5 && rc_get_state() != EXITING)
             {
                 // Determine the angle of the robot relative to where it was when the last measurement was completed
                 theta = odometry_GetAngle(robot.R, robot.L);
-                if (counter % 40 == 0)
-                    printf("Target angle: %f\t Robot angle: %f\n", targetAngle, theta);
-                
-                ++counter;
+                // Print out every 0.2 seconds
+                curTime = rc_nanos_since_boot();
+                if ( curTime- lastPrint > 200000000ULL)
+                {
+                    // printf("Target angle: %f\t Robot angle: %f\n", targetAngle, theta);
+                    printf("Angle error: %f\n", anglediff);
+                    lastPrint = curTime;
+                }
+
+                anglediff = fabs(theta - targetAngle);
             }
 #endif
 

### 2021-04-15 code/Lib/robot.h
Updated with weighted moving average

@@ -42,7 +42,7 @@ int robot_init(Robot_t* robot)
     // Assign robot variables
     robot->L = 0.199;
     robot->R = 0.0492125;
-    robot->vMax = 0.2;
+    robot->vMax = 0.25;
     robot->omegaMax = M_PI/4;
     robot->left_motor = 1;
     robot->right_motor = 2;

### 2021-04-15 code/MainProgram/MainProgram.c

@@ -37,7 +37,7 @@
 #define STEPS_PER_MEASUREMENT 5
 #define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*STEP_MOTOR_DEG_PER_STEP)
 #define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
-#define MOVING_AVG_SIZE 2 // Size of the moving average window
+#define MOVING_AVG_SIZE 4 // Size of the moving average window
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
@@ -204,9 +204,19 @@ int main(){
             // TODO: Get rid of this once the angle part is working
             targetDistance = 1; 
             
-            // Find the target angle
-            targetAngle = avg_i(angle, MOVING_AVG_SIZE);
+            // Find the target angle (weighted average of the angle array)
+            double weightedSum = 0;
+            double multiplier = 1;
+            double divisor = 0;
+            for (int i = 0; i < MOVING_AVG_SIZE; ++i)
+            {
+                weightedSum += angle[(curMsmt + i)%MOVING_AVG_SIZE]*multiplier;
+                divisor += multiplier;
+                multiplier *= 0.5;
+            }
+            targetAngle = weightedSum/divisor;
             // printf("Angle to remote: %.0f\n", targetAngle);
+
             //Saturate the target angle to avoid turning too fast
             targetAngle = clamp(targetAngle, -maxTargetAngle, maxTargetAngle);
             

### 2021-04-20 code/Lib/robot.h
Main Program Updates From Jason

@@ -46,7 +46,7 @@ int robot_init(Robot_t* robot)
     // Assign robot variables
     robot->L = 0.199;
     robot->R = 0.0492125;
-    robot->vMax = 0.5;
+    robot->vMax = 0.4;
     robot->omegaMax = M_PI/2;
     robot->left_motor = 1;
     robot->right_motor = 2;
@@ -103,7 +103,7 @@ int robot_setSpeeds(Robot_t* robot, double v, double omega)
 {
     // Minimum duty cycle to apply to make sure the robot moves
     // (does not apply if velocity is 0)
-    static const double minDuty = 0.25;
+    static const double minDuty = 0.2;
     
     // Velocities below this threshold will be treated as 0
     static const double threshold = 1E-3;

### 2021-04-20 code/MainProgram/MainProgram.c

@@ -37,7 +37,7 @@
 #define STEPS_PER_MEASUREMENT 5
 #define DEG_PER_MEASUREMENT (int)(STEPS_PER_MEASUREMENT*STEP_MOTOR_DEG_PER_STEP)
 #define NUM_MEASUREMENTS 90/DEG_PER_MEASUREMENT
-#define MOVING_AVG_SIZE 4 // Size of the moving average window
+#define MOVING_AVG_SIZE 2 // Size of the moving average window
 
 // interrupt handler to catch ctrl-c
 static void __signal_handler(__attribute__ ((unused)) int dummy)
@@ -123,7 +123,7 @@ int main(){
     double targetDistance = 0; // Average of distance array in meters
     double targetAngle = 0; // Average of angle array in degrees
     double targetAngle_rad = 0; // Average of angle array in radians
-    double targetX = 0; // Estimated X coordinate of remote w.r.t. robot's local frame
+    // double targetX = 0; // Estimated X coordinate of remote w.r.t. robot's local frame
     // double targetY = 0; // Estimated Y coordinate of remote w.r.t. robot's local frame
     double v = 0; // Desired linear velocity
     double omega = 0; // Desired angular velocity
@@ -224,11 +224,11 @@ int main(){
             targetAngle_rad = targetAngle*M_PI/180;
 
             // Get rectangular coordinates
-            targetX = targetDistance*cos(targetAngle_rad);
+            // targetX = targetDistance*cos(targetAngle_rad);
             // targetY = targetDistance*sin(targetAngle);
 
             // Calculate motor control signals
-            v = sign(targetX)*Kv*targetDistance;
+            v = Kv*targetDistance;
             omega = Kw*targetAngle_rad;
 
             // Reset the encoder positions to 0

### 2021-04-28 parts/20-system_architecture.tex
Final report updates

@@
     \centering
-    \includegraphics[scale=0.9]{figs/system_block_diagram_2}
+    \includegraphics[width=\textwidth]{figs/img/systemBlockDiagram.png}
     \caption{System level block diagram detailing inputs and outputs to the
@@
   \centering
-  \includegraphics[scale=0.9]{figs/remote_target_block_diagram}
+  \includegraphics[width=\textwidth]{figs/img/remoteBlockDiagram.png}
   \caption{Remote Target block diagram}
@@
   \centering
-  \includegraphics[scale=0.82]{figs/mobile_cart_block_diagram}
+  \includegraphics[width=\textwidth]{figs/img/mobileCartBlockDiagram.png}
   \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
@@
       4 & LM1117 Regulator\\
-      2 & Battery Packs for Budget Bot\\
       8 & 9V Batteries\\
@@
 
-\vspace*{12pt}
+\vspace*{6pt}
 \noindent

### 2021-04-28 parts/40-algorithms.tex
Final report updates

@@
 %----------------------------------------------------------------------
-\section{Robot Model}
+\section{Robot Model}\label{sec:robotModel}
 %----------------------------------------------------------------------
-The robot used in this project was a differential drive mobile robot.
+The robot used in this project was a differential drive mobile robot, which has two drive wheels and a caster wheel for balance.
+The robot turns by applying different speeds to the left and right wheels.
+As shown in Fig.
+\ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance between the wheels is $L$.
+The pose of the robot is given by the $x$-coordinate ($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in Fig.
+\ref{fig:robotPose}.
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.3\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figs/img/robotGeometry.png}
+        \caption{Robot Geometry}
+        \label{fig:robotGeometry}
+    \end{subfigure}%
+    \begin{subfigure}{0.7\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figs/img/robotPose.png}
+        \caption{Robot Pose}
+        \label{fig:robotPose}
+    \end{subfigure}
+    \caption{Robot Model Parameters}
+    \label{fig:robotModelParameters}
+\end{figure}
+
+\vspace*{12pt}
+\noindent
+Generally the robot is controlled by commanding a linear and angular speed ($v$ and $\omega$, respectively).
+These speeds must be converted into left and right wheel speeds.
+The following equations are used to calculate the angular left and right wheel speeds ($\omega_l$ and $\omega_r$, respectively):
+$$\omega_l = \left(v - \omega\frac{L}{2}\right)\frac{1}{R}$$
+$$\omega_r = \left(v + \omega\frac{L}{2}\right)\frac{1}{R}$$
+To control DC motors in this way, the relationship between duty cycle and angular speed must be determined.
+Then the duty cycles to apply to the wheels can be calculated for the commanded $v$ and $\omega$.
 
@@
 The localization algorithm is used to estimate the position of the remote with respect to the robot's local coordinate system.
+First the omnidirectional transceiver on top of the reflectors sends a signal strength request to the remote.
+The remote then replies with a message containing the strength of the signal it just received.
+This reply is detected by the receivers inside the reflectors as well as the omnidirectional transceiver.
+The strength detected by each of the directional receivers and the strength contained in the reply are then recorded.
+At this point, the entire reflector array is rotated 9\textdegree, and this process is repeated.
+The robot continues taking measurements in this way until the reflectors have been rotated one quarter turn.
+Since there are four reflectors at 90\textdegree to each other, a strength measurement has been recorded for every 9\textdegree increment around the robot.
+The angle of the remote is then estimated as the direction from which the strongest signal was received.
+The distance to the remote is calculated using the free-space path loss formula.
+The direction of reflector rotation is then reversed since the wires connecting the RF modules in the reflectors prevent the reflector from freely spinning.
+A flowchart of this algorithm is shown in Fig.
+\ref{fig:localizationAlgoFlowchart}.
+\begin{figure}
+    \centering
+    \includegraphics[width=3.5in]{figs/img/localizationAlgoFlowchart.png}
+    \caption{Flowchart of Localization Algorithm}
+    \label{fig:localizationAlgoFlowchart}
+\end{figure}
 
@@
 The navigation algorithm is used to drive the robot toward the remote.
+The inputs to the navigation algorithm are the angle to the remote ($\theta_r$) and the distance to the remote ($d_r$).
+A target point is then calculated as the point that is in the same direction as the remote, but closer to the robot by a fixed following distance ($d_{follow}$), as shown in Fig.
+\ref{fig:navAlgoDiagram}.
+The distance to the target point is calculated as $d_{tgt} = d_r - d_{follow}$, and the angle to the target point is $\theta_{tgt} = \theta_r$.
+The linear and angular speeds of the robot ($v$ and $\omega$, respectively) are then calculated using proportional control by the following equations:
+$$v = K_vd_{tgt}$$
+$$\omega = K_\omega\theta_{tgt}$$
+The appropriate duty cycles are then calculated as specified in section \ref{sec:robotModel} and applied to the wheel motors.
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.95\textwidth]{figs/img/navAlgoDiagram.png}
+        \caption{Target Point Diagram}
+        \label{fig:navAlgoDiagram}
+    \end{subfigure}%
+    \begin{subfigure}{0.55\textwidth}
+        \centering
+        \includegraphics[width=0.95\textwidth]{figs/img/navigationAlgoFlowchart.png}
+        \caption{Flowchart}
+        \label{fig:navAlgoFlowchart}
+    \end{subfigure}
+    \caption{Navigation Algorithm Details}
+    \label{fig:navAlgoDetails}
+\end{figure}
 

### 2021-04-28 parts/20-system_architecture.tex
Update 20-system_architecture.tex

@@
 \ref{fig:sys_block_diag}.
-There are four inputs to the proposed cart system.
+There are three inputs to the proposed cart system.
 The robotic cart is supplied with power through a battery that is mounted in the chassis of the robotic cart.
 There will be an on/off switch to allow the system to be powered down when not in use.
-The motion of the cart is dependent on the motion of the remote.
-A stretch-goal for the project are mode selection buttons that allow the user to put the robotic cart system into different operating modes.
+This will save the battery from being drained by the XBees in the reflector array.
+The motion of the robotic cart is dependent on the motion of the remote.
 
@@
 \noindent
-The main output of the system is the position trajectory of the robotic cart in its environment.
-When the user moves with the remote, the cart is designed to follow the user.
-The other output of the robotic cart system is a status indication in the form of LED lights.
-These lights will be used to notify the user of the status of the robotic cart.
+The main output of the system is the position trajectory of the robotic cart in its environment. When the user moves with the remote target, the robotic cart is designed to follow the user.
 
@@
     \caption{System level block diagram detailing inputs and outputs to the
-      mobile cart system.}
+      robotic cart system.}
 	\label{fig:sys_block_diag}
@@
 Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 7.4V Li-Po battery with a voltage regulation circuit since the XBee has a smaller input voltage of 3.3 volts.
+The two inputs for this system are the battery power and the incoming RF messages which are passed through the RF transceiver Module and output the outgoing RF messages.
 
@@
 \noindent
-The Mobile Cart subsystem block diagram is shown in Fig.
-\ref{fig:mobile_block_diag}.
+The Mobile Cart subsystem block diagram, shown in Fig.
+\ref{fig:mobile_block_diag}, is the most complex of the two subsystems.
 The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue).
 The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart.
-The mode selection buttons for changing the operating mode of the robotic cart is a stretch-goal of the project and will be implemented on the cart if we have time.
-The final input to the mobile cart subsystem is the XBee network messages received from the remote target.
+The final input to the mobile cart subsystem is the incoming RF signals.
+These incoming RF signals are passed to the direction sensitive RF receivers which output the signals to the dual-direction multiplexer which takes the four inputs from the direction sensitive RF receivers and passes one output into the embedded computer.
+Once the embedded computer gets these signals it can calculate the localization and navigation algorithms and pass the information to the DC motors.
 
@@
 \noindent
-There are three outputs of the mobile cart subsystem.
-The first is the wheel velocities that move the cart.
-There will also be LEDs to indicate the status of the system to the user.
-Lastly, the cart will send radio messages to the remote target by means of a parabolic array of XBee radio modules.
+There are two outputs of the mobile cart subsystem.
+The first is the wheel velocities that move the cart and are passed from the DC motors.
+Lastly, the incoming RF signals are passed to our omnidirectional RF transceiver which outputs the outgoing RF signals.
 

### 2021-04-28 parts/20-system_architecture.tex
Update 20-system_architecture.tex

@@
 The final input to the mobile cart subsystem is the incoming RF signals.
-These incoming RF signals are passed to the direction sensitive RF receivers which output the signals to the dual-direction multiplexer which takes the four inputs from the direction sensitive RF receivers and passes one output into the embedded computer.
+These incoming RF signals are passed to the direction sensitive RF receivers which output the signals to the dual-direction multiplexer.
+The dual-direction multiplexer then takes the four inputs from the direction sensitive RF receivers and passes one output into the embedded computer.
 Once the embedded computer gets these signals it can calculate the localization and navigation algorithms and pass the information to the DC motors.

### 2021-05-01 parts/10-introduction.tex
Final report updates
Initial feedback from Dr. Miah

@@
 
+\todo[inline]{Please see the introduction chapter of one of my senior project
+  reports at \url{http://ee.bradley.edu/projects/proj2017/ekf_slam/Downloads/seniorProject_finalReport.pdf}}
+
+\todo[inline]{The idea is to write everything you talked about in your final
+  presentation from slide 5- 11}
+
 %----------------------------------------------------------------------
-\section{Problem Statement}
+\section{Report Organization}
+%----------------------------------------------------------------------
+This report is organized into six chapters:
+\todo[inline]{This section should go at the end of the chapter.}
+
+\begin{itemize}
+    \item Chapter \ref{ch: Chapter1} discusses the background and goals of the project and what other similar projects have accomplished.
+    \item Chapter \ref{ch: Chapter2} explains how the robotic cart system in this project is broken down fundamentally, and the components used to build the robot.
+    \item Chapter \ref{ch: Chapter3} goes over the design of the parabolic reflector arrays and how they were set up on the robot.
+    \item Chapter \ref{ch: Chapter4} provides an explanation of the algorithms that were used to create the code to make the robot move.
+    \item Chapter \ref{ch: Chapter5} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
+    \item Chapter \ref{ch: Chapter6} concludes the project work and discusses future endeavors on this project.
+\end{itemize}
+
+%----------------------------------------------------------------------
+\section{Motivation and Problem Statement}
 %----------------------------------------------------------------------
@@
 One major drawback, however, is that people with disabilities cannot push one cart let alone have a second cart to carry more items.
-Moreover, robots used for this purpose are costlier than they are worth.
+Moreover, robots used for this purpose are more costly than they are worth.
 
@@
 %----------------------------------------------------------------------
+
+\todo[inline]{In this section, include all the figures from the final
+  presentation! You will need to write the explanation of each of the existing 
+  mobile carts (you already talked about it during your presentation)}
+
 Abundant research in the field of mobile robotics shows various ways to develop robotic carts that will help consumers in carrying groceries through stores~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}.
@@
 
-%----------------------------------------------------------------------
-\section{Report Organization}
-%----------------------------------------------------------------------
-This report is organized into six chapters:
-
-\begin{itemize}
-	\item Chapter \ref{ch: Chapter1} discusses the background and goals of the project and what other similar projects have accomplished.
-	\item Chapter \ref{ch: Chapter2} explains how the robotic cart system in this project is broken down fundamentally, and the components used to build the robot.
-	\item Chapter \ref{ch: Chapter3} goes over the design of the parabolic reflector arrays and how they were set up on the robot.
-	\item Chapter \ref{ch: Chapter4} provides an explanation of the algorithms that were used to create the code to make the robot move.
-	\item Chapter \ref{ch: Chapter5} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
-	\item Chapter \ref{ch: Chapter6} concludes the project work and discusses future endeavors on this project.
-\end{itemize}
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "../finalReportMainV1"
+%%% TeX-master: "../finalReport"
 %%% End:

### 2021-05-01 parts/20-system_architecture.tex
Initial feedback from Dr. Miah

@@
 %----------------------------------------------------------------------
-The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target, which is held by the user or customer, as shown in Fig.
-\ref{fig:sys_block_diag}.
-The proposed smart robotic cart is a wheeled robot that sends and receives radio signals to follow the remote target which acts as the beacon for the robotic cart system.
+The overall system architecture of this project consists of two subsystems which
+are the Mobile Cart and the Remote Target, which is held by the user or
+customer, as shown in Fig. \ref{fig:sys_block_diag}. The proposed smart robotic
+cart is a wheeled robot that sends and receives radio signals to follow the
+remote target which acts as the beacon for the robotic cart system. %
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/img/systemBlockDiagram.png}
+  \caption{System level block diagram detailing inputs and outputs to the
+    robotic cart system.}
+	\label{fig:sys_block_diag}
+\end{figure}
+%
 
@@
 
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=\textwidth]{figs/img/systemBlockDiagram.png}
-    \caption{System level block diagram detailing inputs and outputs to the
-      robotic cart system.}
-	\label{fig:sys_block_diag}
-\end{figure}
-
 %----------------------------------------------------------------------
@@
 %----------------------------------------------------------------------
-The Mobile Cart and the Remote Target subsystems are two separate operations within the robotic cart system that run simultaneously.
-The two subsystems communicate with one another by relaying radio messages between them.
-The first block diagram is of the Remote Target subsystem shown in Fig.
-\ref{fig:remote_block_diag}.
-Of the two subsystems the Remote Target is the simplest since it only requires an XBee module attached to a 7.4V Li-Po battery with a voltage regulation circuit since the XBee has a smaller input voltage of 3.3 volts.
-The two inputs for this system are the battery power and the incoming RF messages which are passed through the RF transceiver Module and output the outgoing RF messages.
-
-\begin{figure}[h!]
+The Mobile Cart and the Remote Target subsystems are two separate operations
+within the robotic cart system that run simultaneously. The two subsystems
+communicate with one another by relaying radio messages between them. The first
+block diagram is of the Remote Target subsystem shown in Fig.
+\ref{fig:remote_block_diag}. Of the two subsystems the Remote Target is the
+simplest since it only requires an XBee module attached to a 7.4V Li-Po battery
+with a voltage regulation circuit since the XBee has a smaller input voltage of
+3.3 volts. The two inputs for this system are the battery power and the incoming
+RF messages which are passed through the RF transceiver Module and output the
+outgoing RF messages. %
+%
+\begin{figure}
   \centering
@@
 \end{figure}
+%
 
-\vspace*{12pt}
-\noindent
 The Mobile Cart subsystem block diagram, shown in Fig.
-\ref{fig:mobile_block_diag}, is the most complex of the two subsystems.
-The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the Li-Po works well with powering the embedded computer (BeagleBone Blue).
-The power to the subsystem will be toggled by an on/off switch located on the chassis of the robotic cart.
-The final input to the mobile cart subsystem is the incoming RF signals.
-These incoming RF signals are passed to the direction sensitive RF receivers which output the signals to the dual-direction multiplexer.
-The dual-direction multiplexer then takes the four inputs from the direction sensitive RF receivers and passes one output into the embedded computer.
-Once the embedded computer gets these signals it can calculate the localization and navigation algorithms and pass the information to the DC motors.
+\ref{fig:mobile_block_diag}, is the most complex of the two subsystems. %
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/img/mobileCartBlockDiagram.png}
+  \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
+  \label{fig:mobile_block_diag}
+\end{figure}
+%
+
+The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the
+Li-Po works well with powering the embedded computer (BeagleBone Blue). The
+power to the subsystem will be toggled by an on/off switch located on the
+chassis of the robotic cart. The final input to the mobile cart subsystem is the
+incoming RF signals. These incoming RF signals are passed to the direction
+sensitive RF receivers which output the signals to the dual-direction
+multiplexer. The dual-direction multiplexer then takes the four inputs from the
+direction sensitive RF receivers and passes one output into the embedded
+computer. Once the embedded computer gets these signals it can calculate the
+localization and navigation algorithms and pass the information to the DC
+motors.
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=\textwidth]{figs/img/mobileCartBlockDiagram.png}
-  \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
-  \label{fig:mobile_block_diag}
-\end{figure}
-
 %----------------------------------------------------------------------
@@
 %----------------------------------------------------------------------
+
 There are several components that are required for the mobile cart system.
-Although some of these parts are available in the Bradley University laboratory, other parts must be purchased.
-The parts that exist in the lab are listed in \autoref{tab:Partslablist}.
-Also, Fig.
-\ref{tab:Partslist} shows the list of parts that were purchased.
-The parts compiled in the lists are the required parts needed to build two smart robotic cart systems.
+Although some of these parts are available in the Bradley University laboratory,
+other parts must be purchased. The parts that exist in the lab are listed in
+\autoref{tab:Partslablist}. Also, \autoref{tab:Partslist} shows the list of
+parts that were purchased. The parts compiled in the lists are the required
+parts needed to build two smart robotic cart systems.
 
@@
 \ref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (Fig.
-\ref{fig:beagleboneBlue}), and the XBee S2C Modules (Fig.
-\ref{fig:XBeeModule}).
-Another major component is the reflector array that will be used to directionally receive the RF signals from the remote target that is with the user.
+\ref{fig:beagleboneBlue}), and the XBee S2C Modules (Fig. \ref{fig:XBeeModule}).
+Another major component is the reflector array that will be used to
+directionally receive the RF signals from the remote target that is with the
+user.
 
@@
 The reflector array will be mounted on top of the cart with a stepper motor.
-There are two reflector designs that were evaluated in this project.
-The first, shown in Fig.
-\ref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of the signals that come into the reflector perpendicularly.
-Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array.
-The paraboloidal reflector design may not be able to pick up the signals from the remote as well because of this.
-
-\vspace*{12pt}
-\noindent
-To solve this problem, a combination parabolic/paraboloidal reflector was designed, as shown in Fig.
-\ref{fig:parabolicReflector1}.
-The lower half of this reflector is paraboloidal in shape to limit the signals coming from below.
-The upper part of the reflector is strictly parabolic.
-This shape focuses the signals in the horizontal plane, but allows signals from above to still be received.
-The plan is to construct both of these reflector designs by 3D printing the frames, then lining them with reflective foil tape.
-Both models will then be tested to determine which design works better.
-
-\begin{figure}[h!]
+There are two reflector designs that were evaluated in this project. The first,
+shown in Fig. \ref{fig:parabolodialReflector}, is a paraboloidal reflector which
+maximizes the signal strength of the signals that come into the reflector
+perpendicularly. Since the remote will be carried by the user, it is likely that
+it will be positioned at a higher altitude than the reflector array. The
+paraboloidal reflector design may not be able to pick up the signals from the
+remote as well because of this. %
+%
+%
+\begin{figure}
   \centering
@@
 \end{figure}
+%
+
+To solve this problem, a combination parabolic/paraboloidal reflector was
+designed, as shown in Fig. \ref{fig:parabolicReflector1}. The lower half of this
+reflector is paraboloidal in shape to limit the signals coming from below. The
+upper part of the reflector is strictly parabolic. This shape focuses the
+signals in the horizontal plane, but allows signals from above to still be
+received. The plan is to construct both of these reflector designs by 3D
+printing the frames, then lining them with reflective foil tape. Both models
+will then be tested to determine which design works better.
 

### 2021-05-01 parts/30-customized_parabolic_reflector_array.tex
Final report updates
Initial feedback from Dr. Miah

@@
 %======================================================================
+
+\todo[inline]{Add an introductory paragraph (4/5 sentences maximum). What are
+  you trying to talk about in this chapter, for example}
 
@@
 %----------------------------------------------------------------------
-With the recent advancements in 3D printing technology, it is not difficult to create an object with a parabolic shape.
-In this project, the reflector dishes were created using a 3D printer.
-The reflector array was designed to be modular, where the dishes, top plate, and bottom frame were printed separately.
-After printing, the dishes were lined with foil tape to provide the reflective surface to focus the signals onto the antenna of the XBee.
-A layer of foil tape was also placed on the top plate to provide a ground plane for the XBee.
-The parts were then fastened together using M3 screws and nuts.
+With the recent advancements in 3D printing technology, it is not difficult to
+create an object with a parabolic shape. In this project, the reflector dishes
+were created using a 3D printer. The reflector array was designed to be modular,
+where the dishes, top plate, and bottom frame were printed separately. After
+printing, the dishes were lined with foil tape to provide the reflective surface
+to focus the signals onto the antenna of the XBee. A layer of foil tape was also
+placed on the top plate to provide a ground plane for the XBee. The parts were
+then fastened together using M3 screws and nuts (Fig.
+\ref{fig:reflectorConstruction}).
+%
+\begin{figure}
+    \centering
+    \includegraphics[width=3.5in]{figs/img/reflectorConstruction.jpg}
+    \caption{Reflector Construction}
+    \label{fig:reflectorConstruction}
+\end{figure}
 

### 2021-05-01 parts/40-algorithms.tex
Initial feedback from Dr. Miah

@@
 %======================================================================
-\chapter{Algorithms}
+\chapter{Localization and Navigation}
 \label{ch: Chapter4}
 %======================================================================
+
+\todo[inline]{Add an introductory paragraph. For example, ``In this Chapter, we
+  illustrate localization and navigation algorithms for the mobile cart to operate in an
+  indoor/outdoor environment. For that, we first model the proposed robotic cart
+  as a differential drive mobile robot (DDMR). The position of the cart is then
+  determined using a localization algorithm. $\ldots$''}
 
@@
 %----------------------------------------------------------------------
-The robot used in this project was a differential drive mobile robot, which has two drive wheels and a caster wheel for balance.
-The robot turns by applying different speeds to the left and right wheels.
-As shown in Fig.
-\ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance between the wheels is $L$.
-The pose of the robot is given by the $x$-coordinate ($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in Fig.
-\ref{fig:robotPose}.
+The robot used in this project was a differential drive mobile robot, which has
+two drive wheels and a caster wheel for balance. The robot turns by applying
+different speeds to the left and right wheels. As shown in Fig.
+\ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance
+between the wheels is $L$. The pose of the robot is given by the $x$-coordinate
+($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in
+Fig. \ref{fig:robotPose}. %
+%
 \begin{figure}
@@
 \end{figure}
+%
 
-\vspace*{12pt}
-\noindent
 Generally the robot is controlled by commanding a linear and angular speed ($v$ and $\omega$, respectively).

### 2021-05-01 parts/10-introduction.tex
Update 10-introduction.tex

--- 2021-04-13 parts/10-introduction.tex
@@
 %----------------------------------------------------------------------
-\section{Problem Statement}
+\section{Motivation and Problem Statement}
 %----------------------------------------------------------------------
@@
 \noindent
-One such method that has been utilized to make a cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}.
-Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
-Therein, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.
+One such method, shown in Fig.
+\ref{fig:CompaRob}, that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}.
+Another method, shown in Fig.
+\ref{fig:ShoppingSup}, that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
+Therein, in Fig.
+\ref{fig:SmartCart}, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.
+
+\begin{figure}[b]
+   \centering
+   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
+   \caption{CompaRob Robot}
+   \label{fig:CompaRob}
+\end{figure}
+
+\begin{figure}[b]
+   \centering
+   \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
+   \caption{Shopping Support Robot}
+   \label{fig:ShoppingSup}
+\end{figure}
+
+\begin{figure}[b]
+   \centering
+   \includegraphics[width=0.45\textwidth]{figs/img/SmartCart}
+   \caption{Smart Cart Robot}
+   \label{fig:SmartCart}
+\end{figure}
 
@@
 This report is organized into six chapters:
+\todo[inline]{This section should go at the end of the chapter.}
 

### 2021-05-02 parts/50-implementation.tex
Initial feedback from Dr. Miah
Updated Final Report

@@
 
+For this project we needed a Remote Target and Smart Robotic Cart that we designed and implemented from off the shelf components.
+As mentioned above in \autoref{sec:System Components} some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslablist}.\par
+Since the school already owned the Budget Bot chassis, we opted to use these base cart chassis frames to build our Smart Robotic Cart upon.
+The base Budget Bot chassis did need to be modified slightly to work with our project.
+The main change was that we swapped out the motors that came with the Budget Bot for Pololu 27D Meatal Gear motors since the original motors spin at max speed is 212 RPM or 1.09m/s and the new motors max speed is 530 RPM or 2.72m/s when using the base wheels that have a diameter of 98mm.
+By switching out the motors we are able to achieve our goal of  matching an average person's walking speed of 1.5m/s since the build in motors can not achieve this.
+The other modifications to the chassis are that a hard power switch was added to directly cut off power to the XBee modules in the reflector as well as a power indicator LED.
+\par
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figs/img/Finalized_robot.png}
+	\caption{Final Version of the Robotic Cart}
+ 	\label{fig:FinalizedRobot}
+\end{figure}
+
+As can be seen in \autoref{fig:FinalizedRobot} our next step was to attach the Beagle Bone Blue microcomputer, XBee reflector array assembly, and breadboard to the top of the robot.
+We also installed a 2-cell LiPo battery inside the body of the mobile cart that delivers power to the Beagle Bone Blue directly and power to the breadboard through the switch.
+\par
+The power supplied to the breadboard is sent through a regulator circuit to drop it down from 7.4v from the LiPo to 3.3v.
+This same circuit also is used on the remote which consists only of a 9v battery and the XBee module with this voltage regulator in between.
+This voltage regulator is build out of a LM117 regulator and a 10uF ceramic capacitor between the input and output pins of the regulator as shown in \autoref{fig:PowerConverter}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figs/img/PowerConverter.png}
+	\caption{Final Version of the Robotic Cart}
+ 	\label{fig:PowerConverter}
+\end{figure}
+
+The Reflector array assembly from \autoref{ch: Chapter3} was mounted on a stepper motor that was then attached to the robot chasse using a 3D printed bracket.
+This bracket was the attached to the chasse using bolts.
+Another feature of this bracket is that it had a stop block built into the top of it that is used to automatically zero the reflector array when the robot starts up.\par
+The Xbee modules from the reflector posed a bit of a problem when it came to connecting them to the Beagle Bone Blue.
+This problem comes from that the Beagle Bone Blue has five UART ports if we are using the one found in the USB and the UART-GPS along with the three normal UART ports.
+This unfortunately dose not work though since UART port zero is tied to the council used to communicate with it from a computer.
+Since this port is reserved for this function that reduces the number of usable ports down to four which does not work since we have five XBees in it.
+Our solution to this was to use two of the GPIO pins, two of the UART ports, and a two-way multiplexer.
+With this setup we can directly connect one of the UARTs to the top XBee and then rout the other four side XBee modules through the MUX so only one UART port is needed for them.
+
 %----------------------------------------------------------------------
-\section{Code Trial and Implementation}
+\section{Code Base}
+%----------------------------------------------------------------------
+
+\todo[inline]{Please complete this section}
+
+%----------------------------------------------------------------------
+\section{Algorithm Testing}
 %----------------------------------------------------------------------
@@
 
+\todo[inline]{See page 23 of~\url{http://ee.bradley.edu/projects/proj2017/ekf_slam/Downloads/seniorProject_finalReport.pdf}}
+
+\section{Simulation using Robot Simulator}
+
+\todo[inline]{In this section, we detail the steps of simulating the proposed
+  robotic cart using a commercial robot simulator CoppeliaSim. $\ldots \ldots$}
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "../finalReportMainV1"
+%%% TeX-master: "../finalReport"
 %%% End:

### 2021-05-02 parts/50-implementation.tex
updated final report

@@
 
-\todo[inline]{Please complete this section}
+For the project we needed some base functionality to use with the main follower program so it can interact with the other components in the system.
+The Beagle Bone Blue already has a set of ports on it that we can access and control using the Robot Control Library from Strawson Design for the beagle bone blue ~\cite{Robot_Control_Library}.
+\par
+For the project we also build some custom libraries on top of the Robot Control Library to hand XBee Frames, AT Commands, and the stepper motor.
+The XBee frames library takes a given block of data containing our message and then packages it into a XBee Frame to send over UART to the XBee module we want to interact with.
+The XBee communications library also handles received messages from the XBee module and validates the received frames integrity and extracts the message data from it.
+On top of the XBee communications library we also have a library that generates AT Commands to package in the XBee Frames.
+The AT Command library also handles extracting response data from the AT Response Command structure and validating it.\par
+The final custom library is the stepper motor control library.
+This library had to be written ourselves since instead of using a dedicated stepper motor controller for our project we were using two of the regular DC motor control ports that are build into the Beagle Bone Blue.
+This library handled translating how many steps to turn into proper cycling of the DC motor ports to get the stepper motor to move the desired distance.
+The library also helped to keep track of basic information related to the stepper motor such as what its current angel should be.
 

### 2021-05-02 parts/50-implementation.tex
Updated Chapter 5

@@
 
+For the Implementation of this project we had to start mostly from scratch since this was a new project for Bradley and not inherited.
+The main starting point is that there have bean senior project in the past that used XBees to get signal strength as well but past that there is very little overlap between them.
+So for this project we had to first build a robot and a remote to use for testing.
+Then we had to build code base to control the mobile robot that we then implement our test algorithms with.
+
 %----------------------------------------------------------------------
 \section{Robot Assembly}
+\label{sec:Robot Assembly}
 %----------------------------------------------------------------------
@@
 \section{Code Base}
+\label{sec:Code Base}
 %----------------------------------------------------------------------
@@
 On top of the XBee communications library we also have a library that generates AT Commands to package in the XBee Frames.
-The AT Command library also handles extracting response data from the AT Response Command structure and validating it.\par
+The AT Command library also handles extracting response data from the AT Response Command structure and validating it.
+
+\begin{figure} [b]
+  \centering
+  \includegraphics[width=\textwidth]{figs/img/Command Process Diagram.png}
+  \caption{Process for XBee Communication over UART}
+  \label{fig:CommandProcessDiagram}
+\end{figure}
+
 The final custom library is the stepper motor control library.
@@
 %----------------------------------------------------------------------
-\section{Algorithm Testing}
+\section{Experimental Results}
+\label{sec:Experimental Results}
 %----------------------------------------------------------------------
 
-%----------------------------------------------------------------------
-\section{Experimental Results}
-%----------------------------------------------------------------------
+In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in \autoref{ch: Chapter4}.
+There were two main types of variants we put together, one type the stepper motor is locked preventing the reflector from turning and in the other we use the stepper motor to sweep through a set of angles.
 
-\todo[inline]{See page 23 of~\url{http://ee.bradley.edu/projects/proj2017/ekf_slam/Downloads/seniorProject_finalReport.pdf}}
+\subsection{Rotating Reflector Tests}
+
+The first type of test we ran was where the robot would zero out the arrays rotation with the stepper motor then move in nine degree increments taking measurements as it went.
+A sweep ends when the motor has turned 81 degrees since at that point with the fore sides of the reflector a full 360 degrees has bean scanned.\par
+This method offers us a sufficiently dense set of data to base our angle predictions off of but at the cost of having to wait until a entire sweep is completed.
+With this data we first put together a simple test that would continuously be sweeping and moving at the same time.
+Though this version did successful follow the remote it was incredibly unstable.
+The result of this instability was that the robot would most of the time correctly turn towards the remote and then start moving towards it but as it went it would slowly pick up a osculation in its movement until the wobble got to great and it would drive off in a random direction then find its way back into alignment and resume moving towards the remote.\par
+The next version that used a rotating reflector as well as the final version works mostly the same as the first version but with some improvements to its navigation.
+The first big fix is that we determined that the result of the osculation we were seeing in the first test was a result of turning while also rotating the reflector which would add additional rotation to the measurements in global scope.
+Do to how are robot is designed we can only rotate the reflector array 90 degrees but to properly fix this rotation issue we would need to rotate the reflector more or less during a sweep to compensate for the robots rotation.
+Our compromise was simply to allow the robot to always move forward but to alternate between rotating the reflector and getting a measurement and then rotating the robot based on that measurement.
+In this version we also added some additional windowed filters to average out the angle measurements which did help to reduce the effects of random angles from noise in the system.
+We also applied offsets to each of the directional receivers revived signal strengths based of of data that we had collected while testing it when we noticed that each side had a different minimum that it would cap out at.
+
+\subsection{Locked Reflector Tests}
+
+The locked reflector test were some tests that we ran in between our first sweeping algorithm and our final algorithm which ultimately used sweeping.
+These algorithms were an attempt to reduce the time needed to get a set of measurements from the reflector by zeroing its rotation and then keeping it locked in the zeroed position.
+Since the data from this is relatively sparse we tried three different ways to fill in the gaps in the data from only the four cardinal directions.
+The first of these three methods was to try and select a strongest direction that the signal was coming from and then witch of its two neighbor directions had the next strongest signal.
+With these two strengths the algorithm would then try to interpolate between these two angles based on difference of the strength between them.
+This method probably can work but in our implementation we ran out of time to try and tune it since it would take a fairly large amount of data to be collected to try and tune it in.\par
+The other two methods that we tried with the locked reflector were both different variants on machine learning based on a small poll of data we had collected.
+The first algorithm tested was K Nearest Neighbors then followed up by a Neural Network for our final fixed rotation test.
+Both of these algorithms failed to produce any meaningful results.
+This would appear to be due to the fact that we had a very small pool of data to work off compared to usual attempts to use machine learning.
+They also with the small data pool size did not cope particularly well with the noise in the signal.
+
+\subsection{System noise}
+
+In both our fixed and seeping experiments a underlying issue is the amount of noise our system produces.
+The first type of noise that occurs is noise from the Multipath Effect where the signals bounce off of obsticals around it adding constructing and destructive interference randomly based off of the robots surroundings.
+The second noise was from internal noise in the XBees which was worse that we had expected.
+We to some degree managed to isolate the XBee internal noise by using an anecoic chamber where we did see all the signals strengths become stronger but the base noise from the XBees persisted.
+The noise coming from the XBees tends to be about 2 to 6 dBm around the average and the change from facing towards to away from the remote is about 13 to 15 dBm.
+This ranges result in the occasional measurement that flip flops which reflector is actually facing the remote.
+The noise can be seen in our test measurements we collected where we at set rotations record a burst of 300 measurements as seen inf \autoref{fig:SensorDataGraphs}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.50\textwidth}
+        \centering
+        \includegraphics[width=0.95\textwidth]{figs/img/Side1_Data.png}
+        \label{fig:Side1Dat}
+    \end{subfigure}%
+    \begin{subfigure}{0.50\textwidth}
+        \centering
+        \includegraphics[width=0.95\textwidth]{figs/img/Side2_Data.png}
+        \label{fig:Side2Dat}
+    \end{subfigure}
+        \begin{subfigure}{0.50\textwidth}
+        \centering
+        \includegraphics[width=0.95\textwidth]{figs/img/Side3_Data.png}
+        \label{fig:Side3Dat}
+    \end{subfigure}%
+    \begin{subfigure}{0.50\textwidth}
+        \centering
+        \includegraphics[width=0.95\textwidth]{figs/img/Side4_Data.png}
+        \label{fig:Side4Dat}
+    \end{subfigure}
+    \caption{Navigation Algorithm Details}
+    \label{fig:SensorDataGraphs}
+\end{figure}
+
+\subsection{Distance}
+
+\todo[inline]{Was going back over this and realized I should add this section in will do later don't have time at this exact moment. -Darrah}
+
+[Uhhh what?]
+\todo[inline]{What am I looking at on page 23 exactly? -Darrah}
+\todo[inline]{See page 23 of~\url{http://ee.bradley.edu/projects/proj2017/ekf_slam/Downloads/seniorProject_finalReport.pdf} -Dr. Miah}
 
@@
 
+\todo[inline]{Jason can you write something up on this?
+not sure exactly what you did there or if you just want me to say the bear bones about it based on the video?
+also I know Miah put it down hear but should it be in chapter 4 since its more a test of the pure algorithm than of the actual robot?
+-Darrah}
 \todo[inline]{In this section, we detail the steps of simulating the proposed
-  robotic cart using a commercial robot simulator CoppeliaSim. $\ldots \ldots$}
+  robotic cart using a commercial robot simulator CoppeliaSim. $\ldots \ldots$ -Dr. Miah}
 

### 2021-05-03 parts/40-algorithms.tex
Updates to final report based on feedback from Dr. Miah

--- 2021-04-28 parts/40-algorithms.tex
@@
 %======================================================================
-\chapter{Algorithms}
+\chapter{Localization and Navigation}
 \label{ch: Chapter4}
 %======================================================================
+
+This chapter illustrates the localization and navigation algorithms for the mobile cart to operate in an indoor/outdoor environment.
+The proposed robotic cart was modeled as a differential drive mobile robot (DDMR).
+The direction and distance of the remote relative to the cart are determined using a localization algorithm.
+This distance and angle are then passed to a navigation algorithm which calculates and applies the wheel speeds to move the robot toward the remote.
 

### 2021-05-03 parts/50-implementation.tex
Added CoppeliaSim section and appendix

@@
 For this project we needed a Remote Target and Smart Robotic Cart that we designed and implemented from off the shelf components.
-As mentioned above in \autoref{sec:System Components} some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslablist}.\par
+As mentioned above in \autoref{sec:System Components} some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslablist}.
+
+\vspace*{12pt}
+\noindent
 Since the school already owned the Budget Bot chassis, we opted to use these base cart chassis frames to build our Smart Robotic Cart upon.
@@
 The other modifications to the chassis are that a hard power switch was added to directly cut off power to the XBee modules in the reflector as well as a power indicator LED.
-\par
 
@@
 
+\vspace*{12pt}
+\noindent
 As can be seen in \autoref{fig:FinalizedRobot} our next step was to attach the Beagle Bone Blue microcomputer, XBee reflector array assembly, and breadboard to the top of the robot.
@@
 
+\vspace*{12pt}
+\noindent
 The Reflector array assembly from \autoref{ch: Chapter3} was mounted on a stepper motor that was then attached to the robot chasse using a 3D printed bracket.
 This bracket was the attached to the chasse using bolts.
-Another feature of this bracket is that it had a stop block built into the top of it that is used to automatically zero the reflector array when the robot starts up.\par
+Another feature of this bracket is that it had a stop block built into the top of it that is used to automatically zero the reflector array when the robot starts up.
+
+\vspace*{12pt}
+\noindent
 The Xbee modules from the reflector posed a bit of a problem when it came to connecting them to the Beagle Bone Blue.
@@
 The Beagle Bone Blue already has a set of ports on it that we can access and control using the Robot Control Library from Strawson Design for the beagle bone blue ~\cite{Robot_Control_Library}.
-\par
+
+\vspace*{12pt}
+\noindent
 For the project we also build some custom libraries on top of the Robot Control Library to hand XBee Frames, AT Commands, and the stepper motor.
@@
 
+\vspace*{12pt}
+\noindent
 The final custom library is the stepper motor control library.
@@
 The first type of test we ran was where the robot would zero out the arrays rotation with the stepper motor then move in nine degree increments taking measurements as it went.
-A sweep ends when the motor has turned 81 degrees since at that point with the fore sides of the reflector a full 360 degrees has bean scanned.\par
+A sweep ends when the motor has turned 81 degrees since at that point with the fore sides of the reflector a full 360 degrees has bean scanned.
+
+\vspace*{12pt}
+\noindent
 This method offers us a sufficiently dense set of data to base our angle predictions off of but at the cost of having to wait until a entire sweep is completed.
@@
 Though this version did successful follow the remote it was incredibly unstable.
-The result of this instability was that the robot would most of the time correctly turn towards the remote and then start moving towards it but as it went it would slowly pick up a osculation in its movement until the wobble got to great and it would drive off in a random direction then find its way back into alignment and resume moving towards the remote.\par
+The result of this instability was that the robot would most of the time correctly turn towards the remote and then start moving towards it but as it went it would slowly pick up a osculation in its movement until the wobble got to great and it would drive off in a random direction then find its way back into alignment and resume moving towards the remote.
+
+\vspace*{12pt}
+\noindent
 The next version that used a rotating reflector as well as the final version works mostly the same as the first version but with some improvements to its navigation.
@@
 With these two strengths the algorithm would then try to interpolate between these two angles based on difference of the strength between them.
-This method probably can work but in our implementation we ran out of time to try and tune it since it would take a fairly large amount of data to be collected to try and tune it in.\par
+This method probably can work but in our implementation we ran out of time to try and tune it since it would take a fairly large amount of data to be collected to try and tune it in.
+
+\vspace*{12pt}
+\noindent
 The other two methods that we tried with the locked reflector were both different variants on machine learning based on a small poll of data we had collected.
@@
 This ranges result in the occasional measurement that flip flops which reflector is actually facing the remote.
-The noise can be seen in our test measurements we collected where we at set rotations record a burst of 300 measurements as seen inf \autoref{fig:SensorDataGraphs}
+The noise can be seen in our test measurements we collected where we at set rotations record a burst of 300 measurements as seen in \autoref{fig:SensorDataGraphs}
 
@@
 
-\todo[inline]{Jason can you write something up on this?
-not sure exactly what you did there or if you just want me to say the bear bones about it based on the video?
-also I know Miah put it down hear but should it be in chapter 4 since its more a test of the pure algorithm than of the actual robot?
--Darrah}
-\todo[inline]{In this section, we detail the steps of simulating the proposed
-  robotic cart using a commercial robot simulator CoppeliaSim. $\ldots \ldots$ -Dr. Miah}
+Before constructing the physical robot prototype, a simulation was performed using a commercial robot simulator CoppeliaSim.
+However, since RF signal behavior depends highly on the environment, the system could not be fully simulated.
+This section explains the steps taken to simulate the proposed robotic cart.
+
+\vspace*{12pt}
+\noindent
+First, a model of the Budget Bot chassis was created in CoppeliaSim.
+The model is shown in Fig.
+\ref{fig:budgetBotModel}.
+The model was designed with the same dimensions as the physical chassis to accurately simulate the robot kinematics.
+Details on modeling a robot chassis in CoppeliaSim can be found in \autoref{ch:coppSimModeling}.
+Although \autoref{ch:coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\textwidth]{figs/img/budgetBotModel.png}
+    \caption{Model of Budget Bot Chassis}
+    \label{fig:budgetBotModel}
+\end{figure}
+
+\vspace*{12pt}
+\noindent
+MATLAB code was written to control the simulation.
+The actual distance between the robot and the remote was measured, then random noise was added with a mean of 0 and a standard deviation of 0.07.
+This noisy measurement was then used in the navigation algorithm to determine how to drive the robot (see \autoref{sec:navAlgo}).
+An image of the simulation is shown in Fig.
+\ref{fig:coppSimExample}, where the blue sphere represents the remote, and the green dot represents the target point.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/img/coppSimExample.png}
+    \caption{CoppeliaSim Simulation}
+    \label{fig:coppSimExample}
+\end{figure}
 

### 2021-05-03 parts/A-coppSimModeling.tex
Added CoppeliaSim section and appendix

@@
 \chapter{Modeling in CoppeliaSim}
-\label{ch:Chapter1}
+\label{ch:coppSimModeling}
 %======================================================================
@@
 The Runt Rover robot is geometrically simple, with only a few dimensions being necessary to model the shape of the body and wheels.
-The dimensions used in this guide are shown in \autoref{fig:runtRoverDims}
+The dimensions used in this guide are shown in Fig.
+\ref{fig:runtRoverDims}
 
@@
 
-The final 3D models are shown in \autoref{fig:runtRoverModels}. An arrow was placed on the body to indicate orientation during simulation.
+The final 3D models are shown in Fig. \ref{fig:runtRoverModels}. An arrow was placed on the body to indicate orientation during simulation.
 
@@
 %----------------------------------------------------------------------
-To save this model, go to File \textgreater Save model as \textgreater CoppeliaSim model.
+To save this model, go to File \textgreater \ Save model as \textgreater \ CoppeliaSim model.
 The default location should be in the CoppeliaSim models directory.

### 2021-05-04 parts/20-system_architecture.tex
Updated Final Report
Added CoppeliaSim section and appendix
Update 20-system_architecture.tex

@@
 cart is a wheeled robot that sends and receives radio signals to follow the
-remote target which acts as the beacon for the robotic cart system. %
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/img/systemBlockDiagram.png}
-  \caption{System level block diagram detailing inputs and outputs to the
-    robotic cart system.}
-	\label{fig:sys_block_diag}
-\end{figure}
-%
+remote target which acts as the beacon for the robotic cart system.
 
@@
 The motion of the robotic cart is dependent on the motion of the remote.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{figs/img/systemBlockDiagram.png}
+  \caption{System level block diagram detailing inputs and outputs to the
+    robotic cart system.}
+	\label{fig:sys_block_diag}
+\end{figure}
 
@@
 RF messages which are passed through the RF transceiver Module and output the
-outgoing RF messages. %
-%
-\begin{figure}
+outgoing RF messages.
+
+\begin{figure}[H]
   \centering
@@
 \end{figure}
-%
 
+\vspace*{12pt}
+\noindent
 The Mobile Cart subsystem block diagram, shown in Fig.
-\ref{fig:mobile_block_diag}, is the most complex of the two subsystems. %
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/img/mobileCartBlockDiagram.png}
-  \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
-  \label{fig:mobile_block_diag}
-\end{figure}
-%
-
-The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the
+\ref{fig:mobile_block_diag}, is the most complex of the two subsystems.The cart requires a power source, which will be a 7.4V, 8,000 mAh Li-Po battery since the
 Li-Po works well with powering the embedded computer (BeagleBone Blue). The
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{figs/img/mobileCartBlockDiagram.png}
+  \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
+  \label{fig:mobile_block_diag}
+\end{figure}
+
 \vspace*{12pt}
@@
 \section{System Components}
+\label{sec:System Components}
 %----------------------------------------------------------------------
@@
   \centering
-  \begin{minipage}[t]{0.32\textwidth}
+  \begin{minipage}[H]{0.32\textwidth}
     \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
@@
   \end{minipage}%
-  \begin{minipage}[t]{0.32\textwidth}
+  \begin{minipage}[H]{0.32\textwidth}
     \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
@@
   \end{minipage}
-  \begin{minipage}[t]{0.32\textwidth}
+  \begin{minipage}[H]{0.32\textwidth}
     \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
@@
   \centering
-  \begin{minipage}[t]{0.5\textwidth}
+  \begin{minipage}[H]{0.5\textwidth}
     \centering
@@
   \end{minipage}
-  \begin{minipage}[t]{0.4\textwidth}
+  \begin{minipage}[H]{0.4\textwidth}
     \centering
@@
 %
-
 To solve this problem, a combination parabolic/paraboloidal reflector was
@@
 
-\subsection{Operation of Robotic Cart System}
+%----------------------------------------------------------------------
+\section{Operation of Robotic Cart System}
+\label{sec:Operation of Robotic Cart System}
+%----------------------------------------------------------------------
 The mobile cart was controlled by a central embedded computer which is the BeagleBone Blue since it is ideal in robotics control.

### 2021-05-04 parts/50-implementation.tex
Update 50-implementation.tex

@@
 
-For the Implementation of this project we had to start mostly from scratch since this was a new project for Bradley and not inherited.
-The main starting point is that there have bean senior project in the past that used XBees to get signal strength as well but past that there is very little overlap between them.
-So for this project we had to first build a robot and a remote to use for testing.
-Then we had to build code base to control the mobile robot that we then implement our test algorithms with.
+For the implementation of this project we had to start from scratch since this was a new project concept introduced by our advisor Dr.
+Miah.
+There have been senior projects in the past that have used XBees to get signal strength but there is very little overlap between these projects to substantiate where our project needed to start from.
+For this project we had to first build a mobile robot and a remote to use for testing.
+We then had to build a code base to control the mobile robot that was then implemented with our test algorithms.
 
@@
 For this project we needed a Remote Target and Smart Robotic Cart that we designed and implemented from off the shelf components.
-As mentioned above in \autoref{sec:System Components} some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslablist}.
+As mentioned above in section \ref{sec:System Components} some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslist}.
 
@@
 \noindent
-Since the school already owned the Budget Bot chassis, we opted to use these base cart chassis frames to build our Smart Robotic Cart upon.
-The base Budget Bot chassis did need to be modified slightly to work with our project.
-The main change was that we swapped out the motors that came with the Budget Bot for Pololu 27D Meatal Gear motors since the original motors spin at max speed is 212 RPM or 1.09m/s and the new motors max speed is 530 RPM or 2.72m/s when using the base wheels that have a diameter of 98mm.
-By switching out the motors we are able to achieve our goal of  matching an average person's walking speed of 1.5m/s since the build in motors can not achieve this.
-The other modifications to the chassis are that a hard power switch was added to directly cut off power to the XBee modules in the reflector as well as a power indicator LED.
+Since the school already owned the Budget Bot chassis, we decided to build our Smart Robotic Cart with them.
+The Budget Bot chassis needed to be modified slightly to work with our project.
+The main change we made was swapping out the motors that came with the Budget Bot for Pololu 27D Meatal Gear motors since the original motors have a max speed of 212 RPM or 1.09m/s and the new motors have a max speed of 530 RPM or 2.72m/s when using the wheels with a diameter of 98mm.
+By switching out the motors we are able to achieve our goal of matching an average person's walking speed of 1.5m/s.
+The other modifications to the chassis are a hard power switch to directly cut off power to the XBee modules in the reflector and a power indicator LED to let us know when this switch was on.
 
-\begin{figure}
+\vspace*{12pt}
+\noindent
+As shown in Fig.
+\ref{fig:FinalizedRobot}, our next step was to attach the BeagleBone Blue microcomputer, XBee reflector array assembly, and breadboard to the top of the robot.
+We also installed a 2-cell LiPo battery inside the chassis of the mobile cart that delivers power to the BeagleBone Blue directly and the breadboard through the switch.
+\par
+
+\begin{figure}[H]
 	\centering
@@
 
-\vspace*{12pt}
-\noindent
-As can be seen in \autoref{fig:FinalizedRobot} our next step was to attach the Beagle Bone Blue microcomputer, XBee reflector array assembly, and breadboard to the top of the robot.
-We also installed a 2-cell LiPo battery inside the body of the mobile cart that delivers power to the Beagle Bone Blue directly and power to the breadboard through the switch.
-\par
-The power supplied to the breadboard is sent through a regulator circuit to drop it down from 7.4v from the LiPo to 3.3v.
-This same circuit also is used on the remote which consists only of a 9v battery and the XBee module with this voltage regulator in between.
-This voltage regulator is build out of a LM117 regulator and a 10uF ceramic capacitor between the input and output pins of the regulator as shown in \autoref{fig:PowerConverter}.
+The power supplied to the breadboard is sent through a regulator circuit to drop it down from the 7.4V of the LiPo to 3.3V of the XBee.
+This circuit is also used on the remote which consists of a 7.4V LiPo battery and the XBee module with voltage regulator in between.
+This voltage regulator is built out of a LM117 regulator and a 10uF ceramic capacitor between the input and output pins of the regulator as shown in Fig.
+\ref{fig:PowerConverter}.
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 \noindent
-The Reflector array assembly from \autoref{ch: Chapter3} was mounted on a stepper motor that was then attached to the robot chasse using a 3D printed bracket.
-This bracket was the attached to the chasse using bolts.
-Another feature of this bracket is that it had a stop block built into the top of it that is used to automatically zero the reflector array when the robot starts up.
+The Reflector array assembly from Chapter \ref{ch: Chapter3} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket.
+This bracket was then attached to the chassis using bolts.
+Another feature of this bracket is that it had a stop block built into the top of it to automatically zero the reflector array when the robot starts up.
 
@@
 \noindent
-The Xbee modules from the reflector posed a bit of a problem when it came to connecting them to the Beagle Bone Blue.
-This problem comes from that the Beagle Bone Blue has five UART ports if we are using the one found in the USB and the UART-GPS along with the three normal UART ports.
-This unfortunately dose not work though since UART port zero is tied to the council used to communicate with it from a computer.
-Since this port is reserved for this function that reduces the number of usable ports down to four which does not work since we have five XBees in it.
+The Xbee modules from the reflector array posed a bit of a problem when it came to connecting them to the BeagleBone Blue.
+This problem comes from that the BeagleBone Blue has five UART ports if we are using the one found in the USB and the UART-GPS along with the three normal UART ports.\todo[inline]{This sentence needs to be revised.
+-Kalli}.
+This does not work since UART port zero is tied to the council used to communicate with it from a computer.
+Since this port is reserved for this function that reduces the number of usable ports down to four and we need to have five XBees in these ports.
 Our solution to this was to use two of the GPIO pins, two of the UART ports, and a two-way multiplexer.
@@
 For the project we needed some base functionality to use with the main follower program so it can interact with the other components in the system.
-The Beagle Bone Blue already has a set of ports on it that we can access and control using the Robot Control Library from Strawson Design for the beagle bone blue ~\cite{Robot_Control_Library}.
+The BeagleBone Blue already has a set of ports on it that we can access and control using the Robot Control Library from Strawson Design ~\cite{Robot_Control_Library}.
 
@@
 \noindent
-For the project we also build some custom libraries on top of the Robot Control Library to hand XBee Frames, AT Commands, and the stepper motor.
-The XBee frames library takes a given block of data containing our message and then packages it into a XBee Frame to send over UART to the XBee module we want to interact with.
+For the project we also built some custom libraries on top of the Robot Control Library to handle XBee Frames, AT Commands, and the stepper motor.
+The XBee Frames library takes a given block of data containing our message and then packages it into a XBee Frame to send over UART to the XBee module we want to interact with.
 The XBee communications library also handles received messages from the XBee module and validates the received frames integrity and extracts the message data from it.
 On top of the XBee communications library we also have a library that generates AT Commands to package in the XBee Frames.
-The AT Command library also handles extracting response data from the AT Response Command structure and validating it.
+The AT Command library also handles extracting response data from the AT Response Command structure and validates it.
 
-\begin{figure} [b]
+\begin{figure}[H]
   \centering
@@
 The final custom library is the stepper motor control library.
-This library had to be written ourselves since instead of using a dedicated stepper motor controller for our project we were using two of the regular DC motor control ports that are build into the Beagle Bone Blue.
-This library handled translating how many steps to turn into proper cycling of the DC motor ports to get the stepper motor to move the desired distance.
-The library also helped to keep track of basic information related to the stepper motor such as what its current angel should be.
+This library had to be written ourselves since instead of using a dedicated stepper motor controller for our project we were using two of the regular DC motor control ports that are build into the BeagleBone Blue.
+The library handled translating how many steps to turn into proper cycling of the DC motor ports to get the stepper motor to move the desired distance.
+\todo[inline]{This sentence needs to be revised since it makes no sense.
+-Kalli}.
+The library also helped to keep track of basic information related to the stepper motor such as what its current angle should be.
 
@@
 
-In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in \autoref{ch: Chapter4}.
+In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in Chapter \ref{ch: Chapter4}.
 There were two main types of variants we put together, one type the stepper motor is locked preventing the reflector from turning and in the other we use the stepper motor to sweep through a set of angles.
@@
 The first type of test we ran was where the robot would zero out the arrays rotation with the stepper motor then move in nine degree increments taking measurements as it went.
-A sweep ends when the motor has turned 81 degrees since at that point with the fore sides of the reflector a full 360 degrees has bean scanned.
+A sweep ends when the motor has turned 81 degrees since at that point, with the four sides of the reflector, a full 360 degrees has bean scanned.
 
@@
 \noindent
-This method offers us a sufficiently dense set of data to base our angle predictions off of but at the cost of having to wait until a entire sweep is completed.
+This method offers us a sufficiently dense set of data to base our angle predictions off of but at the cost of having to wait until a entire sweep of the reflectors is completed.
 With this data we first put together a simple test that would continuously be sweeping and moving at the same time.
-Though this version did successful follow the remote it was incredibly unstable.
-The result of this instability was that the robot would most of the time correctly turn towards the remote and then start moving towards it but as it went it would slowly pick up a osculation in its movement until the wobble got to great and it would drive off in a random direction then find its way back into alignment and resume moving towards the remote.
+Though this version did successfully follow the remote it had some errors in the robot's navigation trajectory.
+For example, the robot would correctly turn towards the remote, however, if it picked up a stronger signal from the XBee reverberations, it would drive off in a different direction.
+The robot would eventually find its way back into alignment and resume moving towards the remote.
 
@@
 \noindent
+\todo[inline]{This section needs to be fixed.
+I have done grammar corrections but I do not have any clue how to fix your wording issues.
+You have run-on sentences and duplicative language describing the same thing.
+-Kalli}
 The next version that used a rotating reflector as well as the final version works mostly the same as the first version but with some improvements to its navigation.
-The first big fix is that we determined that the result of the osculation we were seeing in the first test was a result of turning while also rotating the reflector which would add additional rotation to the measurements in global scope.
-Do to how are robot is designed we can only rotate the reflector array 90 degrees but to properly fix this rotation issue we would need to rotate the reflector more or less during a sweep to compensate for the robots rotation.
+The first big fix is that we determined that the result of the oscillation we were seeing in the first test was a result of turning while also rotating the reflector which would add additional rotation to the measurements in global scope.
+Due to how our robot is designed we can only rotate the reflector array 90 degrees but to properly fix this rotation issue we would need to rotate the reflector more or less during a sweep to compensate for the robots rotation.
 Our compromise was simply to allow the robot to always move forward but to alternate between rotating the reflector and getting a measurement and then rotating the robot based on that measurement.
 In this version we also added some additional windowed filters to average out the angle measurements which did help to reduce the effects of random angles from noise in the system.
-We also applied offsets to each of the directional receivers revived signal strengths based of of data that we had collected while testing it when we noticed that each side had a different minimum that it would cap out at.
+We also applied offsets to each of the directional receivers revived signal strengths based off of data that we had collected while testing it when we noticed that each side had a different minimum that it would cap out at.
 
@@
 
-The locked reflector test were some tests that we ran in between our first sweeping algorithm and our final algorithm which ultimately used sweeping.
+The locked reflector tests were ran in between our first algorithm and our final algorithm which ultimately used a sweeping function to capture the XBee signals.
 These algorithms were an attempt to reduce the time needed to get a set of measurements from the reflector by zeroing its rotation and then keeping it locked in the zeroed position.
 Since the data from this is relatively sparse we tried three different ways to fill in the gaps in the data from only the four cardinal directions.
-The first of these three methods was to try and select a strongest direction that the signal was coming from and then witch of its two neighbor directions had the next strongest signal.
-With these two strengths the algorithm would then try to interpolate between these two angles based on difference of the strength between them.
-This method probably can work but in our implementation we ran out of time to try and tune it since it would take a fairly large amount of data to be collected to try and tune it in.
+The first of these three methods was to try and select a strongest direction that the signal was coming from and then which of its two neighbor directions had the next strongest signal.
+With these two strengths the algorithm would then try to interpolate between these two angles based on the difference of the strengths between them.
+This method could work but due to the time constraints of our project, we did not have enough time to implement and test this method.
 
@@
 \noindent
-The other two methods that we tried with the locked reflector were both different variants on machine learning based on a small poll of data we had collected.
+The other two methods that we tried with the locked reflector were both different variants on machine learning algorithms based on a small pool of data we had collected.
 The first algorithm tested was K Nearest Neighbors then followed up by a Neural Network for our final fixed rotation test.
-Both of these algorithms failed to produce any meaningful results.
-This would appear to be due to the fact that we had a very small pool of data to work off compared to usual attempts to use machine learning.
-They also with the small data pool size did not cope particularly well with the noise in the signal.
+Both of these algorithms failed to produce any meaningful results due to the fact that we had a very small pool of data to work off of compared to the large amounts of data needed to perform machine learning algorithms.
+These algorithms, with the small data pool size, did not perform well with the noise in the signals.
 
@@
 
-In both our fixed and seeping experiments a underlying issue is the amount of noise our system produces.
+In both our fixed and sweeping experiments a underlying issue is the amount of noise our system produces.
 The first type of noise that occurs is noise from the Multipath Effect where the signals bounce off of obsticals around it adding constructing and destructive interference randomly based off of the robots surroundings.
 The second noise was from internal noise in the XBees which was worse that we had expected.
-We to some degree managed to isolate the XBee internal noise by using an anecoic chamber where we did see all the signals strengths become stronger but the base noise from the XBees persisted.
-The noise coming from the XBees tends to be about 2 to 6 dBm around the average and the change from facing towards to away from the remote is about 13 to 15 dBm.
-This ranges result in the occasional measurement that flip flops which reflector is actually facing the remote.
-The noise can be seen in our test measurements we collected where we at set rotations record a burst of 300 measurements as seen in \autoref{fig:SensorDataGraphs}
+We managed to isolate the XBee internal noise by using an anechoic chamber where we did see all the signals strengths become stronger but the base noise from the XBees persisted.
+The noise coming from the XBees tends to be about 2 to 6 dBm on average.
+The change from facing towards the remote then away from the remote is about 13 to 15 dBm.
+These ranges result in the occasional measurement that flip flops which reflector is actually facing the remote.
+The noise can be seen in our test measurements we collected where we, at set rotations, record a burst of 300 measurements as seen in Fig.
+\ref{fig:SensorDataGraphs}
 
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
 
-[Uhhh what?]
-\todo[inline]{What am I looking at on page 23 exactly? -Darrah}
-\todo[inline]{See page 23 of~\url{http://ee.bradley.edu/projects/proj2017/ekf_slam/Downloads/seniorProject_finalReport.pdf} -Dr. Miah}
-
 \section{Simulation using Robot Simulator}
@@
 Although \autoref{ch:coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.
+
 \begin{figure}

### 2021-05-04 parts/50-implementation.tex
Update 50-implementation.tex

@@
 For this project we needed a Remote Target and Smart Robotic Cart that we designed and implemented from off the shelf components.
-As mentioned above in section \ref{sec:System Components} some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslist}.
+As mentioned above in section \ref{sec:System Components}, some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslist}.
 
@@
 We also installed a 2-cell LiPo battery inside the chassis of the mobile cart that delivers power to the BeagleBone Blue directly and the breadboard through the switch.
-\par
 
@@
 \noindent
-The Reflector array assembly from Chapter \ref{ch: Chapter3} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket.
+The reflector array assembly from Chapter \ref{ch: Chapter3} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket.
 This bracket was then attached to the chassis using bolts.
@@
 This problem comes from that the BeagleBone Blue has five UART ports if we are using the one found in the USB and the UART-GPS along with the three normal UART ports.\todo[inline]{This sentence needs to be revised.
--Kalli}.
-This does not work since UART port zero is tied to the council used to communicate with it from a computer.
+-Kalli} This does not work since UART port zero is tied to the council used to communicate with it from a computer.
 Since this port is reserved for this function that reduces the number of usable ports down to four and we need to have five XBees in these ports.
@@
 \todo[inline]{This sentence needs to be revised since it makes no sense.
--Kalli}.
-The library also helped to keep track of basic information related to the stepper motor such as what its current angle should be.
+-Kalli} The library also helped to keep track of basic information related to the stepper motor such as what its current angle should be.
 
@@
 \noindent
-\todo[inline]{This section needs to be fixed.
-I have done grammar corrections but I do not have any clue how to fix your wording issues.
-You have run-on sentences and duplicative language describing the same thing.
--Kalli}
+\todo[inline]{This section needs to be fixed. You have some wording issues that makes it hard for me to understand what you are saying. -Kalli}
 The next version that used a rotating reflector as well as the final version works mostly the same as the first version but with some improvements to its navigation.

### 2021-05-05 parts/30-customized_parabolic_reflector_array.tex

@@
 
-\todo[inline]{Add an introductory paragraph (4/5 sentences maximum). What are
-  you trying to talk about in this chapter, for example}
+The XBee RF modules that were used are omnidirectional.
+In this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming.
+Therefore, one of the major components of this project is the reflector array that enables the XBee modules to be direction sensitive.
+This section discusses the steps that were taken to construct such a reflector array.
 
@@
 %----------------------------------------------------------------------
-The XBee RF modules that were used detect signals from any direction.
-In this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming.
-To accomplish this, two different models of reflector arrays were designed and constructed.
+Two different models of reflector arrays were designed and constructed.
+The first design was a paraboloidal reflector with the focus on the antenna of the XBee module.
+The second design was a combination of a paraboloidal shape and a simpler parabolic shape.
+The motivation for each design will be discussed in sections \ref{subsec:paraboloidalReflector} and \ref{subsec:parabolicReflector}.
 
-\subsection{Paraboloidal Reflector}
+\subsection{Paraboloidal Reflector}\label{subsec:paraboloidalReflector}
 The first design, shown in Fig.
@@
 
-\subsection{Combined Parabolic/Paraboloidal Reflector}
+\subsection{Combined Parabolic/Paraboloidal Reflector}\label{subsec:parabolicReflector}
 The second design, shown in Fig.

### 2021-05-10 parts/20-system_architecture.tex
Update 20-system_architecture.tex
Combined sections 2, 3, and 4

@@
   \centering
-  \includegraphics[width=\textwidth]{figs/img/systemBlockDiagram.png}
+  \includegraphics[width=\textwidth]{figs/systemBlockDiagram.pdf}
   \caption{System level block diagram detailing inputs and outputs to the
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/img/remoteBlockDiagram.png}
+  \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
   \caption{Remote Target block diagram}
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/img/mobileCartBlockDiagram.png}
+  \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
   \caption{Block diagram showing the subsystem-level components of the proposed robotic cart.}
@@
 
-\begin{table}[h!]
+\begin{table}[H]
   \centering
@@
 directionally receive the RF signals from the remote target that is with the
-user.
+user, which will be discussed in detail in the next section.
 
-\begin{figure}
+\begin{figure}[H]
   \centering
-  \begin{minipage}[H]{0.32\textwidth}
+  \begin{subfigure}[t]{0.32\textwidth}
     \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
@@
     \label{fig:budgetBotChassis}
-  \end{minipage}%
-  \begin{minipage}[H]{0.32\textwidth}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.32\textwidth}
     \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
@@
     \label{fig:beagleboneBlue}
-  \end{minipage}
-  \begin{minipage}[H]{0.32\textwidth}
+  \end{subfigure}
+  \begin{subfigure}[t]{0.32\textwidth}
     \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
@@
     \label{fig:XBeeModule}
-  \end{minipage}
+  \end{subfigure}
+  \caption{Main System Components}
 \end{figure}
+
+%----------------------------------------------------------------------
+\section{Customized Reflector Array}
+%----------------------------------------------------------------------
+The XBee RF modules that were used are omnidirectional.
+In this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming.
+Therefore, one of the major components of this project is the reflector array that enables the XBee modules to be direction sensitive.
+This section discusses the steps that were taken to construct such a reflector array.
+
+\subsection{Reflector Design}
+Two different models of reflector arrays were designed and constructed.
+The first design was a paraboloidal reflector with the focus on the antenna of the XBee module.
+The second design was a combination of a paraboloidal shape and a simpler parabolic shape.
+The motivation for each design will be discussed in sections \ref{subsec:paraboloidalReflector} and \ref{subsec:parabolicReflector}.
+
+\subsubsection{Paraboloidal Reflector}\label{subsec:paraboloidalReflector}
+The first design, shown in Fig.
+\ref{fig:paraboloidalReflector}, uses a reflector with a paraboloidal shape.
+This shape was selected since all signals entering the reflector parallel to the axis of the reflector will be focused at the focal point of the paraboloid.
+By mounting the XBee such that the center of the antenna coincides with the focal point of the paraboloid, the signal strength of the signals entering parallel to the axis will be maximized.
+\begin{figure}
+    \centering
+    \includegraphics[width=3.5in]{figs/img/paraboloidalReflector.png}
+    \caption{Purely Paraboloidal Reflector Array}
+    \label{fig:paraboloidalReflector}
+\end{figure}
+
+\subsubsection{Combined Parabolic/Paraboloidal Reflector}\label{subsec:parabolicReflector}
+The second design, shown in Fig.
+\ref{fig:parabolicReflector}, is the same on the lower half as the first design.
+However, the upper half is simply a surface where the horizontal cross-section is a parabola.
+The purpose for this design is similar to that of the first design, but the parabolic shape on the top will allow stronger detected signal strength of signals coming from above the reflector.
+Since the remote will be held by a person, it will generally be above the robot.
+The parabolic/paraboloidal reflector design is intended to allow better reception of signals from above.
+\begin{figure}
+    \centering
+    \includegraphics[width=3.5in]{figs/img/parabolicReflector.png}
+    \caption{Parabolic/Paraboloidal Reflector Array}
+    \label{fig:parabolicReflector}
+\end{figure}
+
+\subsection{Reflector Construction}
+With the recent advancements in 3D printing technology, it is not difficult to
+create an object with a parabolic shape. In this project, the reflector dishes
+were created using a 3D printer. The reflector array was designed to be modular,
+where the dishes, top plate, and bottom frame were printed separately. After
+printing, the dishes were lined with foil tape to provide the reflective surface
+to focus the signals onto the antenna of the XBee. A layer of foil tape was also
+placed on the top plate to provide a ground plane for the XBee. The parts were
+then fastened together using M3 screws and nuts (Fig.
+\ref{fig:reflectorConstruction}).
+%
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=2.5in]{figs/img/reflectorConstruction.jpg}
+    \caption{Reflector Construction}
+    \label{fig:reflectorConstruction}
+\end{figure}
+
+%----------------------------------------------------------------------
+\section{Localization and Navigation}
+%----------------------------------------------------------------------
+
+This section illustrates the localization and navigation algorithms for the mobile cart to operate in an indoor/outdoor environment.
+The proposed robotic cart was modeled as a differential drive mobile robot (DDMR).
+The direction and distance of the remote relative to the cart are determined using a localization algorithm.
+This distance and angle are then passed to a navigation algorithm which calculates and applies the wheel speeds to move the robot toward the remote.
+
+\subsection{Robot Model}\label{subsec:robotModel}
+The robot used in this project was a differential drive mobile robot, which has
+two drive wheels and a caster wheel for balance. The robot turns by applying
+different speeds to the left and right wheels. As shown in Fig.
+\ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance
+between the wheels is $L$. The pose of the robot is given by the $x$-coordinate
+($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in
+Fig. \ref{fig:robotPose}. %
+%
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{0.3\textwidth}
+        \centering
+        \includegraphics[width=0.7\textwidth]{figs/robotGeometry.pdf}
+        \caption{Robot Geometry}
+        \label{fig:robotGeometry}
+    \end{subfigure}%
+    \begin{subfigure}{0.7\textwidth}
+        \centering
+        \includegraphics[width=0.7\textwidth]{figs/robotPose.pdf}
+        \caption{Robot Pose}
+        \label{fig:robotPose}
+    \end{subfigure}
+    \caption{Robot Model Parameters}
+    \label{fig:robotModelParameters}
+\end{figure}
+%
 
@@
 \noindent
-The reflector array will be mounted on top of the cart with a stepper motor.
-There are two reflector designs that were evaluated in this project. The first,
-shown in Fig. \ref{fig:parabolodialReflector}, is a paraboloidal reflector which
-maximizes the signal strength of the signals that come into the reflector
-perpendicularly. Since the remote will be carried by the user, it is likely that
-it will be positioned at a higher altitude than the reflector array. The
-paraboloidal reflector design may not be able to pick up the signals from the
-remote as well because of this. %
-%
-%
-\begin{figure}
+Generally the robot is controlled by commanding a linear and angular speed ($v$ and $\omega$, respectively).
+These speeds must be converted into left and right wheel speeds.
+The following equations are used to calculate the angular left and right wheel speeds ($\omega_l$ and $\omega_r$, respectively):
+$$\omega_l = \left(v - \omega\frac{L}{2}\right)\frac{1}{R}$$
+$$\omega_r = \left(v + \omega\frac{L}{2}\right)\frac{1}{R}$$
+To control DC motors in this way, the relationship between duty cycle and angular speed must be determined.
+Then the duty cycles to apply to the wheels can be calculated for the commanded $v$ and $\omega$.
+
+\subsection{Localization Algorithm}
+The localization algorithm is used to estimate the position of the remote with respect to the robot's local coordinate system.
+First the omnidirectional transceiver on top of the reflectors sends a signal strength request to the remote.
+The remote then replies with a message containing the strength of the signal it just received.
+This reply is detected by the receivers inside the reflectors as well as the omnidirectional transceiver.
+The strength detected by each of the directional receivers and the strength contained in the reply are then recorded.
+At this point, the entire reflector array is rotated 9\textdegree, and this process is repeated.
+The robot continues taking measurements in this way until the reflectors have been rotated one quarter turn.
+Since there are four reflectors at 90\textdegree to each other, a strength measurement has been recorded for every 9\textdegree increment around the robot.
+The angle of the remote is then estimated as the direction from which the strongest signal was received.
+The distance to the remote is calculated using the free-space path loss formula.
+The direction of reflector rotation is then reversed since the wires connecting the RF modules in the reflectors prevent the reflector from freely spinning.
+A flowchart of this algorithm is shown in Fig.
+\ref{fig:localizationAlgoFlowchart}.
+\begin{figure}[H]
     \centering
-  \begin{minipage}[H]{0.5\textwidth}
+    \includegraphics[width=3.5in]{figs/localizationAlgorithmFlowchart.pdf}
+    \caption{Flowchart of Localization Algorithm}
+    \label{fig:localizationAlgoFlowchart}
+\end{figure}
+
+\subsection{Navigation Algorithm}
+The navigation algorithm is used to drive the robot toward the remote.
+The inputs to the navigation algorithm are the angle to the remote ($\theta_r$) and the distance to the remote ($d_r$).
+A target point is then calculated as the point that is in the same direction as the remote, but closer to the robot by a fixed following distance ($d_{follow}$), as shown in Fig.
+\ref{fig:navAlgoDiagram}.
+The distance to the target point is calculated as $d_{tgt} = d_r - d_{follow}$, and the angle to the target point is $\theta_{tgt} = \theta_r$.
+The linear and angular speeds of the robot ($v$ and $\omega$, respectively) are then calculated using proportional control by the following equations:
+$$v = K_vd_{tgt}$$
+$$\omega = K_\omega\theta_{tgt}$$
+The appropriate duty cycles are then calculated as specified in section \ref{subsec:robotModel} and applied to the wheel motors.
+\begin{figure}[H]
     \centering
-    \includegraphics[height=2in]{figs/img/paraboloidalReflector}
-    \captionsetup{width=\textwidth, justification=raggedright}
-    \caption{Paraboloidal Reflector Model}
-    \label{fig:parabolodialReflector}
-  \end{minipage}
-  \begin{minipage}[H]{0.4\textwidth}
+    \begin{subfigure}{0.45\textwidth}
         \centering
-    \includegraphics[height=2in]{figs/img/parabolicReflector}
-    \captionsetup{width=\textwidth, justification=raggedright}
-    \caption{Combined Parabolic/Paraboloidal Reflector}
-    \label{fig:parabolicReflector1}
-  \end{minipage}
+        \includegraphics[width=0.95\textwidth]{figs/navigationAlgorithmDiagram.pdf}
+        \caption{Target Point Diagram}
+        \label{fig:navAlgoDiagram}
+    \end{subfigure}%
+    \begin{subfigure}{0.55\textwidth}
+        \centering
+        \includegraphics[width=0.95\textwidth]{figs/navigationAlgorithmFlowchart.pdf}
+        \caption{Flowchart}
+        \label{fig:navAlgoFlowchart}
+    \end{subfigure}
+    \caption{Navigation Algorithm Details}
+    \label{fig:navAlgoDetails}
 \end{figure}
-%
-To solve this problem, a combination parabolic/paraboloidal reflector was
-designed, as shown in Fig. \ref{fig:parabolicReflector1}. The lower half of this
-reflector is paraboloidal in shape to limit the signals coming from below. The
-upper part of the reflector is strictly parabolic. This shape focuses the
-signals in the horizontal plane, but allows signals from above to still be
-received. The plan is to construct both of these reflector designs by 3D
-printing the frames, then lining them with reflective foil tape. Both models
-will then be tested to determine which design works better.
-
-%----------------------------------------------------------------------
-\section{Operation of Robotic Cart System}
-\label{sec:Operation of Robotic Cart System}
-%----------------------------------------------------------------------
-The mobile cart was controlled by a central embedded computer which is the BeagleBone Blue since it is ideal in robotics control.
-Two DC motors were used to drive wheels and move the cart.
-Five XBee modules on the cart were used to allow communication with the remote target.
-One of these radio sensors was mounted on top of the cart to broadcast in all directions.
-The other four sensors were placed inside parabolic reflectors at right angles to each other.
-This sensor array was mounted on a stepper motor to allow rotation.
 

### 2021-05-10 parts/30-implementation.tex
Combined sections 2, 3, and 4

--- 2021-05-04 parts/50-implementation.tex
@@
 The Budget Bot chassis needed to be modified slightly to work with our project.
-The main change we made was swapping out the motors that came with the Budget Bot for Pololu 27D Meatal Gear motors since the original motors have a max speed of 212 RPM or 1.09m/s and the new motors have a max speed of 530 RPM or 2.72m/s when using the wheels with a diameter of 98mm.
+The main change we made was swapping out the motors that came with the Budget Bot for Pololu 27D Metal Gear motors since the original motors have a max speed of 212 RPM or 1.09m/s and the new motors have a max speed of 530 RPM or 2.72m/s when using the wheels with a diameter of 98mm.
 By switching out the motors we are able to achieve our goal of matching an average person's walking speed of 1.5m/s.
@@
 In both our fixed and sweeping experiments a underlying issue is the amount of noise our system produces.
-The first type of noise that occurs is noise from the Multipath Effect where the signals bounce off of obsticals around it adding constructing and destructive interference randomly based off of the robots surroundings.
+The first type of noise that occurs is noise from the Multipath Effect where the signals bounce off of obstacles around it adding constructing and destructive interference randomly based off of the robots surroundings.
 The second noise was from internal noise in the XBees which was worse that we had expected.

### 2021-05-10 parts/30-implementation.tex
Updated chapter labeling

@@
 \chapter{Implementation}
-\label{ch: Chapter5}
+\label{ch: implementation}
 %======================================================================
@@
 \noindent
-The reflector array assembly from Chapter \ref{ch: Chapter3} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket.
+The reflector array assembly from \autoref{sec:customReflector} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket.
 This bracket was then attached to the chassis using bolts.
@@
 
-In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in Chapter \ref{ch: Chapter4}.
+In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in \autoref{sec:locAndNavAlgos}.
 There were two main types of variants we put together, one type the stepper motor is locked preventing the reflector from turning and in the other we use the stepper motor to sweep through a set of angles.
@@
 The model was designed with the same dimensions as the physical chassis to accurately simulate the robot kinematics.
-Details on modeling a robot chassis in CoppeliaSim can be found in \autoref{ch:coppSimModeling}.
-Although \autoref{ch:coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.
+Details on modeling a robot chassis in CoppeliaSim can be found in \autoref{ch: coppSimModeling}.
+Although \autoref{ch: coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.
 
@@
 The actual distance between the robot and the remote was measured, then random noise was added with a mean of 0 and a standard deviation of 0.07.
-This noisy measurement was then used in the navigation algorithm to determine how to drive the robot (see \autoref{sec:navAlgo}).
+This noisy measurement was then used in the navigation algorithm to determine how to drive the robot (see \autoref{subsec:navAlgo}).
 An image of the simulation is shown in Fig.

### 2021-05-10 parts/10-introduction.tex
Update 10-introduction.tex
Fixed figures in introduction

@@
 \chapter{Introduction}
-\label{ch: Chapter1}
+\label{ch: intro}
 %======================================================================
@@
 \ref{fig:CompaRob}, that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}.
-Another method, shown in Fig.
-\ref{fig:ShoppingSup}, that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
-Therein, in Fig.
-\ref{fig:SmartCart}, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.
-
-\begin{figure}[b]
+\begin{figure}[H]
    \centering
@@
 \end{figure}
-
-\begin{figure}[b]
+Another method, shown in Fig.
+\ref{fig:ShoppingSup}, that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow the customer through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}.
+\begin{figure}[H]
    \centering
@@
 \end{figure}
-
-\begin{figure}[b]
+Therein, in Fig.
+\ref{fig:SmartCart}, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.
+\begin{figure}[H]
    \centering
@@
 %----------------------------------------------------------------------
-This report is organized into six chapters:
-\todo[inline]{This section should go at the end of the chapter.}
-
 \begin{itemize}
-    \item Chapter \ref{ch: Chapter1} discusses the background and goals of the project and what other similar projects have accomplished.
-    \item Chapter \ref{ch: Chapter2} explains how the robotic cart system in this project is broken down fundamentally, and the components used to build the robot.
-    \item Chapter \ref{ch: Chapter3} goes over the design of the parabolic reflector arrays and how they were set up on the robot.
-    \item Chapter \ref{ch: Chapter4} provides an explanation of the algorithms that were used to create the code to make the robot move.
-    \item Chapter \ref{ch: Chapter5} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
-    \item Chapter \ref{ch: Chapter6} concludes the project work and discusses future endeavors on this project.
+    \item Chapter \ref{ch: intro} discusses the background and goals of the project and what other similar projects have accomplished.
+    \item Chapter \ref{ch: sysArchitecture} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
+    \item Chapter \ref{ch: implementation} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
+    \item Chapter \ref{ch: conclusionAndFuture} concludes the project work and discusses future endeavors on this project.
+    \item Appendix \ref{ch: coppSimModeling} goes through the steps to build and simulate the Budget Bot chassis in CoppeliaSim
 \end{itemize}

### 2021-05-10 parts/10-introduction.tex
Added assembly instructions appendix

@@
     \item Chapter \ref{ch: intro} discusses the background and goals of the project and what other similar projects have accomplished.
-    \item Chapter \ref{ch: sysArchitecture} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
+    \item Chapter \ref{ch: sysDesign} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
     \item Chapter \ref{ch: implementation} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.

### 2021-05-10 parts/B-assemblyInstructions.tex
Added assembly instructions appendix

%======================================================================
\chapter{Assembly Instructions}
\label{ch: assemblyInstructions}
%======================================================================

This appendix explains how to assemble the robot from the individual components. Some useful tools to have on hand during the assembly are a 2.5mm Allen key, a pair of needlenose pliers, a wire stripper, a scissors, and an exacto knife. Follow the steps below to assemble the robot.

\vspace*{18pt}
\noindent
\begin{Large}\textbf{Instructions}\end{Large}

\begin{enumerate}[label = \textbf{Step \arabic*.}]
    \item Get a Budget Bot Chassis (Fig. \ref{fig:assemblyBudgetBot}). For this project, a fuse, power switch, and power indicator LED were added to the Budget Bot Chassis. Install a 2-cell LiPo battery inside the Budget Bot. Route the balance plug and battery output cable up through the center hole on top of the Budget Bot.
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.6in]{figs/img/assembly/01-BudgetBot.png}
        \caption{Modified Budget Bot Chassis}
        \label{fig:assemblyBudgetBot}
    \end{figure}

    \item Install a BeagleBone Blue and a solderless breadboard on the Budget Bot using 6mm M3 screws (Fig. \ref{fig:bbblueInstallation}, red circles). Connect the battery's balance plug to the terminal on the BBBlue, and the power output to the breadboard (Fig. \ref{fig:bbblueInstallation}, green circles). Finally, insert the motor cables into the breadboard (Fig. \ref{fig:bbblueInstallation}, blue circle).
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.6in]{figs/img/assembly/02-bbblueInstallation.png}
        \caption{BBBlue and Breadboard Installation}
        \label{fig:bbblueInstallation}
    \end{figure}

    \item Connect the motor terminals to the motor output channels on the BBBlue (left: ch1, right: ch2) using two 2-pin JST-ZH connectors. Connect the motor encoders to the encoder channels on the BBBlue (left: ch1, right: ch2) using two 4-pin JST-SH connectors (Fig. \ref{fig:motorWiring}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.6in]{figs/img/assembly/03-motorWiring.png}
        \caption{Motor Wiring}
        \label{fig:motorWiring}
    \end{figure}

    \item Prepare the stepper motor, the stepper motor bracket, four 6mm M3 screws, and four 8mm M3 screws (Fig. \ref{fig:stepperParts}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4in]{figs/img/assembly/04-stepperParts.jpg}
        \caption{Stepper Motor Parts}
        \label{fig:stepperParts}
    \end{figure}

    \item Insert four 6mm M3 screws through the holes on the top of the bracket and secure the stepper motor to the stepper motor bracket by threading the screws into the holes in the stepper motor (Fig. \ref{fig:stepperAssembly}). Make sure the motor connector comes out on the side of the bracket with the notch.
    \begin{figure}[H]
        \centering
        \includegraphics[width=4in]{figs/img/assembly/05-stepperAssembly.png}
        \caption{Mounting Stepper Motor onto Bracket}
        \label{fig:stepperAssembly}
    \end{figure}
    \pagebreak

    \item Insert four 8mm M3 screws through the holes in the feet of the bracket and secure the bracket to the Budget Bot (Fig. \ref{fig:stepperMounting}). Holes must be drilled in the Budget Bot Chassis to thread the screws into. Insert the stepper motor connector into the breadboard and tuck away the excess cable inside the Budget Bot.
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.7in]{figs/img/assembly/06-stepperMounting.png}
        \caption{Mounting Stepper Motor onto Budget Bot}
        \label{fig:stepperMounting}
    \end{figure}

    \item Using two 2-pin JST-ZH connectors, connect motor output channels 3 and 4 to the stepper motor windings (Fig. \ref{fig:stepperWiring}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4in]{figs/img/assembly/07-stepperWiring.png}
        \caption{Stepper Motor Wiring}
        \label{fig:stepperWiring}
    \end{figure}
    \pagebreak

    \item Insert a DG409DJ+ multiplexer across the center of the breadboard (Fig. \ref{fig:multiplexer}). Make sure the divot is toward the end of the breadboard to prevent mistakes during the rest of the assembly.
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.2in]{figs/img/assembly/08-multiplexer.png}
        \caption{Multiplexer Installation}
        \label{fig:multiplexer}
    \end{figure}

    \item Connect battery power to the multiplexer by connecting V+ to pin 14 and GND to pin 15 of the multiplexer (Fig. \ref{fig:multiplexerPower}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.2in]{figs/img/assembly/09-multiplexerPower.png}
        \caption{Powering the Multiplexer}
        \label{fig:multiplexerPower}
    \end{figure}
    \pagebreak

    \item Insert an LM1117 3.3V regulator into the breadboard. Place a 10\textmu F capacitor between the output terminal and ground. Connect the ground terminal to the battery ground and the input power terminal to the battery V+ (Fig. \ref{fig:regulator})
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.8in]{figs/img/assembly/10-regulatorWiring.png}
        \caption{Regulator Installation}
        \label{fig:regulator}
    \end{figure}

    \item Connect +3.3V from GPIO1 to pin 2 on the multiplexer (Fig. \ref{fig:multiplexerWiring}, red arrows). Connect GPIO1 pins 1 and 2 to multiplexer pins 1 and 16, respectively (Fig. \ref{fig:multiplexerWiring}, green and orange arrows). Connect UART1 TX and RX to multiplexer pins 8 and 9, respectively (Fig. \ref{fig:multiplexerWiring}, yellow and purple arrows). Finally, connect UART5 TX and RX into the breadboard (Fig. \ref{fig:multiplexerWiring}, blue arrows).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.8in]{figs/img/assembly/11-multiplexerBBBlueWiring.png}
        \caption{Connecting the Multiplexer to the BBBlue}
        \label{fig:multiplexerWiring}
    \end{figure}
    \pagebreak

    \item Prepare the reflector dishes, top plate, and bottom frame. Also prepare some 8mm and 10mm M3 screws and some M3 nuts (Fig. \ref{fig:reflectorParts}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.4in]{figs/img/assembly/12-reflectorParts.jpg}
        \caption{Reflector Parts}
        \label{fig:reflectorParts}
    \end{figure}

    \item Insert an M3 nut into the slot at the top of one of the reflector dishes (Fig. \ref{fig:reflectorTopNut}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.6in]{figs/img/assembly/13-reflectorTopNut.png}
        \caption{Top Reflector Nut}
        \label{fig:reflectorTopNut}
    \end{figure}
    \pagebreak

    \item Attach the top plate using an 8mm M3 screw (Fig. \ref{fig:reflectorTopPlate}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.1in]{figs/img/assembly/14-reflectorTopPlate.jpg}
        \caption{Attaching Top Plate}
        \label{fig:reflectorTopPlate}
    \end{figure}

    \item Repeat steps 13 and 14 to attach all of the reflector dishes to the top plate (Fig. \ref{fig:finishedTopPlate}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.1in]{figs/img/assembly/15-finishedReflectorTopPlate.jpg}
        \caption{Finished Top Plate}
        \label{fig:finishedTopPlate}
    \end{figure}
    \pagebreak

    \item Insert wires from the bottom of the reflectors up through the left slot (when viewed from above) and connect them to the VCC (red), DOUT (purple), DIN (yellow), and VSS (black) pins of an XBee adapter board (Fig. \ref{fig:topXBeeWiring}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.2in]{figs/img/assembly/16-topXBeeWiring.jpg}
        \caption{Wiring for Top XBee}
        \label{fig:topXBeeWiring}
    \end{figure}

    \item Insert two M3 nuts into the slots on the underside of the top plate (Fig. \ref{fig:topXBeeNuts}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.2in]{figs/img/assembly/17-topXBeeNuts.png}
        \caption{Nuts for top XBee}
        \label{fig:topXBeeNuts}
    \end{figure}
    \pagebreak

    \item Attach the XBee adapter board to the top plate using two 8mm M3 screws (Fig. \ref{fig:topXBeeMounting}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.2in]{figs/img/assembly/18-topXBeeMounting.png}
        \caption{Mounting the Top XBee}
        \label{fig:topXBeeMounting}
    \end{figure}

    \item Insert wires through the back of a reflector dish and connect them to the VCC (red), DOUT (purple), DIN (yellow), and VSS (black) pins of an XBee adapter board (Fig. \ref{fig:sideXBeeWiring}). It is useful to number the purple and yellow wires at both ends with the reflector number. The reflectors should be numbered 1 through 4 going clockwise.
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.2in]{figs/img/assembly/19-sideXBeeWiring.jpg}
        \caption{Wiring a Side XBee}
        \label{fig:sideXBeeWiring}
    \end{figure}
    \pagebreak

    \item Insert two M3 nuts into the underside of the support protruding from the reflector (Fig. \ref{fig:sideXBeeNuts})
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.2in]{figs/img/assembly/20-sideXBeeNuts.png}
        \caption{Nuts for Side XBee}
        \label{fig:sideXBeeNuts}
    \end{figure}

    \item Mount the XBee adapter board using two 8mm M3 screws (Fig. \ref{fig:sideXBeeMounting}). Make sure the board is oriented such that the antenna of the XBee will be toward the reflective surface.
    \begin{figure}[H]
        \centering
        \includegraphics[width=4.2in]{figs/img/assembly/21-sideXBeeMounting.png}
        \caption{Mounting a Side XBee}
        \label{fig:sideXBeeMounting}
    \end{figure}
    \pagebreak

    \item Repeat steps 19 through 21 to mount XBee adapter boards into each of the four reflectors (Fig. \ref{fig:finishedSideXBees}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.9in]{figs/img/assembly/22-finishedSideXBees.jpg}
        \caption{All Side XBees Mounted}
        \label{fig:finishedSideXBees}
    \end{figure}

    \item Wrap the wires coming from the reflector to keep them bundled into a single cable. Terminate the ends such that there is a 2-pin connector for +3.3V and GND (Fig. \ref{fig:reflectorWires}, red arrow), a 2-pin connector for the TX and RX to the top XBee (Fig. \ref{fig:reflectorWires}, blue arrow), a 4-pin connector for the TX pins of all four side XBees (Fig. \ref{fig:reflectorWires}, purple arrow), and a 4-pin connector for the RX pins of all four side XBees (Fig. \ref{fig:reflectorWires}, yellow arrow). Once again, it is useful to number both ends of the TX and RX wires to the side XBees.
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.9in]{figs/img/assembly/23-reflectorWireEnds.png}
        \caption{Reflector Wire Ends}
        \label{fig:reflectorWires}
    \end{figure}
    \pagebreak

    \item Insert two M3 nuts into the slots at the bottom of a reflector (Fig. \ref{fig:bottomNuts}). The nuts should recess into a hexagonal slot that prevents them from rotating.
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.6in]{figs/img/assembly/24-reflectorBottomNuts.png}
        \caption{Nuts for Bottom Frame}
        \label{fig:bottomNuts}
    \end{figure}

    \item Place the bottom frame onto the reflectors, with the stop plate pointed upward toward reflector 3. Route the wires through the hole between reflectors 1 and 2 (Fig. \ref{fig:reflectorWireRouting}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.9in]{figs/img/assembly/25-reflectorWireRouting.png}
        \caption{Reflector Wire Routing}
        \label{fig:reflectorWireRouting}
    \end{figure}
    \pagebreak

    \item Attach the bottom plate to the reflectors using eight 10mm M3 screws (Fig. \ref{fig:bottomMounting}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.6in]{figs/img/assembly/26-reflectorBottomMounting.png}
        \caption{Mounting the Bottom Frame}
        \label{fig:bottomMounting}
    \end{figure}

    \item Insert an XBee into each of the 5 XBee adapter boards (one on top and one in each reflector). Again, make sure that the XBees inside the reflectors are oriented with the antenna on the side toward the reflective surface (Fig. \ref{fig:XBeeInstallation}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.6in]{figs/img/assembly/27-XBeeInstallation.jpg}
        \caption{XBee Installation}
        \label{fig:XBeeInstallation}
    \end{figure}
    \pagebreak

    \item Make sure the flat side of the stepper motor shaft is toward the back of the robot. Slide the reflector array onto this motor shaft, making sure the stop plate is pointed toward the back of the robot and is between the two stops on the stepper motor bracket (Fig. \ref{fig:reflectorMounting}).
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.8in]{figs/img/assembly/28-reflectorMounting.png}
        \caption{Mounting the Reflectors on the Stepper Motor}
        \label{fig:reflectorMounting}
    \end{figure}

    \item Verify that the stop plate on the reflector array is between the stops on the stepper motor bracket (Fig. \ref{fig:installedReflector})
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.8in]{figs/img/assembly/29-installedReflector.png}
        \caption{Reflector Stop Verification}
        \label{fig:installedReflector}
    \end{figure}
    \pagebreak

    \item Connect the reflector to the rest of the system by connecting the power cables to the output of the LM1117 regulator (Fig. \ref{fig:reflectorWiring}, red arrow), the top XBee TX and RX to the UART5 TX and RX (Fig. \ref{fig:reflectorWiring}, blue arrow), the side XBee TX wires to multiplexer pins 10 - 13 (Fig. \ref{fig:reflectorWiring}, purple arrow), and the side XBee RX wires to multiplexer pins 4 - 7 (Fig. \ref{fig:reflectorWiring}, yellow arrow). The side XBees should be connected to the multiplexer in order, with XBee 1 connecting to multiplexer pins 4 and 13.
    \begin{figure}[H]
        \centering
        \includegraphics[width=3.4in]{figs/img/assembly/30-reflectorWiring.png}
        \caption{Reflector Wiring}
        \label{fig:reflectorWiring}
    \end{figure}
\end{enumerate}

The robot assembly is complete! The fully assembled robot should look like the one shown in Fig. \ref{fig:assembledRobot}.
\begin{figure}[H]
    \centering
    \includegraphics[width=3.4in]{figs/img/assembly/31-assembledRobot.jpg}
    \caption{Assembled Robot}
    \label{fig:assembledRobot}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:

### 2021-05-10 parts/10-introduction.tex
Minor updates

@@
     \item Chapter \ref{ch: conclusionAndFuture} concludes the project work and discusses future endeavors on this project.
-    \item Appendix \ref{ch: coppSimModeling} goes through the steps to build and simulate the Budget Bot chassis in CoppeliaSim
+    \item Appendix \ref{ch: coppSimModeling} goes through the steps to model and simulate the Budget Bot chassis in CoppeliaSim
+    \item Appendix \ref{ch: assemblyInstructions} gives the step-by-step procedure for assembling the robot
 \end{itemize}

### 2021-05-10 parts/20-system_architecture.tex
Updated chapter labeling
Added assembly instructions appendix
Minor updates

@@
 %======================================================================
-\chapter{System Architecture}
-\label{ch: Chapter2}
+\chapter{System Design}
+\label{ch: sysDesign}
 %======================================================================
@@
 %----------------------------------------------------------------------
-\section{Customized Reflector Array}
+\section{Customized Reflector Array}\label{sec:customReflector}
 %----------------------------------------------------------------------
@@
 %----------------------------------------------------------------------
-\section{Localization and Navigation}
+\section{Localization and Navigation Algorithms}\label{sec:locAndNavAlgos}
 %----------------------------------------------------------------------
@@
 
-\subsection{Navigation Algorithm}
+\subsection{Navigation Algorithm}\label{subsec:navAlgo}
 The navigation algorithm is used to drive the robot toward the remote.

### 2021-05-11 parts/40-conclusion_and_future_work.tex
Combined sections 2, 3, and 4
Updated chapter labeling
Conclusion added

--- 2021-04-08 parts/60-conclusion_and_future_work.tex
@@
 \label{ch: Chapter6}
+=======
+\label{ch: conclusionAndFuture}
 %======================================================================
@@
 
+This project shows that it is possible to use signal strength alone to make a mobile cart follow a target remotes position.
+From this project, a functional design for a mobile cart was developed and tested.
+In these tests, it was concluded that with the robot's current design, it would be impossible to calculate an accurate distance to the remote from the signal strength alone.
+Since the distance was determent to be impossible, the current design follows the target remote based on angle measurements alone.
+Due to this limitation or not having a usable distance value, the current implementation is unable to dynamically adjust its behavior.
+One such planned parameter was the robot's velocity, which would have been reduced as the robot approached the remote target to prevent it from running into the user via momentum.
+Based on the literature review from before the project was started, we also determined that our Smart Following Cart design is more cost-effective than most if not all existing solutions.
+Another feature was validated through some sparse testing where it was shown that the robot could successfully track the remote target through obstacles.
+
 %----------------------------------------------------------------------
@@
 
+Although the robotic cart prototype did successfully follow the remote based on signal strength alone, there is still much to be desired from future work.
+The first problem that would need to be addressed is a proper obstacle avoidance system.
+For the current robotic cart prototype, it was initially planned to have a basic version of user avoidance, but this was scrapped due to the inaccuracy of our distance measurement.
+This user avoidance in a future project can also be incorporated into an obstacle detection and avoidance system, most likely using inferred or sonar sensors mounted around the side of the robot.
+This is a necessary continuation of this project since, as it currently stands, it can detect and follow the remote through obstacles but will attempt to drive in a straight path towards the remote despite the obstacle in between them.
+\par{}
+The project also requires more overall tuning in any future work that is done on it.
+The two main places that need more tuning are the weights used to normalize the signal strengths out of the reflector array and the specs of the reflector array's design to optimize its performance.
+The values for normalizing the signal strengths coming out of the array currently are based on a relatively small and limited set of recorded data from the robot.
+For a future extension of this project, more measurements would be required to better determine the quality of the data coming out of each reflector.
+These values would most likely be obtained by taking many measurements in an anechoic chamber, which was also used for the current smaller set of sensor data.
+The data currently is only being used to calculate a base offset for each reflector's strength.
+Though with enough data, it may be possible to use the top radio module's strength to adjust for overall degradation to the signal strength.
+The reflectors themselves also most likely need to be redesigned again.
+During testing, it was noted that the difference from facing the target to facing away from the target is barely a greater difference in signal strength than the difference in signal strengths' measurement noise.
+\par{}
+The last problem that needs to be addressed in this project is determining a reasonably accurate distance measurement.
+The problem with distance stems from that the remote and robot are relative to each other, so there is no global reference point that can be used to stabilize the measurements.
+The second problem then is that the only way with the signal strength to get distance is to use a version of free space path loss which fails the second a use stands between the remote and the robot.
+For this, two possible solutions were thought up after it was determined that signal strength alone would not work.
+These solutions were also determined to be outside the scope of what could be reasonably achieved within the allotted project time.
+The two possible solutions are to use signal strength with multi-frequency radio modules or to use the travel time of the message from the robot.
+The multi-frequency approach would still use signal strength but would potentially allow for a profile to be put together from the signal strength of each frequency to try and ignore the interference from objects.
+The other approach of using a messages' travel time has been shown to work in such applications as GPS over large distances.
+This approach may work since the speed of the radio signal is generally less affected by objects in its path than signal strength is.
+The main challenge with this approach would be getting a sufficiently accurate time measurement for short distances.
+If either of these approaches to determining distance ended up working, then the following algorithm could be more dynamic in its behavior and interpretation of the signal strengths.
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "../finalReportMainV1"
+%%% TeX-master: "../finalReport"
 %%% End:

### 2021-05-11 parts/30-implementation.tex
Updated Final Report

@@
     \includegraphics[width=0.5\textwidth]{figs/img/Finalized_robot.png}
-    \caption{Final Version of the Robotic Cart}
+    \caption{Overall Prototype of the Robotic Cart}
     \label{fig:FinalizedRobot}
@@
 The Xbee modules from the reflector array posed a bit of a problem when it came to connecting them to the BeagleBone Blue.
-This problem comes from that the BeagleBone Blue has five UART ports if we are using the one found in the USB and the UART-GPS along with the three normal UART ports.\todo[inline]{This sentence needs to be revised.
--Kalli} This does not work since UART port zero is tied to the council used to communicate with it from a computer.
+The BeagleBone Blue has five UART ports if one were the three standard UART ports and tow others found in the USB and UART-GPS.
+Unfortunately though this does not work since UART port zero is tied to the council used to communicate with it from a computer.
 Since this port is reserved for this function that reduces the number of usable ports down to four and we need to have five XBees in these ports.
@@
 This library had to be written ourselves since instead of using a dedicated stepper motor controller for our project we were using two of the regular DC motor control ports that are build into the BeagleBone Blue.
-The library handled translating how many steps to turn into proper cycling of the DC motor ports to get the stepper motor to move the desired distance.
-\todo[inline]{This sentence needs to be revised since it makes no sense.
--Kalli} The library also helped to keep track of basic information related to the stepper motor such as what its current angle should be.
+The library handled translating how many steps to turn into the phase states to be sent to the DC motor ports that are connected to the stepper motor.
+The library also helped to keep track of basic information related to the stepper motor such as what its current angle should be.
 
@@
 \noindent
-\todo[inline]{This section needs to be fixed. You have some wording issues that makes it hard for me to understand what you are saying. -Kalli}
-The next version that used a rotating reflector as well as the final version works mostly the same as the first version but with some improvements to its navigation.
-The first big fix is that we determined that the result of the oscillation we were seeing in the first test was a result of turning while also rotating the reflector which would add additional rotation to the measurements in global scope.
+The next version that used a rotating reflector, as well as the final version, works mostly the same as the first version but with some improvements to its navigation.
+The first big fix is that we determined that the oscillation we were seeing in the first test were a result of turning while also rotating the reflector which would add additional rotation to the measurements in global scope.
 Due to how our robot is designed we can only rotate the reflector array 90 degrees but to properly fix this rotation issue we would need to rotate the reflector more or less during a sweep to compensate for the robots rotation.
-Our compromise was simply to allow the robot to always move forward but to alternate between rotating the reflector and getting a measurement and then rotating the robot based on that measurement.
-In this version we also added some additional windowed filters to average out the angle measurements which did help to reduce the effects of random angles from noise in the system.
-We also applied offsets to each of the directional receivers revived signal strengths based off of data that we had collected while testing it when we noticed that each side had a different minimum that it would cap out at.
+Our compromise was simply to allow the robot to always move forward but to alternate between getting measurements and then rotating the robot based on the measurements.
+In this version some additional windowed filters to average out the angle measurements were added, which did help to reduce the effects of random angles from noise in the system.
+We also applied offsets to each of the directional receivers revived signal strengths based off the data that we had collected while testing it.
+This offset was needed due to each side having a different minimum that it would cap out at.
 
@@
 \subsection{Distance}
-
-\todo[inline]{Was going back over this and realized I should add this section in will do later don't have time at this exact moment. -Darrah}
+This project initially planned to use the top XBee modules signal strength to determine the distance to the remote.
+In practice, though, it was determined to be practically impossible with our setup.
+The free space path loss equation was used as a base equation to work from for implementing this feature in the project.
+The issue arises initially from that the free space path loss failed to return a usable distance by itself whenever any form of obstacle ends up in the line of sight path to the remote.
+The free space path loss equation also is thrown off by any reflective surfaces around it due to the multipath effect.
+These issues could be potentially solved by Simultanius Localization and Mapping algorithms like EKF-SLAM.
+Unfortunately, this approach also does not work since it relies on a known global reference point that is absent in this project design.
+Since within the allotted time for the project, no viable solution was found, it was decided that the distance measurement would be put on hold for future work on the project
 

### 2021-05-12 parts/30-implementation.tex
Update 30-implementation.tex
Edits

@@
 
-For the implementation of this project we had to start from scratch since this was a new project concept introduced by our advisor Dr.
-Miah.
-There have been senior projects in the past that have used XBees to get signal strength but there is very little overlap between these projects to substantiate where our project needed to start from.
-For this project we had to first build a mobile robot and a remote to use for testing.
-We then had to build a code base to control the mobile robot that was then implemented with our test algorithms.
+Since this project was a new concept, the implementation had to start from scratch.
+Although there have been projects in the past that have used XBees to get signal strength, none of them used it in the same way as this project.
+For this project a mobile robot and a remote first had to be built to use for testing.
+Then a code base needed to be created to control the mobile robot according to the design algorithms.
 
@@
 
-For this project we needed a Remote Target and Smart Robotic Cart that we designed and implemented from off the shelf components.
-As mentioned above in section \ref{sec:System Components}, some of our components came from what the school already owned as well as some we had to buy specifically for this project listed in \autoref{tab:Partslablist} and \autoref{tab:Partslist}.
+For this project, a Remote Target and Smart Robotic Cart were designed and implemented from off-the-shelf components.
+As mentioned above in section \ref{sec:System Components}, some of the components were already available at Bradley University, and others had to be purchased specifically for this project.
+The parts are listed in \autoref{tab:Partslablist} and \autoref{tab:Partslist}.
 
@@
 \noindent
-Since the school already owned the Budget Bot chassis, we decided to build our Smart Robotic Cart with them.
-The Budget Bot chassis needed to be modified slightly to work with our project.
-The main change we made was swapping out the motors that came with the Budget Bot for Pololu 27D Metal Gear motors since the original motors have a max speed of 212 RPM or 1.09m/s and the new motors have a max speed of 530 RPM or 2.72m/s when using the wheels with a diameter of 98mm.
-By switching out the motors we are able to achieve our goal of matching an average person's walking speed of 1.5m/s.
-The other modifications to the chassis are a hard power switch to directly cut off power to the XBee modules in the reflector and a power indicator LED to let us know when this switch was on.
+Since the school already owned the Budget Bot chassis, it was a good choice for the base of the  Smart Robotic Cart.
+However, the Budget Bot chassis was modified slightly to work for this project.
+The main change was swapping out the motors that came with the Budget Bot for Pololu 27D Metal Gear motors since the original motors have a max speed of 212 RPM or 1.09m/s and the new motors have a max speed of 530 RPM or 2.72m/s when using the wheels with a diameter of 98mm.
+By switching out the motors enabled the robot to move faster to make it better able to achieve the goal of matching an average person's walking speed.
+The other modifications to the chassis were a hard power switch to directly cut off power to the XBee modules in the reflector and a power LED to indicate when this switch was on.
 
@@
 \noindent
-As shown in Fig.
-\ref{fig:FinalizedRobot}, our next step was to attach the BeagleBone Blue microcomputer, XBee reflector array assembly, and breadboard to the top of the robot.
-We also installed a 2-cell LiPo battery inside the chassis of the mobile cart that delivers power to the BeagleBone Blue directly and the breadboard through the switch.
-
+The next step was to attach the BeagleBone Blue microcomputer, XBee reflector array assembly, and breadboard to the top of the robot.
+A 2-cell LiPo battery was also installed inside the chassis of the mobile cart to provide power to the BeagleBone Blue directly and the breadboard through the switch.
+The power supplied to the breadboard is sent through a regulator circuit to drop it down from the 7.4V of the LiPo to 3.3V of the XBee.
+This circuit is also used on the remote which consists of a 7.4V LiPo battery and the XBee module with voltage regulator in between.
+This voltage regulator is built out of a LM117 regulator and a 10uF ceramic capacitor between the input and output pins of the regulator.
+The circuit diagrams for the robot and remote are shown in Figs.
+\ref{fig:robotCircuit} and \ref{fig:remoteCircuit}.
 \begin{figure}[H]
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/img/Finalized_robot.png}
-    \caption{Overall Prototype of the Robotic Cart}
-    \label{fig:FinalizedRobot}
+    \includegraphics[width=\textwidth]{figs/robotCircuit.pdf}
+    \caption{Circuit Diagram for Robotic Cart}
+    \label{fig:robotCircuit}
 \end{figure}
-
-The power supplied to the breadboard is sent through a regulator circuit to drop it down from the 7.4V of the LiPo to 3.3V of the XBee.
-This circuit is also used on the remote which consists of a 7.4V LiPo battery and the XBee module with voltage regulator in between.
-This voltage regulator is built out of a LM117 regulator and a 10uF ceramic capacitor between the input and output pins of the regulator as shown in Fig.
-\ref{fig:PowerConverter}.
-
 \begin{figure}[H]
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/img/PowerConverter.png}
-    \caption{Final Version of the Robotic Cart}
-    \label{fig:PowerConverter}
+    \includegraphics[width=0.7\textwidth]{figs/remoteCircuit.pdf}
+    \caption{Circuit Diagram for Remote}
+    \label{fig:remoteCircuit}
 \end{figure}
@@
 \noindent
-The reflector array assembly from \autoref{sec:customReflector} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket.
-This bracket was then attached to the chassis using bolts.
-Another feature of this bracket is that it had a stop block built into the top of it to automatically zero the reflector array when the robot starts up.
+The reflector array assembly from \autoref{sec:customReflector} was mounted on a stepper motor that was then attached to a 3D printed bracket.
+This bracket was then attached to the chassis using M3 screws.
+Another feature of this bracket is that it had a stop block built into the top  to allow the robot to automatically initialize the reflector array to the zero position when the robot starts up.
+This is accomplished by commanding a turn of 90\textdegree and allowing the reflectors to hit the stop block and be held there until this turn is complete.
 
@@
 The Xbee modules from the reflector array posed a bit of a problem when it came to connecting them to the BeagleBone Blue.
-The BeagleBone Blue has five UART ports if one were the three standard UART ports and tow others found in the USB and UART-GPS.
-Unfortunately though this does not work since UART port zero is tied to the council used to communicate with it from a computer.
-Since this port is reserved for this function that reduces the number of usable ports down to four and we need to have five XBees in these ports.
-Our solution to this was to use two of the GPIO pins, two of the UART ports, and a two-way multiplexer.
-With this setup we can directly connect one of the UARTs to the top XBee and then rout the other four side XBee modules through the MUX so only one UART port is needed for them.
+The BeagleBone Blue has three standard UART ports and two others found in the USB and UART-GPS, which makes a total of five UARTs.
+Unfortunately not all five ports can be used to communicate with XBees since UART0 is used to provide communication with a computer through the console.
+Since port 0 is reserved for this function, the number of usable ports is only four, but the project requires communication with five XBees.
+The solution to this problem was to use two of the GPIO pins, two of the UART ports, and a dual 4-channel multiplexer.
+One of the UARTs can be directly connected to the top XBee, and the other UART can be routed through the multiplexer to the four side XBee modules.
+Then two UART ports are used to communicate with all five XBees.
+
+\vspace*{12pt}
+\noindent
+Instructions for assembling the robot can be found in \autoref{ch: assemblyInstructions}.
+Therein, the sequence of steps is explained in detail with pictures to show the state of the robot.
+The finished prototype robot and remote are shown in Fig.
+\ref{fig:finishedPrototypes}.
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/img/Finalized_robot.png}
+        \captionsetup{width=\textwidth}
+        \caption{Robotic Cart Prototype}
+        \label{fig:overallPrototype}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/remote.pdf}
+        \captionsetup{width=\textwidth}
+        \caption{Remote Prototype}
+        \label{fig:remotePrototype}
+    \end{subfigure}
+    \caption{Finished Prototypes}
+    \label{fig:finishedPrototypes}
+\end{figure}
 
@@
 
-For the project we needed some base functionality to use with the main follower program so it can interact with the other components in the system.
-The BeagleBone Blue already has a set of ports on it that we can access and control using the Robot Control Library from Strawson Design ~\cite{Robot_Control_Library}.
+For the project some base functionality was needed to use with the main follower program so it could interact with the other components in the system.
+The BeagleBone Blue already has a set of ports on it that can be accessed and controlled using the Robot Control Library from Strawson Design ~\cite{Robot_Control_Library}.
 
@@
 \noindent
-For the project we also built some custom libraries on top of the Robot Control Library to handle XBee Frames, AT Commands, and the stepper motor.
-The XBee Frames library takes a given block of data containing our message and then packages it into a XBee Frame to send over UART to the XBee module we want to interact with.
-The XBee communications library also handles received messages from the XBee module and validates the received frames integrity and extracts the message data from it.
-On top of the XBee communications library we also have a library that generates AT Commands to package in the XBee Frames.
+Some custom libraries were built on top of the Robot Control Library to handle XBee Frames, AT Commands, and the stepper motor control.
+The XBee Frames library takes a given block of data containing the message and then packages it into a XBee Frame to send over UART to the XBee desired module.
+The XBee communications library also handles received messages from the XBee module and validates the received frame's integrity and extracts the message data from it.
+On top of the XBee communications library there is a library that generates AT Commands to package in the XBee Frames.
 The AT Command library also handles extracting response data from the AT Response Command structure and validates it.
@@
 The final custom library is the stepper motor control library.
-This library had to be written ourselves since instead of using a dedicated stepper motor controller for our project we were using two of the regular DC motor control ports that are build into the BeagleBone Blue.
+This library had to be written since instead of using a dedicated stepper motor controller, two of the regular BBBlue DC motor control ports were used to power the stepper motor.
 The library handled translating how many steps to turn into the phase states to be sent to the DC motor ports that are connected to the stepper motor.
@@
 
-In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in \autoref{sec:locAndNavAlgos}.
-There were two main types of variants we put together, one type the stepper motor is locked preventing the reflector from turning and in the other we use the stepper motor to sweep through a set of angles.
+After the Robotic Cart, Remote Target, and code base were built, several different variants of the algorithms explained in \autoref{sec:locAndNavAlgos} were tested.
+There were two main types of variants tested.
+In one variant, the stepper motor is locked, preventing the reflector from rotating.
+In the other variant, the stepper motor is used to sweep through the angles.
 
@@
 
-The first type of test we ran was where the robot would zero out the arrays rotation with the stepper motor then move in nine degree increments taking measurements as it went.
-A sweep ends when the motor has turned 81 degrees since at that point, with the four sides of the reflector, a full 360 degrees has bean scanned.
+The first type of test was where the robot would initialize the reflector array to the zero point with the stepper motor, then rotate in nine degree increments taking measurements as it went.
+A sweep ends when the motor has turned 81 degrees since at that point, with the four sides of the reflector, a full 360 degrees has been scanned.
 
@@
 \noindent
-This method offers us a sufficiently dense set of data to base our angle predictions off of but at the cost of having to wait until a entire sweep of the reflectors is completed.
-With this data we first put together a simple test that would continuously be sweeping and moving at the same time.
-Though this version did successfully follow the remote it had some errors in the robot's navigation trajectory.
+This method offers a sufficiently dense set of data to base the angle predictions off of, but at the cost of having to wait until a entire sweep of the reflectors is completed for a single estimation of the remote location.
+The first attempt with this method was a simple test that would continuously sweep the reflectors and move the robot at the same time.
+Though this version did eventually make its way toward the remote, it had some errors in the robot's navigation trajectory.
 For example, the robot would correctly turn towards the remote, however, if it picked up a stronger signal from the XBee reverberations, it would drive off in a different direction.
@@
 \noindent
-The next version that used a rotating reflector, as well as the final version, works mostly the same as the first version but with some improvements to its navigation.
-The first big fix is that we determined that the oscillation we were seeing in the first test were a result of turning while also rotating the reflector which would add additional rotation to the measurements in global scope.
-Due to how our robot is designed we can only rotate the reflector array 90 degrees but to properly fix this rotation issue we would need to rotate the reflector more or less during a sweep to compensate for the robots rotation.
-Our compromise was simply to allow the robot to always move forward but to alternate between getting measurements and then rotating the robot based on the measurements.
+The next version that used a rotating reflector, as well as the final version, works mostly the same as the first version, but with some improvements to the navigation.
+It was determined that the oscillations in the robot's trajectory in the first test were a result of turning the robot while also rotating the reflector.
+This adds additional rotation to the measurements in the global scope.
+Due to the design of the robot, the reflector array can only be rotated 90 degrees, but to properly fix this rotation issue the reflector array would need to be rotated more or less during a sweep to compensate for the robot's rotation.
+The solution was simply to alternate between sweeping the reflector and rotating the robot, all the while allowing the robot to always move forward.
+The rotation of the robot was limited to 15\textdegree before another measurement would be taken.
 In this version some additional windowed filters to average out the angle measurements were added, which did help to reduce the effects of random angles from noise in the system.
-We also applied offsets to each of the directional receivers revived signal strengths based off the data that we had collected while testing it.
-This offset was needed due to each side having a different minimum that it would cap out at.
+Based on data collected in an anechoic chamber, offsetsfor each of the directional receivers were applied to try to convert the received signal strengths to use the same baseline.
+This offset was needed since each XBee would receive slightly different signal strengths when it was pointed directly at the remote.
 
@@
 
-The locked reflector tests were ran in between our first algorithm and our final algorithm which ultimately used a sweeping function to capture the XBee signals.
-These algorithms were an attempt to reduce the time needed to get a set of measurements from the reflector by zeroing its rotation and then keeping it locked in the zeroed position.
-Since the data from this is relatively sparse we tried three different ways to fill in the gaps in the data from only the four cardinal directions.
-The first of these three methods was to try and select a strongest direction that the signal was coming from and then which of its two neighbor directions had the next strongest signal.
-With these two strengths the algorithm would then try to interpolate between these two angles based on the difference of the strengths between them.
-This method could work but due to the time constraints of our project, we did not have enough time to implement and test this method.
+The locked reflector tests were run in between the first algorithm and the final algorithm which ultimately used a sweeping function to capture the XBee signals.
+The locked reflector algorithms were an attempt to reduce the time needed to get a set of measurements from the reflector by zeroing its rotation and then keeping it locked in the zero position.
+Since the data from this is relatively sparse, three different methods for estimating the angle of the remote were attempted.
+The first of these three methods was to try to select the direction that the signal was coming strongest from and then which of its two neighbor directions had the second strongest signal.
+With these two strengths the algorithm would then try to interpolate the angle based on the difference of the strengths between them.
+This method could possibly work, but due to the time constraints of the project, there was not enough time to implement and test this method.
 
@@
 \noindent
-The other two methods that we tried with the locked reflector were both different variants on machine learning algorithms based on a small pool of data we had collected.
-The first algorithm tested was K Nearest Neighbors then followed up by a Neural Network for our final fixed rotation test.
-Both of these algorithms failed to produce any meaningful results due to the fact that we had a very small pool of data to work off of compared to the large amounts of data needed to perform machine learning algorithms.
-These algorithms, with the small data pool size, did not perform well with the noise in the signals.
+The other two methods that were tried with the locked reflector were both different variants on machine learning algorithms.
+A small pool of data was collected both in an anechoic chamber and in a normal operating environment.
+The first algorithm attempted to use the K Nearest Neighbors algorithm to estimate the angle of the remote based on the relative signal strengths received by the directional XBees.
+The second algorithm used a neural network to predict the angle.
+Both of these algorithms failed to produce meaningful results, probably due to the fact that there was a very small pool of data to work with compared to the large amounts of data needed to perform machine learning algorithms.
+The noise in the signals proved too much for these algorithms to handle elegantly.
+If data were collected in many operating environments, machine learning techniques may be able to yield favorable results.
 
@@
 
-In both our fixed and sweeping experiments a underlying issue is the amount of noise our system produces.
-The first type of noise that occurs is noise from the Multipath Effect where the signals bounce off of obstacles around it adding constructing and destructive interference randomly based off of the robots surroundings.
-The second noise was from internal noise in the XBees which was worse that we had expected.
-We managed to isolate the XBee internal noise by using an anechoic chamber where we did see all the signals strengths become stronger but the base noise from the XBees persisted.
+In both the fixed and sweeping experiments, an underlying issue was the amount of noise in the system.
+The first type of noise that occurs is noise from the multipath effect, where the signals bounce off obstacles in the environment, adding constructing and destructive interference randomly based on the robot's surroundings.
+The second source of noise was internal noise in the XBees, which was worse than what was expected.
+The XBee internal noise was isolated using an anechoic chamber where all the signals strengths did become stronger, but the base noise from the XBees persisted.
 The noise coming from the XBees tends to be about 2 to 6 dBm on average.
@@
 These ranges result in the occasional measurement that flip flops which reflector is actually facing the remote.
-The noise can be seen in our test measurements we collected where we, at set rotations, record a burst of 300 measurements as seen in Fig.
-\ref{fig:SensorDataGraphs}
+The noise can be seen in the test measurements that were collected where 300 measurements were taken at several intervals around the robot as seen in Fig.
+\ref{fig:SensorDataGraphs}.
 
@@
 \subsection{Distance}
-This project initially planned to use the top XBee modules signal strength to determine the distance to the remote.
-In practice, though, it was determined to be practically impossible with our setup.
-The free space path loss equation was used as a base equation to work from for implementing this feature in the project.
-The issue arises initially from that the free space path loss failed to return a usable distance by itself whenever any form of obstacle ends up in the line of sight path to the remote.
-The free space path loss equation also is thrown off by any reflective surfaces around it due to the multipath effect.
-These issues could be potentially solved by Simultanius Localization and Mapping algorithms like EKF-SLAM.
-Unfortunately, this approach also does not work since it relies on a known global reference point that is absent in this project design.
-Since within the allotted time for the project, no viable solution was found, it was decided that the distance measurement would be put on hold for future work on the project
+This project initially planned to use the top XBee module's signal strength to determine the distance to the remote.
+In practice, however, it was determined to be nearly impossible with the current setup.
+The free-space path loss equation was used as a base equation to attempt to implement this feature in the project.
+One problem is that the free-space path loss formula is for use in free space, so it fails to yield the correct distance whenever any form of obstacle ends up in the line-of-sight path to the remote.
+The free-space path loss formula is also thrown off by any reflective surfaces around it due to the multipath effect.
+These issues could be potentially solved using a simultaneous localization and mapping algorithm such as EKF-SLAM.
+Unfortunately, this approach would be very difficult since it relies on a known global reference point, but the robot in this project has no such global reference.
+It was decided that the distance measurement would be put on hold for future work on this project.
 
@@
 
-Before constructing the physical robot prototype, a simulation was performed using a commercial robot simulator CoppeliaSim.
+Before constructing the physical robot prototype, a simulation was performed using a commercial robot simulator, CoppeliaSim.
 However, since RF signal behavior depends highly on the environment, the system could not be fully simulated.
@@
 Although \autoref{ch: coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.
-
-\begin{figure}
+\begin{figure}[H]
     \centering
-    \includegraphics[width=0.6\textwidth]{figs/img/budgetBotModel.png}
+    \includegraphics[width=0.4\textwidth]{figs/img/budgetBotModel.png}
     \caption{Model of Budget Bot Chassis}
@@
 
-\vspace*{12pt}
 \noindent
@@
 \ref{fig:coppSimExample}, where the blue sphere represents the remote, and the green dot represents the target point.
-\begin{figure}
+\begin{figure}[H]
     \centering

### 2021-05-12 parts/40-conclusion_and_future_work.tex
Updated Final Report
Edits

--- 2021-04-08 parts/60-conclusion_and_future_work.tex
@@
 \label{ch: Chapter6}
+\label{ch: conclusionAndFuture}
 %======================================================================
@@
 
+This project shows that it is possible to use signal strength alone to make a mobile cart follow a remote target.
+A functional design for a mobile cart was developed and tested.
+In these tests, it was concluded that with the robot's current design, it would be extremely difficult to calculate an accurate distance to the remote from the signal strength alone.
+Therefore, the current design follows the target remote based on angle measurements alone.
+Due to the limitation of not having a usable distance value, the current implementation is unable to dynamically adjust its behavior based on proximity to the remote.
+One such planned parameter was the robot's velocity, which would have been reduced as the robot approached the remote target to prevent it from running into the user.
+Based on the literature review, it was determined that the Smart Robotic Cart design from this project is more cost-effective than most, if not all, of the existing solutions.
+It was shown that the robot could successfully track the remote target even when obstacles were obstructing the line-of-sight path between the robot and remote.
+
 %----------------------------------------------------------------------
@@
 
+Although the robotic cart prototype did successfully follow the remote based on signal strength alone, there is still much to be desired.
+The first item that would need to be addressed is a proper obstacle avoidance system.
+For the current robotic cart prototype, it was initially planned to have the robot avoid collision with the user by using the distance between the robot and remote, but this was dropped due to the inaccuracy of the distance measurement.
+This user avoidance could be incorporated into an obstacle detection and avoidance system in a future project, most likely using infrared or sonar sensors mounted on the robot.
+This is a necessary continuation of this project since, as it currently stands, it can detect and follow the remote through obstacles but will attempt to drive in a straight path towards the remote despite the obstacle between them.
+
+\vspace*{12pt}
+\noindent
+The project also requires more overall tuning in any future work that is done on it.
+The two main places that need more tuning are the weights used to normalize the signal strengths out of the reflector array and the specs of the reflector array's design to optimize its performance.
+The values for normalizing the signal strengths coming out of the array currently are based on a relatively small and limited set of recorded data from the robot.
+For a future extension of this project, more measurements would be required to better determine the quality of the data coming out of each reflector.
+These values would most likely be obtained by taking many measurements in an anechoic chamber, which was also used for the current smaller set of sensor data.
+The data currently is only being used to calculate a base offset for each reflector's strength, though with enough data, it may be possible to use the top radio module's strength to adjust for overall degradation to the signal strength.
+The reflectors themselves also most likely need to be redesigned again.
+During testing, it was noted that the difference from facing the target to facing away from the target is only slightly greater than the average signal strength measurement noise.
+
+\vspace*{12pt}
+\noindent
+Another problem that needs to be addressed in this project is determining a reasonably accurate distance measurement.
+The problem with distance stems from the fact that the locations remote and robot are relative to each other, so there is no global reference point that can be used to stabilize the measurements.
+The second problem is that the only way with the signal strength to get distance is to use a version of free-space path loss, which fails when the user stands between the remote and the robot.
+For this, two possible solutions were thought up after it was determined that signal strength alone would not work.
+These solutions were also determined to be outside the scope of what could be reasonably achieved within the allotted project time.
+The two possible solutions are to use signal strength with multi-frequency radio modules or to use the travel time of the message from the robot.
+The multi-frequency approach would still use signal strength but would potentially allow for a profile to be put together from the signal strength of each frequency to try and ignore the interference from objects.
+The other approach of using a message's travel time has been shown to work in such applications as GPS over large distances.
+This approach may work since the speed of the radio signal is generally less affected by objects in its path than signal strength is.
+The main challenge with this approach would be getting a sufficiently accurate time measurement for short distances.
+If either of these approaches to determining distance ended up working, then the algorithm could be more dynamic in its behavior and interpretation of the signal strengths.
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "../finalReportMainV1"
+%%% TeX-master: "../finalReport"
 %%% End:

### 2021-07-19 paperIEEE-ROSE2021-BrBeAlShMi.tex
Conference paper
Pushed latex code and matlab code to generate frames placed in the paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,bm,physics}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[list=true,labelformat=simple]{subcaption}
\captionsetup[sub]{skip=2pt}
\renewcommand\thesubfigure{(\alph{subfigure})}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{siunitx}
\usepackage{nohyperref}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{A Smart Robotic Cart Prototype using RF Signal Strength \thanks{Authors would like to acknowledge Illinois Space
    Grants Consortium for funding this project under grand no. \#}
  \thanks{The results presented in this paper were produced by a group of senior
    undergraduate students: Jason Braker, Darrah Beebe, and Kalistah Allen }
}

\author{\IEEEauthorblockN{Jason Braker, Darrah Beebe, Kallistah Allen, Prasad Shastry, and Md Suruz Miah}
\IEEEauthorblockA{\textit{Department of Electrical and Computer Engineering} \\
\textit{Bradley University}\\
Peoria, Illinois, United States of America \\
\{jbraker, dbeebe, kjallen\}@mail.bradley.edu, \{snp,smiah\}@bradley.edu}
}

\maketitle

\begin{abstract}

  In this paper, we present a prototype of a smart robotic cart using radio
  frequency (RF) signal strength for navigation. The proposed robotic cart is
  cost-effective since it simply utilizes analog signal strengths to localize
  and follow a customer (called herein ``remote''), for example. An array of RF
  modules (model of an antenna array), is mounted on top of the mobile robotic cart,
  and a remote RF module is held by the remote. The direction and the
  line-of-sight (LoS) distance of the remote are estimated based on signal
  strengths received by the RF modules mounted on the robot. The robot employs
  the estimated direction and the LoS distance to compute actuator commands for
  the robotic cart to follow the remote. The robot was first simulated using
  CoppeliaSim, a commercial robot simulator. A prototype was then built and used
  to evaluate the performance of the robot. Applications of the proposed robotic
  cart include, but are not limited to, delivery carts to follow mail personnel
  and carry the deliveries, file transfer carts in offices, hospital carts to
  aid nurses and doctors by carrying medicine or surgery supplies, and carts in
  construction sites to carry tools and other supplies across the job site.

\end{abstract}

\begin{IEEEkeywords}
  mobile robots, navigation, radio frequency identification, robotic cart 
\end{IEEEkeywords}

\section{Introduction}
\label{sec:introduction}

A robotic cart is an invention designed to aid users in a number of important
indoor and outdoor tasks. There are robotic systems currently available in the
market that perform these tasks in a variety of ways. For example, in a grocery
store, a customer may require the need of more than one cart but cannot push or
pull two carts simultaneously. One major drawback, however, is that people with
disabilities cannot push one cart let alone have a second cart to carry more
items. Moreover, robots used for this purpose are costlier than they are worth.
Here we propose a robotic cart that would primarily leverage the emerging radio
frequency identification (RFID) technology, where analog radio frequency signals
are utilized to identify the remote (a customer in a grocery store, for
instance) and the robotic cart be able to track and follow the remote. The
implementation of such a fully functional robotic cart will outreach the scope
of the current work but is the overall goal of this ongoing project.

Abundant research carried out in the field of mobile robotics shows various ways to develop
robotic carts that will help consumers in carrying groceries through stores.
See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example. The operating principle of several robotic carts available in the market focuses on a few different methods of having a
robotic cart interface with the customer and follow them through the store. One such method that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmission technology is shown in Fig.~\ref{fig:CompaRob}~\cite{Sales2016-CompaRob}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob robot~\cite{Sales2016-CompaRob}.}
   \label{fig:CompaRob}
 \end{figure}
% 
 Authors in~\cite{islam_lam_fukuda_kobayashi_kuno_2019} have developed a shopping
 support robot that employs a GRU (Gated Recurrent Unit) network to detect
 shopping habits of customers. The robot is also equipped with a LiDAR (Light
 Detection and Ranging) sensor and camera for detecting and building map of the
 customer's position using a two-dimensional skeleton and follow the customer
 through the store. The robot developed using such an algorithm is  shown in Fig.~\ref{fig:ShoppingSup}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
   \caption{Shopping Support Robot}
   \label{fig:ShoppingSup}
\end{figure}
%
Fig.~\ref{fig:SmartCart} shows a smart cart robot that has been developed by the authors in~\cite{Rawashdeh2017-Person}. The authors utilized an Arduino MEGA 2560, six
ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android
Studio IDE device, and Bluetooth for detecting a customer and following them
through the store. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.45\textwidth]{figs/img/SmartCart}
   \caption{Smart Cart Robot}
   \label{fig:SmartCart}
\end{figure}
%
The operating principle of the proposed prototype of a smart robotic cart relies mainly on the radio frequency identification technology. For that, RF modules, XBee S2C RF radios, are primarily utilized to identify and communicate between the robotic cart and the remote (customer in a store, for example). XBee S2C RF radios are inexpensive and easily configurable. An RF module is configured as a remote target device that is carried
by the user/customer. The robot will be able to track this remote instead of using line
of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF
radios, the robot is equipped with a parabolic reflector, which improves radio
reception at various distances and angles,~\textit{i.e.,} angle of arrivals of
RF signals from the remote, based on research done previously in this type of
robot localization and mapping~\cite{Miah2018-Intelligent,Li2013ANA}. The approach using signal strengths of RF signals also requires an understanding
of multipath interference which is common in RF based wireless positioning
sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using
course estimation calculations such as the received signal strength indicator (RSSI)
 together with the time difference of arrival (TDoA) is key to compensate for the effect of multipath
interference.

The work in ~\cite{ladd_bekris_rudys_kavraki_wallach_2005} shows a different
approach to the multipath issue by using an IEEE 802.11b wireless Ethernet
device to measure RF signals. This device system was used because it is possible to communicate between a mobile device and a localization based service with low
complexity for the user. In~\cite{lindhe_johansson_bicchi_2007}, the research
states several other ways to counteract the multipath fading with methods such
as antenna diversity, frequency spreading, or adaptive antenna arrays. The
method used in this paper was to sample the radio signal strength (RSS) at
discrete points without too much deviation from the robot's desired position in
an indoor environment. Lastly, the method that is utilized in~\cite{Lindhe2009}
exploits multipath fading by measuring the signal-to-noise ratio (SNR) and
adjusting the robot's motion to spend more time where the channel strength is
greater. All solutions reported in the literature referred to here required line-of-sight
communication between the robot and the user. However, in this work, we aim to use the
XBee S2C RF radios and a parabolic reflectors integrated into a rotating system
similar to the one presented in~\cite{Miah2018-Intelligent} in order to have the
robot track the customer through a store without using line-of-sight sensing.
The major challenge of this implementation is the estimation of the distance
between the robot and the remote in various operating environments.

\section{System Architecture}
\label{sec:systemArchitecture}
The proposed smart robotic cart is a wheeled mobile robot that sends and
receives radio signals to follow the remote target (customer in a store, for
example) which acts as a beacon. The high-level system block diagram of the
proposed robotic cart (prototype) is shown in Fig.~\ref{fig:sys_block_diag}. %
% 
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.2]{figs/systemBlockDiagram.pdf}
  \caption{System level block diagram detailing inputs and outputs to the
    robotic cart system.}
	\label{fig:sys_block_diag}
\end{figure}
% 
There are three inputs to the proposed cart system. The robotic cart is supplied
with power through a battery that is mounted in the chassis of the robotic cart.
There will be an on/off switch to allow the cart to be powered down when not in
use. This will save the battery from being drained by other electronic
components of the robot. The motion of the robotic cart is dependent on the
motion of the remote. The main output of the system is the position trajectory
of the robotic cart in its environment. When the user/customer moves with the
remote target, the robotic cart is designed to follow the user.

As can be seen, two subsystems (mobile cart and remote) of the proposed robotic cart communicate with one another by relaying radio messages between them. Fig.~\ref{fig:remote_block_diag} shows the block diagram of the remote. %
%
\begin{figure}[htbp]
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
    \caption{}
    \label{fig:remote_block_diag}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
    \caption{}
    \label{fig:mobile_block_diag}
  \end{subfigure}
  \caption{Block diagrams showing inputs and outputs of:~\subref{fig:remote_block_diag} remote and~\subref{fig:mobile_block_diag}~mobile cart of the proposed smart robotic cart.}
  \label{fig:blockDiagramRemoteMobileCart}
\end{figure}
%
It requires an RF module, XBee, attached to $7.4~[\si{\volt}]$ Li-Po battery
with a voltage regulation circuit since the XBee has a smaller input voltage of
$3.3~[\si{\volt}].$ The two inputs of the remote are the battery power and the
incoming RF messages which are passed through the RF transceiver. The remote
outputs the an RF message back to the mobile cart, which will be discussed
later. The subsystem block diagram of the mobile cart is shown in
Fig.~\ref{fig:mobile_block_diag}. The cart requires a power source, which will
be a $7.4~[\si{\volt}],$ $8000~[\si{\milli\ampere\hour}]$ Li-Po battery since the Li-Po works well with powering the
embedded computer. The power to the subsystem will be toggled
by an on/off switch located on the chassis of the robotic cart. The final input
to the mobile cart subsystem are the incoming RF signals and the wheel velocities for the cart's actuators. These incoming RF
signals are passed to the direction sensitive RF receivers which output the
signals to the dual-direction multiplexer. The dual-direction multiplexer then
takes the four inputs from the direction sensitive RF receivers and passes one
output into the embedded computer. Once the embedded computer gets these signals
it can apply localization and navigation algorithms and pass the necessary actuator commands to the actuators of the robotic cart.

%----------------------------------------------------------------------
\section{Main Construction Components}
\label{sec:mainConstructionComponents}
%----------------------------------------------------------------------

There are several components that are required for constructing the proposed
smart robotic cart. The main components are the Budget Bot Chassis
(Fig.~\ref{fig:budgetBotChassis}), the BeagleBone Blue embedded robotics
computer (Fig.~\ref{fig:beagleboneBlue}), and the XBee S2C RF modules
(Fig.~\ref{fig:xbeemodule}). %
%
\begin{figure}[htbp]
  \centering
  \begin{subfigure}[b]{0.3\linewidth}
    \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
    \caption{}
    \label{fig:budgetBotChassis}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\linewidth}
    \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
    \caption{}
    \label{fig:beagleboneBlue}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\linewidth}
    \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
    \caption{}
    \label{fig:xbeemodule}
  \end{subfigure}
  \caption{The main components for constructing the proposed smart robotic cart:~\subref{fig:budgetBotChassis} Budget Bot robot chassis, ~\subref{fig:beagleboneBlue} BeagleBone Blue embedded robotics computer, and~\subref{fig:xbeemodule} XBee S2C RF module.}
\end{figure}
%
Note that the radiation pattern of XBee RF modules is omnidirectional. However,
it is desired to have differences in the signals received by the RF modules
mounted on the robot based on the angle from which the signal is coming from the
remote. Therefore, one of the major components of the robotic cart is the
reflector array that enables the XBee modules to be direction sensitive.

\subsection{Reflector Array Design}
\label{sec:reflectorArrayDesign}
Two different models of reflector arrays were designed and constructed (see Fig.~\ref{fig:reflectorDesigns}). %
%
\begin{figure}[htbp]
  \centering
  \begin{subfigure}[b]{0.45\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/img/paraboloidalReflector.png}
    \caption{}
    \label{fig:paraboloidalReflector}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/img/parabolicReflector.png}
    \caption{}
    \label{fig:parabolicReflector}
  \end{subfigure}
  \caption[Reflector designs]{Two different reflector design for the robotic cart:~\subref{fig:paraboloidalReflector} Purely paraboloidal reflector array~and~\subref{fig:parabolicReflector} parabolic/paraboloidal reflector array.}
  \label{fig:reflectorDesigns}
\end{figure}
%

The first design, shown in Fig.~\ref{fig:paraboloidalReflector}, uses a
reflector with a paraboloidal shape. This shape was selected since all signals
entering the reflector parallel to the axis of the reflector will be focused at
the focal point of the paraboloid. By mounting the XBee such that the center of
the antenna coincides with the focal point of the paraboloid, the signal
strength of the signals entering parallel to the axis will be maximized. The
second design, shown in Fig.~\ref{fig:parabolicReflector}, is the same on the
lower half as the first design. However, the upper half is simply a surface
where the horizontal cross-section is a parabola. The purpose for this design is
similar to that of the first design, but the parabolic shape on the top will
allow stronger detected signal strength of signals coming from above the
reflector. Since the remote will be held by a person, it will generally be above
the robot. The parabolic/paraboloidal reflector design is intended to allow
better reception of signals from above.

\subsection{Reflector Construction}
With the recent advancements in 3D printing technology, it is not difficult to
create an object with a parabolic shape. Here, the reflector dishes
were created using a 3D printer. The reflector array was designed to be modular,
where the dishes, top plate, and bottom frame were printed separately. After
printing, the dishes were lined with foil tape to provide the reflective surface
to focus the signals onto the antenna of the XBee. A layer of foil tape was also
placed on the top plate to provide a ground plane for the XBee. The parts were
then fastened together using M3 screws and nuts (see Fig.
\ref{fig:reflectorConstruction}).
%
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=0.1]{figs/img/reflectorConstruction.jpg}
    \caption{Reflector construction using 3D printer.}
    \label{fig:reflectorConstruction}
\end{figure}
%

% ----------------------------------------------------------------------
\section{Localization and Navigation}
\label{sec:locAndNavAlgos}
%----------------------------------------------------------------------

This section illustrates the localization and navigation algorithms for the
proposed robotic cart to operate in an indoor/outdoor environment. For the sake
of simplicity, the cart is modeled as a differential drive mobile robot (DDMR).
The direction and distance of the remote relative to the cart are determined
using a localization algorithm. The estimated distance and angle are then passed
to a navigation algorithm which calculates and applies the actuator commands
(in this case, wheel speeds of the robot) to move the robot toward the remote.

\subsection{Robot Model}\label{subsec:robotModel}
The robot used in this work was a differential drive mobile robot, which has
two drive wheels and a caster wheel for the balance. The robot turns by applying
different speeds to the left and right wheels. As shown in Fig.~\ref{fig:robotGeometry}, the radius of the wheels is $R$, and the distance
between the wheels is $L.$ The pose of the robot is given by the $x$-coordinate
($x$), the $y$-coordinate ($y$), and the orientation, ($\theta$), as shown in
Fig.~\ref{fig:robotPose}. %
%
\begin{figure}[htbp]
    \centering
    \begin{subfigure}{0.4\linewidth}
        \centering
        \includegraphics[width=\textwidth]{figs/robotGeometry.pdf}
        \caption{}
        \label{fig:robotGeometry}
    \end{subfigure}%
    \begin{subfigure}{0.4\linewidth}
        \centering
        \includegraphics[width=\textwidth]{figs/robotPose.pdf}
        \caption{}
        \label{fig:robotPose}
    \end{subfigure}
    \caption{Kinematics of the robotic cart modeled as a DDMR.}
    \label{fig:robotModelParameters}
\end{figure}
%
Generally, the robot is controlled by commanding a linear and angular speed ($v$ and $\omega$, respectively). These speeds are converted into left and right wheel speeds. The following equations are used to calculate the angular left and right wheel speeds ($\omega_l$ and $\omega_r$, respectively): %
%
\begin{align*}
  \omega_l = \left(v - \omega\frac{L}{2}\right)\frac{1}{R}\qq{and} \omega_r = \left(v + \omega\frac{L}{2}\right)\frac{1}{R}.
\end{align*}
%
To control DC motors in this way, the relationship between duty cycle and angular speed must be determined. Then the duty cycles to apply to the wheels can be calculated for the commanded $v$ and $\omega$.

\subsection{Relative Localization of Remote}
The localization algorithm is used to estimate the position of the remote with
respect to the mobile robot/cart's local coordinate frame. First, the omnidirectional
transceiver mounted on top of the reflectors sends a signal strength request to the
remote. The remote then replies with a message containing the strength of the
signal it just received. This reply is detected by the receivers inside the
reflectors as well as the omnidirectional transceiver. The strength detected by
each of the directional receivers and the strength contained in the reply are
then recorded. At this point, the entire reflector array is rotated
$\ang{9},$ and this process is repeated. The robot continues taking
measurements in this way until the reflectors have been rotated one quarter
turn. Since there are four reflectors at $\ang{90}$ to each other, a strength
measurement has been recorded for every $\ang{9}$ increment around the robot.
The angle of the remote is then estimated as the direction from which the
strongest signal was received. The distance to the remote is calculated using
the free-space path loss formula. The direction of reflector rotation is then
reversed since the wires connecting the RF modules in the reflectors prevent the
reflector from freely spinning. A flowchart of this algorithm is shown in Fig.~\ref{fig:localizationAlgoFlowchart}. %
%
\begin{figure}[htbp]
    \centering
    \includegraphics[width=.48\textwidth]{figs/localizationAlgorithmFlowchart.pdf}
    \caption{Flowchart localizing the remote.}
    \label{fig:localizationAlgoFlowchart}
\end{figure}

\subsection{Navigation of Mobile Cart}\label{subsec:navAlgo}
The navigation algorithm is used to drive the robot toward the remote. The inputs to the navigation algorithm are the angle to the remote ($\theta_r$) and the distance to the remote ($d_r$). A target point is then calculated as the point that is in the same direction as the remote, but closer to the robot by a fixed following distance ($d_{follow}$), as shown in Fig.~\ref{fig:navAlgoDiagram}. The distance to the target point is calculated as $d_{tgt} = d_r - d_{follow}$, and the angle to the target point is $\theta_{tgt} = \theta_r$. The linear and angular speeds of the robot ($v$ and $\omega$, respectively) are then calculated using proportional control by the following equations: %
%
\begin{align*}
  v = K_vd_{tgt}\qq{and}\omega = K_\omega\theta_{tgt}.
\end{align*}
%
The appropriate duty cycles are then calculated as specified in section~\ref{subsec:robotModel} and applied to the wheel DC motors (robot actuators). %
%
\begin{figure}[htbp]
    \centering
    \begin{subfigure}{0.45\linewidth}
        \centering
        \includegraphics[width=\textwidth]{figs/navigationAlgorithmDiagram.pdf}
        \caption{Target Point Diagram}
        \label{fig:navAlgoDiagram}
    \end{subfigure}%
    \begin{subfigure}{0.45\linewidth}
        \centering
        \includegraphics[width=\textwidth]{figs/navigationAlgorithmFlowchart.pdf}
        \caption{Flowchart}
        \label{fig:navAlgoFlowchart}
    \end{subfigure}
    \caption{Navigation algorithm for the mobile cart to move towards the remote.}
    \label{fig:navAlgoDetails}
\end{figure}

\section{Hardware Implementation and Prototype}
\label{sec:hardwareImplementation}

The remote and mobile cart were designed and implemented using off-the-shelf
components. A customized Budget Bot chassis was the base of the proposed smart
robotic cart. The new DC motors installed in the Budget Bot are Pololu 27D Metal
Gear motors which provide a max speed of $2.72~[\si{\meter\per\second}]$ when
using the wheels with a diameter of $2R = 98~[\si{\milli\meter}].$ These motors
allow the robotic cart to follow the remote that can move at an average person's
walking speed. The next step was to attach the BeagleBone Blue microcomputer,
XBee reflector array assembly, and breadboard to the top of the robot. A 2-cell
LiPo battery was also installed inside the chassis of the mobile cart to provide
power to the BeagleBone Blue directly and the breadboard through the
switch. %The power supplied to the breadboard is sent through a regulator circuit to drop it down from the 7.4V of the LiPo to 3.3V of the XBee. This circuit is also used on the remote which consists of a 7.4V LiPo battery and the XBee module with voltage regulator in between. This voltage regulator is built out of a LM117 regulator and a 10uF ceramic capacitor between the input and output pins of the regulator. %
The circuit diagrams for the robot and remote are shown in Figs.
\ref{fig:robotCircuit} and \ref{fig:remoteCircuit}. %

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[b]{0.47\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/robotCircuit.pdf}
    \caption{}
    \label{fig:robotCircuit}
  \end{subfigure}
  \begin{subfigure}[b]{0.47\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/remoteCircuit.pdf}
    \caption{}
    \label{fig:remoteCircuit}
  \end{subfigure}
    \caption{Circuit diagrams for~\subref{fig:robotCircuit} robotic cart~and~\subref{fig:remoteCircuit} remote.}
    \label{fig:CktDiagramRoboticCartRemote}
\end{figure}
%
The reflector array  was mounted on a stepper motor that was then attached to a 3D printed bracket. This bracket was then attached to the chassis using M3 screws. Another feature of this bracket is that it had a stop block built into the top  to allow the robot to automatically initialize the reflector array to the zero position when the robot starts up. This is accomplished by commanding a turn of \ang{90} and allowing the reflectors to hit the stop block and be held there until this turn is complete. %
The Xbee modules from the reflector array posed a bit of a problem when it came to connecting them to the BeagleBone Blue. The BeagleBone Blue has three standard UART ports and two others found in the USB and UART-GPS, which makes a total of five UARTs. Unfortunately, not all five ports can be used to communicate with XBees since UART0 is used to provide communication with a computer through the console. Since port 0 is reserved for this function, the number of usable ports is only four, but the robot requires communication with five XBees. The solution to this problem was to use two of the GPIO pins, two of the UART ports, and a dual 4-channel multiplexer. One of the UARTs can be directly connected to the top XBee, and the other UART can be routed through the multiplexer to the four side XBee modules. Then two UART ports are used to communicate with all five XBees. %
The complete prototype of the proposed robotic cart and remote are shown in Fig.~\ref{fig:finishedPrototypes}. %
%
\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
        \centering
        \includegraphics[width=\textwidth]{figs/img/Finalized_robot.png}
        \caption{}
        \label{fig:overallPrototype}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\linewidth}
        \centering
        \includegraphics[scale=0.25]{figs/remote.pdf}
        \caption{}
        \label{fig:remotePrototype}
    \end{subfigure}
    \caption{The complete prototype of the proposed smart robotic cart~\subref{fig:overallPrototype} mobile robotic cart~and~\subref{fig:remotePrototype} remote.}
    \label{fig:finishedPrototypes}
\end{figure}
%
The BeagleBone Blue embedded robotics computer already has a set of ports on it
that can be accessed and controlled using the Robot Control Library from
Strawson Design (see
\href{http://strawsondesign.com/docs/librobotcontrol/}{http://strawsondesign.com/docs/librobotcontrol/},
for details). Some custom libraries were built on top of the robot control
library to handle XBee frames, AT commands, and the stepper motor control. The
XBee Frames library takes a given block of data containing the message and then
packages it into a XBee frame to send over UART to the XBee desired module. The
XBee communications library also handles received messages from the XBee module
and validates the received frame's integrity and extracts the message data from
it. On top of the XBee communications library there is a library that generates
AT Commands to package in the XBee frames. The AT command library also handles
extracting response data from the AT response command structure and validates
it. See the process for XBee communication over UART in
Fig.~\ref{fig:CommandProcessDiagram}. %
%
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.48\textwidth]{figs/img/Command Process Diagram.png}
  \caption{Process for XBee communication over UART.}
  \label{fig:CommandProcessDiagram}
\end{figure}
%
The final custom library is the stepper motor control library. This library had
to be written since instead of using a dedicated stepper motor controller, two
of the regular BBBlue DC motor control ports were used to power the stepper
motor. The library handled translating how many steps to turn into the phase
states to be sent to the DC motor ports that are connected to the stepper motor.
The library also helped to keep track of basic information related to the
stepper motor such as what its current angle should be.

%----------------------------------------------------------------------
\section{Experimental Results}
\label{sec:Experimental Results}
%----------------------------------------------------------------------

After the robotic cart and the remote were built, several different variants of
the algorithms were tested. There were two main types of variants tested. In one
variant, the stepper motor is locked, preventing the reflector from rotating. In
the other variant, the stepper motor is used to sweep through the angles. The
experiments with the complete prototype of the proposed smart robotic cart shown
in Fig.~\ref{fig:finishedPrototypes} were conducted on a hallway, a laboratory
floor, and the ground floor of the Business and Engineering Convergence Center
of Bradley University. %
%
\begin{figure}[htbp]
  \centering
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/71.jpeg} 
    \caption{}
    \label{fig:71}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/141.jpeg} 
    \caption{}
    \label{fig:141}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
   \centering
   \includegraphics[width=\textwidth]{videos/frames/211.jpeg} 
   \caption{}
   \label{fig:211}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/351.jpeg} 
    \caption{}
    \label{fig:351}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/491.jpeg} 
    \caption{}
    \label{fig:491}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/561.jpeg} 
    \caption{}
    \label{fig:561}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/631.jpeg} 
    \caption{}
    \label{fig:631}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/701.jpeg} 
    \caption{}
    \label{fig:701}
  \end{subfigure}
  %
  \caption{Experiment results demonstrating the performance of the proposed smart robotic cart in following the remote.}
  \label{fig:experResultsImages}
\end{figure}
%
Fig.~\ref{fig:experResultsImages} summarizes the performance of the proposed smart robotic cart. A person holding the remote shown in Fig.~\ref{fig:remotePrototype} follows a random trajectory. As can be seen, the mobile cart shown in Fig.~\ref{fig:overallPrototype} is able to follow the remote regardless of the navigation environment of both of the remote and the mobile cart.

%----------------------------------------------------------------------
\section{Conclusion and Future Work}
%----------------------------------------------------------------------
In this paper, we have presented a prototype of a smart robotic cart using radio
frequency signal strengths. In the proposed smart robotic cart, the mobile cart
follows a remote. A functional design for a mobile cart was developed and
tested. In these tests, it was concluded that with the robot's current design,
it would be extremely difficult to calculate an accurate distance to the remote
from the signal strength alone. Therefore, the current design follows the remote
based on angle measurements alone. Due to the limitation of not having a proper
estimated line-of-sight distance, the current implementation is unable to
dynamically adjust its behavior based on proximity to the remote. One such
planned parameter was the robot's velocity, which would have been reduced as the
robot approached the remote target to prevent it from running into the user.

Based on the literature review, it was determined that the smart robotic cart
design of this cart is more cost-effective than most, if not all, of the
existing solutions. It was shown that the robot could successfully track the
remote target even when obstacles were obstructing the line-of-sight path
between the robot and remote. An immediate future research avenue of this work
is to implement filtering algorithms for estimating line-of-sight distance
between the mobile cart and the remote.

\bibliographystyle{IEEEtran}
\bibliography{bib/references.bib}

\end{document}

### 2021-07-19 video2_FramesMain.m

@@ -1,0 +1,51 @@
+function video2_FramesMain
+    clear all
+    close all
+    clc    
+    
+    % call the function that converts a video frames
+    readFrames('videos/smartRoboticCartIntroVideo.mp4')
+    
+ function [ frame ] = readFrames( vid )
+
+    readerobj = VideoReader(vid);
+    numFrames = get(readerobj, 'numberOfFrames');    
+    %vidFrames = read(readerobj);
+
+    for k = 1 :70: numFrames
+        mov(k).cdata = read(readerobj, k);%vidFrames(:,:,:,k);
+        mov(k).colormap = [];
+        %imshow(mov(k).cdata);
+        imname=strcat(int2str(k), '.jpeg');
+        filename = ['videos/frames/', imname];
+        imwrite(mov(k).cdata, filename);
+        %extractComponents(mov(k).cdata);
+    end
+    fprintf('Done..\n');
+
+
+% % import the video file
+% obj = VideoReader('org.mp4');
+% vid = read(obj);
+%   
+%  % read the total number of frames
+% frames = obj.NumberOfFrames;
+%   
+% % file format of the frames to be saved in
+% ST ='.jpg';
+%   
+% % reading and writing the frames 
+% for x = 1 : frames
+%   
+%     % converting integer to string
+%     Sx = num2str(x);
+%   
+%     % concatenating 2 strings
+%     Strc = strcat(Sx, ST);
+%     Vid = vid(:, :, :, x);
+%     cd frames
+%   
+%     % exporting the frames
+%     imwrite(Vid, Strc);
+%     cd ..  
+% end

### 2021-09-14 paperIEEE-ROSE2021-BrBeAlShMi.tex
Conference paper version Sep 13, 2021
Update paperIEEE-ROSE2021-BrBeAlShMi.tex

@@
 disabilities cannot push one cart let alone have a second cart to carry more
-items. Moreover, robots used for this purpose are costlier than they are worth.
+items. Moreover, robots used for this purpose can range in cost from \$5,000 to \$10,000 per unit. 
 Here we propose a robotic cart that would primarily leverage the emerging radio
@@
    \centering
-   \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
-   \caption{Shopping Support Robot}
+   \includegraphics[width=0.35\textwidth]{figs/img/ShoppingSuportRobot}
+   \caption{Shopping support robot.}
    \label{fig:ShoppingSup}
@@
    \centering
-   \includegraphics[width=0.45\textwidth]{figs/img/SmartCart}
+   \includegraphics[width=0.40\textwidth]{figs/img/SmartCart}
    \caption{Smart Cart Robot}
@@
   \centering
-  \includegraphics[scale=0.2]{figs/systemBlockDiagram.pdf}
+  \includegraphics[width=0.5\textwidth]{figs/systemBlockDiagram.pdf}
   \caption{System level block diagram detailing inputs and outputs to the
@@
 incoming RF messages which are passed through the RF transceiver. The remote
-outputs the an RF message back to the mobile cart, which will be discussed
+outputs the RF message back to the mobile cart, which will be discussed
 later. The subsystem block diagram of the mobile cart is shown in
@@
   \centering
-  \begin{subfigure}[b]{0.24\linewidth}
+  \begin{subfigure}[b]{0.30\linewidth}
     \centering
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
+  \begin{subfigure}[b]{0.30\linewidth}
     \centering
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
+  \begin{subfigure}[b]{0.30\linewidth}
    \centering
@@
  \end{subfigure}
-  \begin{subfigure}[b]{0.24\linewidth}
+ \\
+  \begin{subfigure}[b]{0.30\linewidth}
     \centering
@@
   \end{subfigure}
-  \\
-  \begin{subfigure}[b]{0.24\linewidth}
+  \begin{subfigure}[b]{0.30\linewidth}
     \centering
@@
   %
-  \begin{subfigure}[b]{0.24\linewidth}
+  \begin{subfigure}[b]{0.30\linewidth}
     \centering
@@
   %
-  \begin{subfigure}[b]{0.24\linewidth}
+  \\
+  \begin{subfigure}[b]{0.30\linewidth}
     \centering

### 2021-09-14 paperIEEE-ROSE2021-BrBeAlShMi.tex
Gramatical changes based on feedback

@@
 of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF
-radios, the robot is equipped with a parabolic reflector, which improves radio
-reception at various distances and angles,~\textit{i.e.,} angle of arrivals of
-RF signals from the remote, based on research done previously in this type of
-robot localization and mapping~\cite{Miah2018-Intelligent,Li2013ANA}. The approach using signal strengths of RF signals also requires an understanding
+radios, the robot is equipped with a parabolic reflector. This reflector helps improves radio reception at various distances and angles,~\textit{i.e.,} the angle of arrival of
+the RF signals from the remote.
+This reflector setup is based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent,Li2013ANA}.
+The approach using signal strengths of RF signals also requires an understanding
 of multipath interference which is common in RF based wireless positioning
 sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using
-course estimation calculations such as the received signal strength indicator (RSSI)
- together with the time difference of arrival (TDoA) is key to compensate for the effect of multipath
-interference.
+course estimation calculations such as the received signal strength indicator (RSSI) together with the time difference of arrival (TDoA) is key to compensate for the effect of multipath interference.
 
@@
 incoming RF messages which are passed through the RF transceiver. The remote
-outputs the RF message back to the mobile cart, which will be discussed
+outputs an RF message back to the mobile cart, which will be discussed
 later. The subsystem block diagram of the mobile cart is shown in

### 2021-09-20 paperIEEE-ROSE2021-BrBeAlShMi.tex
Final version 1.0 of the conference paper

@@
 \usepackage{siunitx}
+\usepackage{tikz}
+% load libraries
+\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,snakes}
+\def\smgrid{0.5}
 \usepackage{nohyperref}
@@
 
-\title{A Smart Robotic Cart Prototype using RF Signal Strength \thanks{Authors would like to acknowledge Illinois Space
-    Grants Consortium for funding this project under grand no. \#}
-  \thanks{The results presented in this paper were produced by a group of senior
-    undergraduate students: Jason Braker, Darrah Beebe, and Kalistah Allen }
+\title{A Smart Robotic Cart Prototype using RF Signal Strength \thanks{Authors
+    would like to thank Mr. Christopher Mattus.  }
 }
@@
 of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF
-radios, the robot is equipped with a parabolic reflector. This reflector helps improves radio reception at various distances and angles,~\textit{i.e.,} the angle of arrival of
+radios, the robot is equipped with a parabolic reflector. This reflector helps improve radio reception at various distances and angles,~\textit{i.e.,} the angle of arrival of
 the RF signals from the remote.
@@
 The approach using signal strengths of RF signals also requires an understanding
-of multipath interference which is common in RF based wireless positioning
+of multipath interference which is common in RF based wireless position
 sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using
-course estimation calculations such as the received signal strength indicator (RSSI) together with the time difference of arrival (TDoA) is key to compensate for the effect of multipath interference.
+course estimation calculations such as the received signal strength indicator (RSSI) together with the time difference of arrival (TDoA) is the key to compensate for the effect of multipath interference.
 
@@
 adjusting the robot's motion to spend more time where the channel strength is
-greater. All solutions reported in the literature referred to here required line-of-sight
+greater. All solutions reported in the literature referenced here required line-of-sight
 communication between the robot and the user. However, in this work, we aim to use the
@@
 \begin{figure}[htbp]
+  % \includegraphics[width=0.5\textwidth]{figs/systemBlockDiagram.pdf}
     \centering
-  \includegraphics[width=0.5\textwidth]{figs/systemBlockDiagram.pdf}
+    \begin{tikzpicture}    
+      % \tikzstyle{every node} = [font=\tiny];
+      \tikzstyle{block} = [draw, rectangle, fill=blue!15, rounded corners, minimum height=0.5 cm, minimum width=0.5cm];
+      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
+      \node[block,text width= 2.0cm, text centered](mobileCart){Mobile cart};
+      \node[block,text width= 2.0cm, text centered, below of=mobileCart, node distance=1.25cm](remote){Remote};
+      % Connections
+      \draw[stealth-stealth,ultra thick]
+      (mobileCart.south) --(remote.north);
+      % Layers
+      \begin{pgfonlayer}{background}
+        \filldraw[fill=red!10,draw = red,dashed,ultra thick, rounded corners]                
+        ($(remote.south west) + (-1.5*\smgrid,-0.25*\smgrid)$)node[](tmp1){} rectangle ($(mobileCart.north east) + (1.2*\smgrid,1.5*\smgrid)$)node[](tmp2){};
+        \draw
+        ($(mobileCart.north) + (-0.25*\smgrid,0.75*\smgrid)$)node{\textbf{Mobile cart system}};
+        % %%% Inputs and outputs
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,4.5*\smgrid)$) --node[near end,above]{Power}++(-3.0*\smgrid,0);
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,3*\smgrid)$) --node[near end,above]{On/Off switch}++(-3.0*\smgrid,0);
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,0.5*\smgrid)$) --node[near end,above]{Motion control}++(-3.0*\smgrid,0);
+        \draw[-stealth,thick]
+        ($(tmp2)+(0,-2.75*\smgrid)$) --node[very near end,above]{Cart position trajectory}++(4.0*\smgrid,0);
+      \end{pgfonlayer}
+    \end{tikzpicture}  
   \caption{System level block diagram detailing inputs and outputs to the
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
+    % \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
+    \begin{tikzpicture}    
+      \tikzstyle{every node} = [font=\footnotesize];
+      \tikzstyle{block} = [draw, rectangle, fill=orange!15, rounded corners, minimum height=0.5 cm, minimum width=0.5cm];
+      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
+      \node[block,text width= 2.5cm, text centered](rfTransceiverModule){RF transceiver module};
+      % Connections
+      % \draw[stealth-stealth,ultra thick]
+      % (mobileCart.south) --(remote.north);
+      % Layers
+      \begin{pgfonlayer}{background}
+        \filldraw[fill=green!10,draw = blue,dotted,thick, rounded corners]                
+        ($(rfTransceiverModule.south west) + (-0.25*\smgrid,-0.25*\smgrid)$)node[](tmp1){} rectangle ($(rfTransceiverModule.north east) + (0.25*\smgrid,0.75*\smgrid)$)node[](tmp2){};
+        \draw
+        ($(rfTransceiverModule.north) + (-0.25*\smgrid,0.5*\smgrid)$)node{\textbf{Remote}};
+        % %%% Inputs and outputs
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,2.0*\smgrid)$) --node[near end,above]{Battery power}++(-3.0*\smgrid,0);
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,0.75*\smgrid)$) --node[very near end,above]{Incoming RF messages}++(-3.5*\smgrid,0);
+        \draw[-stealth,thick]
+        ($(tmp2)+(0,-1.25*\smgrid)$) --node[midway,above]{Outgoing RF messages}++(5.25*\smgrid,0);
+      \end{pgfonlayer}
+    \end{tikzpicture}  
     \caption{}
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
+    % \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
+    \begin{tikzpicture}[scale=1.15,transform shape]    
+      \tikzstyle{every node} = [font=\tiny];
+      \tikzstyle{block} = [draw, rectangle, fill=orange!15, rounded corners, minimum height=0.6 cm, minimum width=0.5cm];
+      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
+      \node[block,text width= 1.0cm, text centered](embeddedComputer){Embedded computer};
+      \node[block,text width= 1.0cm, text centered, right of=embeddedComputer, node distance=2.5cm](DcMotors){DC motors};
+      \node[block,text width= 1.5cm, text centered, below of=DcMotors, node distance=0.75cm](omnidirectionalRfTransciever){Omnidirectional RF transceiver};
+      \node[block,text width= 1.5cm, text centered, below of=embeddedComputer, node distance=1.5cm](multiplexer){Multiplexer};
+      \node[block,text width= 1.5cm, text centered, below of=multiplexer, node distance=0.75cm](RFReceiver1){Direction sensitive RF receiver};
+      \node[block,text width= 1.5cm, text centered, below of=RFReceiver1, node distance=0.75cm](RFReceiver2){Direction sensitive RF receiver};
+      \node[block,text width= 1.5cm, text centered, right of=RFReceiver1, node distance=2.5cm](RFReceiver3){Direction sensitive RF receiver};
+      \node[block,text width= 1.5cm, text centered, right of=RFReceiver2, node distance=2.5cm](RFReceiver4){Direction sensitive RF receiver};
+      % Connections
+      \draw[stealth-,thick]
+      (embeddedComputer.165) --node[near end,above]{Battery power}++(-2.5*\smgrid,0);
+      \draw[stealth-,thick]
+      (embeddedComputer.-165) --node[near end,below]{ON/OFF switch}++(-2.5*\smgrid,0);
+      \draw[-stealth,thick]
+      (embeddedComputer.0) --(DcMotors.180);
+      \draw[-stealth,thick]
+      (DcMotors.0) --node[midway,above]{Wheel velocities}++(2.5*\smgrid,0);
+      \draw[-stealth,thick]
+      (omnidirectionalRfTransciever.0) --node[near end,above]{Outgoing RF signals}++(2.75*\smgrid,0);
+      \draw[stealth-,thick]
+      (omnidirectionalRfTransciever.-170) --node[very near end,above]{Incoming RF signals}++(-7.5*\smgrid,0)node[](tmp1){};
+      \draw[stealth-stealth,very thick]
+      (multiplexer.90) --(embeddedComputer.-90);
+      \draw[stealth-stealth,thick]
+      (embeddedComputer.-45) |-(omnidirectionalRfTransciever.170);
+      \draw[-stealth]
+      ($(tmp1) + (\smgrid,0)$) |- (RFReceiver1.west);
+      \draw[-stealth]
+      ($(tmp1) + (\smgrid,0)$) |- (RFReceiver2.west);
+      \draw[-stealth]
+      ($(tmp1) + (\smgrid,0)$) |- ($(RFReceiver2.south)+(0,-0.5*\smgrid)$) -| ($(RFReceiver3.east)+(0.5*\smgrid,0)$) -- (RFReceiver3.east);
+      \draw[stealth-]
+      (RFReceiver4.east) -- ++(0.5*\smgrid,0);
+      \draw[stealth-stealth]
+      (RFReceiver1.east) -- ++(0.5*\smgrid,0)|-(multiplexer.-10);
+      \draw[stealth-stealth]
+      (multiplexer.10) -| (RFReceiver3.north);
+      \draw[stealth-stealth]
+      (RFReceiver2.east) -- ++(0.75*\smgrid,0)|-(multiplexer.-5);
+      \draw[stealth-stealth]
+      (RFReceiver4.west) -- ++(-0.5*\smgrid,0)|-(multiplexer.0);
+
+      % Layers
+      \begin{pgfonlayer}{background}
+        \filldraw[fill=green!10,draw =blue,dotted,thick, rounded corners]                
+        ($(RFReceiver2.south west) + (-0.25*\smgrid,-0.25*\smgrid)$) rectangle ($(DcMotors.north east) + (0.75*\smgrid,0.75*\smgrid)$);
+        \draw
+        ($(embeddedComputer.north) + (2*\smgrid,0.4*\smgrid)$)node{\textbf{Mobile cart}};
+      \end{pgfonlayer}
+    \end{tikzpicture}  
     \caption{}
@@
 \subsection{Reflector Construction}
-With the recent advancements in 3D printing technology, it is not difficult to
+With the recent advances in 3D printing technology, it is not difficult to
 create an object with a parabolic shape. Here, the reflector dishes
@@
   %
-  \caption{Experiment results demonstrating the performance of the proposed smart robotic cart in following the remote.}
+  \caption{Experimental results demonstrating the performance of the proposed smart robotic cart in following the remote.}
   \label{fig:experResultsImages}

### 2021-09-24 presIEEE-ROSE2021-BrBeAlShMi.tex
Added ROSE 2021 presentation (copy of finalReportPres - updated title slide)

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

% \UseRawInputEncoding
\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
\usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage[font=tiny,labelfont=bf]{caption}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{rotating}

% Customize Warsaw color 
\setbeamercolor*{palette primary}{use=structure,fg=white,bg=red!50!black}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=red!60!black}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=red!70!black}

% Customize Warsaw block title and background colors
\setbeamercolor{block title}{bg=red!50!black,fg=white}

\setbeamertemplate{navigation symbols}{} % Remove navigation symbols
\setbeamertemplate{bibliography item}{\insertbiblabel}  % insert bibliography numbers instead of symbol
\setbeamertemplate{caption}[numbered] % adds the figure or table number to the caption.

% Set up footer manually
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.6\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor\hspace*{1em}(\insertshortinstitute)
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.15\paperwidth,ht=2.25ex,dp=1ex,center]{date in head/foot}%
    \usebeamerfont{date in head/foot}\insertframenumber{} / \inserttotalframenumber
  \end{beamercolorbox}}%
  \vskip0pt%
}

%==============================================================================
%     TITLE
%==============================================================================
\title[A Smart Robotic Cart]{A Smart Robotic Cart Prototype using RF Signal Strength}

\author[J.~Braker, D.~Beebe, K.~Allen, P.~Shastry, S.~Miah]{Jason~Braker \and Darrah~Beebe \and Kallistah~Allen \and Prasad Shastry \and Md Suruz Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Bradley University] % (optional, but mostly needed)
{
  Department of Electrical and Computer Engineering\\
  Bradley University\\
  1501 W. Bradley Avenue\\
  Peoria, IL, 61625, USA
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[]{IEEE International Symposium on ROSE 2021\\
October~28-29,~2021}

% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\logo{\hfill\href{http://www.bradley.edu}{\includegraphics[width=0.75cm]{figs/logoBU1-Print}}}  % place logo in every page

\subject{Mobile Robot Localization}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

%==============================================================================
%==============================================================================
%     START OF SLIDES
%==============================================================================
%==============================================================================

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline} 
  \tableofcontents%[pausesections]
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}

\begin{frame}{Introduction}{}
 \begin{center}
    \href{videos/smartRoboticCartIntroVideo.mp4}{\includegraphics[width=0.8\textwidth]{figs/img/finalPresVideoTitle.png}}
  \end{center}
\end{frame}

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{LARGE}
      Design a robotic cart that follows the user without line of sight (LoS) sensors
    \end{LARGE}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{LARGE}
      Utilize wireless radio frequency (RF) signal strength to locate and then follow the user
    \end{LARGE}
  \end{block}
\end{frame}

%----------------------------------

\begin{frame}{Introduction}{}
%\documentclass{beamer}
  % applications of mobile robot navigation and problem description
  \begin{block}{Applications of Mobile Carts}
    \begin{itemize}
      %\item Mail delivery
      %\item Transferring files in offices
      \item Carrying medical supplies in hospitals (Fig.\ref{fig:medCart})
      \item Carrying materials and tools in factories (Fig. \ref{fig:factCart})
      \item Shopping carts for ease of use and people with disabilities
    \end{itemize}
  \end{block}
      \begin{figure}
      \centering
      \begin{minipage}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=3.0cm]{figs/img/MedicalRoboticCart}
        \caption{Medical Mobile Robotic Cart\textsuperscript{a}}
        \label{fig:medCart}
      \end{minipage}
      \begin{minipage}[t]{0.4\textwidth}
        \centering
        \includegraphics[height=2.0cm]{figs/img/FactoryRoboticCart}
        \caption{Factory Mobile Robotic Cart\textsuperscript{b}}
        \label{fig:factCart}
      \end{minipage}
      \end{figure}
    \begin{tiny}
      \textsuperscript{a}https://www.cnet.com/news/robots-give-a-helping-hand-in-san-franciscos-newest-hospital/\\
      \textsuperscript{b}https://www.greencarcongress.com/2020/05/20200515-nvidia.html
    \end{tiny}
\end{frame}

%----------------------------------

\begin{frame}{Introduction}{Previous Work}
  \begin{block}{Existing Solution}
        Mobile application platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
  \end{block}
    \begin{figure}[b]
        \centering
        \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
        \caption{CompaRob}
        %\label{fig:sysBlockDiag}
    \end{figure}
\end{frame}

%----------------------------------

\begin{frame}{Introduction}{Previous Work}
  \begin{block}{Existing Solution}
        Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
  \end{block}
    \begin{figure}[b]
        \centering
        \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
        \caption{Shopping Support Robot}
        %\label{fig:sysBlockDiag}
    \end{figure}
\end{frame}

%----------------------------------

\begin{frame}{Introduction}{Previous Work}
  \begin{block}{Existing Solution}
    Arduino MEGA 2560, six ultrasonic sensors, two DC motors with Pulse Width Modulation (PWM), an Android Studio IDE device, and Bluetooth~\cite{Rawashdeh2017-Person}
  \end{block}
    \begin{figure}[b]
        \centering
        \includegraphics[width=0.45\textwidth]{figs/img/SmartCart}
        \caption{Smart Cart Robot}
        %\label{fig:sysBlockDiag}
    \end{figure}
\end{frame}

%----------------------------------

\begin{frame}{Introduction}{Existing Solutions}
  \begin{block}{Issues with Existing Solutions}
    \begin{itemize}
      \item Require line-of-sight between robot and user
      \item Some require costly dedicated sensors and hardware
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{Benefits of Proposed Solution}
    \begin{itemize}
      \item Line-of-sight is not required since analog RF signals will be used
      \item RF components are cost-effective and readily available
    \end{itemize}
  \end{block}
\end{frame}

%----------------------------------

\begin{frame}{Introduction}{System Requirements}
  \begin{block}{Specifications}
    \begin{itemize}
      \item Cart is to follow the remote target
      \item Cart is to maintain a distance of 1~[\si{\meter}] to 1.5~[\si{\meter}] from the remote target.
      \item Cart is to be able to attain a speed of at least 1~[\si{\meter\per\second}]
      \item Cart should not require line-of-sight to follow remote
     \end{itemize}
  \end{block}
\end{frame}

%------------------------------------------------------------------------------
%     SECTION BREAK
%------------------------------------------------------------------------------

\section{System Architecture}

\subsection{Block Diagrams}
\begin{frame}{Block Diagrams}
  \begin{block}{}
    Two main components of system
    \begin{itemize}
      \item Mobile Cart
      \item Remote Target
    \end{itemize}
    System Block Diagram shown in Fig. \autoref{fig:sysBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    \includegraphics[width=\textwidth]{figs/systemBlockDiagram.pdf}
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
  \end{figure}
\end{frame}

%----------------------------------

\begin{frame}{Block Diagrams}
  \begin{block}{}
    Remote Target Subsystem Block Diagram shown in Fig. \autoref{fig:sysRemoteBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
    \caption{Block Diagram of Remote Target Subsystem}
    \label{fig:sysRemoteBlockDiag}
  \end{figure}
\end{frame}

%----------------------------------

\begin{frame}{Block Diagrams}
  \begin{block}{}
    Mobile Cart Subsystem Block Diagram shown in Fig. \autoref{fig:sysMobileBlockDiag}
  \end{block}
  \begin{figure}[b]
    \centering
    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
    \caption{Block Diagram of Mobile Cart Subsystem}
    \label{fig:sysMobileBlockDiag}
  \end{figure}
\end{frame}

%----------------------------------

\subsection{System Components}
\begin{frame}{System Components}
  \begin{block}{Main Components}
    \begin{itemize}
      \item Budget Bot Chassis - Physical framework of robotic cart (Fig. \ref{fig:budgetBotChassis})
      \item BeagleBone Blue - Embedded computer to control robotic cart (Fig. \ref{fig:beagleboneBlue})
      \item XBee S2C Module - Wireless communication module (Fig. \ref{fig:XBeeModule})
    \end{itemize}
  \end{block}
  \begin{figure}
    \centering
    \begin{minipage}[t]{0.32\textwidth}
      \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
      \caption{Budget Bot Chassis}
      \label{fig:budgetBotChassis}
    \end{minipage}%
    \begin{minipage}[t]{0.32\textwidth}
      \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
      \caption{BeagleBone Blue}
      \label{fig:beagleboneBlue}
    \end{minipage}
    \begin{minipage}[t]{0.32\textwidth}
      \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
      \caption{XBee S2C Module}
      \label{fig:XBeeModule}
    \end{minipage}
  \end{figure}
\end{frame}

%----------------------------------

\begin{frame}{System Components}
    \begin{block}{Reflector Array}
    Two designs for reflector array:
    \begin{itemize}
      \item Paraboloidal Reflector - Focuses signals coming directly into reflector (Fig. \ref{fig:parabolodialReflector})
      \item Parabolic/Paraboloidal Reflector - Better reception of signals from above (Fig. \ref{fig:parabolicReflector})
    \end{itemize}
    \end{block}
    \begin{figure}
      \centering
      \begin{minipage}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5cm]{figs/img/paraboloidalReflector}
        \caption{Paraboloidal Reflector Model}
        \label{fig:parabolodialReflector}
      \end{minipage}
      \begin{minipage}[t]{0.4\textwidth}
        \centering
        \includegraphics[height=3.5cm]{figs/img/parabolicReflector}
        \caption{Combined Parabolic/Paraboloidal Reflector}
        \label{fig:parabolicReflector}
      \end{minipage}
    \end{figure}
\end{frame}

%----------------------------------

\setlength{\dashlinedash}{2pt}
\setlength{\dashlinegap}{4pt}
\setlength{\arrayrulewidth}{0.3pt}

\begin{frame}{System Components}
  \begin{table}[h!]
      \centering
      \begin{tabular}{c|c}
          \toprule
          \textbf{Quantity} & \textbf{Parts}\\
          \toprule
          2 & Budget Bot Chassis\\
          2 & Battery Packs for Budget Bot\\
          4 & 10 uF Ceramic Capacitor\\
          4 & LM1117 Regulator\\
          2 & 7.4V LiPo Batteries\\
          4 & 5.5 x 8.2 x 0.85 cm Mini Breadboard\\
          3 & XBee USB Adapter\\
          \bottomrule
          %\multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
          %\bottomrule
      \end{tabular}
      \caption{Parts Available in Laboratory}
      \label{tab:Partslablist}
  \end{table}
\end{frame}

%----------------------------------

\begin{frame}{System Components}
  \begin{table}[h!]
    \centering
    \small
    \begin{tabular}{c|c|c|c}
      \toprule
      \textbf{Quantity} & \textbf{Parts} & \textbf{Price} & \textbf{Total}\\
      \toprule
      12 & XBee S2C Module & \$ 23.10 & \$ 277.20\\
      12 & XBee Adapter Board & \$ 4.99 & \$ 59.88\\
      4 & Pololu 37D Metal Gearmotor 4751 & \$ 39.95 & \$ 159.80\\
      2 & Ovonic 7.4V 8,000mAh LiPo Battery & \$ 43.99 & \$ 87.98\\
      2 & Twotrees 4 Lead Nema 17 Stepper Motor & \$ 9.99 & \$ 19.98\\
      2 & DG409DJ+ Multiplexer & \$ 9.07 & \$ 18.14\\
      1 & 4-Pin JST SH Connector - 20 Pack & \$ 7.99 & \$ 7.99\\
      1 & 6-Pin JST SH Connector - 10 Pack & \$ 9.99 & \$ 9.99\\
      1 & Aluminum Foil Tape - 2 in x 5 yd & \$ 6.05 & \$ 6.05\\
      \bottomrule
      \multicolumn{3}{r|}{\textbf{Sub Total}} & \$ 653.88\\
      \bottomrule
    \end{tabular}
    \caption{Purchased parts for the Robotic Cart Project}
    \label{tab:Partslist}
  \end{table}
\end{frame}

%------------------------------------------------------------------------------
%     SECTION BREAK
%------------------------------------------------------------------------------

\section{Customized Reflector Array}

\begin{frame}{Customized Reflector Array}
  \begin{columns}
    \column{0.6\textwidth}
      \begin{block}{Problem}
        \begin{itemize}
          \item XBee S2C modules are omnidirectional
          \item Need to know direction of signals
        \end{itemize}
      \end{block}
    \column{0.4\textwidth}
     \begin{figure}
      \centering
      \includegraphics[height=0.5\textheight]{figs/img/XBee_signal.png}
      \caption{XBee Signal Pattern}
      \label{fig:XBeeSignal}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}{Customized Reflector Array}
  \begin{columns}
    \column{0.6\textwidth}
      \begin{block}{Solution}
        Use a parabolic reflector
        \begin{itemize}
          \item Reduces signal from behind reflector
          \item Maximizes signal entering parallel to axis of parabola
        \end{itemize}
      \end{block}
    \column{0.4\textwidth}
      \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/img/parabolicReflectorDiagram.png}
        \caption{Parabolic Reflector Characteristics}
        \label{fig:parabolicReflectorDiagram}
      \end{figure}
  \end{columns}
\end{frame}

\begin{frame}{Customized Reflector Array}
  \begin{block}{Paraboloidal Reflector Design}
    \begin{itemize}
      \item Maximizes signals entering perfectly horizontally
      \item Works best if remote is held at same level as robot
      \item Shown in Fig. \ref{fig:reflectorDesign1}
    \end{itemize}
  \end{block}
  \begin{figure}
    \centering
    \includegraphics[height=0.5\textheight]{figs/img/paraboloidalReflector.png}
    \caption{Paraboloidal Reflector}
    \label{fig:reflectorDesign1}
  \end{figure}
\end{frame}

\begin{frame}{Customized Reflector Array}
  \begin{block}{Parabolic/Paraboloidal Reflector Design}
    \begin{itemize}
      \item Maximizes signals entering directly in line with reflector
      \item Allows remote to be held higher than the robot
      \item Shown in Fig. \ref{fig:reflectorDesign2}
    \end{itemize}
  \end{block}
  \begin{figure}
    \centering
    \includegraphics[height=0.5\textheight]{figs/img/parabolicReflector.png}
    \caption{Parabolic/Paraboloidal Reflector}
    \label{fig:reflectorDesign2}
  \end{figure}
\end{frame}

\begin{frame}{Customized Reflector Array}
  \begin{block}{Reflector Construction}
    \begin{itemize}
      \item 3D printed parts (dishes, top and bottom frames)
      \item Lined dishes with foil tape
      \item Fastened parts together with M3 screws and nuts
    \end{itemize}
  \end{block}
  \begin{figure}
    \centering
    \includegraphics[height=0.5\textheight]{figs/img/reflectorConstruction.jpg}
    \caption{Reflector Construction}
  \end{figure}
\end{frame}

%------------------------------------------------------------------------------
%     SECTION BREAK
%------------------------------------------------------------------------------

\section{Algorithms}

\begin{frame}{Algorithms}{System Operation}
  \begin{figure}
    \centering
    \includegraphics[height=2.5in]{figs/systemOperationFlowchart.pdf}
    \caption{Flowchart of System Operation}
  \end{figure}
\end{frame}

\begin{frame}{Algorithms}{Localization Algorithm}
  \begin{figure}
    \centering
    \includegraphics[height=2.5in]{figs/localizationAlgorithmFlowchart.pdf}
    \caption{Flowchart of Localization Algorithm}
  \end{figure}
\end{frame}

\begin{frame}{Algorithms}{Navigation Algorithm}
  \begin{columns}
    \column{0.6\textwidth}
      \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{figs/navigationAlgorithmFlowchart.pdf}
        \caption{Flowchart of Navigation Algorithm}
      \end{figure}
    \column{0.4\textwidth}
      \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figs/navigationAlgorithmDiagram.pdf}
        \caption{Parameter Diagram}
      \end{figure}
  \end{columns}
\end{frame}

%------------------------------------------------------------------------------
%     SECTION BREAK
%------------------------------------------------------------------------------

\section{Implementation}

\begin{frame}{Implementation}
  \begin{columns}
    \column{0.6\textwidth}
    \begin{block}{Robot Assembly}
      \begin{itemize}
        \item Power from 2-cell LIPO battery
        \item Added power switch and LED indicator
        \item Swapped out motors to achieve 1 m/s
        \item Stepper motor mount with stop block
        \item BBB to XBee connections using UART
        \begin{itemize}
          \item 4 out of 5 UARTs are available
          \item 1 UART for top XBee
          \item 1 UART for side XBees using dual-direction multiplexer
        \end{itemize}
      \end{itemize}
    \end{block}
    \column{0.4\textwidth}
    \begin{figure}
      \centering
      \includegraphics[width=\textwidth]{figs/img/Finalized_robot.png}
      \caption{Final Version of the Robotic Cart}
      \label{fig:FinalizedRobot}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}{Implementation}
\begin{block}{Code Base}
  Custom libraries were put together to handle:
  \begin{itemize}
    \item Sending XBee frames over UART
    \item Assembling and interpreting AT command frames
    \item Stepper motor control with 2 DC motor control ports
  \end{itemize}
\end{block}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/img/Command Process Diagram.png}
  \caption{Process for XBee Communication over UART}
  \label{fig:CommandProcessDiagram}
\end{figure}
\end{frame}

\begin{frame}{Implementation}
\begin{block}{Code Trials}
Several different methods were tested for estimating the remote angle:
    \begin{itemize}
      \item Reflector Sweeping (40 strengths / 10 steps)
      \begin{itemize}
        \item Continuous Movement
        \item Segmented Movement
      \end{itemize}
      \item Reflector Locked (4 strengths / 1 step)
      \begin{itemize}
        \item Strongest 2-side interpolation
        \item K-Nearest-Neighbors
        \item Neural Network
      \end{itemize}
    \end{itemize}
\end{block}
\begin{block}{Results}
  Currently most stable - sweeping with segmented movement \\
  Most promising - sweeping with continuous movement
\end{block}
\end{frame}

\begin{frame}{Implementation}
\begin{block}{Experimental Results}
    \begin{itemize}
      \item The robot was tested in an Anechoic Chamber to evaluate its performance in an ideal environment. However, the performance did not improve greatly. This is probably due to problems in the algorithms at the time of test.
      \item RF absorbers were placed along the walls in the lab to see if reduced reflections would provide better performance. The robot appeared to perform slightly better in this environment (Fig. \ref{fig:AbsorberTest}).
    \end{itemize}
  \end{block}
    \begin{figure}
      \centering
      \includegraphics[height=3cm]{figs/img/Absorber_test.png}
      \caption{Robot Navigation Test with RF Absorbers}
      \label{fig:AbsorberTest}
    \end{figure}
\end{frame}

%----------------------------------

\begin{frame}{Implementation}{Challenges}
  \begin{block}{Challenges}
  Sources
  \begin{itemize}
    \item Noise in reported XBee signal strength values
    \item Multi-path effect
    \item No known global scope references 
  \end{itemize}    
    Effects
    \begin{itemize}
      \item Reduced angle accuracy and occasional random values
      \item  Accurate distance estimation was determined to be impossible with the current approach to the best of our knowledge
    \end{itemize}
  \end{block}
\end{frame}

%------------------------------------------------------------------------------
%     SECTION BREAK
%------------------------------------------------------------------------------

\section{Conclusions and Future Work}

\begin{frame}{Conclusions and Future Work}
  \begin{block}{Conclusions}
    \begin{itemize}
      \item The algorithm we implemented works the majority of the time
      \item Through tests and gathering data we were able iterate on our approach and tune the algorithms to function more reliably
      \item Our design is cost effective in comparison to other robotic carts
    \end{itemize}
  \end{block}
  \begin{block}{Future Work}
    \begin{itemize}
      \item Improve the localization algorithm for better angle estimation
      \item Test more reflector designs to see if the XBee signals can be more refined
      \item Implement obstacle detection and avoidance
      \item Multi-frequency radio modules to try to improve distance estimation
    \end{itemize}
  \end{block}
\end{frame}

%------------------------------------------------------------------------------
%     SECTION BREAK
%------------------------------------------------------------------------------

\section{References}

\begin{frame}{References}
  \bibliographystyle{IEEEtran}
  \bibliography{bib/references.bib}
\end{frame}

%==============================================================================
%==============================================================================
%     END OF SLIDES
%==============================================================================
%==============================================================================

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-09-27 presIEEE-ROSE2021-BrBeAlShMi.tex
IEEE ROSE 2021 - presentation slides final version 1.0

@@
 \usepackage{rotating}
+
+\usepackage{tikz}
+% load libraries
+\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,snakes}
+\def\smgrid{0.5}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/systemBlockDiagram.pdf}
+    % \includegraphics[width=0.2\textwidth]{figs/systemBlockDiagram.pdf}
+    \begin{tikzpicture}    
+      \tikzstyle{every node} = [font=\footnotesize];
+      \tikzstyle{block} = [draw, rectangle, fill=blue!15, rounded corners, minimum height=0.5 cm, minimum width=0.5cm];
+      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
+      \node[block,text width= 2.0cm, text centered](mobileCart){Mobile cart};
+      \node[block,text width= 2.0cm, text centered, below of=mobileCart, node distance=1.25cm](remote){Remote};
+      % Connections
+      \draw[stealth-stealth,ultra thick]
+      (mobileCart.south) --(remote.north);
+      % Layers
+      \begin{pgfonlayer}{background}
+        \filldraw[fill=red!10,draw = red,dashed,ultra thick, rounded corners]                
+        ($(remote.south west) + (-1.5*\smgrid,-0.25*\smgrid)$)node[](tmp1){} rectangle ($(mobileCart.north east) + (1.2*\smgrid,1.5*\smgrid)$)node[](tmp2){};
+        \draw
+        ($(mobileCart.north) + (-0.25*\smgrid,0.75*\smgrid)$)node{\textbf{Mobile cart system}};
+        % %%% Inputs and outputs
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,4.5*\smgrid)$) --node[near end,above]{Power}++(-3.0*\smgrid,0);
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,3*\smgrid)$) --node[near end,above]{On/Off switch}++(-3.0*\smgrid,0);
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,0.5*\smgrid)$) --node[near end,above]{Motion control}++(-3.0*\smgrid,0);
+        \draw[-stealth,thick]
+        ($(tmp2)+(0,-2.75*\smgrid)$) --node[very near end,above]{Cart position trajectory}++(4.0*\smgrid,0);
+      \end{pgfonlayer}
+    \end{tikzpicture}  
     \caption{Block Diagram of the Robotic Cart System}
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
+    % \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
+    \begin{tikzpicture}    
+      \tikzstyle{every node} = [font=\tiny];
+      \tikzstyle{block} = [draw, rectangle, fill=orange!15, rounded corners, minimum height=0.5 cm, minimum width=0.5cm];
+      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
+      \node[block,text width= 2.5cm, text centered](rfTransceiverModule){RF transceiver module};
+      % Connections
+      % \draw[stealth-stealth,ultra thick]
+      % (mobileCart.south) --(remote.north);
+      % Layers
+      \begin{pgfonlayer}{background}
+        \filldraw[fill=green!10,draw = blue,dotted,thick, rounded corners]                
+        ($(rfTransceiverModule.south west) + (-0.25*\smgrid,-0.25*\smgrid)$)node[](tmp1){} rectangle ($(rfTransceiverModule.north east) + (0.25*\smgrid,0.75*\smgrid)$)node[](tmp2){};
+        \draw
+        ($(rfTransceiverModule.north) + (-0.25*\smgrid,0.5*\smgrid)$)node{\textbf{Remote}};
+        % %%% Inputs and outputs
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,1.75*\smgrid)$) --node[near end,above]{Battery power}++(-3.0*\smgrid,0);
+        \draw[stealth-,thick]
+        ($(tmp1)+(0,0.5*\smgrid)$) --node[very near end,above]{Incoming RF messages}++(-3.5*\smgrid,0);
+        \draw[-stealth,thick]
+        ($(tmp2)+(0,-1.0*\smgrid)$) --node[midway,above]{Outgoing RF messages}++(5.25*\smgrid,0);
+      \end{pgfonlayer}
+    \end{tikzpicture}  
     \caption{Block Diagram of Remote Target Subsystem}
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
+    % \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
+    \begin{tikzpicture}[scale=1.0,transform shape]    
+      \tikzstyle{every node} = [font=\tiny];
+      \tikzstyle{block} = [draw, rectangle, fill=orange!15, rounded corners, minimum height=0.6 cm, minimum width=0.5cm];
+      \tikzstyle{pinstyle} = [pin edge={to-,thin,black}];
+      \node[block,text width= 1.0cm, text centered](embeddedComputer){Embedded computer};
+      \node[block,text width= 1.0cm, text centered, right of=embeddedComputer, node distance=2.5cm](DcMotors){DC motors};
+      \node[block,text width= 1.5cm, text centered, below of=DcMotors, node distance=0.75cm](omnidirectionalRfTransciever){Omnidirectional RF transceiver};
+      \node[block,text width= 1.5cm, text centered, below of=embeddedComputer, node distance=1.5cm](multiplexer){Multiplexer};
+      \node[block,text width= 1.5cm, text centered, below of=multiplexer, node distance=1.0cm](RFReceiver1){Direction sensitive RF receiver};
+      \node[block,text width= 1.5cm, text centered, below of=RFReceiver1, node distance=1.0cm](RFReceiver2){Direction sensitive RF receiver};
+      \node[block,text width= 1.5cm, text centered, right of=RFReceiver1, node distance=2.5cm](RFReceiver3){Direction sensitive RF receiver};
+      \node[block,text width= 1.5cm, text centered, right of=RFReceiver2, node distance=2.5cm](RFReceiver4){Direction sensitive RF receiver};
+      % Connections
+      \draw[stealth-,thick]
+      (embeddedComputer.165) --node[near end,above]{Battery power}++(-2.5*\smgrid,0);
+      \draw[stealth-,thick]
+      (embeddedComputer.-165) --node[near end,below]{ON/OFF switch}++(-2.5*\smgrid,0);
+      \draw[-stealth,thick]
+      (embeddedComputer.0) --(DcMotors.180);
+      \draw[-stealth,thick]
+      (DcMotors.0) --node[midway,above]{Wheel velocities}++(2.5*\smgrid,0);
+      \draw[-stealth,thick]
+      (omnidirectionalRfTransciever.0) --node[near end,above]{Outgoing RF signals}++(2.75*\smgrid,0);
+      \draw[stealth-,thick]
+      (omnidirectionalRfTransciever.-170) --node[very near end,above]{Incoming RF signals}++(-7.5*\smgrid,0)node[](tmp1){};
+      \draw[stealth-stealth,very thick]
+      (multiplexer.90) --(embeddedComputer.-90);
+      \draw[stealth-stealth,thick]
+      (embeddedComputer.-45) |-(omnidirectionalRfTransciever.170);
+      \draw[-stealth]
+      ($(tmp1) + (\smgrid,0)$) |- (RFReceiver1.west);
+      \draw[-stealth]
+      ($(tmp1) + (\smgrid,0)$) |- (RFReceiver2.west);
+      \draw[-stealth]
+      ($(tmp1) + (\smgrid,0)$) |- ($(RFReceiver2.south)+(0,-0.5*\smgrid)$) -| ($(RFReceiver3.east)+(0.5*\smgrid,0)$) -- (RFReceiver3.east);
+      \draw[stealth-]
+      (RFReceiver4.east) -- ++(0.5*\smgrid,0);
+      \draw[stealth-stealth]
+      (RFReceiver1.east) -- ++(0.5*\smgrid,0)|-(multiplexer.-10);
+      \draw[stealth-stealth]
+      (multiplexer.10) -| (RFReceiver3.north);
+      \draw[stealth-stealth]
+      (RFReceiver2.east) -- ++(0.75*\smgrid,0)|-(multiplexer.-5);
+      \draw[stealth-stealth]
+      (RFReceiver4.west) -- ++(-0.5*\smgrid,0)|-(multiplexer.0);
+
+      % Layers
+      \begin{pgfonlayer}{background}
+        \filldraw[fill=green!10,draw =blue,dotted,thick, rounded corners]                
+        ($(RFReceiver2.south west) + (-0.25*\smgrid,-0.25*\smgrid)$) rectangle ($(DcMotors.north east) + (0.75*\smgrid,0.75*\smgrid)$);
+        \draw
+        ($(embeddedComputer.north) + (2*\smgrid,0.4*\smgrid)$)node{\textbf{Mobile cart}};
+      \end{pgfonlayer}
+    \end{tikzpicture}  
     \caption{Block Diagram of Mobile Cart Subsystem}
